### 2021-06-04 paper/paper.tex
add initial paper outline

\documentclass[10pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{natbib}
\usepackage[inline]{enumitem}
\usepackage{tikz}
\usepackage{booktabs}

\usepackage{color}
\usepackage{colortbl}
\definecolor{deepblue}{rgb}{0,0,0.5}
\definecolor{deepred}{rgb}{0.6,0,0}
\definecolor{deepgreen}{rgb}{0,0.5,0}
\definecolor{gray}{rgb}{0.7,0.7,0.7}

\usepackage{hyperref}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = black, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor    = blue  %Colour of citations
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\theoremstyle{definition}
\newtheorem{problem}{Problem}
\newtheorem{defn}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{fact}{Fact}

\newcommand{\R}{\mathbb R}
\DeclareMathOperator{\vcdim}{VCdim}
\DeclareMathOperator{\ddim}{c_{\text{dd}}}
\DeclareMathOperator{\E}{\mathbb E}
\DeclareMathOperator{\nnz}{nnz}
\DeclareMathOperator{\determinant}{det}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\softmax}{softmax}

\newcommand{\I}{\mathbf I}
\newcommand{\Q}{\mathbf Q}
\newcommand{\p}{\mathbf P}
\newcommand{\pb}{\bar {\p}}
\newcommand{\pbb}{\bar {\pb}}
\newcommand{\pr}{\bm \pi}
\newcommand{\epsapp}{\epsilon_{\text{app}}}
\newcommand{\epsest}{\epsilon_{\text{est}}}

\newcommand{\trans}[1]{{#1}^{T}}
\newcommand{\loss}{\ell}
\newcommand{\aaa}{\mathbf a}
\newcommand{\vv}{\mathbf v}
\newcommand{\uu}{\mathbf u}
\newcommand{\w}{\mathbf w}
\newcommand{\x}{\mathbf x}
\newcommand{\y}{\mathbf y}
\newcommand{\lone}[1]{{\lVert {#1} \rVert}_1}
\newcommand{\ltwo}[1]{{\lVert {#1} \rVert}_2}
\newcommand{\lp}[1]{{\lVert {#1} \rVert}_p}
\newcommand{\linf}[1]{{\lVert {#1} \rVert}_\infty}
\newcommand{\lF}[1]{{\lVert {#1} \rVert}_F}

\newcommand{\dist}[2]{d_{{#1},{#2}}}

\newcommand{\h}{\mathcal H}
\newcommand{\D}{\mathcal D}
\DeclareMathOperator*{\erm}{ERM}

\newcommand{\fixme}[1]{\noindent{\color{red}\textbf{FIXME:}  {#1}}}
\newcommand{\fixmemike}[1]{\noindent{\color{blue}\textbf{FIXME (Mike):}  {#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
\Huge
The Cover Tree Loss
\end{center}

\section{Notation}

Assume we are solving a standard multi-class classification problem with $c$ classes and $d$ input feature dimensions.
The softmax cross entropy loss (also called the logistic loss) is the standard loss function for this problem.
It is defined to be
\begin{equation}
    \label{eq:xentropy}
    \ell(W;(\x,y)) = - \log \frac {\exp(-\trans\w_y \x)}{\sum_{j=1}^c \exp(-\trans \w_j \x)}
\end{equation}
where for each class $i\in[c]$,
$\w_i : \R^d$ is the parameter vector associated with class $i$;
the variable $W : \R^{c \times d} = (\w_1; \w_2; ...; \w_k)$ is the full parameter matrix;
$\x : \R^d$ is the feature vector;
and $y \in [c]$ is the class label.

The main theoretical result for the cross entropy loss is that for a dataset with $n$ points,
the generalization error is $O(\sqrt{c/n})$.
There are many theorems that establish this result in different contexts.
The following is an example that relies on properties of SGD.
\begin{theorem}
Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
    and that for each class $i\in[c]$, $\ltwo{\w_i}\le B$.
Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
\begin{equation}
    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt cB\rho}{\sqrt n}
\end{equation}
where $W^* = \argmin L_D(W)$.
\end{theorem}
\begin{proof}
    \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David and the properties of the cross entropy loss from the last set of notes.}
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Alternatives to the softmax cross entropy}

There are many other loss functions that have been proposed for multilabel classification.
In this section, we review these alternatives before presenting our proposed cover tree loss.

\subsection{Hierarchical Softmax}

The cover tree loss is superficially related to the hierarchical softmax (HSM) because both losses are defined based on tree structures.
\cite{morin2005hierarchical} introduced the HSM to speed up the computational time of neural network training,
but the cover tree loss is used to improve sample efficiency rather than computational efficiency.
\cite{mikolov2013distributed} introduce the word2vec model and experiment with using both the hierarchical softmax and cross entropy with negative sampling.
They conclude that negative sampling has the best performance both computationally and statistically.
Since the cover tree loss is a simple extension of the cross entropy loss,
negative sampling can be used to speed up the cross entropy loss as well.
\cite{bojanowski2017enriching} introduce the fastText extension of the word2vec model, which uses sub-word information to improve sample efficiency.
They do not provide any theoretical justification for why their technique should improve sample efficiency,
but their technique is computationally very similar to the cover tree loss,
and so our technique may be able to provide the first theoretical justification for their work.

\fixme{Read the papers mentioned above.  Verify that you agree with the things I wrote.  Then, write a detailed mathematical description of the HSM loss and contrast it with the cover tree loss.}

\fixme{Read 5-10 additional papers about the hierarchical softmax.  For each paper, write a paragraph describing the paper's contributions and how it relates to the cover tree loss.  For the final paper we will reference these papers.  We will have to trim down the notes that you write for this task, but it's useful when writing the paper to have detailed notes about references.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Bounds using L2 regularization}
%
%Recall that when we apply L2 regularization,
%we are minimizing the objective function
%\begin{equation}
    %f(W) = \tfrac 1 m \sum_{i=1}^m \loss(W; (\x_i,y_i)) + \tfrac\lambda2\lF{W}^2
    %.
%\end{equation}
%This function is $\lambda$-strongly convex in $W$.
%(Why?)
%Then Theorem 14.11 tells us that after performing $T$ iterations of SGD, we have that
%\begin{equation}
    %\label{eq:f-bound}
    %\E f(\bar W) - f(W^*) \le \frac{4\rho^2}{\lambda T} ( 1 + \log T)
%\end{equation}
%where $W^* = \argmin f(W)$.
%If we substitute $f(W)=L_D(W)+\tfrac\lambda 2\lF{W}^2$ into Equation \ref{eq:f-bound} above,
%then we get
%\begin{align}
    %\E L_D(\bar W) - L_D(W^*) 
    %&\le \frac{4\rho^2}{\lambda T} ( 1 + \log T) + \tfrac\lambda2\lF{W^*}^2 - \tfrac\lambda2\lF{\bar W}^2
    %\\
    %&\le \frac{4\rho^2}{\lambda T} ( 1 + \log T) + \frac{\lambda c B^2}{2}
    %.
%\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simloss}

\fixme{Write a detailed description of the sim loss}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Weight matrix factorization}

A simple way to reduce sample complexity when $c$ is large is to factor the parameter matrix as $W = VU$,
where $V : \R ^ {c \times e}$, $U : \R^{e \times d}$, and $e<\!<\!c$.
Then, each $\w_i = \vv_i U$, and the cross entropy softmax loss is
\begin{equation}
    \ell(VU;(\x,y)) = - \log \frac {\exp(-\trans\vv_y U \x)}{\sum_{j=1}^c \exp(-\trans \vv_j U \x)}
    .
\end{equation}
Unfortunately, this new parameterization is not simultaneously convex in both $V$ and $U$;
therefore, to analyze this formulation, we will assume that $V$ is fixed and only $U$ is a learned parameter.
In practice, it is fine to set $V$ to be a random matrix (and there is good theory to justify this),
or to simultaneously learn both $V$ and $U$ despite the nonconvexity.

This factorization decreases the statistical complexity of the problem from $O(\sqrt{c/n})$ to $O(\sqrt{e/n})$.
Recall that $e$ is a hyperparameter that is selected to be much less than $c$ and should represent the "intrinsic" dimensionality of the weight matrix.
The following theorem proves this result formally.
\begin{theorem}
Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
    and that for each class $i\in[c]$, $\ltwo{\vv_i}\le 1$ and $\ltwo{\uu_i}\le B$.
Then the parameter vector $\bar W = V \bar U$ estimated from one epoch of SGD satisfies
\begin{equation}
    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt eB\rho}{\sqrt n}
\end{equation}
where $W^* = \argmin L_D(W)$.
\end{theorem}
\begin{proof}
    \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David.}
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The Cover Tree Loss}

Of the previous techniques, only weight matrix factorization can provably reduce the statistical complexity of a problem.
The technique has two limitations, however:
(1) the class labels must have a linear structure and (2) the dimensionality of that structure must be known a priori.
The cover tree loss is able to take advantage of any metric structure and does not need to know the dimensionality in advance.

Like the weight matrix factorization, the cover tree loss works by reparameterizing the weight matrix for the softmax cross entropy loss.
The reparameterization is defined according to a tree structure that captures the similarity between labels.
Every class is represented by a leaf node in the tree,
and internal nodes represent \emph{pseudo-classes} that group the existing classes into a logical hierarchy.
The following figure shows an example tree.

\begin{center}
\begin{tikzpicture}
    [ level distance=1.5cm
    , level 1/.style={sibling distance=3cm}
    , level 2/.style={sibling distance=1.5cm}
    ]
\node {\textit{pseudo1}}
    child {node {\textit{pseudo2}}
      child {node {\texttt{boat}}}
      child {node {\texttt{plane}}}
      child {node {\textit{pseudo3}}
        child {node {\texttt{car}}}
        child {node {\texttt{truck}}}
        child {node {\texttt{van}}}
        child {node {\texttt{motorcycle}}}
      }
      }
    child {node {\texttt{building}}}
    child {node {\textit{pseudo4}}
      child {node {\texttt{cat}}}
      child {node {\texttt{dog}}}
    };
\end{tikzpicture}
\end{center}

We construct the loss function from this tree as follows.
For each leaf node $i$ (equivalently for each class $i$),
we let the sequence $P_i$ denote the path from the leaf node to the root.
Thus, in the example above, 
\begin{align*}
    P_{\texttt{truck}} &= (\texttt{truck}, \textit{pseudo3}, \textit{pseudo2}, \textit{pseudo1} ) \\
    P_{\texttt{cat}} &= (\texttt{cat}, \textit{pseudo4}, \textit{pseudo1} )
\end{align*}
Next, we associate a vector $\vv_i$ to each node $i$ in the tree structure.
That is, there is a vector $\vv_i$ for each class and for each pseudo-class.
Finally, we reparameterize the weights for the softmax cross entropy loss as the sum of the vectors along the paths.
Specifically, we set the weight vector for class $j$ to be 
\begin{equation}
    \label{eq:covertree-reparam}
    \w_j = \sum_{k\in P_j} \vv_k
    .
\end{equation}
Substituting \eqref{eq:covertree-reparam} into \eqref{eq:xentropy} gives us the final cover tree loss
\begin{equation}
    \ell(V;(\x,y)) = - \log \frac {\exp(-\sum_{k\in P_y}\trans\vv_k \x)}{\sum_{j=1}^c \exp(- \sum_{k\in P_j}\trans\vv_k \x)}
\end{equation}
where $V=(\vv_1,...,\vv_k)$,
and our goal is to minimize $\ell$ with respect to $V$.
Note that this loss can easily be computed in libraries like pytorch or tensorflow with the standard cross entropy loss functions.
The only change needed is to define the loss in terms of the sum of vectors $V$ instead of a variable tensor $W$.

\subsection{Theorems}

%Let $\mathcal L$ be a metric space over the set of labels,
%and $\ddim$ be the doubling dimension of $\mathcal L$.
%Then we build a ``cover tree'' from the class labels that respects the metric structure.
%This cover tree will have exactly $c$ leaf nodes, one for each class label,
%and $O(c)$ internal nodes.
\fixmemike{I need to add these results here}
%Why does this small change work?
%Intuitively, classes that have a small distance from each other should have similar weight vectors.

%\begin{lemma}
    %Under the conditions defined above, we have
%\begin{equation}
    %\label{eq:lFV-bound}
    %\lF{V} \le (\ddim \log c) B.
%\end{equation}
%\end{lemma}
%\begin{proof}
%\end{proof}

%Formally, we can bound the Frobenius norm of the weight matrix $V$ by
%which is significantly better than our bound on the weight matrix $W$ of only $\sqrt c B$.
%Substituting \eqref{eq:lFV-bound} into Theorem 14.12 of Shalev-Shwartz and Ben-David gives us that if SGD is run for $T$ iterations to compute parameter estimate $\bar W$,
%then
%\begin{equation}
    %\E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt {\dim \mathcal L}B\rho\log c}{\sqrt T}
%\end{equation}
%where $W^* = \argmin L_D(W)$.

%\subsection{Goal}
%
%Some classes
%
%\begin{align}
    %\Pr(Y = i | X) \approx \Pr(Y = j | X) \qquad\text{if}\qquad i \approx j
%\end{align}
%
%\begin{align}
    %&| \log\Pr(Y = a | X) -  \log\Pr(Y = b | X) |
    %\\&= | \trans\w_a \x + \log \sum_j \exp(-\trans\w_j \x) - \trans\w_b - \log \sum_j \exp(-\trans\w_j \x) |
    %\\&= | \trans\w_a \x - \trans\w_b \x |
    %\\&= | (\trans\w_a - \trans\w_b ) \x |
    %\\&\le | \trans\w_a - \trans\w_b | | \x |
    %\\&\le \dist a b | \x |
%\end{align}

\section{Experiments}

\subsection{Synthetic data}

In this experiment we will demonstrate the cover tree loss's effectiveness on a simple multiclass logistic regression problem.
The problem will be specifically designed to be convex and have low intrinsic dimension in the class labels in order to illustrate the advantages of the cover tree loss.

Let $N$ be the standard normal distribution.
Then sample the matrices
\begin{align}
    U \sim N^{c\times a} \qquad\text{and}\qquad
    A \sim N^{a\times d},
\end{align}
and define the true parameter matrix to be
\begin{equation}
    W^* = UA.
\end{equation}
For all $i \in [c]$, the row $\w_i^*$ of $W^*$ corresponds to the parameter vector for class $i$ and has dimension $d$.
The variable $a$ controls the intrinsic dimensionality of the problem.
When $a$ is small, then many class labels will be similar to each other;
but as $a$ increases, the class labels will have increasingly less structure.
When $a$ is known in advance, then we can use weight matrix factorization and set $e=a$.

For each data point $i\in[n]$,
we sample the data point according to the following rules:
\begin{align}
    y_i &\sim \text{Uniform}([c]), \text{and} \\
    \x_{i} &\sim \mathcal N(\w^*_{y_i}; \sigma),
\end{align}
where $\sigma$ controls the noise in the dataset.
Increasing $\sigma$ adds noise and makes classes harder to distinguish,
whereas decreasing $\sigma$ reduces noise and makes the classes easier to distinguish.

With our problem defined in this way, it is clear that
\begin{equation}
    \argmin_{W} \tfrac 1 n \ell(W; \x_i, y_i)
\end{equation}
converges to $W^*$ using the standard cross entropy loss and both the matrix factorization and cover tree reparameterizations.
\fixme{You should prove this for yourself.}
Figure \ref{fig:synthetic-results} shows that the cover tree loss converges at a faster rate.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.3\textwidth]{example-image-a}
    \includegraphics[width=0.3\textwidth]{example-image-b}
    \includegraphics[width=0.3\textwidth]{example-image-c}
    \caption{
        \fixme{We need a plot of loss vs number of data points ($n$), vs dimension ($d$), and vs randomness ($sigma$). These plots should all be log-log plots.  For each of these experiments, you should write to shell scripts: the first to generate the data and the second to plot the data.  These shell scripts should be easy to run in order to easily replicate your experiments.}}
    \label{fig:synthetic-results}
\end{figure}

\subsubsection{Alternative synthetic experiments}

In multilabel classification, it is common for the classes to be unbalanced.
We would like to show that the cover tree loss works well for unbalanced data.
A good way to do that is to change the distribution that $y_i$ is drawn from,
and a geometric distribution is a likely good alternative.

The covertree loss can work well even when the weight matrix has non-linear intrinsic structure.
We should adapt the $\w*_i$ vectors to sit on a manifold instead of a hyperplane to demonstrate this fact.

\subsection{Pseudo-synthetic data}
In a pseudo-synthetic dataset, we take a non-synthetic dataset and modify it.
\fixme{describe your procedure for generating pseudo-synthetic data and all the experiments that you plan to run}

\begin{table}[h]
    \centering
    \input{fig/datasets.tex}
\end{table}

\subsection{Real world twitter data}
\fixme{Write a description of the experiment.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plainnat}
\bibliography{paper}

\end{document}

### 2021-06-04 paper/paper.tex
update analysis

@@
 \newcommand{\dist}[2]{d_{{#1},{#2}}}
+\newcommand{\level}[1]{\texttt{level}({#1})}
 
@@
 \begin{theorem}
+\label{theorem:xentropy}
 Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
@@
 
-\section{The Cover Tree Loss}
+\section{The Tree Loss}
 
-Of the previous techniques, only weight matrix factorization can provably reduce the statistical complexity of a problem.
-The technique has two limitations, however:
-(1) the class labels must have a linear structure and (2) the dimensionality of that structure must be known a priori.
-The cover tree loss is able to take advantage of any metric structure and does not need to know the dimensionality in advance.
-
-Like the weight matrix factorization, the cover tree loss works by reparameterizing the weight matrix for the softmax cross entropy loss.
-The reparameterization is defined according to a tree structure that captures the similarity between labels.
-Every class is represented by a leaf node in the tree,
+Like the weight matrix factorization, the tree loss works by reparameterizing the weight matrix for the softmax cross entropy loss.
+The reparameterization is defined according to a \emph{label tree} structure that captures the similarity between labels.
+Every class is represented by a leaf node in the label tree,
 and internal nodes represent \emph{pseudo-classes} that group the existing classes into a logical hierarchy.
-The following figure shows an example tree.
+At this point, we assume that the label tree structure is given a priori, and in Section \ref{sec:bias-var} we discuss methods for generating this structure and their tradeoff and their tradeoffss.
+The following figure shows an example label tree for a classification problem with 9 classes.
 
@@
 
-We construct the loss function from this tree as follows.
+We parameterize the weight vectors from the label tree as follows.
 For each leaf node $i$ (equivalently for each class $i$),
 we let the sequence $P_i$ denote the path from the leaf node to the root.
-Thus, in the example above, 
-\begin{align*}
-    P_{\texttt{truck}} &= (\texttt{truck}, \textit{pseudo3}, \textit{pseudo2}, \textit{pseudo1} ) \\
-    P_{\texttt{cat}} &= (\texttt{cat}, \textit{pseudo4}, \textit{pseudo1} )
-\end{align*}
-Next, we associate a vector $\vv_i$ to each node $i$ in the tree structure.
-That is, there is a vector $\vv_i$ for each class and for each pseudo-class.
+For example, using the label tree above,
+we have
+\begin{equation}
+    P_{\texttt{truck}} = (\texttt{truck}, \textit{pseudo3}, \textit{pseudo2}, \textit{pseudo1} ) \qquad\text{and}\qquad
+    P_{\texttt{cat}} = (\texttt{cat}, \textit{pseudo4}, \textit{pseudo1} )
+    .
+\end{equation}
+Next, we associate a vector $\vv_i$ to each leaf and internal node $i$ in the tree structure.
+In particular, there is a there is a vector $\vv_i$ for each class and for each pseudo-class.
 Finally, we reparameterize the weights for the softmax cross entropy loss as the sum of the vectors along the paths.
@@
 
-\subsection{Theorems}
+\subsection{Analysis}
 
+When analyzing stochastic gradient descent using the cross entropy loss,
+it is common to assume that the parameter space is bounded.
+Under the standard parameterization, we have that the weight vector for each class satisfies $\ltwo{\w_j} \le B$.
+It immediately follows that $\lF{W} \le \sqrt{c}B$,
+and from this and convergence results of SGD it follows that the generalization error is $O(\sqrt{k}B/n)$.
+(See Theorem \ref{theorem:xentropy} above.)
+
+The key idea of the tree loss is that we can reduce the bound on the size of the parameter space,
+and this will result in the reduced sample complexity.
+Let $\level k$ denote the level of node $k$ in the label tree.
+Then we replace the constraints on the $\w_j$s with the following constraint on all $\vv_k$:
+\begin{equation}
+    \ltwo{\vv_k} \le \frac{B}{2^{\level k}}
+    .
+    \label{eq:tree-constraint}
+\end{equation}
+Notice that the original constraint \eqref{} immediately follows from the tree constraint \eqref{eq:tree-constraint} and the reparameterization \eqref{eq:covertree-reparam}.
+One way to interpret this is that we have ``factored out'' our bounds on the $\w_i$ into bounds on the smaller $\vv_k$ components,
+and because the $\vv_k$ vectors are shared between classes,
+we can reduce the overall bound.
+The following lemma bounds the Frobenius norm of the weight matrix $V$.
+
+\begin{lemma}
+    Assume that the label tree has at most $q$ nodes per level and $r$ levels.
+    Then,
+    \begin{equation}
+        \lF{V} \le \tfrac12 Bq c^{(1 - 1/\log_2 q)}
+    \end{equation}
+    In particular, if $q=2$, then
+    \begin{equation}
+        \lF{V} \le B,
+    \end{equation}
+    which is independent of the number of classes $c$.
+\end{lemma}
+\begin{proof}
+    We have the following chain of inequalities
+    \begin{align}
+        \lF{V} 
+        &\le \sum_{k\in \text{nodes of the level tree}} \ltwo{\vv_k}
+        \\
+        &= \sum_{i=0}^r \sum_{k\in \text{nodes at level $i$}} \ltwo{\vv_k}
+        \\
+        &\le \sum_{i=0}^r B\left(\frac {q} {2}\right)^i
+        \label{eq:lem:lFV:1}
+        \\
+        &=
+        B\left(\frac{1 - (q/2)^{r+1}}{1-q/2}\right)
+        \label{eq:lem:lFV:2}
+        \\
+        &\le
+        B(q/2)^{r+1}.
+        \label{eq:lem:lFV:3}
+    \end{align}
+    Line \eqref{eq:lem:lFV:1} follows from the fact that the number of nodes at level $i$ in the tree is upper bounded by $q^i$ and the the maximum L2 norm of a vector at level $i$ in the tree is $B/2^i$,so the sum of all vectors at level $i$ is bounded by $B(q/2)^i$.
+    Lines \eqref{eq:lem:lFV:2} and \eqref{eq:lem:lFV:3} are standard properties of geometric series.
+
+    Next, we show that
+    \begin{equation}
+        \left(\frac q 2\right)^r
+        =
+        \left(\frac q 2\right)^{\log_q n}
+        =
+        \frac{n}{2^{\log_q n}}
+        =
+        \frac{n}{2^{{\log_2 n}/{\log_2 q}}}
+        =
+        \frac{n}{n^{1/\log_2 q}}
+        =
+        n^{\left(1 - {1}/{\log_2 q}\right)}
+        .
+        \label{eq:lem:technical2}
+    \end{equation}
+    Substituting \eqref{eq:lem:technical2} into \eqref{eq:lem:lFV:3} gives the stated result.
+\end{proof}
+
+Substituting this Lemma into the SGD bounds gives us our main theorem:
+
+\begin{theorem}
+\label{theorem:xentropy}
+%Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
+    %and that for each class $i\in[c]$, $\ltwo{\w_i}\le B$.
+\fixme{Add assumptions.}
+Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
+\begin{equation}
+    \E L_D(\bar W) - L_D(W^*) \le \frac {B\rho}{\sqrt n}
+    ,
+\end{equation}
+which is independent of the number of classes $c$.
+\end{theorem}
 %Let $\mathcal L$ be a metric space over the set of labels,
@@
 %and $O(c)$ internal nodes.
-\fixmemike{I need to add these results here}
 %Why does this small change work?
@@
 
-%\subsection{Goal}
-%
-%Some classes
-%
-%\begin{align}
-    %\Pr(Y = i | X) \approx \Pr(Y = j | X) \qquad\text{if}\qquad i \approx j
-%\end{align}
-%
-%\begin{align}
-    %&| \log\Pr(Y = a | X) -  \log\Pr(Y = b | X) |
-    %\\&= | \trans\w_a \x + \log \sum_j \exp(-\trans\w_j \x) - \trans\w_b - \log \sum_j \exp(-\trans\w_j \x) |
-    %\\&= | \trans\w_a \x - \trans\w_b \x |
-    %\\&= | (\trans\w_a - \trans\w_b ) \x |
-    %\\&\le | \trans\w_a - \trans\w_b | | \x |
-    %\\&\le \dist a b | \x |
-%\end{align}
+\subsection{Bias-variance tradeoff}
+\label{sec:bias-var}
 

### 2021-06-11 paper/paper.tex
update sythetic data

@@
     \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David and the properties of the cross entropy loss from the last set of notes.}
+    \begin{align}
+    {\| W \|^2_F}&=\sum_{i=1}^c{\| W_i\|^2}\nonumber\\
+                &\le\sum_{i=1}^c{B^2}\nonumber\\
+                &\le cB^2\nonumber\\
+   \| W \|_F  &\le \sqrt c B \nonumber
+    \end{align}
+Then we get:
+    \begin{equation}
+    l(\bar W)-l(W^*)\le\frac {\sqrt cB\rho}{\sqrt n}
+    \end{equation}
+   Take expectation of both side of equation(3):
+   \begin{equation}
+    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt cB\rho}{\sqrt n}\nonumber
+\end{equation}
 \end{proof}
@@
 \fixme{Write a detailed description of the sim loss}
+
+Simloss is similarity based loss function which incorporates class similarities to support the training of neural network classifiers.
+Cross entropy loss assumes only one class is correct and punishes every misclassification, while Simloss indicates classes have similarities and classifying a target as a similar class is better.
+When calculating the loss function, instead of only taking the probability vector at the target index Simloss also adds the product of similarity between target and other classes and probability vector at the corresponding class.
+Non zero values of similarity matrix lead to smaller losses when the network gives a high score to classes similar to the correct one.
+It would allow the classifier to make less severe mistakes as it learns to predict similar classes.
+\begin{align}
+    L_{Simloss}&=-\frac{1}{N}\log(\sum_{c=1}^{C}S_{y_i,c}\cdot p_i[c])\\
+    % L_{Simloss}=-\frac{1}{N}\log(\sum_{c=1}^{C}S_{y_i,c}\cdot\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)})
+    p_i&=\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)}
+\end{align}
 

### 2021-06-11 cifar100_covertree.py

@@ -1,0 +1,166 @@
+from cover_tree import CoverTree
+from loss import CoverTreeLoss
+import numpy as np
+import random
+import time
+import logging
+import torch
+import torch.nn as nn
+import torch.optim as optim
+import torch.nn.functional as F
+import torch.backends.cudnn as cudnn
+import torchvision
+import torchvision.transforms as transforms
+from tqdm import tqdm
+from sklearn.metrics.pairwise import cosine_similarity
+from resnet import *
+from torch.utils.tensorboard import SummaryWriter
+writer = SummaryWriter('runs/cifar100/covertree')
+
+from scipy.spatial.distance import euclidean, cityblock, chebyshev,cosine
+import os
+import argparse
+import numpy as np
+import random
+
+import argparse
+parser = argparse.ArgumentParser(description='PyTorch CiFar100 Example')
+parser.add_argument('--batch_size', type=int, default=256)                      
+parser.add_argument('--epochs', type=int, default=100)
+parser.add_argument('--lr', type=float, default=0.1, metavar='LR')
+parser.add_argument('--seed', type=int, default=666)
+args = parser.parse_args()
+
+device = torch.device("cuda")
+from utilities import gen_data, gen_matrix, set_logger, set_seed, _print, path, norm
+set_seed(args)
+
+def train(model, device, data, label, train_original, m, batch_size, optimizer, criterion):
+    model.train()
+    pred = []
+    correct = 0
+    for start in range(0, len(data), batch_size):
+        train_X = torch.FloatTensor(data[start:start+batch_size])
+        train_Y = torch.LongTensor(label[start:start+batch_size])
+        train_X, train_Y = train_X.to(device), train_Y.to(device)
+        loss, logits = model(train_X, train_Y)
+        pred += criterion.predict(logits)
+        loss.backward()
+        optimizer.step()
+        optimizer.zero_grad()
+
+    for i in range(len(label)):
+        pred_num = pred[i]
+        label_num = train_original[i]
+        correct += m[pred_num, label_num]
+            
+    accuracy = correct/len(label)
+    return accuracy, loss.item()
+    
+def test(model, device, data, label, original_label, m, batch_size, criterion):
+    model.eval()
+    test_pred = []
+    correct = 0
+    with torch.no_grad():
+        for start in range(0, len(data), batch_size):
+            test_X = torch.FloatTensor(data[start:start+batch_size])
[…]

### 2021-06-11 data_generation/cover_tree.py

@@ -1,1081 +1,0 @@
-
-# Copyright Patrick Varilly 2012
-# Released under the scipy license
-#
-# Based on PyCoverTree (http://github.com/emanuele/PyCoverTree), as
-# modified by Emanuele Olivetti, license as follows:
-#
-# File: covertree.py
-# Date of creation: 05/04/07
-# Copyright (c) 2007, Thomas Kollar <tkollar@csail.mit.edu>
-# Copyright (c) 2011, Nil Geisweiller <ngeiswei@gmail.com>
-# All rights reserved.
-#
-# This is a class for the cover tree nearest neighbor algorithm.  For
-# more information please refer to the technical report entitled "Fast
-# Nearest Neighbors" by Thomas Kollar or to "Cover Trees for Nearest
-# Neighbor" by John Langford, Sham Kakade and Alina Beygelzimer
-#
-# If you use this code in your research, kindly refer to the technical
-# report.
-
-# I have rewritten the code to mimic the API of Anne M. Archibald's
-# scipy.spatial.kdtree
-
-from __future__ import division
-
-import numpy as np
-from collections import defaultdict
-import operator
-import math
-import itertools
-import sys
-from heapq import heappush, heappop
-import random
-import scipy.sparse
-
-__all__ = ['CoverTree', 'distance_matrix']
-
-
-class CoverTree(object):
-    """
-    Cover tree for quick nearest-neighbor lookup in general metric spaces.
-    TODO: Write more
-    """
-
-    # A node at level i can have immediate children within a distance d_i =
-    # child_d[i] and descendants within a distance D_i = heir_d[i].
-    # Strictly speaking, the only requirement for using a cover tree is that
-    #
-    #    D_i = d_i + d_(i-1) + ...
-    #
-    # be defined, but the construction algorithm used here (batch
-    # construction in Beygelzimer, Kakade and Langford) only works when
-    #
-    #    ... d_(i-1) < d_i < d_(i+1) < ...
-    #
-    # A convenient choice is d_i = b**i, with b > 1, whereby
-    # D_i = b**i + b**(i-1) + ... = (b/(b-1)) * d_i
-    #
-    # Below, I implement these two fundamental scales as a lazy dictionary
-    class _lazy_child_dist(dict):
-        def __init__(self, base, *a, **kw):
-            dict.__init__(self, *a, **kw)
-            self.b = base
-
-        def __missing__(self, i):
-            self[i] = value = self.b ** i
-            return value
-
[…]

### 2021-06-11 data_generation/gen_data.py

@@ -1,75 +1,0 @@
-import numpy as np, numpy.random
-import random
-import os
-import torch
-from sklearn.metrics.pairwise import cosine_similarity
-
-def gen_data(trainloader, testloader, m):
-    """
-    This function generate data with new labels.
-    New labels are generated by adding a new number which selected uniformly at random from [number].
-    """
-    sim = gen_sim(m)
-    examples = enumerate(trainloader)
-
-    train_data = []
-    train_label = []
-    while True:
-        try:
-            batch_idx, (example_data, example_targets) = next(examples)
-            label = example_targets.numpy()
-            new_train = np.random.choice(np.arange(0,m.shape[0]), p = np.transpose(m[:,label]).flatten())
-            train_label.append(new_train)
-            train_data.append(example_data.squeeze(0).numpy())
-        except:
-            break
-
-    instances = enumerate(testloader)
-
-    test_data = []
-    test_label = []
-    while True:
-        try:
-            batch_index, (instances_data, instances_targets) = next(instances)
-            label = instances_targets.numpy()
-            new_test = np.random.choice(np.arange(0,m.shape[0]), p = np.transpose(m[:,label]).flatten())
-            test_label.append(new_test)
-            test_data.append(instances_data.squeeze(0).numpy())
-        except:
-            break
-
-    return train_data, train_label, test_data, test_label, sim
-
-def gen_matrix(num_label, num_new):
-    """
-    This function get distribution of new labels.
-    The input are number of original labels and number of new labels we want to create.
-    It returns a matrix of shape ba (where a is the number of classes in the original dataset and b is the number of new classes we're creating;
-    """
-    m = np.zeros((num_new, num_label))
-    for i in range(num_label):
-        m[:,i] = np.random.dirichlet(np.ones(num_new),size=1)
-    return m
-
-
-# def gen_sim(m):
-#     """
-#     This function generate similarity matrix.
-#     Every row of input matrix m represent every new label.
-#     """
-
-#     b, a = m.shape
-#     new = []
-#     for i in range(b):
-#         new.append(m[i,:])
-#     cosine_dist = cosine_similarity(new)
-#     sim_matrix = torch.from_numpy(cosine_dist)
-
-#     return sim_matrix
-
-def gen_sim(m):
-    I = np.identity(m.shape[0])
-    sim = np.maximum(I, np.dot(m, np.transpose(m)))
-    sim_matrix = torch.from_numpy(sim)
-    return sim_matrix
-

### 2021-06-11 data_generation/loss.py

@@ -1,42 +1,0 @@
-import typing
-import torch
-import numpy as np
-
-class SimLoss(torch.nn.Module):
-    def __init__(self,
-                 w: typing.Optional[torch.Tensor],
-                 number_of_classes: int = 10,
-                 lower_bound: float = 0.5,
-                 epsilon: float = 1e-8) -> None:
-        super().__init__()
-
-        assert lower_bound >= 0.0
-        assert lower_bound < 1.0
-        assert number_of_classes > 0
-
-        self.w = w.float()
-        self.epsilon = epsilon
-
-    def forward(self,
-                x: torch.Tensor,
-                y: torch.Tensor) -> torch.Tensor:
-        w = self.w[y, :]
-        return torch.mean(-torch.log(torch.sum(w * x, dim=1) + self.epsilon))
-
-    # def __repr__(self) -> str:
-    #     return "SimCE"
-
-class CoverTreeLoss(torch.nn.Module):
-    def __init__(self,
-                 epsilon: float = 1e-8) -> None:
-        super().__init__()
-        self.epsilon = epsilon
-
-    def forward(self,
-                x: torch.Tensor,
-                y: torch.Tensor) -> torch.Tensor:
-        new_vec = 0
-        for i in range(y.size()[1]):
-            new_vec += y[:,i,:] * x
-
-        return torch.mean(-torch.log(torch.sum( new_vec, dim=1) + self.epsilon))

### 2021-06-11 data_generation/test_covertree.py

@@ -1,307 +1,0 @@
-from cover_tree import CoverTree
-from loss import CoverTreeLoss
-import numpy as np
-import random
-import torch
-import torch.nn as nn
-import torch.optim as optim
-import torch.nn.functional as F
-import torch.backends.cudnn as cudnn
-import torchvision
-import torchvision.transforms as transforms
-from tqdm import tqdm
-from sklearn.metrics.pairwise import cosine_similarity
-from torch.utils.tensorboard import SummaryWriter
-writer = SummaryWriter('runs/covertree2')
-
-from scipy.spatial.distance import euclidean, cityblock, chebyshev,cosine
-import os
-import argparse
-import numpy as np
-import random
-
-import argparse
-parser = argparse.ArgumentParser(description='PyTorch CiFar10 Example')
-parser.add_argument('--batch_size', type=int, default=256)                      
-parser.add_argument('--epochs', type=int, default=200)
-parser.add_argument('--lr', type=float, default=0.1, metavar='LR')
-args = parser.parse_args()
-
-device = torch.device("cuda")
-
-def get_labels(label):
-  
-  label2index = dict()
-  index2label = dict()
-  for idx, element in enumerate(label):
-    label2index[element] = idx
-    index2label[idx] = element
-
-  return label2index, index2label
-
-def _print(self):
-    new_label = []
-    def print_node(node, indent):
-        if isinstance(node, CoverTree._LeafNode):
-            print ("-" * indent, node)
-            new_label.append(node.idx)
-        else:
-            print ("-" * indent, node)
-            for child in node.children:
-                print_node(child, indent + 1)
-
-    print_node(self.root, 0)
-    return new_label
-# DLA model
-class BasicBlock(nn.Module):
-    expansion = 1
-
-    def __init__(self, in_planes, planes, stride=1):
-        super(BasicBlock, self).__init__()
-        self.conv1 = nn.Conv2d(
-            in_planes, planes, kernel_size=3, stride=stride, padding=1, bias=False)
-        self.bn1 = nn.BatchNorm2d(planes)
-        self.conv2 = nn.Conv2d(planes, planes, kernel_size=3,
-                               stride=1, padding=1, bias=False)
-        self.bn2 = nn.BatchNorm2d(planes)
-
-        self.shortcut = nn.Sequential()
-        if stride != 1 or in_planes != self.expansion*planes:
-            self.shortcut = nn.Sequential(
[…]

### 2021-06-11 loss.py

@@ -1,18 +1,20 @@
 import typing
 import torch
+from torch._C import FloatStorageBase
+import torch.nn as nn
 import numpy as np
+import torch.nn.functional as F
+
 
 class SimLoss(torch.nn.Module):
     def __init__(self,
                  w: typing.Optional[torch.Tensor],
-                 number_of_classes: int = 80,
                  lower_bound: float = 0.5,
                  epsilon: float = 1e-8) -> None:
         super().__init__()
 
         assert lower_bound >= 0.0
         assert lower_bound < 1.0
-        assert number_of_classes > 0
 
         self.w = w.float()
         self.epsilon = epsilon
@@ -21,7 +23,53 @@ class SimLoss(torch.nn.Module):
                 x: torch.Tensor,
                 y: torch.Tensor) -> torch.Tensor:
         w = self.w[y, :]
+        print(w.size())
+        print(x.size())
         return torch.mean(-torch.log(torch.sum(w * x, dim=1) + self.epsilon))
 
-    def __repr__(self) -> str:
-        return "SimCE"
+    # def __repr__(self) -> str:
+    #     return "SimCE"
+
+class CoverTreeLoss(torch.nn.Module):
+    def __init__(self, true_class_num, class_num, new2index, hidden_size, epsilon: float = 1e-8) -> None:
+        super().__init__()
+        self.epsilon = epsilon
+        self.true_class_num = true_class_num
+        self.new2index = new2index
+        self.linear = nn.Linear(hidden_size, class_num, bias=False)
+        self.criterion = nn.CrossEntropyLoss()
+
+    def forward(self,
+                x: torch.Tensor, #(batch_size, hidden_size)
+                y: torch.Tensor) -> torch.Tensor:
+
+        weights = self.linear.weight #(class_num, hidden_size)
+        
+        added_weights = []
+        for j in range(self.true_class_num):
+            path = self.new2index[j]
+            to_add_list = [weights[j, :]]
+            for ele in range(len(path)-1):
+                to_add_list.append(weights[path[ele], :])
+
+            added_weights.append(torch.stack(to_add_list, dim=0).sum(dim=0))
+
+        added_weights = torch.stack(added_weights, dim=0) # (true_class_num, hidden_size)
+        logits = torch.matmul(x, added_weights.transpose(0, 1)) # (batch_size, true_class_num)
+        
+        loss = self.criterion(logits, y)
+        return loss, logits
+
[…]

### 2021-06-11 resnet.py

@@ -1,0 +1,348 @@
+'''
+resnet for cifar in pytorch
+Reference:
+[1] K. He, X. Zhang, S. Ren, and J. Sun. Deep residual learning for image recognition. In CVPR, 2016.
+[2] K. He, X. Zhang, S. Ren, and J. Sun. Identity mappings in deep residual networks. In ECCV, 2016.
+'''
+import os
+import torch
+import torch.nn as nn
+import math
+import torchvision.models
+from loss import SimLoss
+
+models_dir = os.path.expanduser('~/.torch/models')
+model_name = {
+    'resnet18': 'resnet18-5c106cde.pth',
+    'resnet34': 'resnet34-333f7ec4.pth',
+    'resnet50': 'resnet50-19c8e357.pth',
+    'resnet101': 'resnet101-5d3b4d8f.pth',
+    'resnet152': 'resnet152-b121ed2d.pth',
+}
+
+
+
+def conv3x3(in_planes, out_planes, stride=1):
+    " 3x3 convolution with padding "
+    return nn.Conv2d(in_planes, out_planes, kernel_size=3, stride=stride, padding=1, bias=False)
+
+
+class BasicBlock(nn.Module):
+    expansion=1
+
+    def __init__(self, inplanes, planes, stride=1, downsample=None):
+        super(BasicBlock, self).__init__()
+        self.conv1 = conv3x3(inplanes, planes, stride)
+        self.bn1 = nn.BatchNorm2d(planes)
+        self.relu = nn.ReLU(inplace=True)
+        self.conv2 = conv3x3(planes, planes)
+        self.bn2 = nn.BatchNorm2d(planes)
+        self.downsample = downsample
+        self.stride = stride
+
+    def forward(self, x):
+        residual = x
+
+        out = self.conv1(x)
+        out = self.bn1(out)
+        out = self.relu(out)
+
+        out = self.conv2(out)
+        out = self.bn2(out)
+
+        if self.downsample is not None:
+            residual = self.downsample(x)
+
+        out += residual
+        out = self.relu(out)
+
+        return out
+
+
+class Bottleneck(nn.Module):
+    expansion=4
+
+    def __init__(self, inplanes, planes, stride=1, downsample=None):
+        super(Bottleneck, self).__init__()
+        self.conv1 = nn.Conv2d(inplanes, planes, kernel_size=1, bias=False)
+        self.bn1 = nn.BatchNorm2d(planes)
[…]

### 2021-06-11 sythetic_data.py

@@ -1,0 +1,106 @@
+import numpy as np
+import random
+import math
+import torch
+import torch.nn as nn
+import torch.optim as optim
+import torch.nn.functional as F
+import torch.backends.cudnn as cudnn
+from tqdm import tqdm
+from torch.utils.tensorboard import SummaryWriter
+writer = SummaryWriter('runs/sythetic_data/num_data')
+# writer = SummaryWriter('runs/sythetic_data/dimension')
+# writer = SummaryWriter('runs/sythetic_data/sigma')
+
+import argparse
+parser = argparse.ArgumentParser(description='Synthetic data')
+parser.add_argument('--num_data', type=int, default=100000)                      
+parser.add_argument('--dimension', type=int, default=64)
+parser.add_argument('--seed', type=int, default=666)
+parser.add_argument('--lr', type=float, default=0.0001, metavar='LR')
+args = parser.parse_args()
+from utilities import set_seed
+
+set_seed(args)
+
+class Loss(torch.nn.Module):
+    def __init__(self, class_num, dimension, epsilon: float = 1e-8) -> None:
+        super().__init__()
+        self.epsilon = epsilon
+        self.fc = nn.Linear(dimension, class_num, bias=False)
+        self.criterion = nn.CrossEntropyLoss()
+
+    def forward(self,
+                x: torch.Tensor, #(batch_size, hidden_size)
+                y: torch.Tensor) -> torch.Tensor:
+
+        logits = self.fc(x)
+        
+        loss = self.criterion(logits, y)
+        return loss
+
+# loss vs number of data points
+means = np.zeros((100, args.dimension))
+stds = np.ones((100, args.dimension))
+w = np.random.normal(means, stds)
+sigma = np.random.rand(1, args.dimension)
+synthetic_loss = Loss(100, args.dimension)
+optimizer = optim.SGD(synthetic_loss.parameters(), lr=args.lr,
+                        momentum=0.9, weight_decay=3e-4)
+scheduler = torch.optim.lr_scheduler.CosineAnnealingLR(optimizer, T_max=100000)
+for i in range(1, args.num_data+1):
+    y = np.random.randint(0, 100)
+    x = torch.FloatTensor(np.random.normal(w[y,:], sigma))
+    target = torch.LongTensor([y])
+    loss = synthetic_loss(x, target)
+    loss.backward()
+    optimizer.step()
+    optimizer.zero_grad()
[…]

### 2021-06-11 tool.py

@@ -1,201 +1,0 @@
-import json
-import numpy as np
-from transformers import AutoTokenizer, AutoModel
-import torch
-import torch.nn as nn
-import os
-from collections import defaultdict
-import zipfile
-# from emoji import UNICODE_EMOJI
-import emoji
-
-# emoticon = {'😂', '😷', '😮', '🙋', '🙄', '😐', '🙃', '😇', '😖', '😥', '😑', '😣', '😩', '😛', '😯', '🙁', '😱', '😕', '🙉', '😴', '😵', '😲', '😫', '😈', '😌', '😤', '🙂', '😎', '😨', '😻', '😒', '😰', '😋', '🙈', '😶', '😓', '🙅', '😼', '😧', '😪', '😟', '😘', '🙊', '😡', '😔', '🙀', '🙇', '😠', '🙍', '😬', '😾', '😳', '🙆', '😗', '😽', '😸', '😚', '🙏', '😞', '🙌', '😏', '😉', '😅', '😜', '😄', '😙', '😝', '😁', '😍', '🙎', '😦', '😊', '😀', '😺', '😢', '😿', '😭', '😆', '😃', '😹'}
-emoticon = list(emoji.EMOJI_UNICODE.values())
-
-class BERTSentenceEncoder(nn.Module):
-
-    def __init__(self, pretrain_path, lexical_dropout, lower): 
-        nn.Module.__init__(self)
-        self.bert = AutoModel.from_pretrained(pretrain_path)
-        self.tokenizer = AutoTokenizer.from_pretrained(pretrain_path)
-        self.lower = lower
-
-        if lexical_dropout > 0:
-            self._lexical_dropout = torch.nn.Dropout(p=lexical_dropout)
-        else:
-            self._lexical_dropout = lambda x: x
-        
-    def forward(self, tokens, mask):
-        
-        last_layer, outputs = self.bert(tokens, attention_mask=mask)
-        outputs = torch.mean(last_layer,dim=1)
-        return outputs
-    
-    def tokenize(self, raw_tokens):
-        # token -> index
-           
-        tokens = ['[CLS]']
-
-        for i, token in enumerate(raw_tokens):
-            
-            if self.lower:
-                input_token = token.lower()
-            else:
-                input_token = token
-
-            sub_words = self.tokenizer.tokenize(input_token)
-            tokens += sub_words
-
-        indexed_tokens = self.tokenizer.convert_tokens_to_ids(tokens)
-        
-        return indexed_tokens
-
[…]

### 2021-06-11 tweets.py

@@ -1,405 +1,0 @@
-import numpy as np
-import random
-import os
-import json
-import sys
-import torch
-import torch.nn as nn
-import time
-from tool import get_labels, get_data, BERTSentenceEncoder,split_y,if_include_emoticon,extract_user_id,data_process
-from transformers import AdamW, get_linear_schedule_with_warmup
-from torch.utils.tensorboard import SummaryWriter
-import logging
-from sklearn.metrics import f1_score
-import zipfile
-from loss import SimLoss
-from torch.utils.data import IterableDataset
-import gensim.models as gsm
-from sklearn.metrics.pairwise import cosine_similarity
-from collections import defaultdict
-
-import argparse
-parser = argparse.ArgumentParser(description='Process some integers.')
-
-parser.add_argument('--batch_size',type=int,default=8)
-
-args = parser.parse_args()
-
-writer = SummaryWriter('runs/CCE_experiment')
-import emoji
-# emoticon = ['😂', '😷', '😮', '🙋', '🙄', '😐', '🙃', '😇', '😖', '😥', '😑', '😣', '😩', '😛', '😯', '🙁', '😱', '😕', '🙉', '😴', '😵', '😲', '😫', '😈', '😌', '😤', '🙂', '😎', '😨', '😻', '😒', '😰', '😋', '🙈', '😶', '😓', '🙅', '😼', '😧', '😪', '😟', '😘', '🙊', '😡', '😔', '🙀', '🙇', '😠', '🙍', '😬', '😾', '😳', '🙆', '😗', '😽', '😸', '😚', '🙏', '😞', '🙌', '😏', '😉', '😅', '😜', '😄', '😙', '😝', '😁', '😍', '🙎', '😦', '😊', '😀', '😺', '😢', '😿', '😭', '😆', '😃', '😹']
-emojis = list(emoji.EMOJI_UNICODE.values())
-descrip = list(emoji.EMOJI_UNICODE.keys())
-label2index = get_labels(emojis)
-num_labels = len(label2index)
-
-class Accuracy:
-    def __init__(self):
-
-        self.correct = 0
-        self.count = 1e-10
-
-    def __call__(self, pred, labels):
-
-        _pred = pred.detach().cpu()
-        _labels = labels.detach().cpu()
-
-        self.correct+=torch.eq(_pred, _labels).sum().item()
-        self.count += _labels.size(0)
-
-    def get_metric(self):
-
-        return self.correct/self.count
-
-    def reset(self):
-
-        self.correct = 0
[…]

### 2021-06-11 utilities.py

@@ -1,0 +1,198 @@
+import sys
+import time
+import logging
+import numpy as np, numpy.random
+import random
+import os
+import torch
+from sklearn.metrics.pairwise import cosine_similarity
+from cover_tree import CoverTree
+import shutil
+
+def set_logger(name, timestamp):
+    formatter=logging.Formatter('%(asctime)s %(levelname)s %(message)s')
+    logger=logging.getLogger(f'{name}-Logger')
+    file_handler=logging.FileHandler(f'./log-{name}-{timestamp}.log')
+    file_handler.setFormatter(formatter)
+    logger.addHandler(file_handler)
+    console_handler=logging.StreamHandler(sys.stdout)
+    console_handler.setFormatter(formatter)
+    logger.addHandler(console_handler)
+    logger.setLevel(logging.INFO)
+    return logger
+
+def set_seed(args):
+    random.seed(args.seed) 
+    np.random.seed(args.seed) 
+    torch.manual_seed(args.seed) 
+    if torch.cuda.is_available(): 
+        torch.cuda.manual_seed_all(args.seed) 
+
+def gen_data(trainloader, testloader, m):
+    """
+    This function generate data with new labels.
+    New labels are generated by adding a new number which selected uniformly at random from [number].
+    """
+    sim = gen_sim(m)
+    examples = enumerate(trainloader)
+
+    train_data = []
+    train_label = []
+    train_original = []
+    while True:
+        try:
+            batch_idx, (example_data, example_targets) = next(examples)
+            label = example_targets.numpy()
+            train_original.append(example_targets)
+            new_train = np.random.choice(np.arange(0,m.shape[0]), p = np.transpose(m[:,label]).flatten())
+            train_label.append(new_train)
+            train_data.append(example_data.squeeze(0).numpy())
+        except:
+            break
+
+    instances = enumerate(testloader)
+
+    test_data = []
+    test_label = []
+    original_label = []
+    while True:
+        try:
+            batch_index, (instances_data, instances_targets) = next(instances)
+            label = instances_targets.numpy()
+            original_label.append(instances_targets)
+            new_test = np.random.choice(np.arange(0,m.shape[0]), p = np.transpose(m[:,label]).flatten())
+            test_label.append(new_test)
+            test_data.append(instances_data.squeeze(0).numpy())
+        except:
+            break
+
[…]

### 2021-06-18 paper/paper.tex
updates

@@
 
+\cite{Peng2017IncrementallyLT} introduce
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David.}
+    \begin{align}
+    {\| U \|^2_F}&=\sum_{i=1}^e{\| U_i\|^2}\nonumber\\
+                &\le\sum_{i=1}^e{B^2}\nonumber\\
+                &\le eB^2\nonumber\\
+   \| U \|_F  &\le \sqrt e B \nonumber \\
+   \| W \|_F  &\le \sqrt e B \nonumber
+    \end{align}
+    Then we get:
+    \begin{equation}
+    l(\bar W)-l(W^*)\le\frac {\sqrt eB\rho}{\sqrt n}
+    \end{equation}
+   Take expectation of both side of equation(8):
+   \begin{equation}
+    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt eB\rho}{\sqrt n}\nonumber
+\end{equation}
 \end{proof}
@@
 \label{theorem:xentropy}
-%Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
-    %and that for each class $i\in[c]$, $\ltwo{\w_i}\le B$.
+% Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
+%     and that for each class $i\in[c]$, $\ltwo{\w_i}\le B$.
 \fixme{Add assumptions.}
+Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
+    and that for each class $i\in[c]$, $\ltwo{\w_i}\le \frac{B}{\sqrt k}$.
 Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
@@
 
+For non-synthetic datasets which we cannot obtain specific similarities directly, we would build similarities manually by following procedures.
+We generate a sampling matrix which each row represents the probability distribution of a new label.
+We would sample new labels from the sampling matrix and view each row as embedding of each new label and then get similarities from embeddings.
+Next, we are able to construct a cover tree structure from the new labels and take each leaf node represents a new label and replace all parent nodes with pseudo labels.
+
+For non-synthetic datasets which we are able to get similarities directly, we construct the cover tree structure from the similarities and apply cover tree loss to compare with classic cross entropy loss.
+
 \begin{table}[h]
@@
 
+We apply cover tree loss on emoji prediction in twitter dataset.
+Emojis are popular to express emotions in text messages and tweets are a wildely used social media over the world.
+We trained the multilingual BERT model on tweets to predict which emoji corresponds to a piece of text is best for measuring the emotional content in the text.
+Our 1660 target emojis are defined by emo2vec.
+
+\subsubsection{Data processing}
+We collect all tweets in any languages sent from anywhere in the world and filter the tweets with target emojis.
+For each tweet, we replace all user mentions with a special token \texttt{\text{<}mention\text{>}} and all URLS with a special token \texttt{\text{<}url\text{>}} and delete all emojis.
+We keep all hashtags and duplicate the tweet once for each emoji if a tweet has multiple emojis.
+Then we split the dataset into training validadtion and testing sets by user id to ensure each user appears in only one set in order to prevent data leakage.
+
+\subsubsection{Experiments}
+We apply the multilingual BERT model trained on data from 109 distinct languages which achieves state-of-the-art performance on a wide variety of natural language tasks.
+We get the embeddings of 1660 target emojis defined by emo2vec and construct a cover tree structure from these emojis.
+In this cover tree structure, every leaf node represents each real target emoji and we replace all parent nodes with pseudo labels.
+Then we would adopt cover tree loss and compare the performance with classic cross entropy loss.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-06-18 TreeLoss/loss.py

@@ -4,7 +4,9 @@ from torch._C import FloatStorageBase
 import torch.nn as nn
 import numpy as np
 import torch.nn.functional as F
-
+from cover_tree import CoverTree
+from scipy.spatial.distance import cosine
+from utilities import path
 
 class SimLoss(torch.nn.Module):
     def __init__(self,
@@ -23,30 +25,68 @@ class SimLoss(torch.nn.Module):
                 x: torch.Tensor,
                 y: torch.Tensor) -> torch.Tensor:
         w = self.w[y, :]
-        print(w.size())
-        print(x.size())
         return torch.mean(-torch.log(torch.sum(w * x, dim=1) + self.epsilon))
 
     # def __repr__(self) -> str:
     #     return "SimCE"
 
 class CoverTreeLoss(torch.nn.Module):
-    def __init__(self, true_class_num, class_num, new2index, hidden_size, epsilon: float = 1e-8) -> None:
+    def __init__(self, c, length, dimension, new2index) -> None:
+        '''
+        c: number of existed classes
+        length: number of existed classes and pseudo classes
+        dimension: dimension of parameter matrix W(c,dimension)
+        new2index: a dictionary which we can get a a path of a existed class
+        '''
         super().__init__()
-        self.epsilon = epsilon
-        self.true_class_num = true_class_num
-        self.new2index = new2index
-        self.linear = nn.Linear(hidden_size, class_num, bias=False)
+        self.c = c
+        self.linear = nn.Linear(dimension, length, bias=False)
         self.criterion = nn.CrossEntropyLoss()
+        self.new2index = new2index
+
+    @staticmethod
+    def tree_structure(c, m):
+        '''
+        m: embeddings of existed classes
+        This function constructs cover tree structure.
+        '''
+        distance = cosine
+        tree = CoverTree(m, distance, leafsize=1)
+        new_index = path(tree)
+
+        # new label
+        start_index = c
+        index_map = dict()
+        inverse_index = dict()
+        for p in new_index:
+            for node in p[:-1]:   ## do not include leaf node
+                if node not in index_map:
+                    index_map[node] = start_index
+                    inverse_index[start_index] = node
+                    start_index+=1
+        for p in new_index:
+            for i in range(len(p[:-1])):
+                p[i] = index_map[p[i]]
+
+        length = max(index_map.values()) + 1
+        new2index = dict()
+        for i in range(len(new_index)):
[…]

### 2021-06-18 experiments/cifar100_covertree.py

@@ -1,3 +1,13 @@
+import argparse
+parser = argparse.ArgumentParser(description='PyTorch CiFar100 Example')
+parser.add_argument('--batch_size', type=int, default=256)                      
+parser.add_argument('--epochs', type=int, default=200)
+parser.add_argument('--lr', type=float, default=0.15, metavar='LR')
+parser.add_argument('--weight_decay', type=float, default=8e-4)
+parser.add_argument('--seed', type=int, default=666)
+parser.add_argument('--dimension', type=int, default=64)
+args = parser.parse_args()
+
 from cover_tree import CoverTree
 from loss import CoverTreeLoss
 import numpy as np
@@ -12,24 +22,9 @@ import torch.backends.cudnn as cudnn
 import torchvision
 import torchvision.transforms as transforms
 from tqdm import tqdm
-from sklearn.metrics.pairwise import cosine_similarity
 from resnet import *
 from torch.utils.tensorboard import SummaryWriter
-writer = SummaryWriter('runs/cifar100/covertree')
-
-from scipy.spatial.distance import euclidean, cityblock, chebyshev,cosine
-import os
-import argparse
-import numpy as np
-import random
-
-import argparse
-parser = argparse.ArgumentParser(description='PyTorch CiFar100 Example')
-parser.add_argument('--batch_size', type=int, default=256)                      
-parser.add_argument('--epochs', type=int, default=100)
-parser.add_argument('--lr', type=float, default=0.1, metavar='LR')
-parser.add_argument('--seed', type=int, default=666)
-args = parser.parse_args()
+writer = SummaryWriter('runs/cifar100_50/covertree/lr0.15-dropout0.5')
 
 device = torch.device("cuda")
 from utilities import gen_data, gen_matrix, set_logger, set_seed, _print, path, norm
@@ -99,12 +94,10 @@ test_dataset = torchvision.datasets.CIFAR100(
 testloader = torch.utils.data.DataLoader(test_dataset, batch_size=1, shuffle=False)
 
 timestamp = str(time.time())
-# covertree_cifar100_logger = set_logger('covertree_cifar100', timestamp)
 
-for number in range(1, 101):
-    num_label = 100
-    num_new = num_label
-    m = gen_matrix(num_label, num_new, number)
+for number in range(50, 101):
+    c = 100
+    m = gen_matrix(c, number)
     credit = norm(m)
 
[…]

### 2021-06-18 experiments/resnet.py

@@ -184,6 +184,7 @@ class ResNet_Cifar(nn.Module):
         self.fc = nn.Linear(64 * block.expansion, num_classes)
         self.softmax = nn.Softmax(dim=-1)
         self.criterion = criterion
+        self.dropout = nn.Dropout(p=0.5)
 
         for m in self.modules():
             if isinstance(m, nn.Conv2d):
@@ -216,6 +217,7 @@ class ResNet_Cifar(nn.Module):
 
         x = self.layer1(x)
         x = self.layer2(x)
+        x = self.dropout(x)
         x = self.layer3(x)
 
         x = self.avgpool(x)
@@ -245,6 +247,7 @@ class PreAct_ResNet_Cifar(nn.Module):
         self.relu = nn.ReLU(inplace=True)
         self.avgpool = nn.AvgPool2d(8, stride=1)
         self.fc = nn.Linear(64*block.expansion, num_classes)
+        self.dropout = nn.Dropout(p=0.5)
 
         for m in self.modules():
             if isinstance(m, nn.Conv2d):
@@ -280,7 +283,7 @@ class PreAct_ResNet_Cifar(nn.Module):
         x = self.avgpool(x)
         x = x.view(x.size(0), -1)
         x = self.fc(x)
-
+        
         return x
 
 

### 2021-06-18 experiments/synthetic/run_experiment.py

@@ -62,6 +62,7 @@ import torch
 import torch.nn as nn
 import torch.optim as optim
 import torch.nn.functional as F
+from torch.utils.tensorboard import SummaryWriter
 
 # set the seed
 def set_seed(seed):
@@ -111,7 +112,7 @@ for i in range(args.n):
     X.append(x_i)
 X = np.array(X)
 
-Y = torch.Tensor(Y)
+Y = torch.LongTensor(Y)
 X = torch.Tensor(X)
 logging.debug("Y.shape="+str(Y.shape))
 logging.debug("X.shape="+str(X.shape))
@@ -133,7 +134,7 @@ logging.debug('create SummaryWriter')
 # FIXME: uncomment
 #experiment_name=f'a={args.a},c={args.c},d={args.d},n={args.n},sigma={args.sigma},lr={args.lr},loss={args.loss},seed={args.seed}'
 #logging.info(f'experiment_name={experiment_name}')
-experiment_name='test'
+experiment_name=f'lossvsn{args.n}'
 writer = SummaryWriter(os.path.join(args.logdir, experiment_name))
 
 logging.debug('create optimizer')
@@ -146,27 +147,32 @@ optimizer = optim.SGD(
 
 logging.debug('training loop')
 for training_iter in range(args.max_iter):
-
     logging.debug('training_iter='+str(training_iter))
-
+    
     # i is the current data point
-    i = training_iter%args.n
-
-    # calculate the loss
-    logits = model(X[i])
-    loss = criterion(logits, Y[i]) # FIXME: notation is incorrect
-
-    # backprop
-    loss.backward()
-    optimizer.step()
-    optimizer.zero_grad()
-
-    # log to tensorboard
-    W_err = 0 # FIXME: should be |W-W*|
-    accuracy = 0 # FIXME
-    writer.add_scalar('losses/loss', loss, i)
-    writer.add_scalar('losses/W_err', W_err, i)
-    writer.add_scalar('losses/accuracy', accuracy, i)
+    # i = training_iter%args.n
+    i = 0
+    correct = 0
+    while i < args.n - 1:
+        # calculate the loss
+        logits = model(X[i].view(1,args.d))
+        W = model.weight
+        loss = criterion(logits, Y[i].view(1)) # FIXME: notation is incorrect
+        # backprop
+        loss.backward()
+        optimizer.step()
+        optimizer.zero_grad()
+        i += 1
+        # log to tensorboard
[…]

### 2021-06-25 TreeLoss/loss.py
update

@@ -1,12 +1,11 @@
 import typing
 import torch
-from torch._C import FloatStorageBase
 import torch.nn as nn
 import numpy as np
 import torch.nn.functional as F
-from cover_tree import CoverTree
+from .cover_tree import CoverTree
 from scipy.spatial.distance import cosine
-from utilities import path
+from .utilities import path
 
 class SimLoss(torch.nn.Module):
     def __init__(self,
@@ -31,16 +30,16 @@ class SimLoss(torch.nn.Module):
     #     return "SimCE"
 
 class CoverTreeLoss(torch.nn.Module):
-    def __init__(self, c, length, dimension, new2index) -> None:
+    def __init__(self, c, length, d, new2index) -> None:
         '''
         c: number of existed classes
         length: number of existed classes and pseudo classes
-        dimension: dimension of parameter matrix W(c,dimension)
+        d: dimension of parameter matrix W(c,d)
         new2index: a dictionary which we can get a a path of a existed class
         '''
         super().__init__()
         self.c = c
-        self.linear = nn.Linear(dimension, length, bias=False)
+        self.linear = nn.Linear(d, length, bias=False)
         self.criterion = nn.CrossEntropyLoss()
         self.new2index = new2index
 
@@ -100,16 +99,15 @@ class CoverTreeLoss(torch.nn.Module):
         loss = self.criterion(logits, y)
         return loss, logits
 
-    def predict(self, x):
-        '''
-        x: logits
-        This function computes the prediction of model.
-        '''
+    # def predict(self, x):
+    #     '''
+    #     x: logits
+    #     This function computes the prediction of model.
+    #     '''
 
-        prob = F.softmax(x, dim=-1)
+    #     prob = F.softmax(x, dim=-1)
 
-        _, pred = torch.max(prob, dim=-1)
-        _pred = pred.detach().cpu().tolist()
+    #     _, pred = torch.max(prob, dim=-1)
+    #     _pred = pred.detach().cpu().tolist()
 
-        return _pred
-        
+    #     return _pred

### 2021-06-25 experiments/cifar100_covertree.py

@@ -1,135 +1,0 @@
-import argparse
-parser = argparse.ArgumentParser(description='PyTorch CiFar100 Example')
-parser.add_argument('--batch_size', type=int, default=256)                      
-parser.add_argument('--epochs', type=int, default=200)
-parser.add_argument('--lr', type=float, default=0.15, metavar='LR')
-parser.add_argument('--weight_decay', type=float, default=8e-4)
-parser.add_argument('--seed', type=int, default=666)
-parser.add_argument('--dimension', type=int, default=64)
-args = parser.parse_args()
-
-from cover_tree import CoverTree
-from loss import CoverTreeLoss
-import numpy as np
-import random
-import time
-import logging
-import torch
-import torch.nn as nn
-import torch.optim as optim
-import torch.nn.functional as F
-import torch.backends.cudnn as cudnn
-import torchvision
-import torchvision.transforms as transforms
-from tqdm import tqdm
-from resnet import *
-from torch.utils.tensorboard import SummaryWriter
-writer = SummaryWriter('runs/cifar100_50/covertree/lr0.15-dropout0.5')
-
-device = torch.device("cuda")
-from utilities import gen_data, gen_matrix, set_logger, set_seed, _print, path, norm
-set_seed(args)
-
-def train(model, device, data, label, train_original, m, batch_size, optimizer, criterion):
-    model.train()
-    pred = []
-    correct = 0
-    for start in range(0, len(data), batch_size):
-        train_X = torch.FloatTensor(data[start:start+batch_size])
-        train_Y = torch.LongTensor(label[start:start+batch_size])
-        train_X, train_Y = train_X.to(device), train_Y.to(device)
-        loss, logits = model(train_X, train_Y)
-        pred += criterion.predict(logits)
-        loss.backward()
-        optimizer.step()
-        optimizer.zero_grad()
-
-    for i in range(len(label)):
-        pred_num = pred[i]
-        label_num = train_original[i]
-        correct += m[pred_num, label_num]
-            
-    accuracy = correct/len(label)
-    return accuracy, loss.item()
-    
-def test(model, device, data, label, original_label, m, batch_size, criterion):
-    model.eval()
-    test_pred = []
-    correct = 0
-    with torch.no_grad():
-        for start in range(0, len(data), batch_size):
-            test_X = torch.FloatTensor(data[start:start+batch_size])
-            test_Y = torch.LongTensor(label[start:start+batch_size])
[…]

### 2021-06-25 experiments/pseudo_synthetic/data_loader.py

@@ -1,0 +1,57 @@
+import torch
+import torchvision
+import torchvision.transforms as transforms
+import torchvision.datasets as datasets
+
+def data_loader(data):
+    if data == 'mnist':
+        transform=transforms.Compose([
+                transforms.ToTensor(),
+                transforms.Normalize((0.1307,), (0.3081,))
+                ])
+        trainset = datasets.MNIST('./data', train=True, download=True,
+                            transform=transform)
+        testset = datasets.MNIST('./data', train=False,
+                            transform=transform)
+        trainloader = torch.utils.data.DataLoader(trainset, batch_size=1, shuffle=False)
+        testloader = torch.utils.data.DataLoader(testset, batch_size=1, shuffle=False)
+    elif data == 'cifar10':
+        transform_train = transforms.Compose([
+                            transforms.RandomCrop(32, padding=4),
+                            transforms.RandomHorizontalFlip(),
+                            transforms.ToTensor(),
+                            transforms.Normalize((0.4914, 0.4822, 0.4465), (0.2023, 0.1994, 0.2010)),
+                        ])
+
+        transform_test = transforms.Compose([
+                            transforms.ToTensor(),
+                            transforms.Normalize((0.4914, 0.4822, 0.4465), (0.2023, 0.1994, 0.2010)),
+                        ])
+        trainset = torchvision.datasets.CIFAR10(
+            root='./cifar10', train=True, download=True, transform=transform_train)
+        trainloader = torch.utils.data.DataLoader(
+            trainset, batch_size=1, shuffle=False)
+
+        testset = torchvision.datasets.CIFAR10(
+            root='./cifar10', train=False, download=True, transform=transform_test)
+        testloader = torch.utils.data.DataLoader(
+            testset, batch_size=1, shuffle=False)
+
+    elif data == 'cifar100':
+        normalize = transforms.Normalize(mean=[0.491, 0.482, 0.447], std=[0.247, 0.243, 0.262])
+        train_dataset = torchvision.datasets.CIFAR100(
+                    root='./cifar100', train=True, download=True,
+                    transform=transforms.Compose([
+                        transforms.RandomCrop(32, padding=4),
+                        transforms.RandomHorizontalFlip(),
+                        transforms.ToTensor(),
+                        normalize,]))
+        trainloader = torch.utils.data.DataLoader(train_dataset, batch_size=1, shuffle=False)
+
+        test_dataset = torchvision.datasets.CIFAR100(
[…]

### 2021-06-25 experiments/pseudo_synthetic/pseudo_synthetic.py

@@ -1,0 +1,149 @@
+import sys
+sys.path.append('../..')
+
+import argparse
+parser = argparse.ArgumentParser(description='Pseudo Synthetic Data Experiment')
+parser.add_argument('--data', choices=['mnist', 'cifar10', 'cifar100'], required=True)
+parser.add_argument('--loss', choices=['xentropy', 'simloss', 'covertreeloss'], required=True)
+parser.add_argument('--seed', type=int, default=666)
+
+parser.add_argument('--batch_size', type=int, default=256)                      
+parser.add_argument('--epochs', type=int, default=200)
+parser.add_argument('--lr', type=float, default=0.15, metavar='LR')
+parser.add_argument('--weight_decay', type=float, default=8e-4)
+parser.add_argument('--d', type=int, default=64)
+parser.add_argument('--lower_bound', type=float, default=0.5)
+args = parser.parse_args()
+
+import numpy as np
+import random
+import time
+import logging
+import torch
+import torch.nn as nn
+import torch.optim as optim
+import torch.nn.functional as F
+from tqdm import tqdm
+from resnet import *
+from data_loader import data_loader
+from torch.utils.tensorboard import SummaryWriter
+writer = SummaryWriter(f'runs/{args.data}/{args.loss}')
+
+device = torch.device("cuda")
+from TreeLoss.loss import CoverTreeLoss
+from TreeLoss.utilities import gen_data, gen_matrix, set_logger, set_seed, _print, path, norm
+set_seed(args.seed)
+
+################################################################################
+# training/testing functions
+################################################################################
+def train(model, device, data, label, train_original, m, batch_size, optimizer, loss_fun):
+    model.train()
+    train_pred = []
+    correct = 0
+    for start in range(0, len(data), batch_size):
+        train_X = torch.FloatTensor(data[start:start+batch_size])
+        train_Y = torch.LongTensor(label[start:start+batch_size])
+        train_X, train_Y = train_X.to(device), train_Y.to(device)
+        loss, logits = model(train_X, train_Y, loss_fun)
+        prob = F.softmax(logits, dim=-1)
+
+        _, pred = torch.max(prob, dim=-1)
+        train_pred += pred.detach().cpu().tolist()
+        loss.backward()
+        optimizer.step()
+        optimizer.zero_grad()
+
+    for i in range(len(label)):
+        pred_num = train_pred[i]
+        label_num = train_original[i]
+        correct += m[pred_num, label_num]
+            
+    accuracy = correct/len(label)
[…]

### 2021-06-25 experiments/synthetic/create_figure_1b.sh

@@ -1,0 +1,3 @@
+for d in 2 4 8 16 32 64 128; do
+    python3 run.py --d=$d --experiment=loss_vs_d 
+done

### 2021-06-25 experiments/synthetic/create_figure_1c.sh

@@ -1,0 +1,3 @@
+for sigma in 1.0 1.25 1.5 1.75 2.0 2.25 2.5; do
+    python3 run.py --sigma=$sigma --experiment=loss_vs_sigma --max_iter=1
+done

### 2021-06-25 experiments/synthetic/run_experiment.py

@@ -45,10 +45,11 @@ parser_model.add_argument('--lr', type=float, default=1e-4, metavar='LR')
 parser_model.add_argument('--max_iter', type=int, default=int(1e1))
 parser_model.add_argument('--momentum', type=float, default=0.9)
 parser_model.add_argument('--weight_decay', type=float, default=3e-4)
-parser_model.add_argument('--loss', choices=['tree','xentropy'], required=True)
+parser_model.add_argument('--loss', choices=['tree','xentropy'], default='xentropy')
 
 parser_debug = parser.add_argument_group(title='debug')
 parser_model.add_argument('--logdir', default='log')
+parser_model.add_argument('--experiment', choices=['loss_vs_n','loss_vs_d', 'loss_vs_sigma'], required=True)
 args = parser.parse_args()
 
 # load imports;
@@ -63,15 +64,12 @@ import torch.nn as nn
 import torch.optim as optim
 import torch.nn.functional as F
 from torch.utils.tensorboard import SummaryWriter
+# from TreeLoss.utilities import set_seed
+from utilities import set_seed
+import pickle as pkl
 
 # set the seed
-def set_seed(seed):
-    logging.debug('set_seed('+str(args.seed)+')')
-    random.seed(seed) 
-    np.random.seed(seed) 
-    torch.manual_seed(seed) 
-    if torch.cuda.is_available(): 
-        torch.cuda.manual_seed_all(seed) 
+logging.debug('set_seed('+str(args.seed)+')')
 set_seed(args.seed)
 
 # FIXME:
@@ -79,10 +77,6 @@ set_seed(args.seed)
 # add the required libraries to requirements.txt
 # FIXME:
 # your set_seed function should take an int as a parameter and not args; see above
-'''
-from TreeLoss.utilities import set_seed
-set_seed(args.seed)
-'''
 
 ################################################################################
 # generate the data
@@ -134,7 +128,7 @@ logging.debug('create SummaryWriter')
 # FIXME: uncomment
 #experiment_name=f'a={args.a},c={args.c},d={args.d},n={args.n},sigma={args.sigma},lr={args.lr},loss={args.loss},seed={args.seed}'
 #logging.info(f'experiment_name={experiment_name}')
-experiment_name=f'lossvsn{args.n}'
+experiment_name='test'
 writer = SummaryWriter(os.path.join(args.logdir, experiment_name))
 
 logging.debug('create optimizer')
[…]

### 2021-06-25 experiments/pseudo_synthetic/pseudo_synthetic.py
updates

@@ -30,7 +30,7 @@ from torch.utils.tensorboard import SummaryWriter
 writer = SummaryWriter(f'runs/{args.data}/{args.loss}')
 
 device = torch.device("cuda")
-from TreeLoss.loss import CoverTreeLoss
+from TreeLoss.loss import CoverTreeLoss, SimLoss
 from TreeLoss.utilities import gen_data, gen_matrix, set_logger, set_seed, _print, path, norm
 set_seed(args.seed)
 

### 2021-06-25 experiments/synthetic/create_figure_1a.sh

@@ -1,5 +1,5 @@
 #!/bin/bash
 
 for n in 2 4 8 16 32 64 128; do
-    python3 experiments/synthetic/run_experiment.py --n=$n
+    python3 experiments/synthetic/run_experiment.py --n=$n --experiment=loss_vs_n
 done

### 2021-06-25 experiments/synthetic/create_figure_1b.sh

@@ -1,3 +1,3 @@
 for d in 2 4 8 16 32 64 128; do
-    python3 run.py --d=$d --experiment=loss_vs_d 
+    python3 experiments/synthetic/run_experiment.py --d=$d --experiment=loss_vs_d 
 done

### 2021-06-25 experiments/synthetic/create_figure_1c.sh

@@ -1,3 +1,3 @@
 for sigma in 1.0 1.25 1.5 1.75 2.0 2.25 2.5; do
-    python3 run.py --sigma=$sigma --experiment=loss_vs_sigma --max_iter=1
+    python3 experiments/synthetic/run_experiment.py --sigma=$sigma --experiment=loss_vs_sigma --max_iter=1
 done

### 2021-07-02 paper/paper.tex
update

@@
 
-Simloss is similarity based loss function which incorporates class similarities to support the training of neural network classifiers.
+Simloss\cite{Kobs2020SimLossCS} is similarity based loss function which incorporates class similarities to support the training of neural network classifiers.
 Cross entropy loss assumes only one class is correct and punishes every misclassification, while Simloss indicates classes have similarities and classifying a target as a similar class is better.
@@
 
-For non-synthetic datasets which we cannot obtain specific similarities directly, we would build similarities manually by following procedures.
-We generate a sampling matrix which each row represents the probability distribution of a new label.
+For non-synthetic datasets which do not have specific similarities, we would build pseudo-synthetic datasets with similarities manually by following procedures. 
+\begin{itemize}
+  \item [1)] 
+  For $o% original classes, we want to generate a sampling matrix $m$ for c new classes which each row represents the probability distribution of a new class. 
+  i.e. If a new class is mixed by $k$ original labels, we sample a probability distribution $p$ of size $k$ and sum to 1. 
+  So the sampling matrix is as below:
+\begin{align}
+    row &= (i+j) \bmod c\nonumber \\
+    m[row,i] &= p[j]  \nonumber
+\end{align}
+where $i$=1,\dots,$o$ $j$=1,\dots,$k$
+
+  \item [2)]
   We would sample new labels from the sampling matrix and view each row as embedding of each new label and then get similarities from embeddings.
+  \item [3)]
   Next, we are able to construct a cover tree structure from the new labels and take each leaf node represents a new label and replace all parent nodes with pseudo labels. 
-
+\end{itemize}
 For non-synthetic datasets which we are able to get similarities directly, we construct the cover tree structure from the similarities and apply cover tree loss to compare with classic cross entropy loss.
@@
 We trained the multilingual BERT model on tweets to predict which emoji corresponds to a piece of text is best for measuring the emotional content in the text. 
-Our 1660 target emojis are defined by emo2vec.
+Our 1660 target emojis are defined by emo2vec\cite{Eisner2016emoji2vecLE}.
 
 \subsubsection{Data processing}
-We collect all tweets in any languages sent from anywhere in the world and filter the tweets with target emojis.
+We collect all tweets\cite{Izbicki2019GeolocatingTI} in any languages sent from anywhere in the world and filter the tweets with target emojis. 
 For each tweet, we replace all user mentions with a special token \texttt{\text{<}mention\text{>}} and all URLS with a special token \texttt{\text{<}url\text{>}} and delete all emojis. 
@@
 \subsubsection{Experiments}
-We apply the multilingual BERT model trained on data from 109 distinct languages which achieves state-of-the-art performance on a wide variety of natural language tasks.
+We apply the multilingual BERT model\cite{Feng2020LanguageagnosticBS} trained on data from 109 distinct languages which achieves state-of-the-art performance on a wide variety of natural language tasks.
 We get the embeddings of 1660 target emojis defined by emo2vec and construct a cover tree structure from these emojis. 

### 2021-07-02 experiments/synthetic/create_figure_1a.sh

@@ -1,5 +1,5 @@
 #!/bin/bash
 
-for n in 2 4 8 16 32 64 128; do
+for n in 16 32 64 128 256 512 1024 2048 4096 8192; do
     python3 experiments/synthetic/run_experiment.py --n=$n --experiment=loss_vs_n
 done

### 2021-07-02 experiments/synthetic/create_figure_1b.sh

@@ -1,3 +1,3 @@
-for d in 2 4 8 16 32 64 128; do
+for d in 2 4 8 16 32 64 128 256 512 1024; do
     python3 experiments/synthetic/run_experiment.py --d=$d --experiment=loss_vs_d 
 done

### 2021-07-02 experiments/synthetic/create_figure_1c.sh

@@ -1,3 +1,3 @@
-for sigma in 1.0 1.25 1.5 1.75 2.0 2.25 2.5; do
+for sigma in 1.0 1.25 1.5 1.75 2.0 2.25 2.5 2.75 3.0 3.25; do
     python3 experiments/synthetic/run_experiment.py --sigma=$sigma --experiment=loss_vs_sigma --max_iter=1
 done

### 2021-07-16 paper/paper.tex
update paper and synthetic data experiment

@@
 \usepackage{booktabs}
+\usepackage{subfigure}
 
@@
     \begin{align}
-    {\| W \|^2_F}&=\sum_{i=1}^c{\| W_i\|^2}\nonumber\\
-                &\le\sum_{i=1}^c{B^2}\nonumber\\
-                &\le cB^2\nonumber\\
-   \| W \|_F  &\le \sqrt c B \nonumber
+    {\| W \|^2_F}&=\sum_{i=1}^c{\| W_i\|^2}\\
+                &\le\sum_{i=1}^c{B^2}\\
+                &\le cB^2\\
+   \| W \|_F  &\le \sqrt c B 
     \end{align}
@@
    \begin{equation}
-    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt cB\rho}{\sqrt n}\nonumber
+    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt cB\rho}{\sqrt n}
 \end{equation}
@@
 
-\cite{Peng2017IncrementallyLT} introduce
+\cite{Peng2017IncrementallyLT} introduce a training method incrementally train the hierarchical softmax function for neural network language models. 
+To be specific, the incremental training split the cost function to model old and update corpora separately and factorize the objective function for the hierarchical softmax. 
+They also provide a new stochastic gradient based method to update all the word vectors and parameters and their theoretical analysis shows the mean square error of the parameter vectors can be bounded by a function of the number of changed words related to the parameter node which is similar to our idea of cover tree loss.
+Their experimental results show the incremental training can save a lot of time.
+
+\cite{Mohammed2018EffectivenessOH} compare the performance of normal softmax and hierarchical softmax in large scale classification tasks. 
+Normal softmax is computationally expensive for large scale datasets with large number of possible outputs.
+Their experimental results show that normal softmax and hierarchical softmax underperforms on datasets with large number of labels.
+That is also one of our motivations of cover tree loss function. 
+Compared to classic cross entropy loss function, cover tree loss function performs better on datasets with large number of labels.
 
@@
     \begin{align}
-    {\| U \|^2_F}&=\sum_{i=1}^e{\| U_i\|^2}\nonumber\\
-                &\le\sum_{i=1}^e{B^2}\nonumber\\
-                &\le eB^2\nonumber\\
-   \| U \|_F  &\le \sqrt e B \nonumber \\
-   \| W \|_F  &\le \sqrt e B \nonumber
+    {\| U \|^2_F}&=\sum_{i=1}^e{\| U_i\|^2}\\
+                &\le\sum_{i=1}^e{B^2}\\
+                &\le eB^2\\
+   \| U \|_F  &\le \sqrt e B  \\
+   \| W \|_F  &\le \sqrt e B
     \end{align}
@@
    \begin{equation}
-    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt eB\rho}{\sqrt n}\nonumber
+    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt eB\rho}{\sqrt n}
 \end{equation}
@@
     \centering
-    \includegraphics[width=0.3\textwidth]{example-image-a}
-    \includegraphics[width=0.3\textwidth]{example-image-b}
-    \includegraphics[width=0.3\textwidth]{example-image-c}
+    \subfigure{
+        \label{Fig.sub.1}
+        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_n.png}}
+    \subfigure{
+        \label{Fig.sub.2}
+        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_n.png}}
+    \subfigure{
+        \label{Fig.sub.3}
+        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_n.png}}
+    \caption{Loss value, parameter matrix error, accuracy versus number of data points}
+    \label{Fig.1}
+
+    \subfigure{
+        \label{Fig.sub.1}
+        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_d.png}}
+    \subfigure{
+        \label{Fig.sub.2}
+        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_d.png}}
+    \subfigure{
+        \label{Fig.sub.3}
+        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_d.png}}
+    \caption{Loss value, parameter matrix error, accuracy versus dimension of parameter matrix}
+    \label{Fig.2}
+
+    \subfigure{
+        \label{Fig.sub.1}
+        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_sigma.png}}
+    \subfigure{
+        \label{Fig.sub.2}
+        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_sigma.png}}
+    \subfigure{
+        \label{Fig.sub.3}
+        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_sigma.png}}
+    \caption{Loss value, parameter matrix error, accuracy versus randomness}
+    \label{Fig.3}
+
     \caption{
@@
 
-For non-synthetic datasets which do not have specific similarities, we would build pseudo-synthetic datasets with similarities manually by following procedures. 
+In order to compare the performance between classic cross entropy loss function and cover tree loss function, we need datasets which the classes have clear similarities.
+Besides, we would like to construct pseudo-synthetic datasets which we can control the similarities.
+The idea is we can sample the new classes from the original classes of datasets.
+We get the similarities of new classes from probability distribution and control the complexity of similarities by changing probability distribution.
+
+For non-synthetic datasets that do not have specific similarities, we would build pseudo-synthetic datasets with similarities manually by following procedures. 
 \begin{itemize}
-  \item [1)] 
-  For $o% original classes, we want to generate a sampling matrix $m$ for c new classes which each row represents the probability distribution of a new class. 
-  i.e. If a new class is mixed by $k$ original labels, we sample a probability distribution $p$ of size $k$ and sum to 1. 
+  \item
+  For $o$ original classes, we want to generate a sampling matrix $m$ for c new classes which each row represents the probability distribution of a new class. 
+  Each new class is uniformly sampled from $k$ original class.
   So the sampling matrix is as below:
 \begin{align}
-    row &= (i+j) \bmod c\nonumber \\
-    m[row,i] &= p[j]  \nonumber
+    row &= (j+col) \bmod c \\
+    m[i+row,col] &= \frac{o}{c \times n}  
 \end{align}
-where $i$=1,\dots,$o$ $j$=1,\dots,$k$
+where $i \in [c]$ $col \in [o]$ $j \in [k]$
 
-  \item [2)]
-  We would sample new labels from the sampling matrix and view each row as embedding of each new label and then get similarities from embeddings.
-  \item [3)]
-  Next, we are able to construct a cover tree structure from the new labels and take each leaf node represents a new label and replace all parent nodes with pseudo labels. 
+  \item
+  We would sample new classes from the sampling matrix and view each row as vector representation of each new class and then get similarities from vector representations.
+  The new class is defined as below:
+ \begin{align}
+    c[i] = o[j] \cdot m[i,j] 
+\end{align}
+  \item
+  Next, we are able to construct a cover tree structure from the new labels and take each leaf node represents a new class and replace all parent nodes with pseudo classes. 
 \end{itemize}
-For non-synthetic datasets which we are able to get similarities directly, we construct the cover tree structure from the similarities and apply cover tree loss to compare with classic cross entropy loss.
 

### 2021-07-16 TreeLoss/loss.py

@@ -72,6 +72,7 @@ class CoverTreeLoss(torch.nn.Module):
         return new2index, length
 
     def forward(self,
+                weights: torch.Tensor,
                 x: torch.Tensor, #(batch_size, hidden_size)
                 y: torch.Tensor) -> torch.Tensor:
         '''
@@ -80,7 +81,7 @@ class CoverTreeLoss(torch.nn.Module):
         This function computes the cover tree loss.
         '''
 
-        weights = self.linear.weight #(class_num, hidden_size)
+        # weights = self.linear.weight #(class_num, hidden_size)
         
         added_weights = []
         for j in range(self.c):
@@ -95,4 +96,4 @@ class CoverTreeLoss(torch.nn.Module):
         logits = torch.matmul(x, added_weights.transpose(0, 1)) # (batch_size, true_class_num)
         
         loss = self.criterion(logits, y)
-        return loss, logits
+        return loss, logits, added_weights

### 2021-07-16 TreeLoss/utilities.py

@@ -1,14 +1,13 @@
 import sys
 import time
 import logging
-import numpy as np, numpy.random
+import numpy as np
 import random
 import os
 import torch
 from sklearn.metrics.pairwise import cosine_similarity
-from cover_tree import CoverTree
+from .cover_tree import CoverTree
 import math
-# import shutil
 
 def set_logger(name, timestamp):
     formatter=logging.Formatter('%(asctime)s %(levelname)s %(message)s')

### 2021-07-16 experiments/pseudo_synthetic/resnet.py

@@ -215,7 +215,6 @@ class ResNet_Cifar(nn.Module):
 
         x = self.layer1(x)
         x = self.layer2(x)
-        x = self.dropout(x)
         x = self.layer3(x)
 
         x = self.avgpool(x)

### 2021-07-16 experiments/synthetic/create_figure_1a.sh

@@ -1,5 +1,5 @@
 #!/bin/bash
 
 for n in 16 32 64 128 256 512 1024 2048 4096 8192; do
-    python3 experiments/synthetic/run_experiment.py --n=$n --experiment=loss_vs_n
+    python3 run_experiment.py --n=$n --experiment=loss_vs_n
 done

### 2021-07-16 experiments/synthetic/create_figure_1b.sh

@@ -1,3 +1,3 @@
 for d in 2 4 8 16 32 64 128 256 512 1024; do
-    python3 experiments/synthetic/run_experiment.py --d=$d --experiment=loss_vs_d 
+    python3 run_experiment.py --d=$d --experiment=loss_vs_d 
 done

### 2021-07-16 experiments/synthetic/create_figure_1c.sh

@@ -1,3 +1,3 @@
 for sigma in 1.0 1.25 1.5 1.75 2.0 2.25 2.5 2.75 3.0 3.25; do
-    python3 experiments/synthetic/run_experiment.py --sigma=$sigma --experiment=loss_vs_sigma --max_iter=1
+    python3 run_experiment.py --sigma=$sigma --experiment=loss_vs_sigma
 done

### 2021-07-16 experiments/synthetic/plot_figure.py

@@ -1,0 +1,142 @@
+import matplotlib.pyplot as plt
+import argparse
+parser = argparse.ArgumentParser(description='create figures')
+parser.add_argument('--experiment', choices=['loss_vs_n','loss_vs_d', 'loss_vs_sigma'], required=True)
+args = parser.parse_args()
+
+f = open(f'{args.experiment}_tree.txt', 'r')
+f_ = open(f'{args.experiment}_xentropy.txt', 'r')
+loss = []
+W_err = []
+accuracy = []
+for line in f:
+    line = line.strip()
+    if len(line)>1:
+
+        loss_start = line.find('Loss:')
+        loss_end  = loss_start + len('Loss:')
+
+        W_err_start = line.find('W_err:')
+        W_err_end = W_err_start + len('W_err:')
+
+        accuracy_start = line.find('Accuracy:')
+        accuracy_end = accuracy_start + len('Accuracy:')
+
+        loss__ = float(line[loss_end:W_err_start].strip())
+        W_err__ = float(line[W_err_end:accuracy_start].strip())
+        accuracy__ = float(float(line[accuracy_end:].strip()))
+
+        loss.append(loss__)
+        W_err.append(W_err__)
+        accuracy.append(accuracy__)
+loss_ = []
+W_err_ = []
+accuracy_ = []
+for line in f_:
+    line = line.strip()
+    if len(line)>1:
+
+        loss_start = line.find('Loss:')
+        loss_end  = loss_start + len('Loss:')
+
+        W_err_start = line.find('W_err:')
+        W_err_end = W_err_start + len('W_err:')
+
+        accuracy_start = line.find('Accuracy:')
+        accuracy_end = accuracy_start + len('Accuracy:')
+
+        loss__ = float(line[loss_end:W_err_start].strip())
+        W_err__ = float(line[W_err_end:accuracy_start].strip())
+        accuracy__ = float(float(line[accuracy_end:].strip()))
+
+        loss_.append(loss__)
+        W_err_.append(W_err__)
+        accuracy_.append(accuracy__)
+
+if args.experiment == 'loss_vs_n' :
[…]

### 2021-07-16 experiments/synthetic/run_experiment.py

@@ -113,10 +113,13 @@ logging.debug("X.shape="+str(X.shape))
 # define the model
 ################################################################################
 logging.info('defining the model')
-
-model = nn.Linear(args.d, args.c)
-criterion = nn.CrossEntropyLoss()
-
+if args.loss == 'xentropy':
+    model = nn.Linear(args.d, args.c)
+    criterion = nn.CrossEntropyLoss()
+if args.loss == 'tree':
+    new2index, length = CoverTreeLoss.tree_structure(args.c,U)
+    criterion = CoverTreeLoss(args.c, length, args.d, new2index)
+    model = nn.Linear(args.d, length)
 ################################################################################
 # train the model
 ################################################################################
@@ -126,7 +129,7 @@ logging.debug('create SummaryWriter')
 # FIXME: uncomment
 experiment_name=f'a={args.a},c={args.c},d={args.d},n={args.n},sigma={args.sigma},lr={args.lr},loss={args.loss},seed={args.seed}'
 logging.info(f'experiment_name={experiment_name}')
-writer = SummaryWriter(os.path.join(args.logdir, experiment_name))
+# writer = SummaryWriter(os.path.join(args.logdir, experiment_name))
 
 logging.debug('create optimizer')
 optimizer = optim.SGD(
@@ -141,9 +144,14 @@ logging.debug('training loop')
 correct = 0
 for i in range(args.n):
     # calculate the loss
-    logits = model(X[i].view(1,args.d))
-    W = model.weight
-    loss = criterion(logits, Y[i].view(1)) # FIXME: notation is incorrect
+    if args.loss == 'xentropy':
+        W = model.weight
+        logits = model(X[i].view(1,args.d))
+        loss = criterion(logits, Y[i].view(1)) # FIXME: notation is incorrect
+    if args.loss == 'tree':
+        W_ = model.weight
+        loss, logits, W = criterion(W_, X[i].view(1,args.d), Y[i].view(1))
+
     # backprop
     loss.backward()
     optimizer.step()
@@ -156,9 +164,9 @@ for i in range(args.n):
         correct += 1
     accuracy = correct/(i+1) # FIXME
 
-    writer.add_scalar('losses/loss', loss, i)
-    writer.add_scalar('losses/W_err', W_err, i)
-    writer.add_scalar('losses/accuracy', accuracy, i)
+    # writer.add_scalar('losses/loss', loss, i)
[…]

### 2021-07-30 paper/paper.tex
updates

@@
 Compared to classic cross entropy loss function, cover tree loss function performs better on datasets with large number of labels.
+
+Extreme multi-label classification is difficult, but organizing labels as a tree can handle this problem. 
+Hierarchical softmax approach commonly used for multi-class problems.
+\cite{Wydmuch2018ANG} investigate probabilistic label trees that have been recently devised for tackling extreme multi-label classification and show that probabilistic label trees are a no-regret multi-label generation of hierarchical softmax when precision $@k$ is used as a model evaluation metric.
+They also show that their implementation of probabilistic label trees obtains significantly better results than hierarchical softmax with the pick-one-label heuristic.
+
+Neural networks are widely used for computational linguistics.
+These neural models leverage knowledge from massive corpora but they are extremely slow.
+\cite{Jiang2017ExplorationOT} explore the tree-based hierarchical softmax method and reform its architecture, making it compatible
+with modern GPUs and introducing a compact tree-based loss function.
+Their tree-based loss function is the negative log-likelihood of the joint product of the probability of the route taken from the root to the corresponding leaf node. 
+It is different from our cover tree loss function which parameterize the weight vectors.
+
+\cite{Yang2017OptimizeHS} gives a theoretic analysis on how should organize the hierarchical tree by treating the tree structure as a parameter of the training objective function.
+They propose SemHuff, a new tree constructing scheme based on adjusting the Huffman tree with word similarity knowledge.
+Their experiments results also show that word embeddings trained with optimized hierarchical tree can give better results in various tasks.
 
@@
         \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_n.png}}
-    \caption{Loss value, parameter matrix error, accuracy versus number of data points}
+    \caption{Loss value, parameter matrix error, accuracy versus number of data points(Dimension: 64, Randomness: 1.0, Number of Classes: 10)}
     \label{Fig.1}
@@
         \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_d.png}}
-    \caption{Loss value, parameter matrix error, accuracy versus dimension of parameter matrix}
+    \caption{Loss value, parameter matrix error, accuracy versus dimension of parameter matrix(Number of Data Points: 100, Randomness: 1.0, Number of Classes: 10)}
     \label{Fig.2}
@@
         \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_sigma.png}}
-    \caption{Loss value, parameter matrix error, accuracy versus randomness}
+    \caption{Loss value, parameter matrix error, accuracy versus randomness(Number of Data Points: 100, Dimension: 64, Number of classes: 10)}
     \label{Fig.3}
+
+    \subfigure{
+        \label{Fig.sub.1}
+        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_class.png}}
+    \subfigure{
+        \label{Fig.sub.2}
+        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_class.png}}
+    \subfigure{
+        \label{Fig.sub.3}
+        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_class.png}}
+    \caption{Loss value, parameter matrix error, accuracy versus number of classes(Number of Data Points: 100, Dimension: 64, Randomness: 1.0)}
+    \label{Fig.4}
 
@@
 \fixme{describe your procedure for generating pseudo-synthetic data and all the experiments that you plan to run}
-
+\subsubsection{Constructing Pseudo-synthetic datasets}
+\label{sec:pseu-syn}
 In order to compare the performance between classic cross entropy loss function and cover tree loss function, we need datasets which the classes have clear similarities.
 Besides, we would like to construct pseudo-synthetic datasets which we can control the similarities.
-The idea is we can sample the new classes from the original classes of datasets.
+The idea is we can generate the new classes from the original classes of datasets.
+It means only the labels are synthetic and the features are real.
 We get the similarities of new classes from probability distribution and control the complexity of similarities by changing probability distribution.
@@
   \item
-  For $o$ original classes, we want to generate a sampling matrix $m$ for c new classes which each row represents the probability distribution of a new class. 
-  Each new class is uniformly sampled from $k$ original class.
-  So the sampling matrix is as below:
+  For $o$ original classes, we want to generate a matrix $M : \R^{c\times o}$ for c new classes which each row represents the probability distribution of a new class. 
+  Each new class is uniformly generated from $k$ original classes.
+  So $M$ is as below:
 \begin{align}
-    row &= (j+col) \bmod c \\
-    m[i+row,col] &= \frac{o}{c \times n}  
+    r &= (j+l) \bmod c \\
+    M_{i+r,l} &= \frac{o}{ck}  
 \end{align}
-where $i \in [c]$ $col \in [o]$ $j \in [k]$
+where $i \in [c]$ $l \in [o]$ $j \in [k]$
 
   \item
-  We would sample new classes from the sampling matrix and view each row as vector representation of each new class and then get similarities from vector representations.
-  The new class is defined as below:
+  We generate new classes by the matrix $M$.
+  To be specific, each column of $M$ represents the probability distribution of each original class.
+  For each original class, we generate new classes by corresponding column of $M$.
+  For example, we have $100$ data points with original class $1$ and $M_{1,1}=0.5$ $M_{2,1}=0.5$, all other elements of the first column of $M$ are $0$.
+  From the first column of $M$, we generate $50$ data points with new class $1$ and $50$ data points with new class $2$.
+  If so, we can generate a pseudo-synthetic datasets with new classes $c$.
+
+  For each data point $i\in[n]$, 
+  $y$ are new classes and $Y$ are original classes,
+  we sample the data point according to the following rules:
 \begin{align}
-    c[i] = o[j] \cdot m[i,j] 
+    y_i &\sim \text{Uniform}([r_1, r_2,...,r_j,...])
 \end{align}
+where $r_j$ is row number of $M$ and $M_{r_j,Y_i} \ne 0$
+
+  We view each row of $M$ as vector representation of each new class and then get similarities from the vector representations.
+
   \item
-  Next, we are able to construct a cover tree structure from the new labels and take each leaf node represents a new class and replace all parent nodes with pseudo classes. 
+  Next, we are able to construct a cover tree structure from the new classes and take each leaf node represents a new class and replace all parent nodes with pseudo classes. 
 \end{itemize}
+
+\subsubsection{Pseudo-synthetic experiments}
+As for pseudo-synthetic experiments, we select three datasets: MNIST, CIFAR10 and CIFAR100. 
+Table 1 shows the parameters of three datasets. We modify the three non-synthetic datasets to pseudo-synthetic datasets. 
+The point is we want to construct pseudo-synthetic datasets with $c=10o$ classes as described in Section~\ref{sec:pseu-syn}.
+We would like to run experiments with different complexity of similarities by changing $k$.
+To start with $k=1$, the elements of similarity is $0$ or $1$.
+Then we take image classification task on pseudo-synthetic datasets.
 

### 2021-07-30 experiments/synthetic/create_figure_1a.sh
updates

@@ -1,5 +1,8 @@
 #!/bin/bash
 
-for n in 16 32 64 128 256 512 1024 2048 4096 8192; do
-    python3 run_experiment.py --n=$n --experiment=loss_vs_n
+for num in {1..50};
+do
+    for n in 16 32 64 128 256 512 1024 2048 4096 8192; do
+        python3 run_experiment.py --exp_num=$num --loss=xentropy --n=$n --experiment=loss_vs_n
+    done
 done

### 2021-07-30 experiments/synthetic/create_figure_1b.sh

@@ -1,3 +1,8 @@
-for d in 2 4 8 16 32 64 128 256 512 1024; do
-    python3 run_experiment.py --d=$d --experiment=loss_vs_d 
+#!/bin/bash
+
+for num in {1..50};
+do
+    for d in 2 4 8 16 32 64 128 256 512 1024; do
+        python3 run_experiment.py --exp_num=$num --loss=tree --d=$d --experiment=loss_vs_d 
+    done
 done

### 2021-07-30 experiments/synthetic/create_figure_1c.sh

@@ -1,3 +1,8 @@
-for sigma in 1.0 1.25 1.5 1.75 2.0 2.25 2.5 2.75 3.0 3.25; do
-    python3 run_experiment.py --sigma=$sigma --experiment=loss_vs_sigma
+#!/bin/bash
+
+for num in {1..50};
+do
+    for sigma in 1.0 2.0 3.0 4.0 5.0 6.0 7.0 8.0 9.0 10.0; do
+        python3 run_experiment.py --exp_num=$num --sigma=$sigma --loss=simloss --experiment=loss_vs_sigma
+    done
 done

### 2021-07-30 experiments/synthetic/create_figure_1d.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+for num in {1..50};
+do
+    for c in 10 20 30 40 50 60 70 80 90 100; do
+        python3 run_experiment.py --exp_num=$num --loss=simloss --c=$c --experiment=loss_vs_c
+    done
+done

### 2021-07-30 experiments/synthetic/plot_figure.py

@@ -1,15 +1,95 @@
-import matplotlib.pyplot as plt
 import argparse
 parser = argparse.ArgumentParser(description='create figures')
-parser.add_argument('--experiment', choices=['loss_vs_n','loss_vs_d', 'loss_vs_sigma'], required=True)
+parser.add_argument('--experiment', choices=['loss_vs_n','loss_vs_d', 'loss_vs_sigma', 'loss_vs_c'], required=True)
 args = parser.parse_args()
 
-f = open(f'{args.experiment}_tree.txt', 'r')
-f_ = open(f'{args.experiment}_xentropy.txt', 'r')
-loss = []
-W_err = []
-accuracy = []
-for line in f:
+import matplotlib.pyplot as plt
+import numpy as np
+
+f_tree = open(f'{args.experiment}_tree.txt', 'r')
+f_xentropy = open(f'{args.experiment}_xentropy.txt', 'r')
+f_simloss = open(f'{args.experiment}_simloss.txt', 'r')
+
+loss_tree_all = []
+W_err_tree_all = []
+accuracy_tree_all = []
+for line in f_tree:
+    line = line.strip()
+    if len(line)>1:
+
+        loss_start = line.find('Loss:')
+        loss_end  = loss_start + len('Loss:')
+
+        W_err_start = line.find('W_err:')
+        W_err_end = W_err_start + len('W_err:')
+
+        accuracy_start = line.find('Accuracy:')
+        accuracy_end = accuracy_start + len('Accuracy:')
+
+        loss = float(line[loss_end:W_err_start].strip())
+        W_err = float(line[W_err_end:accuracy_start].strip())
+        accuracy = float(float(line[accuracy_end:].strip()))
+
+        loss_tree_all.append(loss)
+        W_err_tree_all.append(W_err)
+        accuracy_tree_all.append(accuracy)
+loss_tree = []
+W_err_tree = []
+accuracy_tree = []
+for num in range(10):
+    loss_mid = []
+    W_err_mid = []
+    accuracy_mid = []
+    for i in range(50):
+        loss_mid.append(loss_tree_all[num+i*10])
+        W_err_mid.append(W_err_tree_all[num+i*10])
+        accuracy_mid.append(accuracy_tree_all[num+i*10])
[…]

### 2021-07-30 experiments/synthetic/run_experiment.py

@@ -30,6 +30,7 @@ parser_data = parser.add_argument_group(
         title='data generation',
         description='the variable names for these arguments match exactly the variable names used in the paper'
         )
+parser_data.add_argument('--exp_num', type=int, default=1)
 parser_data.add_argument('--a', type=int, default=5)
 parser_data.add_argument('--c', type=int, default=10)
 parser_data.add_argument('--n', type=int, default=100)
@@ -44,11 +45,12 @@ parser_model = parser.add_argument_group(
 parser_model.add_argument('--lr', type=float, default=1e-4, metavar='LR') 
 parser_model.add_argument('--momentum', type=float, default=0.9)
 parser_model.add_argument('--weight_decay', type=float, default=3e-4)
-parser_model.add_argument('--loss', choices=['tree','xentropy'], default='xentropy')
+parser_model.add_argument('--loss', choices=['tree','xentropy','simloss'], default='xentropy')
+parser.add_argument('--lower_bound', type=float, default=0.5)
 
 parser_debug = parser.add_argument_group(title='debug')
 parser_model.add_argument('--logdir', default='log')
-parser_model.add_argument('--experiment', choices=['loss_vs_n','loss_vs_d', 'loss_vs_sigma'], required=True)
+parser_model.add_argument('--experiment', choices=['loss_vs_n','loss_vs_d', 'loss_vs_sigma', 'loss_vs_c'], required=True)
 args = parser.parse_args()
 
 # load imports;
@@ -57,18 +59,19 @@ args = parser.parse_args()
 logging.info('load imports')
 import random
 import numpy as np
+import math
 import os
 import torch
 import torch.nn as nn
 import torch.optim as optim
 import torch.nn.functional as F
 from torch.utils.tensorboard import SummaryWriter
-from TreeLoss.utilities import set_seed
-from TreeLoss.loss import CoverTreeLoss
+from TreeLoss.utilities import set_seed, gen_sim
+from TreeLoss.loss import CoverTreeLoss, SimLoss
 
 # set the seed
 logging.debug('set_seed('+str(args.seed)+')')
-set_seed(args.seed)
+set_seed(args.exp_num*10)
 
 # FIXME:
 # the code below doesn't work because I can't import cover_tree;
@@ -120,6 +123,12 @@ if args.loss == 'tree':
     new2index, length = CoverTreeLoss.tree_structure(args.c,U)
[…]

### 2021-08-20 paper/paper.tex
update abstract and images

@@
 \end{center}
+
+\section{Abstract}
+Softmax Cross Entropy loss function is widely used in neural network multi-class classification tasks. 
+It treats every class equally while classes often have an inherent structure.
+We introduce cover tree loss function that build a cover tree structure between all classes by their similarities and provide the theoretical justification.
+We reparameterize the weight matrix by the cover tree structure of classes.
+We compare cover tree loss with softmax cross entropy loss function on fully synthetic dataset and pseudo-synthetic dataset and real word dataset for multi-class classification tasks. 
+The cover tree loss outperforms than softmax cross entropy loss function on metrics.
+
+\section{Introduction}
+When people do a standard multi-class classification task, the standard loss function is softmax cross entropy loss function.
+The softmax cross entropy loss function
 
@@
         \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_n.png}}
-    \caption{Loss value, parameter matrix error, accuracy versus number of data points(Dimension: 64, Randomness: 1.0, Number of Classes: 10)}
+    \caption{Loss value, parameter matrix error, accuracy versus number of data points($d=64, \sigma=1.0, c=10$)}
     \label{Fig.1}
@@
         \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_d.png}}
-    \caption{Loss value, parameter matrix error, accuracy versus dimension of parameter matrix(Number of Data Points: 100, Randomness: 1.0, Number of Classes: 10)}
+    \caption{Loss value, parameter matrix error, accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, c=10$)}
     \label{Fig.2}
@@
         \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_sigma.png}}
-    \caption{Loss value, parameter matrix error, accuracy versus randomness(Number of Data Points: 100, Dimension: 64, Number of classes: 10)}
+    \caption{Loss value, parameter matrix error, accuracy versus randomness($n=100, d=64, c=10$)}
     \label{Fig.3}
@@
         \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_class.png}}
-    \caption{Loss value, parameter matrix error, accuracy versus number of classes(Number of Data Points: 100, Dimension: 64, Randomness: 1.0)}
+    \caption{Loss value, parameter matrix error, accuracy versus number of classes($n=100, d=64, \sigma=1.0$)}
     \label{Fig.4}
@@
 The idea is we can generate the new classes from the original classes of datasets.
-It means only the labels are synthetic and the features are real.
+This impilies only the labels are synthetic and the features are real.
 We get the similarities of new classes from probability distribution and control the complexity of similarities by changing probability distribution.

### 2021-08-20 experiments/synthetic/create_figure_1a.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for n in 16 32 64 128 256 512 1024 2048 4096 8192; do
-        python3 run_experiment.py --exp_num=$num --loss=xentropy --n=$n --experiment=loss_vs_n
+        python3 run_experiment.py --exp_num=$num --loss=entropy --n=$n --experiment=loss_vs_n
     done
 done

### 2021-08-20 experiments/synthetic/create_figure_1b.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for d in 2 4 8 16 32 64 128 256 512 1024; do
-        python3 run_experiment.py --exp_num=$num --loss=tree --d=$d --experiment=loss_vs_d 
+        python3 run_experiment.py --exp_num=$num --loss=xentropy --d=$d --experiment=loss_vs_d 
     done
 done

### 2021-08-20 experiments/synthetic/create_figure_1d.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for c in 10 20 30 40 50 60 70 80 90 100; do
-        python3 run_experiment.py --exp_num=$num --loss=simloss --c=$c --experiment=loss_vs_c
+        python3 run_experiment.py --exp_num=$num --loss=xentropy --c=$c --experiment=loss_vs_c
     done
 done

### 2021-08-20 experiments/synthetic/plot_figure.py

@@ -5,6 +5,7 @@ args = parser.parse_args()
 
 import matplotlib.pyplot as plt
 import numpy as np
+import math
 
 f_tree = open(f'{args.experiment}_tree.txt', 'r')
 f_xentropy = open(f'{args.experiment}_xentropy.txt', 'r')
@@ -125,14 +126,15 @@ for num in range(10):
     accuracy_simloss.append(np.mean(accuracy_mid))
 
 if args.experiment == 'loss_vs_n' :
-    x = [16,32, 64, 128, 256, 512, 1024, 2048, 4096, 8192]
+    x = [math.log(16), math.log(32), math.log(64), math.log(128), math.log(256), math.log(512), math.log(1024),
+         math.log(2048), math.log(4096), math.log(8192)]
     plt.figure(0)
     l1, = plt.plot(x, loss_tree)
     l2, = plt.plot(x, loss_xentropy, linestyle="-.")
     l3, = plt.plot(x, loss_simloss, linestyle="--")
     plt.legend(handles=[l1,l2,l3],labels=['Cover Tree Loss','Cross Entropy Loss', 'SimLoss'])
-    plt.xlabel('Number of Data Points')
-    plt.ylabel('Loss')
+    plt.xlabel('Log(Number of Data Points)')
+    plt.ylabel('Log(Loss)')
     plt.savefig('loss_vs_n.png', dpi=300)
 
     plt.figure(1)
@@ -140,8 +142,8 @@ if args.experiment == 'loss_vs_n' :
     l2, = plt.plot(x, W_err_xentropy, linestyle="-.")
     l3, = plt.plot(x, W_err_simloss, linestyle="--")
     plt.legend(handles=[l1,l2,l3],labels=['Cover Tree Loss','Cross Entropy Loss', 'SimLoss'])
-    plt.xlabel('Number of Data Points')
-    plt.ylabel('|W_error|')
+    plt.xlabel('Log(Number of Data Points)')
+    plt.ylabel('Log|W_error|')
     plt.savefig('error_vs_n.png', dpi=300)
 
     plt.figure(2)
@@ -149,33 +151,35 @@ if args.experiment == 'loss_vs_n' :
     l2, = plt.plot(x, accuracy_xentropy, linestyle="-.")
     l3, = plt.plot(x, accuracy_simloss, linestyle="--")
[…]

### 2021-08-20 experiments/synthetic/run_experiment.py

@@ -192,5 +192,5 @@ logging.info('saving results')
 loss_log = math.log(loss+1e-10)
 W_err_log = math.log(W_err)
 accuracy_log = math.log(accuracy)
-with open(f'{args.experiment}_{args.loss}.txt', 'a') as f:
-    f.write(f'Loss: {loss_log} \t W_err: {W_err_log} \t Accuracy: {accuracy_log} \n')
+with open(f'{args.experiment}_{args.loss}_original.txt', 'a') as f:
+    f.write(f'Loss: {loss} \t W_err: {W_err} \t Accuracy: {accuracy} \n')

### 2021-09-03 paper/paper.tex
update

@@
 and so our technique may be able to provide the first theoretical justification for their work.
+
+HSM:
+\begin{equation}
+    \label{eq:xentropy}
+    \ell(W;(\x,y)) = - \log \prod_{k\in P_y}\frac {\exp(-\trans\w_k \x)}{\sum_{j=1}^c \exp(-\trans \w_j \x)}
+\end{equation}
+where $P_y$ is path from root to node of Huffman Tree
 
@@
         \label{Fig.sub.1}
-        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_n.png}}
+        \includegraphics[width=0.3\textwidth]{fig/log_images/loss_vs_n.png}}
     \subfigure{
         \label{Fig.sub.2}
-        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_n.png}}
+        \includegraphics[width=0.3\textwidth]{fig/log_images/error_vs_n.png}}
     \subfigure{
         \label{Fig.sub.3}
-        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_n.png}}
+        \includegraphics[width=0.3\textwidth]{fig/log_images/accuracy_vs_n.png}}
     \caption{Loss value, parameter matrix error, accuracy versus number of data points($d=64, \sigma=1.0, c=10$)}
@@
         \label{Fig.sub.1}
-        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_d.png}}
+        \includegraphics[width=0.3\textwidth]{fig/log_images/loss_vs_d.png}}
     \subfigure{
         \label{Fig.sub.2}
-        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_d.png}}
+        \includegraphics[width=0.3\textwidth]{fig/log_images/error_vs_d.png}}
     \subfigure{
         \label{Fig.sub.3}
-        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_d.png}}
+        \includegraphics[width=0.3\textwidth]{fig/log_images/accuracy_vs_d.png}}
     \caption{Loss value, parameter matrix error, accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, c=10$)}
@@
         \label{Fig.sub.1}
-        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_sigma.png}}
+        \includegraphics[width=0.3\textwidth]{fig/log_images/loss_vs_sigma.png}}
     \subfigure{
         \label{Fig.sub.2}
-        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_sigma.png}}
+        \includegraphics[width=0.3\textwidth]{fig/log_images/error_vs_sigma.png}}
     \subfigure{
         \label{Fig.sub.3}
-        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_sigma.png}}
+        \includegraphics[width=0.3\textwidth]{fig/log_images/accuracy_vs_sigma.png}}
     \caption{Loss value, parameter matrix error, accuracy versus randomness($n=100, d=64, c=10$)}
@@
         \label{Fig.sub.1}
-        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_class.png}}
+        \includegraphics[width=0.3\textwidth]{fig/log_images/loss_vs_class.png}}
     \subfigure{
         \label{Fig.sub.2}
-        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_class.png}}
+        \includegraphics[width=0.3\textwidth]{fig/log_images/error_vs_class.png}}
     \subfigure{
         \label{Fig.sub.3}
-        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_class.png}}
+        \includegraphics[width=0.3\textwidth]{fig/log_images/accuracy_vs_class.png}}
     \caption{Loss value, parameter matrix error, accuracy versus number of classes($n=100, d=64, \sigma=1.0$)}
@@
 \end{figure}
+
+\subsubsection{Analysis of Synthetic Experiment results}
+
+From \ref{Fig.1}, as number of data points increases loss value and parameter matrix error decrease while accuracy increases. 
+We compare the performance of cover tree loss, softmax cross entropy loss and simloss, it is clear that cover tree loss converges faster than the other two loss functions.
+Besides, cover tree loss achieves lower loss value and parameter matrix error over number of data points.
+
+As shown in \ref{Fig.2}, loss value decreases and accuracy increases over dimension. 
+Similar to \ref{Fig.1}, cover tree loss converges faster and achieve lower loss value.
+We take the line of parameter matrix error of cover tree loss as a benchmark and draw the difference of parameter matrix error between cover tree loss and the other two loss functions.
+The middle sub-figure indicates that cover tree loss has lower parameter matrix error with dimension than cross entropy and simloss.
+
+According to \ref{Fig.3}, if we increase the randomness and fix the other parameters, loss value increases and accuracy decreases.
+Cover tree loss performs similarly with cross entropy loss and simloss in terms of loss value and accuracy.
+The middle sub-figure implies that parameter matrix error of cover tree loss decreases even though the randomness increases.
+
+\ref{Fig.4} indicates that, as number of classes increases, the loss value and parameter matrix error also increases and accuracy certainly decrease.
+From middle sub-figure, the parameter matrix error of cover tree loss is lower than the other two loss functions.
+The right sub-figure shows that the accuracy of cover tree loss decreases slower and can keep higher value than the other two loss functions.
 
@@
 The idea is we can generate the new classes from the original classes of datasets.
-This impilies only the labels are synthetic and the features are real.
+This implies that only the labels are synthetic and the features are real.
 We get the similarities of new classes from probability distribution and control the complexity of similarities by changing probability distribution.

### 2021-09-03 experiments/synthetic/plot_figure.py

@@ -48,9 +48,6 @@ for num in range(10):
     loss_tree.append(np.mean(loss_mid))
     W_err_tree.append(np.mean(W_err_mid))
     accuracy_tree.append(np.mean(accuracy_mid))
-loss_tree = [math.log(y) for y in loss_tree]
-W_err_tree = [math.log(y) for y in W_err_tree]
-accuracy_tree = [math.log(y) for y in accuracy_tree]
 
 
 loss_xentropy_all = []
@@ -90,9 +87,6 @@ for num in range(10):
     loss_xentropy.append(np.mean(loss_mid))
     W_err_xentropy.append(np.mean(W_err_mid))
     accuracy_xentropy.append(np.mean(accuracy_mid))
-loss_xentropy = [math.log(y) for y in loss_xentropy]
-W_err_xentropy = [math.log(y) for y in W_err_xentropy]
-accuracy_xentropy = [math.log(y) for y in accuracy_xentropy]
 
 loss_simloss_all = []
 W_err_simloss_all = []
@@ -131,35 +125,53 @@ for num in range(10):
     loss_simloss.append(np.mean(loss_mid))
     W_err_simloss.append(np.mean(W_err_mid))
     accuracy_simloss.append(np.mean(accuracy_mid))
-loss_simloss = [math.log(y) for y in loss_simloss]
-W_err_simloss = [math.log(y) for y in W_err_simloss]
-accuracy_simloss = [math.log(y) for y in accuracy_simloss]
+
+W_diff_xentropy = np.array(W_err_xentropy) - np.array(W_err_tree)
+W_diff_simloss = np.array(W_err_simloss) - np.array(W_err_tree) 
+W_diff_tree = np.array(W_err_tree) - np.array(W_err_tree)
+
+# W_diff_xentropy = [math.log(y+1e-5) for y in W_diff_xentropy]
+# W_diff_simloss = [math.log(y+1e-5) for y in W_diff_simloss]
+# W_diff_tree = [math.log(y+1e-5) for y in W_diff_tree]
+
+# loss_tree = [math.log(y) for y in loss_tree]
+# W_err_tree = [math.log(y) for y in W_err_tree]
+# accuracy_tree = [math.log(y) for y in accuracy_tree]
+
+# loss_xentropy = [math.log(y) for y in loss_xentropy]
+# W_err_xentropy = [math.log(y) for y in W_err_xentropy]
[…]

### 2021-09-17 paper/paper.tex
update paper

--- 2021-07-30 paper/paper.tex
@@
-\documentclass[10pt]{article}
+\documentclass[twoside]{article}
 
+\usepackage{aistats2022}
+% If your paper is accepted, change the options for the package
+% aistats2022 as follows:
+%
+%\usepackage[accepted]{aistats2022}
+%
+% This option will print headings for the title of your paper and
+% headings for the authors names, plus a copyright note at the end of
+% the first column of the first page.
+
+% If you set papersize explicitly, activate the following three lines:
+%\special{papersize = 8.5in, 11in}
+%\setlength{\pdfpageheight}{11in}
+%\setlength{\pdfpagewidth}{8.5in}
+
+% If you use natbib package, activate the following three lines:
+%\usepackage[round]{natbib}
+%\renewcommand{\bibname}{References}
+%\renewcommand{\bibsection}{\subsubsection*{\bibname}}
+
+% If you use BibTeX in apalike style, activate the following line:
+%\bibliographystyle{apalike}
 \usepackage[margin=1in]{geometry}
@@
 \usepackage{booktabs}
+\usepackage{multirow}
 \usepackage{subfigure}
@@
 
-\begin{center}
-\Huge
-The Cover Tree Loss
-\end{center}
+% If your paper is accepted and the title of your paper is very long,
+% the style will print as headings an error message. Use the following
+% command to supply a shorter title of your paper so that it can be
+% used as headings.
+%
+%\runningtitle{I use this title instead because the last one was very long}
+
+% If your paper is accepted and the number of authors is large, the
+% style will print as headings an error message. Use the following
+% command to supply a shorter version of the authors names so that
+% they can be used as headings (for example, use only the surnames)
+%
+%\runningauthor{Surname 1, Surname 2, Surname 3, ...., Surname n}
+
+\twocolumn[
+
+\aistatstitle{The Cover Tree Loss}
+
+\aistatsauthor{ Yujie Wang \And Michael Izbicki  }
+
+\aistatsaddress{ Claremont Graduate University \And  Claremont McKenna College } ]
+
+\begin{abstract}
+Softmax Cross Entropy loss function is widely used in neural network multi-class classification tasks. 
+It treats every class equally while classes often have an internal structure. 
+We introduce cover tree loss function which takes advantage of this internal class structure.
+Compare to softmax cross entropy which has generalization error $O(\sqrt{c/n})$, the generalization error of cover tree loss is $O(\sqrt{1/n})$ which is independent of the number of classes. 
+We provide the theoretical justification and conduct extensive experiments on fully synthetic data and real world data. 
+The cover tree loss outperforms than softmax cross entropy loss function on metrics.  
+\end{abstract}
+
+\section{Introduction}
+When people do a standard multi-class classification task, the standard loss function is softmax cross entropy loss function.
+The softmax cross entropy loss function
 
@@
 \end{theorem}
-\begin{proof}
-    \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David and the properties of the cross entropy loss from the last set of notes.}
-    \begin{align}
-    {\| W \|^2_F}&=\sum_{i=1}^c{\| W_i\|^2}\\
-                &\le\sum_{i=1}^c{B^2}\\
-                &\le cB^2\\
-   \| W \|_F  &\le \sqrt c B 
-    \end{align}
-Then we get:
-    \begin{equation}
-    l(\bar W)-l(W^*)\le\frac {\sqrt cB\rho}{\sqrt n}
-    \end{equation}
-   Take expectation of both side of equation(3):
-   \begin{equation}
-    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt cB\rho}{\sqrt n}
-\end{equation}
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{proof}
+%     \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David and the properties of the cross entropy loss from the last set of notes.}
+%     \begin{align}
+%     {\| W \|^2_F}&=\sum_{i=1}^c{\| W_i\|^2}\\
+%                 &\le\sum_{i=1}^c{B^2}\\
+%                 &\le cB^2\\
+%   \| W \|_F  &\le \sqrt c B 
+%     \end{align}
+% Then we get:
+%     \begin{equation}
+%     l(\bar W)-l(W^*)\le\frac {\sqrt cB\rho}{\sqrt n}
+%     \end{equation}
+%   Take expectation of both side of equation(3):
+%   \begin{equation}
+%     \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt cB\rho}{\sqrt n}
+% \end{equation}
+% \end{proof}
 
@@
 
-\fixme{Read the papers mentioned above.  Verify that you agree with the things I wrote.  Then, write a detailed mathematical description of the HSM loss and contrast it with the cover tree loss.}
+HSM:
+\begin{equation}
+    \label{eq:xentropy}
+    \ell(W;(\x,y)) = - \log \prod_{k\in P_y}\frac {\exp(-\trans\w_k \x)}{\sum_{j=1}^c \exp(-\trans \w_j \x)}
+\end{equation}
+where $P_y$ is path from root to node of Huffman Tree
 
-\fixme{Read 5-10 additional papers about the hierarchical softmax.
+% \fixme{Read the papers mentioned above.  Verify that you agree with the things I wrote.  Then, write a detailed mathematical description of the HSM loss and contrast it with the cover tree loss.}
+
+% \fixme{Read 5-10 additional papers about the hierarchical softmax.
 For each paper, write a paragraph describing the paper's contributions and how it relates to the cover tree loss.
@@
 
-\fixme{Write a detailed description of the sim loss}
+% \fixme{Write a detailed description of the sim loss}
 
-Simloss\cite{Kobs2020SimLossCS} is similarity based loss function which incorporates class similarities to support the training of neural network classifiers.
+Simloss \cite{Kobs2020SimLossCS} is similarity based loss function which incorporates class similarities to support the training of neural network classifiers.
 Cross entropy loss assumes only one class is correct and punishes every misclassification, while Simloss indicates classes have similarities and classifying a target as a similar class is better.
@@
 \end{theorem}
-\begin{proof}
-    \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David.}
-    \begin{align}
-    {\| U \|^2_F}&=\sum_{i=1}^e{\| U_i\|^2}\\
-                &\le\sum_{i=1}^e{B^2}\\
-                &\le eB^2\\
-   \| U \|_F  &\le \sqrt e B  \\
-   \| W \|_F  &\le \sqrt e B
-    \end{align}
-    Then we get:
-    \begin{equation}
-    l(\bar W)-l(W^*)\le\frac {\sqrt eB\rho}{\sqrt n}
-    \end{equation}
-   Take expectation of both side of equation(8):
-   \begin{equation}
-    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt eB\rho}{\sqrt n}
-\end{equation}
-\end{proof}
+% \begin{proof}
+%     \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David.}
+%     \begin{align}
+%     {\| U \|^2_F}&=\sum_{i=1}^e{\| U_i\|^2}\\
+%                 &\le\sum_{i=1}^e{B^2}\\
+%                 &\le eB^2\\
+%   \| U \|_F  &\le \sqrt e B  \\
+%   \| W \|_F  &\le \sqrt e B
+%     \end{align}
+%     Then we get:
+%     \begin{equation}
+%     l(\bar W)-l(W^*)\le\frac {\sqrt eB\rho}{\sqrt n}
+%     \end{equation}
+%   Take expectation of both side of equation(8):
+%   \begin{equation}
+%     \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt eB\rho}{\sqrt n}
+% \end{equation}
+% \end{proof}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{The Tree Loss}
@@
 and internal nodes represent \emph{pseudo-classes} that group the existing classes into a logical hierarchy.
-At this point, we assume that the label tree structure is given a priori, and in Section \ref{sec:bias-var} we discuss methods for generating this structure and their tradeoff and their tradeoffss.
+At this point, we assume that the label tree structure is given a priori, and in Section \ref{sec:bias-var} we discuss methods for generating this structure and their tradeoffs.
 The following figure shows an example label tree for a classification problem with 9 classes.
@@
 \begin{center}
+\small
 \begin{tikzpicture}
@@
 we have
+
 \begin{equation}
-    P_{\texttt{truck}} = (\texttt{truck}, \textit{pseudo3}, \textit{pseudo2}, \textit{pseudo1} ) \qquad\text{and}\qquad
-    P_{\texttt{cat}} = (\texttt{cat}, \textit{pseudo4}, \textit{pseudo1} )
-    .
+\begin{split}
+    P_{\texttt{truck}} &= (\texttt{truck}, \textit{pseudo3}, \textit{pseudo2}, \textit{pseudo1} ) \\
+    P_{\texttt{cat}} &= (\texttt{cat}, \textit{pseudo4}, \textit{pseudo1} )
+\end{split}
 \end{equation}
+
+% \end{equation}
+
 Next, we associate a vector $\vv_i$ to each leaf and internal node $i$ in the tree structure.
@@
     \begin{equation}
+    \begin{split}
         \left(\frac q 2\right)^r
-        =
-        \left(\frac q 2\right)^{\log_q n}
-        =
-        \frac{n}{2^{\log_q n}}
-        =
-        \frac{n}{2^{{\log_2 n}/{\log_2 q}}}
-        =
-        \frac{n}{n^{1/\log_2 q}}
-        =
+        &=
+        \left(\frac q 2\right)^{\log_q n}\\
+        &=
+        \frac{n}{2^{\log_q n}}\\
+        &=
+        \frac{n}{2^{{\log_2 n}/{\log_2 q}}}\\
+        &=
+        \frac{n}{n^{1/\log_2 q}}\\
+        &=
         n^{\left(1 - {1}/{\log_2 q}\right)}
@@
         \label{eq:lem:technical2}
+    \end{split}
     \end{equation}
@@
 %     and that for each class $i\in[c]$, $\ltwo{\w_i}\le B$.
-\fixme{Add assumptions.}
+% \fixme{Add assumptions.}
 Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
-    and that for each class $i\in[c]$, $\ltwo{\w_i}\le \frac{B}{\sqrt k}$.
+    and that for each class $i\in[c]$, $\ltwo{\w_i}\le \frac{B}{2^{\level k}}$.
 Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
@@
 converges to $W^*$ using the standard cross entropy loss and both the matrix factorization and cover tree reparameterizations.
-\fixme{You should prove this for yourself.}
-Figure \ref{fig:synthetic-results} shows that the cover tree loss converges at a faster rate.
 
 \begin{figure}[h]
+\vspace{.3in}
 \centering
-    \subfigure{
-        \label{Fig.sub.1}
-        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_n.png}}
-    \subfigure{
-        \label{Fig.sub.2}
-        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_n.png}}
-    \subfigure{
-        \label{Fig.sub.3}
-        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_n.png}}
-    \caption{Loss value, parameter matrix error, accuracy versus number of data points(Dimension: 64, Randomness: 1.0, Number of Classes: 10)}
+\includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_n.png}
+\vspace{.3in}
+\caption{Accuracy versus number of data points($d=64, \sigma=1.0, c=10$)}
 \label{Fig.1}
+\end{figure}
 
-    \subfigure{
-        \label{Fig.sub.1}
-        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_d.png}}
-    \subfigure{
-        \label{Fig.sub.2}
-        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_d.png}}
-    \subfigure{
-        \label{Fig.sub.3}
-        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_d.png}}
-    \caption{Loss value, parameter matrix error, accuracy versus dimension of parameter matrix(Number of Data Points: 100, Randomness: 1.0, Number of Classes: 10)}
+\begin{figure}[h]
+\vspace{.3in}
+\centering
+\includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_d.png}
+\vspace{.3in}
+\caption{Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, c=10$)}
 \label{Fig.2}
+\end{figure}
 
-    \subfigure{
-        \label{Fig.sub.1}
-        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_sigma.png}}
-    \subfigure{
-        \label{Fig.sub.2}
-        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_sigma.png}}
-    \subfigure{
-        \label{Fig.sub.3}
-        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_sigma.png}}
-    \caption{Loss value, parameter matrix error, accuracy versus randomness(Number of Data Points: 100, Dimension: 64, Number of classes: 10)}
+\begin{figure}[h]
+\vspace{.3in}
+\centering
+\includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_sigma.png}
+\vspace{.3in}
+\caption{Accuracy versus randomness($n=100, d=64, c=10$)}
 \label{Fig.3}
+\end{figure}
 
-    \subfigure{
-        \label{Fig.sub.1}
-        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_class.png}}
-    \subfigure{
-        \label{Fig.sub.2}
-        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_class.png}}
-    \subfigure{
-        \label{Fig.sub.3}
-        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_class.png}}
-    \caption{Loss value, parameter matrix error, accuracy versus number of classes(Number of Data Points: 100, Dimension: 64, Randomness: 1.0)}
+\begin{figure}[h]
+\vspace{.3in}
+\centering
+\includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_class.png}
+\vspace{.3in}
+\caption{Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)}
 \label{Fig.4}
+\end{figure}
 
-    \caption{
-        \fixme{We need a plot of loss vs number of data points ($n$), vs dimension ($d$), and vs randomness ($sigma$).
-These plots should all be log-log plots.
-For each of these experiments, you should write to shell scripts: the first to generate the data and the second to plot the data.
-These shell scripts should be easy to run in order to easily replicate your experiments.}}
-    \label{fig:synthetic-results}
-\end{figure}
+% \subsubsection{Analysis of Synthetic Experiment results}
+% From \ref{Fig.1}, as number of data points increases loss value and parameter matrix error decrease while accuracy increases. 
+% We compare the performance of cover tree loss, softmax cross entropy loss and simloss, it is clear that cover tree loss converges faster than the other two loss functions.
+% Besides, cover tree loss achieves lower loss value and parameter matrix error over number of data points.
+
+% As shown in \ref{Fig.2}, loss value decreases and accuracy increases over dimension. 
+% Similar to \ref{Fig.1}, cover tree loss converges faster and achieve lower loss value.
+% We take the line of parameter matrix error of cover tree loss as a benchmark and draw the difference of parameter matrix error between cover tree loss and the other two loss functions.
+% The middle sub-figure indicates that cover tree loss has lower parameter matrix error with dimension than cross entropy and simloss.
+
+% According to \ref{Fig.3}, if we increase the randomness and fix the other parameters, loss value increases and accuracy decreases.
+% Cover tree loss performs similarly with cross entropy loss and simloss in terms of loss value and accuracy.
+% The middle sub-figure implies that parameter matrix error of cover tree loss decreases even though the randomness increases.
+
+% \ref{Fig.4} indicates that, as number of classes increases, the loss value and parameter matrix error also increases and accuracy certainly decrease.
+% From middle sub-figure, the parameter matrix error of cover tree loss is lower than the other two loss functions.
+% The right sub-figure shows that the accuracy of cover tree loss decreases slower and can keep higher value than the other two loss functions.
 
@@
 
-In multilabel classification, it is common for the classes to be unbalanced.
+In multi-label classification, it is common for the classes to be unbalanced.
 We would like to show that the cover tree loss works well for unbalanced data.
@@
 
-The covertree loss can work well even when the weight matrix has non-linear intrinsic structure.
+The cover tree loss can work well even when the weight matrix has non-linear intrinsic structure.
 We should adapt the $\w*_i$ vectors to sit on a manifold instead of a hyperplane to demonstrate this fact.
 
-\subsection{Pseudo-synthetic data}
-In a pseudo-synthetic dataset, we take a non-synthetic dataset and modify it.
-\fixme{describe your procedure for generating pseudo-synthetic data and all the experiments that you plan to run}
-\subsubsection{Constructing Pseudo-synthetic datasets}
-\label{sec:pseu-syn}
-In order to compare the performance between classic cross entropy loss function and cover tree loss function, we need datasets which the classes have clear similarities.
-Besides, we would like to construct pseudo-synthetic datasets which we can control the similarities.
-The idea is we can generate the new classes from the original classes of datasets.
-It means only the labels are synthetic and the features are real.
-We get the similarities of new classes from probability distribution and control the complexity of similarities by changing probability distribution.
+\subsection{Real world data}
+% \fixme{Write a description of the experiment.}
+In this experiment, we will compare cover tree loss with softmax corss entropy and simloss on some real world data.
+We conduct image classification tasks on CIFAR-100 dataset and ImageNet dataset and emoji prediction task on twitter dataset.
+Our goal is to investigate the effects of changing the loss function on our example experiments.
+We do not focus on if we have state-of-the-art performance on specific models, but rather on the evaluation of cover tree loss as a general loss function which can be applied on various tasks.
+These three tasks and datasets are typical examples for using softmax cross entropy loss.
 
-For non-synthetic datasets that do not have specific similarities, we would build pseudo-synthetic datasets with similarities manually by following procedures. 
-\begin{itemize}
-  \item
-  For $o$ original classes, we want to generate a matrix $M : \R^{c\times o}$ for c new classes which each row represents the probability distribution of a new class. 
-  Each new class is uniformly generated from $k$ original classes.
-  So $M$ is as below:
-\begin{align}
-    r &= (j+l) \bmod c \\
-    M_{i+r,l} &= \frac{o}{ck}  
-\end{align}
-where $i \in [c]$ $l \in [o]$ $j \in [k]$
+\subsubsection{CIFAR-100 Data}
+We use CIFAR-100 dataset which has 100 classes for image classification.
+We also get word embeddings from a word2vec model pretrained on Google News \cite{Mikolov2013EfficientEO} of class names and construct cover tree structure and calculate similarity between classes from word embeddings.
+If the class name include more than one word, we take a sum of the embedding of each word.
 
-  \item
-  We generate new classes by the matrix $M$.
-  To be specific, each column of $M$ represents the probability distribution of each original class.
-  For each original class, we generate new classes by corresponding column of $M$.
-  For example, we have $100$ data points with original class $1$ and $M_{1,1}=0.5$ $M_{2,1}=0.5$, all other elements of the first column of $M$ are $0$.
-  From the first column of $M$, we generate $50$ data points with new class $1$ and $50$ data points with new class $2$.
-  If so, we can generate a pseudo-synthetic datasets with new classes $c$.
-
-  For each data point $i\in[n]$, 
-  $y$ are new classes and $Y$ are original classes,
-  we sample the data point according to the following rules:
-\begin{align}
-    y_i &\sim \text{Uniform}([r_1, r_2,...,r_j,...])
-\end{align}
-where $r_j$ is row number of $M$ and $M_{r_j,Y_i} \ne 0$
-
-  We view each row of $M$ as vector representation of each new class and then get similarities from the vector representations.
-
-  \item
-  Next, we are able to construct a cover tree structure from the new classes and take each leaf node represents a new class and replace all parent nodes with pseudo classes. 
-\end{itemize}
-
-\subsubsection{Pseudo-synthetic experiments}
-As for pseudo-synthetic experiments, we select three datasets: MNIST, CIFAR10 and CIFAR100. 
-Table 1 shows the parameters of three datasets. We modify the three non-synthetic datasets to pseudo-synthetic datasets. 
-The point is we want to construct pseudo-synthetic datasets with $c=10o$ classes as described in Section~\ref{sec:pseu-syn}.
-We would like to run experiments with different complexity of similarities by changing $k$.
-To start with $k=1$, the elements of similarity is $0$ or $1$.
-Then we take image classification task on pseudo-synthetic datasets.
+To evaluate our cover tree loss, we rely on two metrics: accuracy (Acc.) which focus on correct predictions and similarity accuracy (SA) which focus on the similarity of predicted and target class.
+We take ResNet20 model \cite{He2016DeepRL} and SGD optimizer with a learning rate 0.1 and a batch size of 1021. 
+We stop early to get the highest accuracy on validation set.
 
 \begin{table}[h]
-    \centering
-    \input{fig/datasets.tex}
+\small
+\caption{Validation and test results with early stopping on CIFAR-100 dataset. Best values are written in bold.} \label{cifar100}
+\begin{center}
+\begin{tabular}{@{}lcccc@{}}
+\toprule
+\multicolumn{1}{c}{\multirow{2}{*}{Loss}} & \multicolumn{2}{c}{VALIDATION} & \multicolumn{2}{c}{TEST}       \\ \cmidrule(l){2-5} 
+\multicolumn{1}{c}{}                      & Acc.       & SA            & Acc.      & SA             \\ \cmidrule(r){1-1}
+Cover Tree Loss                           & \textbf{53.44} & \textbf{66.7} & \textbf{53.5} & \textbf{65.89} \\
+Cross Entropy                             & 52.08          & 65.46         & 51.87         & 65.58          \\
+SimLoss                                   & 52.50           & 65.76         & 52.43         & 65.82          \\ \bottomrule
+\end{tabular}
+\end{center}
 \end{table}
 
-\subsection{Real world twitter data}
-\fixme{Write a description of the experiment.}
+\subsubsection{ImageNet Data}
+ImageNet dataset \cite{Russakovsky2015ImageNetLS} has 1000 classes and many of the classes are similar and related, we consider the internal class structure has a impact on performance of loss function.
+We use class names to get class representations from a pretrained BERT model \cite{Devlin2019BERTPO}.
+We take ResNet50 model \cite{He2016DeepRL} and SGD optimizer with a learning rate 0.01.
+Our metrics are top 1 accuracy and top 5 accuracy.
+
+\begin{table}[h]
+\small
+\caption{Validation and test results on ImageNet dataset. Best values are written in bold.} \label{imagenet}
+\begin{center}
+\begin{tabular}{@{}lll@{}}
+\toprule
+\multicolumn{1}{c}{\multirow{2}{*}{Loss}} & \multicolumn{2}{c}{VALIDATION} \\ \cmidrule(l){2-3} 
+\multicolumn{1}{c}{}                      & Top1 Acc.      & Top5 Acc.     \\ \cmidrule(r){1-1}
+Cover Tree Loss                           &                &               \\
+Cross Entropy                             &                &               \\
+SimLoss                                   &                &               \\ \bottomrule
+\end{tabular}
+\end{center}
+\end{table}
+
+\subsubsection{Twitter Data}
 
@@
 We trained the multilingual BERT model on tweets to predict which emoji corresponds to a piece of text is best for measuring the emotional content in the text. 
-Our 1660 target emojis are defined by emo2vec\cite{Eisner2016emoji2vecLE}.
+Our 1661 target emojis are defined by emo2vec \cite{Eisner2016emoji2vecLE}.
 
-\subsubsection{Data processing}
-We collect all tweets\cite{Izbicki2019GeolocatingTI} in any languages sent from anywhere in the world and filter the tweets with target emojis. 
+We collect all tweets \cite{Izbicki2019GeolocatingTI} in any languages sent from anywhere in the world and filter the tweets with target emojis. 
 For each tweet, we replace all user mentions with a special token \texttt{\text{<}mention\text{>}} and all URLS with a special token \texttt{\text{<}url\text{>}} and delete all emojis. 
@@
 
-\subsubsection{Experiments}
-We apply the multilingual BERT model\cite{Feng2020LanguageagnosticBS} trained on data from 109 distinct languages which achieves state-of-the-art performance on a wide variety of natural language tasks.
-We get the embeddings of 1660 target emojis defined by emo2vec and construct a cover tree structure from these emojis. 
+We take the multilingual BERT model \cite{Feng2020LanguageagnosticBS} pretrained on data from 109 distinct languages which achieves state-of-the-art performance on a wide variety of natural language tasks.
+We get the embeddings of 1661 target emojis defined by emo2vec and construct a cover tree structure from these emojis. 
 In this cover tree structure, every leaf node represents each real target emoji and we replace all parent nodes with pseudo labels. 
-Then we would adopt cover tree loss and compare the performance with classic cross entropy loss.
+Then we would adopt cover tree loss and compare the performance with softmax cross entropy loss and SimLoss.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[h]
+\small
+\caption{Validation and test results of emoji prediction task on twitter dataset. Best values are written in bold.} \label{twitter}
+\begin{center}
+\begin{tabular}{@{}lcccc@{}}
+\toprule
+\multicolumn{1}{c}{\multirow{2}{*}{Loss}} & \multicolumn{2}{c}{VALIDATION} & \multicolumn{2}{c}{TEST}       \\ \cmidrule(l){2-5} 
+\multicolumn{1}{c}{}                      & Acc.       & SA       & Acc.      & SA             \\ \cmidrule(r){1-1}
+Cover Tree Loss                           &   \textbf{20.81}    &   \textbf{50.26}  &  \textbf{20.96}    &   \textbf{50.45}        \\
+Cross Entropy                             &   19.90    &   48.27  &  19.95    &   48.33        \\
+SimLoss                                   &   19.91    &   48.25  &  19.96    &   48.32         \\ \bottomrule
+\end{tabular}
+\end{center}
+\end{table}
+
+\subsubsection{Analysis}
+
+\section{Conclusion}
+
 \bibliographystyle{plainnat}
 \bibliography{paper}
-
 \end{document}

### 2021-09-17 experiments/synthetic/create_figure_1a.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for n in 16 32 64 128 256 512 1024 2048 4096 8192; do
-        python3 run_experiment.py --exp_num=$num --loss=entropy --n=$n --experiment=loss_vs_n
+        python3 run_experiment.py --exp_num=$num --loss=simloss --n=$n --lower_bound=0.9 --experiment=loss_vs_n
     done
 done

### 2021-09-17 experiments/synthetic/create_figure_1b.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for d in 2 4 8 16 32 64 128 256 512 1024; do
-        python3 run_experiment.py --exp_num=$num --loss=xentropy --d=$d --experiment=loss_vs_d 
+        python3 run_experiment.py --exp_num=$num --loss=simloss --d=$d --lower_bound=0.9 --experiment=loss_vs_d 
     done
 done

### 2021-09-17 experiments/synthetic/create_figure_1c.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for sigma in 1.0 2.0 3.0 4.0 5.0 6.0 7.0 8.0 9.0 10.0; do
-        python3 run_experiment.py --exp_num=$num --sigma=$sigma --loss=simloss --experiment=loss_vs_sigma
+        python3 run_experiment.py --exp_num=$num --sigma=$sigma --loss=simloss --lower_bound=0.6 --experiment=loss_vs_sigma
     done
 done

### 2021-09-17 experiments/synthetic/create_figure_1d.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for c in 10 20 30 40 50 60 70 80 90 100; do
-        python3 run_experiment.py --exp_num=$num --loss=xentropy --c=$c --experiment=loss_vs_c
+        python3 run_experiment.py --exp_num=$num --loss=simloss --c=$c --lower_bound=0.6 --experiment=loss_vs_c
     done
 done

### 2021-09-17 experiments/synthetic/plot_figure.py

@@ -9,7 +9,12 @@ import math
 
 f_tree = open(f'{args.experiment}_tree_original.txt', 'r')
 f_xentropy = open(f'{args.experiment}_xentropy_original.txt', 'r')
-f_simloss = open(f'{args.experiment}_simloss_original.txt', 'r')
+f_simloss_1 = open(f'{args.experiment}_simloss_original.txt', 'r')
+f_simloss_2 = open(f'{args.experiment}_simloss_original_0.6.txt', 'r')
+f_simloss_3 = open(f'{args.experiment}_simloss_original_0.7.txt', 'r')
+f_simloss_4 = open(f'{args.experiment}_simloss_original_0.8.txt', 'r')
+f_simloss_5 = open(f'{args.experiment}_simloss_original_0.9.txt', 'r')
+f_simloss = [f_simloss_1, f_simloss_2, f_simloss_3, f_simloss_4, f_simloss_5]
 
 loss_tree_all = []
 W_err_tree_all = []
@@ -88,46 +93,58 @@ for num in range(10):
     W_err_xentropy.append(np.mean(W_err_mid))
     accuracy_xentropy.append(np.mean(accuracy_mid))
 
-loss_simloss_all = []
-W_err_simloss_all = []
-accuracy_simloss_all = []
-for line in f_simloss:
-    line = line.strip()
-    if len(line)>1:
-
-        loss_start = line.find('Loss:')
-        loss_end  = loss_start + len('Loss:')
-
-        W_err_start = line.find('W_err:')
-        W_err_end = W_err_start + len('W_err:')
-
-        accuracy_start = line.find('Accuracy:')
-        accuracy_end = accuracy_start + len('Accuracy:')
-
-        loss__ = float(line[loss_end:W_err_start].strip())
-        W_err__ = float(line[W_err_end:accuracy_start].strip())
-        accuracy__ = float(float(line[accuracy_end:].strip()))
-
-        loss_simloss_all.append(loss__)
-        W_err_simloss_all.append(W_err__)
-        accuracy_simloss_all.append(accuracy__)
 loss_simloss = []
 W_err_simloss = []
 accuracy_simloss = []
-for num in range(10):
-    loss_mid = []
-    W_err_mid = []
-    accuracy_mid = []
-    for i in range(50):
[…]

### 2021-09-17 experiments/synthetic/run_experiment.py

@@ -192,5 +192,5 @@ logging.info('saving results')
 loss_log = math.log(loss+1e-10)
 W_err_log = math.log(W_err)
 accuracy_log = math.log(accuracy)
-with open(f'{args.experiment}_{args.loss}_original.txt', 'a') as f:
+with open(f'{args.experiment}_{args.loss}_original_{args.lower_bound}.txt', 'a') as f:
     f.write(f'Loss: {loss} \t W_err: {W_err} \t Accuracy: {accuracy} \n')

### 2021-10-06 paper/paper.tex
update

@@
 \usepackage{multirow}
-\usepackage{subfigure}
+\usepackage{graphicx}
+\usepackage{subcaption}
+\usepackage{mwe}
 
@@
 \begin{abstract}
-Softmax Cross Entropy loss function is widely used in neural network multi-class classification tasks. 
-It treats every class equally while classes often have an internal structure. 
+Softmax Cross Entropy loss function treats every class equally while classes often have an internal structure. 
 We introduce cover tree loss function which takes advantage of this internal class structure.
+The cover tree loss works by reparameterizing the weight matrix for the softmax cross entropy loss.
 Compare to softmax cross entropy which has generalization error $O(\sqrt{c/n})$, the generalization error of cover tree loss is $O(\sqrt{1/n})$ which is independent of the number of classes. 
 We provide the theoretical justification and conduct extensive experiments on fully synthetic data and real world data. 
+For real world data, we take CIFAR100 dataset, IMAGENET dataset and TWITTER dataset.
 The cover tree loss outperforms than softmax cross entropy loss function on metrics.
@@
 \section{Introduction}
-When people do a standard multi-class classification task, the standard loss function is softmax cross entropy loss function.
-The softmax cross entropy loss function
+When people do a multi-class classification task, the standard loss function is softmax cross entropy.
+The mechanism of softmax cross entropy loss function is to maximize the assigned target class probability and punishes every misclassification equally, independent of some other information about the predicted class.
+However, classes often have an internal structure. 
+For example, dog and cat belong to same 'parent': animal and many transportations have same 'parent' while they have different brothers.
+Take the internal structure in the training procedure would allow the classifier to make less sever mistakes as it learns to predict similar classes.
+In terms of theoretical result, the parameter matrix of softmax cross entropy loss is bounded by $\sqrt{c}B$ (where $c$ is the number of classes) and for $n$ data points, the generalization error is $O(\sqrt{c/n})$ which is dependent on $c$.
+
+In this paper, we introduce cover tree loss which works by reparameterizing the weight matrix for the softmax cross entropy loss. 
+The reparameterization is defined by a cover tree structure that constructed by similarity between all classes. 
+Every class is represented by a leaf node in the cover tree and all other internal nodes represent pseudo-classes. 
+Our cover tree loss is based on softmax cross entropy and easily implement.
+The idea of cover tree is that we use tree structure to reduce the bound of the size of the parameter space and then the generalization error of cover tree loss is $O(\sqrt{1/n})$ which is independent of $c$.
+
+Our contributions are as below:
+\begin{itemize}
+    \item [1] 
+    We introduce cover tree loss which take advantage of internal structure between all classes.
+    \item [2] 
+    We provide theoretical justification that the generalization error of cover tree loss is independent of the number of classes.
+    \item [3]
+    We evaluate our cover tree loss on experiments.
+One is experiment on fully synthetic data which is designed to be convex.
+The another one is on real world data: CIFAR100, IMAGENET and TWITTER dataset.
+
+\end{itemize}
 
@@
     \label{eq:xentropy}
-    \ell(W;(\x,y)) = - \log \prod_{k\in P_y}\frac {\exp(-\trans\w_k \x)}{\sum_{j=1}^c \exp(-\trans \w_j \x)}
+    \ell(W;(\x,y)) = - \log \prod_{k\in P_y}\frac {\exp(-\trans\w_k \x)}{j\in L_k \exp(-\trans \w_j \x)}
 \end{equation}
-where $P_y$ is path from root to node of Huffman Tree
+where $P_y$ is path from root to node of Huffman Tree,
+$L_k$ are nodes on the level where $k$ are
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{The Tree Loss}
@@
 \begin{center}
-\small
 \begin{tikzpicture}
@@
 %     and that for each class $i\in[c]$, $\ltwo{\w_i}\le B$.
-% \fixme{Add assumptions.}
+\fixme{Add assumptions.}
 Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
-    and that for each class $i\in[c]$, $\ltwo{\w_i}\le \frac{B}{2^{\level k}}$.
+    and that for each class $i\in[c]$,  $\ltwo{\w _i} \le \frac{B}{2^{\level i}}$.
 Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
@@
 converges to $W^*$ using the standard cross entropy loss and both the matrix factorization and cover tree reparameterizations.
+% \fixme{You should prove this for yourself.}
+% Figure \ref{fig:synthetic-results} shows that the cover tree loss converges at a faster rate.
 
-\begin{figure}[h]
-\vspace{.3in}
+\begin{figure*}
         \centering
-\includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_n.png}
-\vspace{.3in}
-\caption{Accuracy versus number of data points($d=64, \sigma=1.0, c=10$)}
-\label{Fig.1}
-\end{figure}
+        \begin{subfigure}[b]{0.45\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{fig/images/accuracy_vs_n.png}
+            % \caption[Accuracy versus number of data points($d=64, \sigma=1.0, c=10$)]%
+            {{\small Accuracy versus number of data points($d=64, \sigma=1.0, c=10$)}}  
+            \label{subfig.1}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.45\textwidth}  
+            \centering 
+            \includegraphics[width=\textwidth]{fig/images/accuracy_vs_d.png}
+            % \caption[Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, c=10$)]%
+            {{\small Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, c=10$)}}
+            \label{subfig.2}
+        \end{subfigure}
+        \vskip\baselineskip
+        \begin{subfigure}[b]{0.45\textwidth}   
+            \centering 
+            \includegraphics[width=\textwidth]{fig/images/accuracy_vs_sigma.png}
+            % \caption[Accuracy versus randomness($n=100, d=64, c=10$)]%
+            {{\small Accuracy versus randomness($n=100, d=64, c=10$)}}
+            \label{subfig.3}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.45\textwidth}   
+            \centering 
+            \includegraphics[width=\textwidth]{fig/images/accuracy_vs_class.png}
+            % \caption[Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)]%
+            {{\small Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)}}   
+            \label{subfig.4}
+        \end{subfigure}
+        % \caption[ Figures of Synthetic Data Experiment ]
+        % {{\small Figures of Synthetic Data Experiment}}
+        \label{fig.1}
+    \end{figure*}
 
-\begin{figure}[h]
-\vspace{.3in}
+\begin{figure*}
         \centering
-\includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_d.png}
-\vspace{.3in}
-\caption{Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, c=10$)}
-\label{Fig.2}
-\end{figure}
+        \begin{subfigure}[b]{0.45\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{fig/new_img/loss_vs_structure.png}
+            % \caption[Accuracy versus number of data points($d=64, \sigma=1.0, c=10$)]%
+            {{\small Accuracy versus cover tree structure($n=1000, d=64, \sigma=1.0, c=100$)}}   
+            \label{subfig.1}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.45\textwidth}  
+            \centering 
+            \includegraphics[width=\textwidth]{fig/new_img/accuracy_vs_base.png}
+            % \caption[Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, c=10$)]%
+            {{\small Accuracy versus base of cover tree($n=1000, d=10, \sigma=1.0, c=100$)}}    
+            \label{subfig.2}
+        \end{subfigure}
+        \vskip\baselineskip
+        \begin{subfigure}[b]{0.45\textwidth}   
+            \centering 
+            \includegraphics[width=\textwidth]{fig/new_img/height_vs_base.png}
+            % \caption[Accuracy versus randomness($n=100, d=64, c=10$)]%
+            {{\small Height versus base of cover tree($n=1000, d=10, \sigma=1.0, c=100$)}}  
+            \label{subfig.3}
+        \end{subfigure}
+        \hfill
+        % \begin{subfigure}[b]{0.45\textwidth}   
+        %     \centering 
+        %     \includegraphics[width=\textwidth]{fig/new_img/loss_vs_base.png}
+        %     % \caption[Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)]%
+        %     {{\small Loss versus base of cover tree($n=1000, d=10, \sigma=1.0, c=100$)}}    
+        %     \label{subfig.4}
+        % \end{subfigure}
+        % \caption[ Figures of Synthetic Data Experiment ]
+        % {{\small Figures of Synthetic Data Experiment}} 
+        \label{fig.2}
+    \end{figure*}
 
-\begin{figure}[h]
-\vspace{.3in}
-\centering
-\includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_sigma.png}
-\vspace{.3in}
-\caption{Accuracy versus randomness($n=100, d=64, c=10$)}
-\label{Fig.3}
-\end{figure}
-
-\begin{figure}[h]
-\vspace{.3in}
-\centering
-\includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_class.png}
-\vspace{.3in}
-\caption{Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)}
-\label{Fig.4}
-\end{figure}
-
-% \subsubsection{Analysis of Synthetic Experiment results}
-% From \ref{Fig.1}, as number of data points increases loss value and parameter matrix error decrease while accuracy increases. 
-% We compare the performance of cover tree loss, softmax cross entropy loss and simloss, it is clear that cover tree loss converges faster than the other two loss functions.
-% Besides, cover tree loss achieves lower loss value and parameter matrix error over number of data points.
-
-% As shown in \ref{Fig.2}, loss value decreases and accuracy increases over dimension. 
-% Similar to \ref{Fig.1}, cover tree loss converges faster and achieve lower loss value.
-% We take the line of parameter matrix error of cover tree loss as a benchmark and draw the difference of parameter matrix error between cover tree loss and the other two loss functions.
-% The middle sub-figure indicates that cover tree loss has lower parameter matrix error with dimension than cross entropy and simloss.
-
-% According to \ref{Fig.3}, if we increase the randomness and fix the other parameters, loss value increases and accuracy decreases.
-% Cover tree loss performs similarly with cross entropy loss and simloss in terms of loss value and accuracy.
-% The middle sub-figure implies that parameter matrix error of cover tree loss decreases even though the randomness increases.
-
-% \ref{Fig.4} indicates that, as number of classes increases, the loss value and parameter matrix error also increases and accuracy certainly decrease.
-% From middle sub-figure, the parameter matrix error of cover tree loss is lower than the other two loss functions.
-% The right sub-figure shows that the accuracy of cover tree loss decreases slower and can keep higher value than the other two loss functions.
+\subsubsection{Analysis of Synthetic Experiment results}
 
@@
 We also get word embeddings from a word2vec model pretrained on Google News \cite{Mikolov2013EfficientEO} of class names and construct cover tree structure and calculate similarity between classes from word embeddings.
-If the class name include more than one word, we take a sum of the embedding of each word.
+Four class names do not yield a word embedding and are therefore eliminated.
 
-To evaluate our cover tree loss, we rely on two metrics: accuracy (Acc.) which focus on correct predictions and similarity accuracy (SA) which focus on the similarity of predicted and target class.
+To evaluate our cover tree loss, we rely on three metrics: accuracy (Acc.) which focus on correct predictions and similarity accuracy (Similarity Acc.) which focus on the similarity of predicted and target class and superclass accuracy (SA).
+Every example in CIFAR-100 dataset has a main class and a superclass.
+Superclass accuracy is the fraction of examples that are correctly put into the corresponding superclass.
 We take ResNet20 model \cite{He2016DeepRL} and SGD optimizer with a learning rate 0.1 and a batch size of 1021. 
@@
 
-\begin{table}[h]
-\small
+\begin{table}[]
 \caption{Validation and test results with early stopping on CIFAR-100 dataset. Best values are written in bold.} \label{cifar100}
 \begin{center}
-\begin{tabular}{@{}lcccc@{}}
+\begin{tabular}{@{}cccc@{}}
 \toprule
-\multicolumn{1}{c}{\multirow{2}{*}{Loss}} & \multicolumn{2}{c}{VALIDATION} & \multicolumn{2}{c}{TEST}       \\ \cmidrule(l){2-5} 
-\multicolumn{1}{c}{}                      & Acc.       & SA            & Acc.      & SA             \\ \cmidrule(r){1-1}
-Cover Tree Loss                           & \textbf{53.44} & \textbf{66.7} & \textbf{53.5} & \textbf{65.89} \\
-Cross Entropy                             & 52.08          & 65.46         & 51.87         & 65.58          \\
-SimLoss                                   & 52.50           & 65.76         & 52.43         & 65.82          \\ \bottomrule
+\multirow{2}{*}{Loss} & \multicolumn{3}{c}{Test}    \\ \cmidrule(l){2-4} 
+                      & Acc. & Similarity Acc. & SA \\ \cmidrule(r){1-1}
+Cover Tree Loss       & \textbf{52.78}     &  \textbf{65.90}               &  \textbf{62.55}  \\
+Cross Entropy         &  51.87    &   65.58              &  62.14  \\
+SimLoss               &    52.43  &    65.82             & 62.34  \\\bottomrule
 \end{tabular}
@@
 ImageNet dataset \cite{Russakovsky2015ImageNetLS} has 1000 classes and many of the classes are similar and related, we consider the internal class structure has a impact on performance of loss function.
-We use class names to get class representations from a pretrained BERT model \cite{Devlin2019BERTPO}.
-We take ResNet50 model \cite{He2016DeepRL} and SGD optimizer with a learning rate 0.01.
-Our metrics are top 1 accuracy and top 5 accuracy.
+We use class names to get class representations from a pretrained FastText model.
+We take ResNet50 model \cite{He2016DeepRL} trained on 1.28 mollion training images and evaluated on the 50k validation images and SGD optimizer with a learning rate 0.01.
+We use top1 accuracy and top5 accuracy to evaluate our loss functions.
 
-\begin{table}[h]
-\small
-\caption{Validation and test results on ImageNet dataset. Best values are written in bold.} \label{imagenet}
+\begin{table}[]
+\caption{Validation results on ImageNet dataset. Best values are written in bold.} \label{imagenet}
 \begin{center}
-\begin{tabular}{@{}lll@{}}
+\begin{tabular}{@{}ccc@{}}
 \toprule
-\multicolumn{1}{c}{\multirow{2}{*}{Loss}} & \multicolumn{2}{c}{VALIDATION} \\ \cmidrule(l){2-3} 
-\multicolumn{1}{c}{}                      & Top1 Acc.      & Top5 Acc.     \\ \cmidrule(r){1-1}
-Cover Tree Loss                           &                &               \\
-Cross Entropy                             &                &               \\
-SimLoss                                   &                &               \\ \bottomrule
+\multirow{2}{*}{Loss} & \multicolumn{2}{c}{Validation} \\ \cmidrule(l){2-3} 
+                      & Top1 Acc.      & Top5 Acc.     \\ \cmidrule(r){1-1}
+Cover Tree Loss       & \textbf{76.52} & \textbf{92.92} \\
+Cross Entropy         & 75.30          & 92.36         \\
+SimLoss               & 76.24          & 92.83         \\ \bottomrule
 \end{tabular}
@@
 We trained the multilingual BERT model on tweets to predict which emoji corresponds to a piece of text is best for measuring the emotional content in the text. 
-Our 1661 target emojis are defined by emo2vec \cite{Eisner2016emoji2vecLE}.
+Our 1660 target emojis are defined by emo2vec \cite{Eisner2016emoji2vecLE}.
 
@@
 We take the multilingual BERT model \cite{Feng2020LanguageagnosticBS} pretrained on data from 109 distinct languages which achieves state-of-the-art performance on a wide variety of natural language tasks.
-We get the embeddings of 1661 target emojis defined by emo2vec and construct a cover tree structure from these emojis. 
+We get the embeddings of 1660 target emojis defined by emo2vec and construct a cover tree structure from these emojis. 
 In this cover tree structure, every leaf node represents each real target emoji and we replace all parent nodes with pseudo labels. 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{plainnat}
 \bibliography{paper}
+% \begin{abstract}
+%   The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
+%   both left and right-hand margins. Use 10~point type, with a vertical
+%   spacing of 11~points. The \textbf{Abstract} heading must be centered,
+%   bold, and in point size 12. Two line spaces precede the
+%   Abstract. The Abstract must be limited to one paragraph.
+% \end{abstract}
+
+% \section{GENERAL FORMATTING INSTRUCTIONS}
+
+% The camera-ready versions of the accepted papers are 8 pages,
+% plus any additional pages needed for references.
+
+% Papers are in 2 columns with the overall line width of 6.75~inches (41~picas).
+% Each column is 3.25~inches wide (19.5~picas).  The space
+% between the columns is .25~inches wide (1.5~picas).  The left margin is 0.88~inches (5.28~picas).
+% Use 10~point type with a vertical spacing of
+% 11~points. Please use US Letter size paper instead of A4.
+
+% Paper title is 16~point, caps/lc, bold, centered between 2~horizontal rules.
+% Top rule is 4~points thick and bottom rule is 1~point thick.
+% Allow 1/4~inch space above and below title to rules.
+
+% Author descriptions are center-justified, initial caps.  The lead
+% author is to be listed first (left-most), and the Co-authors are set
+% to follow.  If up to three authors, use a single row of author
+% descriptions, each one center-justified, and all set side by side;
+% with more authors or unusually long names or institutions, use more
+% rows.
+
+% Use one-half line space between paragraphs, with no indent.
+
+% \section{FIRST LEVEL HEADINGS}
+
+% First level headings are all caps, flush left, bold, and in point size
+% 12. Use one line space before the first level heading and one-half line space
+% after the first level heading.
+
+% \subsection{Second Level Heading}
+
+% Second level headings are initial caps, flush left, bold, and in point
+% size 10. Use one line space before the second level heading and one-half line
+% space after the second level heading.
+
+% \subsubsection{Third Level Heading}
+
+% Third level headings are flush left, initial caps, bold, and in point
+% size 10. Use one line space before the third level heading and one-half line
+% space after the third level heading.
+
+% \paragraph{Fourth Level Heading}
+
+% Fourth level headings must be flush left, initial caps, bold, and
+% Roman type.  Use one line space before the fourth level heading, and
+% place the section text immediately after the heading with no line
+% break, but an 11 point horizontal space.
+
+% %%%
+% \subsection{Citations, Figure, References}
+
+% \subsubsection{Citations in Text}
+
+% Citations within the text should include the author's last name and
+% year, e.g., (Cheesman, 1985). 
+% %Apart from including the author's last name and year, citations can follow any style, as long as the style is consistent throughout the paper.  
+% Be sure that the sentence reads
+% correctly if the citation is deleted: e.g., instead of ``As described
+% by (Cheesman, 1985), we first frobulate the widgets,'' write ``As
+% described by Cheesman (1985), we first frobulate the widgets.''
+
+% The references listed at the end of the paper can follow any style as long as it is used consistently.
+
+% %Be sure to avoid
+% %accidentally disclosing author identities through citations.
+
+% \subsubsection{Footnotes}
+
+% Indicate footnotes with a number\footnote{Sample of the first
+%   footnote.} in the text. Use 8 point type for footnotes. Place the
+% footnotes at the bottom of the column in which their markers appear,
+% continuing to the next column if required. Precede the footnote
+% section of a column with a 0.5 point horizontal rule 1~inch (6~picas)
+% long.\footnote{Sample of the second footnote.}
+
+% \subsubsection{Figures}
+
+% All artwork must be centered, neat, clean, and legible.  All lines
+% should be very dark for purposes of reproduction, and art work should
+% not be hand-drawn.  Figures may appear at the top of a column, at the
+% top of a page spanning multiple columns, inline within a column, or
+% with text wrapped around them, but the figure number and caption
+% always appear immediately below the figure.  Leave 2 line spaces
+% between the figure and the caption. The figure caption is initial caps
+% and each figure should be numbered consecutively.
+
+% Make sure that the figure caption does not get separated from the
+% figure. Leave extra white space at the bottom of the page rather than
+% splitting the figure and figure caption.
+% \begin{figure}[h]
+% \vspace{.3in}
+% \centerline{\fbox{This figure intentionally left non-blank}}
+% \vspace{.3in}
+% \caption{Sample Figure Caption}
+% \end{figure}
+
+% \subsubsection{Tables}
+
+% All tables must be centered, neat, clean, and legible. Do not use hand-drawn tables.
+% Table number and title always appear above the table.
+% See Table~\ref{sample-table}.
+
+% Use one line space before the table title, one line space after the table title,
+% and one line space after the table. The table title must be
+% initial caps and each table numbered consecutively.
+
+% \begin{table}[h]
+% \caption{Sample Table Title} \label{sample-table}
+% \begin{center}
+% \begin{tabular}{ll}
+% \textbf{PART}  &\textbf{DESCRIPTION} \\
+% \hline \\
+% Dendrite         &Input terminal \\
+% Axon             &Output terminal \\
+% Soma             &Cell body (contains cell nucleus) \\
+% \end{tabular}
+% \end{center}
+% \end{table}
+
+% \section{SUPPLEMENTARY MATERIAL}
+
+% If you need to include additional appendices during submission, you can include them in the supplementary material file.
+% You can submit a single file of additional supplementary material which may be either a pdf file (such as proof details) or a zip file for other formats/more files (such as code or videos). 
+% Note that reviewers are under no obligation to examine your supplementary material. 
+% If you have only one supplementary pdf file, please upload it as is; otherwise gather everything to the single zip file.
+
+% You must use \texttt{aistats2022.sty} as a style file for your supplementary pdf file and follow the same formatting instructions as in the main paper. 
+% The only difference is that it must be in a \emph{single-column} format.
+% You can use \texttt{supplement.tex} in our starter pack as a starting point.
+% Alternatively, you may append the supplementary content to the main paper and split the final PDF into two separate files.
+
+% \section{SUBMISSION INSTRUCTIONS}
+
+% To submit your paper to AISTATS 2022, please follow these instructions.
+
+% \begin{enumerate}
+%     \item Download \texttt{aistats2022.sty}, \texttt{fancyhdr.sty}, and \texttt{sample\_paper.tex} provided in our starter pack. 
+%     Please, do not modify the style files as this might result in a formatting violation.
+
+%     \item Use \texttt{sample\_paper.tex} as a starting point.
+%     \item Begin your document with
+%     \begin{flushleft}
+%     \texttt{\textbackslash documentclass[twoside]\{article\}}\\
+%     \texttt{\textbackslash usepackage\{aistats2022\}}
+%     \end{flushleft}
+%     The \texttt{twoside} option for the class article allows the
+%     package \texttt{fancyhdr.sty} to include headings for even and odd
+%     numbered pages.
+%     \item When you are ready to submit the manuscript, compile the latex file to obtain the pdf file.
+%     \item Check that the content of your submission, \emph{excluding} references, is limited to \textbf{8 pages}. The number of pages containing references alone is not limited.
+%     \item Upload the PDF file along with other supplementary material files to the CMT website.
+% \end{enumerate}
+
+% \subsection{Camera-ready Papers}
+
+% %For the camera-ready paper, if you are using \LaTeX, please make sure
+% %that you follow these instructions.  
+% % (If you are not using \LaTeX,
+% %please make sure to achieve the same effect using your chosen
+% %typesetting package.)
+
+% If your papers are accepted, you will need to submit the camera-ready version. Please make sure that you follow these instructions:
+% \begin{enumerate}
+%     %\item Download \texttt{fancyhdr.sty} -- the
+%     %\texttt{aistats2022.sty} file will make use of it.
+%     \item Change the beginning of your document to
+%     \begin{flushleft}
+%     \texttt{\textbackslash documentclass[twoside]\{article\}}\\
+%     \texttt{\textbackslash usepackage[accepted]\{aistats2022\}}
+%     \end{flushleft}
+%     The option \texttt{accepted} for the package
+%     \texttt{aistats2022.sty} will write a copyright notice at the end of
+%     the first column of the first page. This option will also print
+%     headings for the paper.  For the \emph{even} pages, the title of
+%     the paper will be used as heading and for \emph{odd} pages the
+%     author names will be used as heading.  If the title of the paper
+%     is too long or the number of authors is too large, the style will
+%     print a warning message as heading. If this happens additional
+%     commands can be used to place as headings shorter versions of the
+%     title and the author names. This is explained in the next point.
+%     \item  If you get warning messages as described above, then
+%     immediately after $\texttt{\textbackslash
+%     begin\{document\}}$, write
+%     \begin{flushleft}
+%     \texttt{\textbackslash runningtitle\{Provide here an alternative
+%     shorter version of the title of your paper\}}\\
+%     \texttt{\textbackslash runningauthor\{Provide here the surnames of
+%     the authors of your paper, all separated by commas\}}
+%     \end{flushleft}
+%     Note that the text that appears as argument in \texttt{\textbackslash
+%       runningtitle} will be printed as a heading in the \emph{even}
+%     pages. The text that appears as argument in \texttt{\textbackslash
+%       runningauthor} will be printed as a heading in the \emph{odd}
+%     pages.  If even the author surnames do not fit, it is acceptable
+%     to give a subset of author names followed by ``et al.''
+
+%     %\item Use the file sample\_paper.tex as an example.
+
+%     \item The camera-ready versions of the accepted papers are 8
+%       pages, plus any additional pages needed for references.
+
+%     \item If you need to include additional appendices,
+%       you can include them in the supplementary
+%       material file.
+
+%     \item Please, do not change the layout given by the above
+%       instructions and by the style file.
+
+% \end{enumerate}
+
+% \subsubsection*{Acknowledgements}
+% All acknowledgments go at the end of the paper, including thanks to reviewers who gave useful comments, to colleagues who contributed to the ideas, and to funding agencies and corporate sponsors that provided financial support.
+% To preserve the anonymity, please include acknowledgments \emph{only} in the camera-ready papers.
+
+% \subsubsection*{References}
+
+% References follow the acknowledgements.  Use an unnumbered third level
+% heading for the references section.  Please use the same font
+% size for references as for the body of the paper---remember that
+% references do not count against your page length total.
+
+% \begin{thebibliography}{}
+% \setlength{\itemindent}{-\leftmargin}
+% \makeatletter\renewcommand{\@biblabel}[1]{}\makeatother
+% \bibitem{} J.~Alspector, B.~Gupta, and R.~B.~Allen (1989).
+%     \newblock Performance of a stochastic learning microchip.
+%     \newblock In D. S. Touretzky (ed.),
+%     \textit{Advances in Neural Information Processing Systems 1}, 748--760.
+%     San Mateo, Calif.: Morgan Kaufmann.
+
+% \bibitem{} F.~Rosenblatt (1962).
+%     \newblock \textit{Principles of Neurodynamics.}
+%     \newblock Washington, D.C.: Spartan Books.
+
+% \bibitem{} G.~Tesauro (1989).
+%     \newblock Neurogammon wins computer Olympiad.
+%     \newblock \textit{Neural Computation} \textbf{1}(3):321--323.
+% \end{thebibliography}
+
 \end{document}

### 2021-10-06 TreeLoss/loss.py

@@ -5,7 +5,7 @@ import numpy as np
 import torch.nn.functional as F
 from .cover_tree import CoverTree
 from scipy.spatial.distance import cosine
-from .utilities import path
+from .utilities import path, _print, get_brothernode
 
 class SimLoss(torch.nn.Module):
     def __init__(self,
@@ -42,13 +42,14 @@ class CoverTreeLoss(torch.nn.Module):
         self.new2index = new2index
 
     @staticmethod
-    def tree_structure(c, m):
+    def tree_structure(c, m, base):
         '''
         m: embeddings of existed classes
         This function constructs cover tree structure.
         '''
         distance = cosine
-        tree = CoverTree(m, distance, leafsize=1)
+        tree = CoverTree(m, distance, leafsize=1, base=base)
+        # _print(tree)
         new_index = path(tree)
 
         # new label
@@ -69,7 +70,7 @@ class CoverTreeLoss(torch.nn.Module):
         new2index = dict()
         for i in range(len(new_index)):
             new2index[new_index[i][len(new_index[i])-1]] = new_index[i]
-        return new2index, length
+        return new2index, length, tree
 
     def forward(self,
                 weights: torch.Tensor,
@@ -97,3 +98,67 @@ class CoverTreeLoss(torch.nn.Module):
         
         loss = self.criterion(logits, y)
         return loss, logits, added_weights
+
+class HSM(torch.nn.Module):
+    def __init__(self, c, d, new2index, index2brother, length, epsilon: float = 1e-8) -> None:
+        '''
+        c: number of existed classes
+        length: number of existed classes and pseudo classes
+        d: dimension of parameter matrix W(c,d)
+        new2index: a dictionary which we can get a a path of a existed class
+        '''
+        super().__init__()
+        self.c = c
+        self.linear = nn.Linear(d, c, bias=False)
+        self.criterion = nn.CrossEntropyLoss()
+        self.new2index = new2index
+        self.epsilon = epsilon
+        self.softmax = nn.Softmax(dim=-1)
+        self.length = length
+        self.index2brother = index2brother
+
+    @staticmethod
+    def tree_structure(c, m):
+        '''
+        m: embeddings of existed classes
+        This function constructs cover tree structure.
+        '''
+
+        distance = cosine
+        tree = CoverTree(m, distance, leafsize=1)
+        _print(tree)
+        new_index_ = path(tree)
[…]

### 2021-10-06 TreeLoss/utilities.py

@@ -7,6 +7,8 @@ import os
 import torch
 from sklearn.metrics.pairwise import cosine_similarity
 from .cover_tree import CoverTree
+from transformers import BertModel, BertTokenizer
+from tqdm import tqdm
 import math
 
 def set_logger(name, timestamp):
@@ -27,70 +29,6 @@ def set_seed(seed):
     torch.manual_seed(seed) 
     if torch.cuda.is_available(): 
         torch.cuda.manual_seed_all(seed) 
-
-def gen_data(trainloader, testloader, m):
-    """
-    This function generate data with new labels.
-    New labels are generated by adding a new number which selected uniformly at random from [number].
-    """
-    sim = gen_sim(m)
-    examples = enumerate(trainloader)
-
-    train_data = []
-    train_original = []
-    while True:
-        try:
-            batch_idx, (example_data, example_targets) = next(examples)
-            train_original.append(example_targets)
-            train_data.append(example_data.squeeze(0).numpy())
-        except:
-            break
-    train_dataset = list(zip(train_data, train_original))
-    random.shuffle(train_dataset)
-    train_data, train_original = zip(*train_dataset)
-    train_data = np.array(train_data)
-    train_original = np.array(train_original)
-    train_label = np.copy(train_original)
-    
-    # sampling
-    c, o = m.shape
-    for i in range(o):
-        p = np.nonzero(m[:,i])
-        position = np.where(train_original==i)
-        length = np.sum(train_original==i)
-        t = 0
-        for j in range(p[0].shape[0]):
-            index = position[0][math.ceil(t*length):math.ceil((t+m[p[0][j],i])*length)]
-            train_label[index] = p[0][j]
-            t += m[p[0][j],i]
-
-    instances = enumerate(testloader)
-
-    test_data = []
-    test_original = []
-    while True:
-        try:
-            batch_index, (instances_data, instances_targets) = next(instances)
-            test_original.append(instances_targets)
-            test_data.append(instances_data.squeeze(0).numpy())
-        except:
-            break
-    test_data = np.array(test_data)
-    test_original = np.array(test_original)
-    test_label = np.copy(test_original)
-    
-    for i in range(o):
-        p = np.nonzero(m[:,i])
-        position = np.where(test_original==i)
-        length = np.sum(test_original==i)
-        t = 0
-        for j in range(p[0].shape[0]):
[…]

### 2021-10-06 experiments/synthetic/base_exp.py

@@ -1,0 +1,216 @@
+#!/usr/bin/python3
+
+# this is a temporary hack to allow importing the files in the TreeLoss folder when the library is not yet installed
+import sys
+sys.path.append('../..')
+
+import logging
+import os
+LOGLEVEL = os.environ.get('LOGLEVEL', 'WARNING').upper()
+logging.basicConfig(
+    level=LOGLEVEL,
+    format='%(asctime)s.%(msecs)03d %(levelname)s %(module)s - %(funcName)s: %(message)s',
+    datefmt='%Y-%m-%d %H:%M:%S',
+    )
+
+################################################################################
+# command line arguments
+################################################################################
+logging.info('processing command line arguments')
+import argparse
+parser = argparse.ArgumentParser(description='synthetic data experiment')
+
+parser_data = parser.add_argument_group(
+        title='data generation',
+        description='the variable names for these arguments match exactly the variable names used in the paper'
+        )
+parser_data.add_argument('--exp_num', type=int, default=1)
+parser_data.add_argument('--a', type=int, default=5)
+parser_data.add_argument('--c', type=int, default=100)
+parser_data.add_argument('--n', type=int, default=1000)
+parser_data.add_argument('--d', type=int, default=10)
+parser_data.add_argument('--sigma', type=float, default=1.0)
+parser_data.add_argument('--seed', type=int, default=666)
+parser_data.add_argument('--base', type=float, default=1.1)
+parser_data.add_argument('--batch', type=int, default=1000)
+parser_data.add_argument('--epoch', type=int, default=1)
+
+
+
+parser_model = parser.add_argument_group(
+        title='model hyperparameters',
+        description="it's recommended to always use scientific notation for hyperparameter values since we really care about the order of magnitude",
+        )
+parser_model.add_argument('--lr', type=float, default=1e-4, metavar='LR') 
+parser_model.add_argument('--momentum', type=float, default=0.9)
+parser_model.add_argument('--weight_decay', type=float, default=3e-4)
+parser_model.add_argument('--loss', choices=['tree','xentropy','simloss', 'HSM'], default='xentropy')
[…]

### 2021-10-06 experiments/synthetic/create_figure_1a.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for n in 16 32 64 128 256 512 1024 2048 4096 8192; do
-        python3 run_experiment.py --exp_num=$num --loss=simloss --n=$n --lower_bound=0.9 --experiment=loss_vs_n
+        python3 run_experiment.py --exp_num=$num --loss=HSM --n=$n --experiment=loss_vs_n
     done
 done

### 2021-10-06 experiments/synthetic/create_figure_1b.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for d in 2 4 8 16 32 64 128 256 512 1024; do
-        python3 run_experiment.py --exp_num=$num --loss=simloss --d=$d --lower_bound=0.9 --experiment=loss_vs_d 
+        python3 run_experiment.py --exp_num=$num --loss=HSM --d=$d --experiment=loss_vs_d 
     done
 done

### 2021-10-06 experiments/synthetic/create_figure_1c.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for sigma in 1.0 2.0 3.0 4.0 5.0 6.0 7.0 8.0 9.0 10.0; do
-        python3 run_experiment.py --exp_num=$num --sigma=$sigma --loss=simloss --lower_bound=0.6 --experiment=loss_vs_sigma
+        python3 run_experiment.py --exp_num=$num --sigma=$sigma --loss=HSM --experiment=loss_vs_sigma
     done
 done

### 2021-10-06 experiments/synthetic/create_figure_1d.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for c in 10 20 30 40 50 60 70 80 90 100; do
-        python3 run_experiment.py --exp_num=$num --loss=simloss --c=$c --lower_bound=0.6 --experiment=loss_vs_c
+        python3 run_experiment.py --exp_num=$num --loss=HSM --c=$c --experiment=loss_vs_c
     done
 done

### 2021-10-06 experiments/synthetic/create_figure_1e.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+for num in {1..50};
+do
+    for random in 0.0 0.1 0.2 0.3 0.4 0.5 0.6 0.7 0.8 0.9 1.0; do
+        python3 run_experiment.py --exp_num=$num --random=$random --loss=tree --experiment=loss_vs_structure
+    done
+done

### 2021-10-06 experiments/synthetic/create_figure_base.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+for num in {1..50};
+do
+    for base in 1.1 1.2 1.3 1.4 1.5 1.6 1.7 1.8 1.9 2.0 2.1 2.2 2.3 2.4 2.5 2.6 2.7 2.8 2.9 3.0 4.0 5.0 6.0 7.0; do
+        python3 base_exp.py --exp_num=$num --loss=tree --base=$base
+    done
+done

### 2021-10-06 experiments/synthetic/para_exp.py

@@ -1,0 +1,164 @@
+#!/usr/bin/python3
+
+# this is a temporary hack to allow importing the files in the TreeLoss folder when the library is not yet installed
+import sys
+sys.path.append('../..')
+
+import logging
+import os
+from collections import defaultdict
+################################################################################
+# command line arguments
+################################################################################
+logging.info('processing command line arguments')
+import argparse
+parser = argparse.ArgumentParser(description='synthetic data experiment')
+
+parser_data = parser.add_argument_group(
+        title='data generation',
+        description='the variable names for these arguments match exactly the variable names used in the paper'
+        )
+parser_data.add_argument('--exp_num', type=int, default=1)
+parser_data.add_argument('--a', type=int, default=5)
+parser_data.add_argument('--c', type=int, default=1000)
+parser_data.add_argument('--n', type=int, default=10000)
+parser_data.add_argument('--d', type=int, default=1000)
+parser_data.add_argument('--sigma', type=float, default=1.0)
+parser_data.add_argument('--random', type=float, default=0.0)
+parser_data.add_argument('--seed', type=int, default=666)
+parser_data.add_argument('--batch', type=int, default=1000)
+parser_data.add_argument('--epoch', type=int, default=10)
+
+parser_model = parser.add_argument_group(
+        title='model hyperparameters',
+        description="it's recommended to always use scientific notation for hyperparameter values since we really care about the order of magnitude",
+        )
+parser_model.add_argument('--lr', type=float, default=1e-4, metavar='LR') 
+parser_model.add_argument('--momentum', type=float, default=0.9)
+parser_model.add_argument('--weight_decay', type=float, default=3e-4)
+parser_model.add_argument('--loss', choices=['tree','xentropy','simloss', 'HSM'], default='xentropy')
+parser.add_argument('--lower_bound', type=float, default=0.5)
+
+parser_debug = parser.add_argument_group(title='debug')
+parser_model.add_argument('--logdir', default='log')
+args = parser.parse_args()
+
+# load imports;
+# we do this after parsing the command line arguments because it takes a long time,
[…]

### 2021-10-06 experiments/synthetic/plot_figure.py

@@ -15,6 +15,7 @@ f_simloss_3 = open(f'{args.experiment}_simloss_original_0.7.txt', 'r')
 f_simloss_4 = open(f'{args.experiment}_simloss_original_0.8.txt', 'r')
 f_simloss_5 = open(f'{args.experiment}_simloss_original_0.9.txt', 'r')
 f_simloss = [f_simloss_1, f_simloss_2, f_simloss_3, f_simloss_4, f_simloss_5]
+f_HSM = open(f'{args.experiment}_HSM_original.txt', 'r')
 
 loss_tree_all = []
 W_err_tree_all = []
@@ -139,6 +140,44 @@ for i in f_simloss:
     W_err_simloss.append(W_err_simloss_)
     accuracy_simloss.append(accuracy_simloss_)
 
+loss_HSM_all = []
+W_err_HSM_all = []
+accuracy_HSM_all = []
+for line in f_HSM:
+    line = line.strip()
+    if len(line)>1:
+
+        loss_start = line.find('Loss:')
+        loss_end  = loss_start + len('Loss:')
+
+        W_err_start = line.find('W_err:')
+        W_err_end = W_err_start + len('W_err:')
+
+        accuracy_start = line.find('Accuracy:')
+        accuracy_end = accuracy_start + len('Accuracy:')
+
+        loss_ = float(line[loss_end:W_err_start].strip())
+        W_err_ = float(line[W_err_end:accuracy_start].strip())
+        accuracy_ = float(float(line[accuracy_end:].strip()))
+
+        loss_HSM_all.append(loss_)
+        W_err_HSM_all.append(W_err_)
+        accuracy_HSM_all.append(accuracy_)
+loss_HSM = []
+W_err_HSM = []
+accuracy_HSM = []
+for num in range(10):
+    loss_mid = []
+    W_err_mid = []
+    accuracy_mid = []
+    for i in range(50):
+        loss_mid.append(loss_HSM_all[num+i*10])
+        W_err_mid.append(W_err_HSM_all[num+i*10])
+        accuracy_mid.append(accuracy_HSM_all[num+i*10])
+    loss_HSM.append(np.mean(loss_mid))
+    W_err_HSM.append(np.mean(W_err_mid))
+    accuracy_HSM.append(np.mean(accuracy_mid))
[…]

### 2021-10-06 experiments/synthetic/run_experiment.py

@@ -32,11 +32,13 @@ parser_data = parser.add_argument_group(
         )
 parser_data.add_argument('--exp_num', type=int, default=1)
 parser_data.add_argument('--a', type=int, default=5)
-parser_data.add_argument('--c', type=int, default=10)
-parser_data.add_argument('--n', type=int, default=100)
+parser_data.add_argument('--c', type=int, default=100)
+parser_data.add_argument('--n', type=int, default=1000)
 parser_data.add_argument('--d', type=int, default=64)
 parser_data.add_argument('--sigma', type=float, default=1.0)
+parser_data.add_argument('--random', type=float, default=0.0)
 parser_data.add_argument('--seed', type=int, default=666)
+
 
 parser_model = parser.add_argument_group(
         title='model hyperparameters',
@@ -45,12 +47,12 @@ parser_model = parser.add_argument_group(
 parser_model.add_argument('--lr', type=float, default=1e-4, metavar='LR') 
 parser_model.add_argument('--momentum', type=float, default=0.9)
 parser_model.add_argument('--weight_decay', type=float, default=3e-4)
-parser_model.add_argument('--loss', choices=['tree','xentropy','simloss'], default='xentropy')
+parser_model.add_argument('--loss', choices=['tree','xentropy','simloss', 'HSM'], default='xentropy')
 parser.add_argument('--lower_bound', type=float, default=0.5)
 
 parser_debug = parser.add_argument_group(title='debug')
 parser_model.add_argument('--logdir', default='log')
-parser_model.add_argument('--experiment', choices=['loss_vs_n','loss_vs_d', 'loss_vs_sigma', 'loss_vs_c'], required=True)
+parser_model.add_argument('--experiment', choices=['loss_vs_n','loss_vs_d', 'loss_vs_sigma', 'loss_vs_c', 'loss_vs_structure'], required=True)
 args = parser.parse_args()
 
 # load imports;
@@ -67,7 +69,7 @@ import torch.optim as optim
 import torch.nn.functional as F
 from torch.utils.tensorboard import SummaryWriter
 from TreeLoss.utilities import set_seed, gen_sim
-from TreeLoss.loss import CoverTreeLoss, SimLoss
+from TreeLoss.loss import CoverTreeLoss, SimLoss, HSM
 
 # set the seed
 logging.debug('set_seed('+str(args.seed)+')')
[…]

### 2021-10-06 experiments/synthetic/tree_figure.py

@@ -1,0 +1,343 @@
+import argparse
+parser = argparse.ArgumentParser(description='create tree figures')
+parser.add_argument('--experiment', choices=['loss_vs_structure', 'base_experiment', 'para_norm'], required=True)
+# parser.add_argument('--loss', choices=['xentropy', 'tree', 'simloss', 'HSM'], required=True)
+args = parser.parse_args()
+
+import matplotlib.pyplot as plt
+import numpy as np
+
+f_tree = open(f'{args.experiment}_tree_loss_1.txt', 'r')
+f_xentropy = open(f'{args.experiment}_xentropy_loss_1.txt', 'r')
+# f_simloss = open(f'{args.experiment}_simloss.txt', 'r')
+# f_HSM = open(f'{args.experiment}_HSM.txt', 'r')
+
+if args.experiment == 'loss_vs_structure':
+    loss_tree_all = []
+    W_err_tree_all = []
+    accuracy_tree_all = []
+    for line in f_tree:
+        line = line.strip()
+        if len(line)>1:
+
+            loss_start = line.find('Loss:')
+            loss_end  = loss_start + len('Loss:')
+
+            W_err_start = line.find('W_err:')
+            W_err_end = W_err_start + len('W_err:')
+
+            accuracy_start = line.find('Accuracy:')
+            accuracy_end = accuracy_start + len('Accuracy:')
+
+            loss = float(line[loss_end:W_err_start].strip())
+            W_err = float(line[W_err_end:accuracy_start].strip())
+            accuracy = float(float(line[accuracy_end:].strip()))
+
+            loss_tree_all.append(loss)
+            W_err_tree_all.append(W_err)
+            accuracy_tree_all.append(accuracy)
+    loss_tree = []
+    W_err_tree = []
+    accuracy_tree = []
+    for num in range(11):
+        loss_mid = []
+        W_err_mid = []
+        accuracy_mid = []
+        for i in range(50):
+            loss_mid.append(loss_tree_all[num+i*11])
+            W_err_mid.append(W_err_tree_all[num+i*11])
+            accuracy_mid.append(accuracy_tree_all[num+i*11])
+        loss_tree.append(np.mean(loss_mid))
+        W_err_tree.append(np.mean(W_err_mid))
+        accuracy_tree.append(np.mean(accuracy_mid))
+
+    loss_xentropy_all = []
+    W_err_xentropy_all = []
+    accuracy_xentropy_all = []
+    for line in f_xentropy:
[…]

### 2021-10-06 paper/paper.tex
update

@@
             \centering
-            \includegraphics[width=\textwidth]{fig/new_img/loss_vs_structure.png}
-            % \caption[Accuracy versus number of data points($d=64, \sigma=1.0, c=10$)]%
-            {{\small Accuracy versus cover tree structure($n=1000, d=64, \sigma=1.0, c=100$)}}   
+            \includegraphics[width=\textwidth]{fig/new_img/accuracy_vs_base.png}
+            {{\small Accuracy versus base of cover tree($n=1000, d=10, \sigma=1.0, c=100$)}}
             \label{subfig.1}
@@
             \centering 
-            \includegraphics[width=\textwidth]{fig/new_img/accuracy_vs_base.png}
-            % \caption[Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, c=10$)]%
-            {{\small Accuracy versus base of cover tree($n=1000, d=10, \sigma=1.0, c=100$)}}    
+            \includegraphics[width=\textwidth]{fig/new_img/height_vs_base.png}
+            {{\small Height versus base of cover tree($n=1000, d=10, \sigma=1.0, c=100$)}}   
             \label{subfig.2}
@@
             \centering 
-            \includegraphics[width=\textwidth]{fig/new_img/height_vs_base.png}
+            \includegraphics[width=\textwidth]{fig/new_img/loss_vs_structure.png}
             % \caption[Accuracy versus randomness($n=100, d=64, c=10$)]%
-            {{\small Height versus base of cover tree($n=1000, d=10, \sigma=1.0, c=100$)}}  
+            {{\small Accuracy versus cover tree structure($n=1000, d=64, \sigma=1.0, c=100$)}}  
             \label{subfig.3}

### 2021-10-07 paper/paper.tex
abstract

@@
 
-\aistatstitle{The Cover Tree Loss}
+\aistatstitle{The Tree Loss: Improving Generalization with Many Classes}
 
@@
 \begin{abstract}
-Softmax Cross Entropy loss function treats every class equally while classes often have an internal structure. 
-We introduce cover tree loss function which takes advantage of this internal class structure.
-The cover tree loss works by reparameterizing the weight matrix for the softmax cross entropy loss.
-Compare to softmax cross entropy which has generalization error $O(\sqrt{c/n})$, the generalization error of cover tree loss is $O(\sqrt{1/n})$ which is independent of the number of classes. 
-We provide the theoretical justification and conduct extensive experiments on fully synthetic data and real world data. 
-For real world data, we take CIFAR100 dataset, IMAGENET dataset and TWITTER dataset.
-The cover tree loss outperforms than softmax cross entropy loss function on metrics.
+    %Multiclass logistic regression has generalization error $O(\sqrt{c/n})$, where $c$ is the number of classes and $n$ the number of data points.
+
+    Multiclass classification problems often have many semantically similar classes.
+    For example, 90 of ImageNet's 1000 classes are for different breeds of dog.
+    We should expect that these semantically similar classes will have similar parameter vectors,
+    but the standard cross entropy loss does not enforce this constraint.
+    %These classes are semantically similar to each other,
+    %and so we expect their learned parameter vectors to also be similar.
+    %Unfortunately, the standard cross entropy loss function does not enforce this constraint.
+    %It has generalization error $O(\sqrt{c/n})$, where $c$ is the number of classes and $n$ the number of data points.
+
+    We introduce the tree loss as a drop-in replacement for the cross entropy loss.
+    The tree loss re-parameterizes the parameter matrix in order to guarantee that semantically similar classes will have similar parameter vectors.
+    Using simple properties of stochastic gradient descent,
+    we show that the tree loss's generalization error is asymptotically better than the cross entropy loss's.
+    We then validate these theoretical results on synthetic data, image data (CIFAR100, ImageNet), and text data (Twitter).
+
+    %Whereas The standard softmax cross entropy loss function has generalization error $O(\sqrt{c/n})$,
+    %where $c$ is the number of classes and $n$ the number of data points.
+
+%Softmax Cross Entropy loss function treats every class equally while classes often have an internal structure. 
+%We introduce cover tree loss function which takes advantage of this internal class structure.
+%The cover tree loss works by reparameterizing the weight matrix for the softmax cross entropy loss.
+%Compare to softmax cross entropy which has generalization error $O(\sqrt{c/n})$, the generalization error of cover tree loss is $O(\sqrt{1/n})$ which is independent of the number of classes. 
+%We provide the theoretical justification and conduct extensive experiments on fully synthetic data and real world data. 
+%For real world data, we take CIFAR100 dataset, IMAGENET dataset and TWITTER dataset.
+%The cover tree loss outperforms than softmax cross entropy loss function on metrics.
 \end{abstract}
@@
 \section{Introduction}
+
 When people do a multi-class classification task, the standard loss function is softmax cross entropy.

### 2021-10-11 paper/paper.tex
update introduction/related work

@@
 
-In this paper, we introduce cover tree loss which works by reparameterizing the weight matrix for the softmax cross entropy loss. 
-The reparameterization is defined by a cover tree structure that constructed by similarity between all classes. 
-Every class is represented by a leaf node in the cover tree and all other internal nodes represent pseudo-classes. 
-Our cover tree loss is based on softmax cross entropy and easily implement.
-The idea of cover tree is that we use tree structure to reduce the bound of the size of the parameter space and then the generalization error of cover tree loss is $O(\sqrt{1/n})$ which is independent of $c$.
+In this paper, we introduce the tree loss which take advantage of the internal structure bewtween classes.
+The idea of the tree loss is that we use tree structure to reduce the bound of the size of the parameter space and then the generalization error of the tree loss is $O(\sqrt{1/n})$ which is independent of $c$.
+In the tree loss, we take a tree structure which defined by similarity between classes to re-parameterize the weight matrix for the softmax cross entropy loss.
+We incorporate class similarities with loss function to make the model learn more information about classes.
+It can benefit the tasks on unbalanced datasets.
+Take a emoji prediction task as an example, people often use emojis in tweets.
+However, some emojis are popular and some emojis are rarely used.
+This leads to an unbalanced tweets data and there is not enough training data for unpopular emojis.
+The tree loss can learn more information and work well for unbalanced data.
 
@@
 
-\section{Alternatives to the softmax cross entropy}
-
 There are many other loss functions that have been proposed for multilabel classification.
-In this section, we review these alternatives before presenting our proposed cover tree loss.
+In this section, we review these alternatives before presenting our proposed the tree loss.
 
@@
 
-The cover tree loss is superficially related to the hierarchical softmax (HSM) because both losses are defined based on tree structures.
+The tree loss is superficially related to the hierarchical softmax (HSM) because both losses are defined based on tree structures.
 \cite{morin2005hierarchical} introduced the HSM to speed up the computational time of neural network training,
-but the cover tree loss is used to improve sample efficiency rather than computational efficiency.
+but the tree loss is used to improve sample efficiency rather than computational efficiency.
 \cite{mikolov2013distributed} introduce the word2vec model and experiment with using both the hierarchical softmax and cross entropy with negative sampling.
 They conclude that negative sampling has the best performance both computationally and statistically.
-Since the cover tree loss is a simple extension of the cross entropy loss,
+Since the tree loss is a simple extension of the cross entropy loss,
 negative sampling can be used to speed up the cross entropy loss as well.
@@
 They do not provide any theoretical justification for why their technique should improve sample efficiency,
-but their technique is computationally very similar to the cover tree loss,
+but their technique is computationally very similar to the tree loss,
 and so our technique may be able to provide the first theoretical justification for their work.
@@
 
+The hierarchical softmax loss aims to improve computation efficiency. 
 \cite{Peng2017IncrementallyLT} introduce a training method incrementally train the hierarchical softmax function for neural network language models.
-To be specific, the incremental training split the cost function to model old and update corpora separately and factorize the objective function for the hierarchical softmax. 
-They also provide a new stochastic gradient based method to update all the word vectors and parameters and their theoretical analysis shows the mean square error of the parameter vectors can be bounded by a function of the number of changed words related to the parameter node which is similar to our idea of cover tree loss.
-Their experimental results show the incremental training can save a lot of time.
+They also provide a new stochastic gradient based method to update all the word vectors and their experimental results show the incremental training can save a lot of time.
+\cite{Jiang2017ExplorationOT} explore the tree-based hierarchical softmax method and reform its architecture, making it compatible with modern GPUs.
+\cite{Yang2017OptimizeHS} gives a theoretic analysis on how should organize the hierarchical tree by treating the tree structure as a parameter of the training objective function.
+They propose SemHuff, a new tree constructing scheme based on adjusting the Huffman tree with word similarity knowledge.
+Their experiments results also show that word embeddings trained with optimized hierarchical tree can give better results in various tasks.
 
@@
 Their experimental results show that normal softmax and hierarchical softmax underperforms on datasets with large number of labels.
-That is also one of our motivations of cover tree loss function. 
-Compared to classic cross entropy loss function, cover tree loss function performs better on datasets with large number of labels.
-
+That is also one of our motivations of the tree loss function. 
+Compared to classic cross entropy loss function, the tree loss function performs better on datasets with large number of labels.
 Extreme multi-label classification is difficult, but organizing labels as a tree can handle this problem.
-Hierarchical softmax approach commonly used for multi-class problems.
-\cite{Wydmuch2018ANG} investigate probabilistic label trees that have been recently devised for tackling extreme multi-label classification and show that probabilistic label trees are a no-regret multi-label generation of hierarchical softmax when precision $@k$ is used as a model evaluation metric.
-They also show that their implementation of probabilistic label trees obtains significantly better results than hierarchical softmax with the pick-one-label heuristic.
-
-Neural networks are widely used for computational linguistics.
-These neural models leverage knowledge from massive corpora but they are extremely slow.
-\cite{Jiang2017ExplorationOT} explore the tree-based hierarchical softmax method and reform its architecture, making it compatible
-with modern GPUs and introducing a compact tree-based loss function.
-Their tree-based loss function is the negative log-likelihood of the joint product of the probability of the route taken from the root to the corresponding leaf node. 
-It is different from our cover tree loss function which parameterize the weight vectors.
-
-\cite{Yang2017OptimizeHS} gives a theoretic analysis on how should organize the hierarchical tree by treating the tree structure as a parameter of the training objective function.
-They propose SemHuff, a new tree constructing scheme based on adjusting the Huffman tree with word similarity knowledge.
-Their experiments results also show that word embeddings trained with optimized hierarchical tree can give better results in various tasks.
-
+
+% \cite{Peng2017IncrementallyLT} introduce a training method incrementally train the hierarchical softmax function for neural network language models. 
+% To be specific, the incremental training split the cost function to model old and update corpora separately and factorize the objective function for the hierarchical softmax. 
+% They also provide a new stochastic gradient based method to update all the word vectors and parameters and their theoretical analysis shows the mean square error of the parameter vectors can be bounded by a function of the number of changed words related to the parameter node which is similar to our idea of cover tree loss.
+% Their experimental results show the incremental training can save a lot of time.
+
+% \cite{Mohammed2018EffectivenessOH} compare the performance of normal softmax and hierarchical softmax in large scale classification tasks. 
+% Normal softmax is computationally expensive for large scale datasets with large number of possible outputs.
+% Their experimental results show that normal softmax and hierarchical softmax underperforms on datasets with large number of labels.
+% That is also one of our motivations of cover tree loss function. 
+% Compared to classic cross entropy loss function, cover tree loss function performs better on datasets with large number of labels.
+
+% Extreme multi-label classification is difficult, but organizing labels as a tree can handle this problem. 
+% Hierarchical softmax approach commonly used for multi-class problems.
+% \cite{Wydmuch2018ANG} investigate probabilistic label trees that have been recently devised for tackling extreme multi-label classification and show that probabilistic label trees are a no-regret multi-label generation of hierarchical softmax when precision $@k$ is used as a model evaluation metric.
+% They also show that their implementation of probabilistic label trees obtains significantly better results than hierarchical softmax with the pick-one-label heuristic.
+
+% Neural networks are widely used for computational linguistics.
+% These neural models leverage knowledge from massive corpora but they are extremely slow.
+% \cite{Jiang2017ExplorationOT} explore the tree-based hierarchical softmax method and reform its architecture, making it compatible
+% with modern GPUs and introducing a compact tree-based loss function.
+% Their tree-based loss function is the negative log-likelihood of the joint product of the probability of the route taken from the root to the corresponding leaf node. 
+% It is different from our cover tree loss function which parameterize the weight vectors.
+
+% \cite{Yang2017OptimizeHS} gives a theoretic analysis on how should organize the hierarchical tree by treating the tree structure as a parameter of the training objective function.
+% They propose SemHuff, a new tree constructing scheme based on adjusting the Huffman tree with word similarity knowledge.
+% Their experiments results also show that word embeddings trained with optimized hierarchical tree can give better results in various tasks.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Simloss \cite{Kobs2020SimLossCS} is similarity based loss function which incorporates class similarities to support the training of neural network classifiers.
+SimLoss \cite{Kobs2020SimLossCS} is similarity based loss function which incorporates class similarities to support the training of neural network classifiers.
 Cross entropy loss assumes only one class is correct and punishes every misclassification, while Simloss indicates classes have similarities and classifying a target as a similar class is better.
@@
 It would allow the classifier to make less severe mistakes as it learns to predict similar classes.
+However, SimLoss does not have any theoretical justification to prove why it can outperform softmax cross entropy.
+SimLoss has a hyperparameter lower bound that controls the minimal class similarity that should have an impact on the network punishment.
+Any similarities below lower bound will be all zeros.
+It implies SimLoss would cost more time to fine tune.
+Our tree loss define a tree structure which can be obtained automatically and it is time-saving.
 \begin{align}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Weight matrix factorization}
-
-A simple way to reduce sample complexity when $c$ is large is to factor the parameter matrix as $W = VU$,
-where $V : \R ^ {c \times e}$, $U : \R^{e \times d}$, and $e<\!<\!c$.
-Then, each $\w_i = \vv_i U$, and the cross entropy softmax loss is
-\begin{equation}
-    \ell(VU;(\x,y)) = - \log \frac {\exp(-\trans\vv_y U \x)}{\sum_{j=1}^c \exp(-\trans \vv_j U \x)}
-    .
-\end{equation}
-Unfortunately, this new parameterization is not simultaneously convex in both $V$ and $U$;
-therefore, to analyze this formulation, we will assume that $V$ is fixed and only $U$ is a learned parameter.
-In practice, it is fine to set $V$ to be a random matrix (and there is good theory to justify this),
-or to simultaneously learn both $V$ and $U$ despite the nonconvexity.
-
-This factorization decreases the statistical complexity of the problem from $O(\sqrt{c/n})$ to $O(\sqrt{e/n})$.
-Recall that $e$ is a hyperparameter that is selected to be much less than $c$ and should represent the "intrinsic" dimensionality of the weight matrix.
-The following theorem proves this result formally.
-\begin{theorem}
-Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
-    and that for each class $i\in[c]$, $\ltwo{\vv_i}\le 1$ and $\ltwo{\uu_i}\le B$.
-Then the parameter vector $\bar W = V \bar U$ estimated from one epoch of SGD satisfies
-\begin{equation}
-    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt eB\rho}{\sqrt n}
-\end{equation}
-where $W^* = \argmin L_D(W)$.
-\end{theorem}
-% \begin{proof}
-%     \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David.}
-%     \begin{align}
-%     {\| U \|^2_F}&=\sum_{i=1}^e{\| U_i\|^2}\\
-%                 &\le\sum_{i=1}^e{B^2}\\
-%                 &\le eB^2\\
-%   \| U \|_F  &\le \sqrt e B  \\
-%   \| W \|_F  &\le \sqrt e B
-%     \end{align}
-%     Then we get:
+% \subsection{Weight matrix factorization}
+
+% A simple way to reduce sample complexity when $c$ is large is to factor the parameter matrix as $W = VU$,
+% where $V : \R ^ {c \times e}$, $U : \R^{e \times d}$, and $e<\!<\!c$.
+% Then, each $\w_i = \vv_i U$, and the cross entropy softmax loss is
 % \begin{equation}
-%     l(\bar W)-l(W^*)\le\frac {\sqrt eB\rho}{\sqrt n}
+%     \ell(VU;(\x,y)) = - \log \frac {\exp(-\trans\vv_y U \x)}{\sum_{j=1}^c \exp(-\trans \vv_j U \x)}
+%     .
 % \end{equation}
-%   Take expectation of both side of equation(8):
+% Unfortunately, this new parameterization is not simultaneously convex in both $V$ and $U$;
+% therefore, to analyze this formulation, we will assume that $V$ is fixed and only $U$ is a learned parameter.
+% In practice, it is fine to set $V$ to be a random matrix (and there is good theory to justify this),
+% or to simultaneously learn both $V$ and $U$ despite the nonconvexity.
+
+% This factorization decreases the statistical complexity of the problem from $O(\sqrt{c/n})$ to $O(\sqrt{e/n})$.
+% Recall that $e$ is a hyperparameter that is selected to be much less than $c$ and should represent the "intrinsic" dimensionality of the weight matrix.
+% The following theorem proves this result formally.
+% \begin{theorem}
+% Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
+%     and that for each class $i\in[c]$, $\ltwo{\vv_i}\le 1$ and $\ltwo{\uu_i}\le B$.
+% Then the parameter vector $\bar W = V \bar U$ estimated from one epoch of SGD satisfies
 % \begin{equation}
@@
 % \end{equation}
-% \end{proof}
+% where $W^* = \argmin L_D(W)$.
+% \end{theorem}
+% % \begin{proof}
+% %     \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David.}
+% %     \begin{align}
+% %     {\| U \|^2_F}&=\sum_{i=1}^e{\| U_i\|^2}\\
+% %                 &\le\sum_{i=1}^e{B^2}\\
+% %                 &\le eB^2\\
+% %   \| U \|_F  &\le \sqrt e B  \\
+% %   \| W \|_F  &\le \sqrt e B
+% %     \end{align}
+% %     Then we get:
+% %     \begin{equation}
+% %     l(\bar W)-l(W^*)\le\frac {\sqrt eB\rho}{\sqrt n}
+% %     \end{equation}
+% %   Take expectation of both side of equation(8):
+% %   \begin{equation}
+% %     \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt eB\rho}{\sqrt n}
+% % \end{equation}
+% % \end{proof}
 
@@
 \begin{table}[]
-\caption{Validation and test results with early stopping on CIFAR-100 dataset. Best values are written in bold.} \label{cifar100}
+\caption{Test results with early stopping on CIFAR-100 dataset. Best values are written in bold.} \label{cifar100}
 \begin{center}
@@
                       & Acc. & Similarity Acc. & SA \\ \cmidrule(r){1-1}
-Cover Tree Loss       & \textbf{52.78}     &  \textbf{65.90}               &  \textbf{62.55}  \\
+Tree Loss       & \textbf{52.78}     &  \textbf{65.90}               &  \textbf{62.55}  \\
 Cross Entropy         &  51.87    &   65.58              &  62.14  \\
@@
                       & Top1 Acc.      & Top5 Acc.     \\ \cmidrule(r){1-1}
-Cover Tree Loss       & \textbf{76.52} & \textbf{92.92} \\
+Tree Loss       & \textbf{76.52} & \textbf{92.92} \\
 Cross Entropy         & 75.30          & 92.36         \\
@@
 
-We apply cover tree loss on emoji prediction in twitter dataset. 
+We apply the tree loss on emoji prediction in twitter dataset. 
 Emojis are popular to express emotions in text messages and tweets are a wildely used social media over the world. 
@@
 We take the multilingual BERT model \cite{Feng2020LanguageagnosticBS} pretrained on data from 109 distinct languages which achieves state-of-the-art performance on a wide variety of natural language tasks.
-We get the embeddings of 1660 target emojis defined by emo2vec and construct a cover tree structure from these emojis. 
-In this cover tree structure, every leaf node represents each real target emoji and we replace all parent nodes with pseudo labels. 
-Then we would adopt cover tree loss and compare the performance with softmax cross entropy loss and SimLoss.
+We get the embeddings of 1660 target emojis defined by emo2vec.
 
@@
 \multicolumn{1}{c}{}                      & Acc.       & SA       & Acc.      & SA             \\ \cmidrule(r){1-1}
-Cover Tree Loss                           &   \textbf{20.81}    &   \textbf{50.26}  &  \textbf{20.96}    &   \textbf{50.45}        \\
+Tree Loss                           &   \textbf{20.81}    &   \textbf{50.26}  &  \textbf{20.96}    &   \textbf{50.45}        \\
 Cross Entropy                             &   19.90    &   48.27  &  19.95    &   48.33        \\
@@
 
-\subsubsection{Analysis}
+\subsubsection{Results}
+We evaluate the tree loss on image data(CIFAR100, ImageNet) and text data(Twitter) and the tree loss outperforms cross entropy loss and Simloss on metrics.
+Table \ref{cifar100} shows the results of three loss functions for the test set of the CIFAR-100 dataset.
+Similarity accuracy and superclass accuracy pay attention to more similar classes and the tree loss get
 

### 2021-10-11 experiments/synthetic/base_exp.py

@@ -143,8 +143,8 @@ optimizer = optim.SGD(
     momentum=args.momentum,
     weight_decay=args.weight_decay,
     )
-# scheduler = torch.optim.lr_scheduler.CosineAnnealingLR(optimizer, T_max=args.n)
-scheduler = torch.optim.lr_scheduler.ExponentialLR(optimizer, gamma=0.9)
+scheduler = torch.optim.lr_scheduler.CosineAnnealingLR(optimizer, T_max=args.n)
+# scheduler = torch.optim.lr_scheduler.ExponentialLR(optimizer, gamma=0.9)
 
 for ep in range(args.epoch):
     loss_sum = 0
@@ -211,6 +211,6 @@ test_accuracy = correct/len(Y_)
 
 loss_ = loss_sum
 test_loss_ = test_loss_sum/10
-with open(f'base_experiment_{args.loss}_loss_{args.epoch}.txt', 'a') as f:
+with open(f'base_experiment_{args.loss}_50.txt', 'a') as f:
     f.write(f'Loss: {loss_} \t Accuracy: {accuracy} \t Generlization Loss: {test_loss_} \t Test Accuracy: {test_accuracy}\n')
 # # # Height: {height} \t Training Loss: {training loss} Generlization Loss: {genarlization loss}

### 2021-10-11 experiments/synthetic/create_figure_base.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for base in 1.1 1.2 1.3 1.4 1.5 1.6 1.7 1.8 1.9 2.0 2.1 2.2 2.3 2.4 2.5 2.6 2.7 2.8 2.9 3.0 4.0 5.0 6.0 7.0; do
-        python3 base_exp.py --exp_num=$num --loss=tree --base=$base
+        python3 base_exp.py --exp_num=$num --loss=xentropy --base=$base
     done
 done

### 2021-10-11 experiments/synthetic/para_exp.py

@@ -27,7 +27,7 @@ parser_data.add_argument('--sigma', type=float, default=1.0)
 parser_data.add_argument('--random', type=float, default=0.0)
 parser_data.add_argument('--seed', type=int, default=666)
 parser_data.add_argument('--batch', type=int, default=1000)
-parser_data.add_argument('--epoch', type=int, default=10)
+parser_data.add_argument('--epoch', type=int, default=1)
 
 parser_model = parser.add_argument_group(
         title='model hyperparameters',
@@ -59,6 +59,7 @@ from tqdm import tqdm
 from TreeLoss.cover_tree import CoverTree
 from TreeLoss.utilities import set_seed, gen_sim, level
 from TreeLoss.loss import CoverTreeLoss, SimLoss, HSM
+import matplotlib.pyplot as plt
 
 # set the seed
 logging.debug('set_seed('+str(args.seed)+')')
@@ -101,7 +102,7 @@ class Mod(torch.nn.Module):
 
         weight = self.fc.weight
         loss, logits, added_weights = self.criterion(weight, x, y)
-        return loss, logits, weight
+        return loss, logits, weight, added_weights
 
 model = Mod(length, args.d, args.c, new2index).cuda()
 def get_levelnode(tree):
@@ -134,7 +135,7 @@ for ep in range(args.epoch):
         train_X = torch.FloatTensor(X[start:start+args.batch].view(args.batch,args.d))
         train_Y = torch.LongTensor(Y[start:start+args.batch].view(args.batch))
         train_X, train_Y = train_X.cuda(), train_Y.cuda()
-        loss, logits, W = model(train_X, train_Y)
+        loss, logits, V, W = model(train_X, train_Y)
 
         loss.backward()
         optimizer.step()
@@ -145,20 +146,78 @@ for leaf, path in new2index.items():
     for i, node in enumerate(path):
         level_list[i].add(node)
 
+def para_figure(W_norm, height):
+    level = np.arange(0,height,1)
+    W_ = W_norm
+    l1, = plt.plot(level, W_)
+    plt.xlabel('Level of Cover Tree')
+    plt.ylabel('|W|')
+    plt.savefig('W_vs_level.png', dpi=300)
+
 # W_norm = []
 # for i in level_list:
 #     leng = len(i)
[…]

### 2021-10-11 experiments/synthetic/plot_figure.py

@@ -213,7 +213,7 @@ if args.experiment == 'loss_vs_n' :
     # l6, = plt.loglog(x, loss_simloss[3], 'orange', linestyle="--")
     l3, = plt.loglog(x, loss_simloss[4], linestyle="--")
     l4, = plt.loglog(x, loss_HSM, linestyle="dotted")
-    plt.legend(handles=[l1,l2,l3,l4],labels=['Cover Tree Loss','Cross Entropy Loss','SimLoss', 'HSM'])
+    plt.legend(handles=[l1,l2,l3,l4],labels=['Tree Loss','Cross Entropy Loss','SimLoss', 'HSM'])
     plt.xlabel('Number of Data Points($n$)')
     plt.ylabel('Loss')
     plt.savefig('loss_vs_n.png', dpi=300)
@@ -227,7 +227,7 @@ if args.experiment == 'loss_vs_n' :
     # l6, = plt.loglog(x, W_err_simloss[3], 'orange', linestyle="--")
     l3, = plt.loglog(x, W_err_simloss[4], linestyle="--")
     l4, = plt.loglog(x, W_err_HSM, linestyle="dotted")
-    plt.legend(handles=[l1,l2,l3,l4],labels=['Cover Tree Loss','Cross Entropy Loss','SimLoss', 'HSM'])
+    plt.legend(handles=[l1,l2,l3,l4],labels=['Tree Loss','Cross Entropy Loss','SimLoss', 'HSM'])
     plt.xlabel('Number of Data Points($n$)')
     plt.ylabel('|W_error|')
     plt.savefig('error_vs_n.png', dpi=300)
@@ -241,7 +241,7 @@ if args.experiment == 'loss_vs_n' :
     # l6, = plt.loglog(x, accuracy_simloss[3],'orange', linestyle="--")
     l3, = plt.loglog(x, accuracy_simloss[4], linestyle="--")
     l4, = plt.loglog(x, accuracy_HSM, linestyle="dotted")
-    plt.legend(handles=[l1,l2,l3,l4],labels=['Cover Tree Loss','Cross Entropy Loss','SimLoss', 'HSM'])
+    plt.legend(handles=[l1,l2,l3,l4],labels=['Tree Loss','Cross Entropy Loss','SimLoss', 'HSM'])
     plt.xlabel('Number of Data Points($n$)')
     plt.ylabel('Accuracy')
[…]

### 2021-10-11 experiments/synthetic/run_experiment.py

@@ -206,6 +206,9 @@ logging.info('saving results')
 # # FIXME:
 # # save the W_err to a file
 loss = loss+1e-10
+for i in range(args.c):
+    print(torch.norm(W[i,:]).item())
+
 # print(accuracy)
-with open(f'{args.experiment}_{args.loss}.txt', 'a') as f:
-    f.write(f'Loss: {loss} \t W_err: {W_err} \t Accuracy: {accuracy} \n')
+# with open(f'{args.experiment}_{args.loss}.txt', 'a') as f:
+#     f.write(f'Loss: {loss} \t W_err: {W_err} \t Accuracy: {accuracy} \n')

### 2021-10-11 experiments/synthetic/tree_figure.py

@@ -7,8 +7,8 @@ args = parser.parse_args()
 import matplotlib.pyplot as plt
 import numpy as np
 
-f_tree = open(f'{args.experiment}_tree_loss_1.txt', 'r')
-f_xentropy = open(f'{args.experiment}_xentropy_loss_1.txt', 'r')
+f_tree = open(f'{args.experiment}_tree_50.txt', 'r')
+f_xentropy = open(f'{args.experiment}_xentropy_50.txt', 'r')
 # f_simloss = open(f'{args.experiment}_simloss.txt', 'r')
 # f_HSM = open(f'{args.experiment}_HSM.txt', 'r')
 
@@ -89,81 +89,81 @@ if args.experiment == 'loss_vs_structure':
         W_err_xentropy.append(np.mean(W_err_mid))
         accuracy_xentropy.append(np.mean(accuracy_mid))
 
-    loss_simloss_all = []
-    W_err_simloss_all = []
-    accuracy_simloss_all = []
-    for line in f_simloss:
-        line = line.strip()
-        if len(line)>1:
+    # loss_simloss_all = []
+    # W_err_simloss_all = []
+    # accuracy_simloss_all = []
+    # for line in f_simloss:
+    #     line = line.strip()
+    #     if len(line)>1:
 
-            loss_start = line.find('Loss:')
-            loss_end  = loss_start + len('Loss:')
+    #         loss_start = line.find('Loss:')
+    #         loss_end  = loss_start + len('Loss:')
 
-            W_err_start = line.find('W_err:')
-            W_err_end = W_err_start + len('W_err:')
+    #         W_err_start = line.find('W_err:')
+    #         W_err_end = W_err_start + len('W_err:')
 
-            accuracy_start = line.find('Accuracy:')
-            accuracy_end = accuracy_start + len('Accuracy:')
+    #         accuracy_start = line.find('Accuracy:')
+    #         accuracy_end = accuracy_start + len('Accuracy:')
 
-            loss = float(line[loss_end:W_err_start].strip())
-            W_err = float(line[W_err_end:accuracy_start].strip())
-            accuracy = float(float(line[accuracy_end:].strip()))
+    #         loss = float(line[loss_end:W_err_start].strip())
+    #         W_err = float(line[W_err_end:accuracy_start].strip())
+    #         accuracy = float(float(line[accuracy_end:].strip()))
 
-            loss_simloss_all.append(loss)
-            W_err_simloss_all.append(W_err)
[…]

### 2021-10-12 paper/paper.tex
update results and conclusion

@@
 
-\subsubsection{Analysis of Synthetic Experiment results}
+\subsubsection{Results}
+From figure \ref{fig.1}, it is clear that the tree loss achieves the best performance. 
+The tree loss converges at a faster rate as number of data points and dimension of parameter matrix increase.
+If we increase the number of classes, the tree loss can keep a higher accuracy and the accuracy of SimLoss is higher than cross entropy loss and hierarchical softmax.
+It is as our expected, the tree loss can improve performance on large classes tasks.
+Besides, when we increase the noise in the dataset, the accuracy of all loss functions decrease, yet the tree loss decreases slower.
+Among the four loss functions, hierarchical softmax hurts the performance obviously. 
+We would not apply hierarchical softmax on real world data experiment in terms of computation.
+
+There is a parameter 'base' which can control the height of tree.
+Figure \ref{subfig.2} shows that if we increase the value of base, the tree is shorter.
+As our expected, from figure \ref{subfig.1} we can see that a taller tree has higher accuracy. 
+We add a parameter randomness into the tree structure and the tree structure become more random as the randomness factor increase.
+As figure \ref{subfig.3} shows, when the tree structure become totally random, the performance of the tree loss is close to cross entropy loss.
 
@@
 Table \ref{cifar100} shows the results of three loss functions for the test set of the CIFAR-100 dataset.
-Similarity accuracy and superclass accuracy pay attention to more similar classes and the tree loss get
+Similarity accuracy and superclass accuracy pay attention to more similar classes and the tree loss get higher accuracy.
+Table \ref{imagenet} shows the results for the valdidation set of ImageNet dataset.
+ImageNet has 1000 classes and many classes are semantically  similar.
+The tree loss incorporates the similarities to training and get a higher top1 accuracy and top5 accuracy.
+The emojis of Twitter dataset is typically unbalanced and the tree loss works well for unbalanced data.
+Table \ref{twitter} shows the results for validation set and test set of twitter dataset.
+The tree loss achieve the best performance on accuracy and similarity accuracy.
 
 \section{Conclusion}
+In this paper, we have presented the tree loss, a drop-in replacement for the cross entropy loss that incorporated class relations. 
+We use properties of stochastic gradient descent to provide the theoretical justifications that the generalization error of the tree loss is better. 
+The tree loss works by re-parameterizing the parameter matrix for softmax cross entropy loss and can be easily implement. 
+We evaluate our tree loss on synthetic data and typically real world data. 
+From the results of experiments, we found the tree loss improve the performance significantly and  help with predicting more similar classes if the model misclassified an example. 
+In our analysis, since the tree loss can obtain background knowledge of classes, it works well for tasks with many classes and data with unbalanced classes.
 

### 2021-10-12 paper/paper.tex
change cover tree to tree

@@
     \item [1] 
-    We introduce cover tree loss which take advantage of internal structure between all classes.
+    We introduce the tree loss which take advantage of internal structure between all classes.
     \item [2] 
-    We provide theoretical justification that the generalization error of cover tree loss is independent of the number of classes.
+    We provide theoretical justification that the generalization error of the tree loss is independent of the number of classes.
     \item [3]
-    We evaluate our cover tree loss on experiments.
-One is experiment on fully synthetic data which is designed to be convex.
-The another one is on real world data: CIFAR100, IMAGENET and TWITTER dataset.
+    We evaluate our tree loss on experiments. One is experiment on fully synthetic data which is designed to be convex. The another one is on real world data: CIFAR100, IMAGENET and TWITTER dataset.
 
@@
 \end{equation}
-Substituting \eqref{eq:covertree-reparam} into \eqref{eq:xentropy} gives us the final cover tree loss
+Substituting \eqref{eq:covertree-reparam} into \eqref{eq:xentropy} gives us the final tree loss
 \begin{equation}
@@
 
-In this experiment we will demonstrate the cover tree loss's effectiveness on a simple multiclass logistic regression problem.
+In this experiment we will demonstrate the tree loss's effectiveness on a simple multiclass logistic regression problem.
 The problem will be specifically designed to be convex and have low intrinsic dimension in the class labels in order to illustrate the advantages of the cover tree loss.
@@
 \end{equation}
-converges to $W^*$ using the standard cross entropy loss and both the matrix factorization and cover tree reparameterizations.
+converges to $W^*$ using the standard cross entropy loss and both the matrix factorization and tree reparameterizations.
 % \fixme{You should prove this for yourself.}
@@
             \includegraphics[width=\textwidth]{fig/new_img/accuracy_vs_base.png}
-            {{\small Accuracy versus base of cover tree($n=1000, d=10, \sigma=1.0, c=100$)}}
+            {{\small Accuracy versus base of tree($n=1000, d=10, \sigma=1.0, c=100$)}}
             \label{subfig.1}
@@
             \includegraphics[width=\textwidth]{fig/new_img/height_vs_base.png}
-            {{\small Height versus base of cover tree($n=1000, d=10, \sigma=1.0, c=100$)}}   
+            {{\small Height versus base of tree($n=1000, d=10, \sigma=1.0, c=100$)}}   
             \label{subfig.2}
@@
             % \caption[Accuracy versus randomness($n=100, d=64, c=10$)]%
-            {{\small Accuracy versus cover tree structure($n=1000, d=64, \sigma=1.0, c=100$)}}  
+            {{\small Accuracy versus tree structure($n=1000, d=64, \sigma=1.0, c=100$)}}  
             \label{subfig.3}
@@
 In multi-label classification, it is common for the classes to be unbalanced.
-We would like to show that the cover tree loss works well for unbalanced data.
+We would like to show that the tree loss works well for unbalanced data.
 A good way to do that is to change the distribution that $y_i$ is drawn from,
@@
 
-The cover tree loss can work well even when the weight matrix has non-linear intrinsic structure.
+The tree loss can work well even when the weight matrix has non-linear intrinsic structure.
 We should adapt the $\w*_i$ vectors to sit on a manifold instead of a hyperplane to demonstrate this fact.
@@
 % \fixme{Write a description of the experiment.}
-In this experiment, we will compare cover tree loss with softmax corss entropy and simloss on some real world data.
+In this experiment, we will compare the tree loss with softmax corss entropy and simloss on some real world data.
 We conduct image classification tasks on CIFAR-100 dataset and ImageNet dataset and emoji prediction task on twitter dataset.
 Our goal is to investigate the effects of changing the loss function on our example experiments.
-We do not focus on if we have state-of-the-art performance on specific models, but rather on the evaluation of cover tree loss as a general loss function which can be applied on various tasks.
+We do not focus on if we have state-of-the-art performance on specific models, but rather on the evaluation of the tree loss as a general loss function which can be applied on various tasks.
 These three tasks and datasets are typical examples for using softmax cross entropy loss.
@@
 We use CIFAR-100 dataset which has 100 classes for image classification.
-We also get word embeddings from a word2vec model pretrained on Google News \cite{Mikolov2013EfficientEO} of class names and construct cover tree structure and calculate similarity between classes from word embeddings.
+We also get word embeddings from a word2vec model pretrained on Google News \cite{Mikolov2013EfficientEO} of class names and construct tree structure and calculate similarity between classes from word embeddings.
 Four class names do not yield a word embedding and are therefore eliminated.
 
-To evaluate our cover tree loss, we rely on three metrics: accuracy (Acc.) which focus on correct predictions and similarity accuracy (Similarity Acc.) which focus on the similarity of predicted and target class and superclass accuracy (SA).
+To evaluate our tree loss, we rely on three metrics: accuracy (Acc.) which focus on correct predictions and similarity accuracy (Similarity Acc.) which focus on the similarity of predicted and target class and superclass accuracy (SA).
 Every example in CIFAR-100 dataset has a main class and a superclass.

### 2021-10-12 experiments/synthetic/tree_figure.py
change cover tree to tree

@@ -165,12 +165,10 @@ if args.experiment == 'loss_vs_structure':
     #     W_err_HSM.append(np.mean(W_err_mid))
     #     accuracy_HSM.append(np.mean(accuracy_mid))
 
-    accuracy_ = accuracy_tree[:10]
-    accuracy_.append(0.098)
     accuracy_xentropy.append(accuracy_xentropy[0])
     x = [0.0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1.0]
     plt.figure(0)
-    l1, = plt.plot(x, accuracy_)
+    l1, = plt.plot(x, accuracy)
     l2, = plt.plot(x, accuracy_xentropy, linestyle='-.')
     # l3, = plt.plot(x, accuracy_simloss, linestyle='--')
     # l4, = plt.plot(x, accuracy_HSM, linestyle='dotted')
@@ -288,9 +286,6 @@ if args.experiment == 'base_experiment':
     #     train_accuracy_xentropy.append(np.mean(accuracy_mid))
     #     test_loss_xentropy.append(np.mean(test_loss_mid))
     #     test_accuracy_xentropy.append(np.mean(test_accuracy_mid))
-    train_accuracy_xentropy = []
-    for i in range(24):
-        train_accuracy_xentropy.append(0.028)
 
 
     plt.figure(0)

### 2021-10-12 paper/paper.tex
changes

@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}
 \newtheorem{fact}{Fact}
@@
 
+\renewcommand{\star}[1]{{#1}^{*}}
 \newcommand{\trans}[1]{{#1}^{T}}
@@
 
+\newcommand{\ignore}[1]{}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{abstract}
-    %Multiclass logistic regression has generalization error $O(\sqrt{c/n})$, where $c$ is the number of classes and $n$ the number of data points.
+    %Multiclass logistic regression has generalization error $O(\sqrt{k/n})$, where $k$ is the number of classes and $n$ the number of data points.
 
@@
     %Unfortunately, the standard cross entropy loss function does not enforce this constraint.
-    %It has generalization error $O(\sqrt{c/n})$, where $c$ is the number of classes and $n$ the number of data points.
+    %It has generalization error $O(\sqrt{k/n})$, where $k$ is the number of classes and $n$ the number of data points.
 
@@
 
-    %Whereas The standard softmax cross entropy loss function has generalization error $O(\sqrt{c/n})$,
-    %where $c$ is the number of classes and $n$ the number of data points.
+    %Whereas The standard cross entropy loss function has generalization error $O(\sqrt{k/n})$,
+    %where $k$ is the number of classes and $n$ the number of data points.
 
@@
 %We introduce cover tree loss function which takes advantage of this internal class structure.
-%The cover tree loss works by reparameterizing the weight matrix for the softmax cross entropy loss.
-%Compare to softmax cross entropy which has generalization error $O(\sqrt{c/n})$, the generalization error of cover tree loss is $O(\sqrt{1/n})$ which is independent of the number of classes. 
+%The cover tree loss works by reparameterizing the weight matrix for the cross entropy loss.
+%Compare to cross entropy which has generalization error $O(\sqrt{k/n})$, the generalization error of cover tree loss is $O(\sqrt{1/n})$ which is independent of the number of classes. 
 %We provide the theoretical justification and conduct extensive experiments on fully synthetic data and real world data. 
 %For real world data, we take CIFAR100 dataset, IMAGENET dataset and TWITTER dataset.
-%The cover tree loss outperforms than softmax cross entropy loss function on metrics.
+%The cover tree loss outperforms than cross entropy loss function on metrics.
 \end{abstract}
@@
 
-When people do a multi-class classification task, the standard loss function is softmax cross entropy.
-The mechanism of softmax cross entropy loss function is to maximize the assigned target class probability and punishes every misclassification equally, independent of some other information about the predicted class.
+When people do a multi-class classification task, the standard loss function is cross entropy.
+The mechanism of cross entropy loss function is to maximize the assigned target class probability and punishes every misclassification equally, independent of some other information about the predicted class.
 However, classes often have an internal structure. 
@@
 Take the internal structure in the training procedure would allow the classifier to make less sever mistakes as it learns to predict similar classes.
-In terms of theoretical result, the parameter matrix of softmax cross entropy loss is bounded by $\sqrt{c}B$ (where $c$ is the number of classes) and for $n$ data points, the generalization error is $O(\sqrt{c/n})$ which is dependent on $c$.
+In terms of theoretical result, the parameter matrix of cross entropy loss is bounded by $\sqrt{k}B$ (where $k$ is the number of classes) and for $n$ data points, the generalization error is $O(\sqrt{k/n})$ which is dependent on $k$.
 
 In this paper, we introduce the tree loss which take advantage of the internal structure bewtween classes.
-The idea of the tree loss is that we use tree structure to reduce the bound of the size of the parameter space and then the generalization error of the tree loss is $O(\sqrt{1/n})$ which is independent of $c$.
-In the tree loss, we take a tree structure which defined by similarity between classes to re-parameterize the weight matrix for the softmax cross entropy loss.
+The idea of the tree loss is that we use tree structure to reduce the bound of the size of the parameter space and then the generalization error of the tree loss is $O(\sqrt{1/n})$ which is independent of $k$.
+In the tree loss, we take a tree structure which defined by similarity between classes to re-parameterize the weight matrix for the cross entropy loss.
 We incorporate class similarities with loss function to make the model learn more information about classes.
@@
 
-\section{Notation}
-
-Assume we are solving a standard multi-class classification problem with $c$ classes and $d$ input feature dimensions.
-The softmax cross entropy loss (also called the logistic loss) is the standard loss function for this problem.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{The Tree Loss}
+
+\subsection{Problem Setting}
+
+Assume we are solving a standard multi-class classification problem with $k$ classes and $d$ input feature dimensions.
+The cross entropy loss (also called the logistic loss) is the standard loss function for this problem.
 It is defined to be
@@
     \label{eq:xentropy}
-    \ell(W;(\x,y)) = - \log \frac {\exp(-\trans\w_y \x)}{\sum_{j=1}^c \exp(-\trans \w_j \x)}
-\end{equation}
-where for each class $i\in[c]$,
+    \ell(W;(\x,y)) = - \log \frac {\exp(-\trans\w_y \x)}{\sum_{j=1}^k \exp(-\trans \w_j \x)}
+\end{equation}
+where for each class $i\in[k]$,
 $\w_i : \R^d$ is the parameter vector associated with class $i$;
-the variable $W : \R^{c \times d} = (\w_1; \w_2; ...; \w_k)$ is the full parameter matrix;
+the variable $W : \R^{k \times d} = (\w_1; \w_2; ...; \w_k)$ is the full parameter matrix;
 $\x : \R^d$ is the feature vector;
-and $y \in [c]$ is the class label.
-
-The main theoretical result for the cross entropy loss is that for a dataset with $n$ points,
-the generalization error is $O(\sqrt{c/n})$.
-There are many theorems that establish this result in different contexts.
-The following is an example that relies on properties of SGD.
+and $y \in [k]$ is the class label.
+
+\subsection{The Tree Loss}
+
+The tree loss works by reparameterizing the weight matrix for the cross entropy loss.
+Intuitively, our goal is to enforce that semantically similar labels will have similar weight vectors.
+
+The reparameterization is defined according to a \emph{label tree} structure that captures the similarity between labels.
+Every class is represented by a leaf node in the label tree,
+and internal nodes represent \emph{pseudo-classes} that group the existing classes into a logical hierarchy.
+At this point, we assume that the label tree structure is given a priori, and in Section \ref{sec:bias-var} we discuss methods for generating this structure and their tradeoffs.
+Figure \ref{fig:labeltree} shows an example label tree for a classification problem with 9 classes.
+
+\begin{figure}
+    \resizebox{\columnwidth}{!}{
+\begin{tikzpicture}
+    [ level distance=1.5cm
+    , level 1/.style={sibling distance=3cm}
+    , level 2/.style={sibling distance=1.5cm}
+    ]
+\node {\textit{pseudo1}}
+    child {node {\textit{pseudo2}}
+      child {node {\texttt{boat}}}
+      child {node {\texttt{plane}}}
+      child {node {\textit{pseudo3}}
+        child {node {\texttt{car}}}
+        child {node {\texttt{truck}}}
+        child {node {\texttt{van}}}
+        child {node {\texttt{motorcycle}}}
+      }
+      }
+    child {node {\texttt{building}}}
+    child {node {\textit{pseudo4}}
+      child {node {\texttt{cat}}}
+      child {node {\texttt{dog}}}
+    };
+\end{tikzpicture}
+}
+    \caption{\fixme{caption}}
+    \label{fig:labeltree}
+\end{figure}
+
+We parameterize the weight vectors from the label tree as follows.
+For each leaf node $i$ (equivalently for each class $i$),
+we let the sequence $P_i$ denote the path from the leaf node to the root.
+For example, using the label tree above,
+we have
+
+\begin{equation}
+\begin{split}
+    P_{\texttt{truck}} &= (\texttt{truck}, \textit{pseudo3}, \textit{pseudo2}, \textit{pseudo1} ) \\
+    P_{\texttt{cat}} &= (\texttt{cat}, \textit{pseudo4}, \textit{pseudo1} )
+\end{split}
+\end{equation}
+
+% \end{equation}
+
+Next, we associate a vector $\vv_i$ to each leaf and internal node $i$ in the tree structure.
+In particular, there is a vector $\vv_i$ for each class and for each pseudo-class.
+Finally, we reparameterize the weights for the cross entropy loss as the sum of the vectors along the paths.
+Specifically, we set the weight vector for class $j$ to be 
+\begin{equation}
+    \label{eq:covertree-reparam}
+    \w_j = \sum_{k\in P_j} \vv_k
+    .
+\end{equation}
+Substituting \eqref{eq:covertree-reparam} into \eqref{eq:xentropy} gives us the final tree loss
+\begin{equation}
+    \ell(V;(\x,y)) = - \log \frac {\exp(-\sum_{k\in P_y}\trans\vv_k \x)}{\sum_{j=1}^k \exp(- \sum_{k\in P_j}\trans\vv_k \x)}
+\end{equation}
+where $V=(\vv_1,...,\vv_k)$,
+and our goal is to minimize $\ell$ with respect to $V$.
+Note that this loss can easily be computed in libraries like pytorch or tensorflow with the standard cross entropy loss functions.
+The only change needed is to define the loss in terms of the sum of vectors $V$ instead of a variable tensor $W$.
+
+\subsection{Related loss functions}
+
+Many alternatives to the cross entropy loss have been proposed.
+
+The tree loss is superficially related to the hierarchical softmax (HSM) because both losses are defined based on tree structures.
+\cite{morin2005hierarchical} introduced the HSM to speed up the computational time of neural network training,
+but the tree loss is used to improve sample efficiency rather than computational efficiency.
+
+\cite{mikolov2013distributed} introduce the word2vec model and experiment with using both the hierarchical softmax and cross entropy with negative sampling.
+They conclude that negative sampling has the best performance both computationally and statistically.
+Since the tree loss is a simple extension of the cross entropy loss,
+negative sampling can be used to speed up the cross entropy loss as well.
+
+\cite{bojanowski2017enriching} introduce the fastText extension of the word2vec model, which uses sub-word information to improve sample efficiency.
+They do not provide any theoretical justification for why their technique should improve sample efficiency,
+but their technique is computationally very similar to the tree loss,
+and so our technique may be able to provide the first theoretical justification for their work.
+
+HSM:
+\begin{equation}
+    \label{eq:xentropy}
+    \ell(W;(\x,y)) = - \log \prod_{k\in P_y}\frac {\exp(-\trans\w_k \x)}{j\in L_k \exp(-\trans \w_j \x)}
+\end{equation}
+where $P_y$ is path from root to node of Huffman Tree,
+$L_k$ are nodes on the level where $k$ are
+
+% \fixme{Read the papers mentioned above.  Verify that you agree with the things I wrote.  Then, write a detailed mathematical description of the HSM loss and contrast it with the cover tree loss.}
+
+% \fixme{Read 5-10 additional papers about the hierarchical softmax.
+For each paper, write a paragraph describing the paper's contributions and how it relates to the cover tree loss.
+For the final paper we will reference these papers.
+We will have to trim down the notes that you write for this task, but it's useful when writing the paper to have detailed notes about references.}
+
+The hierarchical softmax loss aims to improve computation efficiency. 
+\cite{Peng2017IncrementallyLT} introduce a training method incrementally train the hierarchical softmax function for neural network language models.
+They also provide a new stochastic gradient based method to update all the word vectors and their experimental results show the incremental training can save a lot of time.
+\cite{Jiang2017ExplorationOT} explore the tree-based hierarchical softmax method and reform its architecture, making it compatible with modern GPUs.
+\cite{Yang2017OptimizeHS} gives a theoretic analysis on how should organize the hierarchical tree by treating the tree structure as a parameter of the training objective function.
+They propose SemHuff, a new tree constructing scheme based on adjusting the Huffman tree with word similarity knowledge.
+Their experiments results also show that word embeddings trained with optimized hierarchical tree can give better results in various tasks.
+
+\cite{Mohammed2018EffectivenessOH} compare the performance of normal softmax and hierarchical softmax in large scale classification tasks. 
+Normal softmax is computationally expensive for large scale datasets with large number of possible outputs.
+Their experimental results show that normal softmax and hierarchical softmax underperforms on datasets with large number of labels.
+That is also one of our motivations of the tree loss function. 
+Compared to classic cross entropy loss function, the tree loss function performs better on datasets with large number of labels.
+Extreme multi-label classification is difficult, but organizing labels as a tree can handle this problem.
+
+% \fixme{Write a detailed description of the sim loss}
+
+SimLoss \cite{Kobs2020SimLossCS} is similarity based loss function which incorporates class similarities to support the training of neural network classifiers.
+Cross entropy loss assumes only one class is correct and punishes every misclassification, while Simloss indicates classes have similarities and classifying a target as a similar class is better.
+When calculating the loss function, instead of only taking the probability vector at the target index Simloss also adds the product of similarity between target and other classes and probability vector at the corresponding class.
+Non zero values of similarity matrix lead to smaller losses when the network gives a high score to classes similar to the correct one. 
+It would allow the classifier to make less severe mistakes as it learns to predict similar classes.
+However, SimLoss does not have any theoretical justification to prove why it can outperform cross entropy.
+SimLoss has a hyperparameter lower bound that controls the minimal class similarity that should have an impact on the network punishment.
+Any similarities below lower bound will be all zeros.
+It implies SimLoss would cost more time to fine tune.
+Our tree loss define a tree structure which can be obtained automatically and it is time-saving.
+\begin{align}
+    L_{Simloss}&=-\frac{1}{N}\log(\sum_{k=1}^{C}S_{y_i,k}\cdot p_i[k])\\
+    % L_{Simloss}=-\frac{1}{N}\log(\sum_{k=1}^{C}S_{y_i,k}\cdot\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)})
+    p_i&=\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)}
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Theoretical Results}
+
+It is well known that the cross entropy loss has generalization error $O(\sqrt{k/n})$.
+Our main theoretical result states that the tree loss significantly improves this generalization error down to $O(\sqrt{1/n})$.
+This is a shocking improvement since it implies that the generalization error is independent of the number of classes in our problem.
+
+Our analysis relies on simple properties of stochastic gradient descent,
+and we view the simplicity of our analysis as a major strength of the tree loss.
+In this section, we first review standard results of stochastic gradient needed for our analysis.
+Then we formally state and prove our main result.
+We conclude with a discussion about the bias-variance tradeoff.
+
+\subsection{SGD Background}
+
+SGD is a standard algorithm for optimizing convex losses,
+and it has many variations.
+Our analysis uses the results from \citet{shalev2014understanding} which are based off of a version of SGD that uses parameter averaging.
+All variants of SGD have similar results, however, and we refer the reader to the above reference for a detailed discussion of these variants and their algorithmic details.
+
+The main result we use is a bound on the convergence rate of SGD for convex Lipschitz functions.
+We reproduce Theorem 14.8 of \citet{shalev2014understanding} in the theorem below.
+
+\begin{theorem}
+    \label{thm:sgd}
+    Let $B,\rho>0$.
+    Let $f$ be a convex function and let $\star W = \argmin_{W : \lF{W}\le B} f(W)$.
+    Assume that SGD is run for $T$ iterations with $\eta = \sqrt{\frac{B^2}{\rho^2 T}}$.
+    Assume that for all $t$, $\ltwo{\nabla f(W_t)} \le \rho$.
+    Then,
+    \begin{equation}
+        \E f(\bar W) - f(\star W) \le \frac{B\rho}{\sqrt{T}}
+        .
+    \end{equation}
+\end{theorem}
+
+The following theorem bounds the generalization error of the cross entropy loss for multiclass classification problems.
+It is an immediate consequence of Theorem \ref{thm:sgd} above when $f$ is the cross entropy loss.
+
 \begin{theorem}
 \label{theorem:xentropy}
-Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
-    and that for each class $i\in[c]$, $\ltwo{\w_i}\le B$.
+Assume that for all $i\in[n]$, $\ltwo{\x_i} \le \rho$,
+    and that for each class $i\in[k]$, $\ltwo{\w_i}\le B$.
 Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
 \begin{equation}
-    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt cB\rho}{\sqrt n}
+    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt kB\rho}{\sqrt n}
 \end{equation}
@@
 \end{theorem}
+
+Intuitively, this theorem states that the generalization error of the cross entropy loss shrinks at the rate $O(\sqrt{k/n})$.
+
+%\begin{theorem}
+    %Let $B,\rho>0$.
+    %Let $f$ be a convex function and let $\star \w = \argmin_{\w : \ltwo{\w}\le B} f(\w)$.
+    %Assume that SGD is run for $T$ iterations with $\eta = \sqrt{\frac{B^2}{\rho^2 T}}$.
+    %Assume that for all $t$, $\ltwo{\nabla f(\w_t)} \le \rho$ with probability 1.
+    %Then,
+    %\begin{equation}
+        %\E f(\bar \w) - f(\star \w) \le \frac{B\rho}{\sqrt{T}}
+        %.
+    %\end{equation}
+%\end{theorem}
+%
+%When analyzing stochastic gradient descent using the cross entropy loss,
+%it is common to assume that the parameter space is bounded.
+%Under the standard parameterization, we have that the weight vector for each class satisfies $\ltwo{\w_j} \le B$.
+%It immediately follows that $\lF{W} \le \sqrt{k}B$,
+%and from this and convergence results of SGD it follows that the generalization error is $O(\sqrt{k}B/n)$.
+%(See Theorem \ref{theorem:xentropy} above.)
+%
+%\begin{defn}
+    %A learning problem is called convex-lipschitz-bounded with parameters $\rho,B$ if
+    %\begin{enumerate}
+        %\item $\ltwo{\w} \le B$
+        %\item the loss
+    %\end{enumerate}
+%\end{defn}
+%
+%\begin{corollary}[Corollary 14.12 \citep{shalev2014understanding}]
+    %Consider a convex-Lipschitz-bounded learning problem with parameters $\rho, B$.
+    %Then for every $\epsilon>0$, if we run the SGD method for minimizing $L_\mathcal D(W)$ with a number of iterations
+        %$T \ge \frac{B^2\rho^2}{\epsilon^2}$
+    %and with
+        %$\eta = \sqrt{\frac{B^2}{\rho^2 T}}$
+    %then the output of SGD satisfies
+    %\begin{equation}
+        %\E L_\mathcal D (\bar W) - L_\mathcal D(\star W) \le \epsilon
+    %\end{equation}
+%\end{corollary}
+%
+%\subsection{Background}
+
+%In this section, we first introduce more notation and definitions needed for our analysis,
+%then we recall a standard result of stochastic gradient descent.
+%We follow the notation of \citet{shalev2014understanding}'s textbook as closely as possible.
+%
+%Let $\mathcal D$ be a distribution over the input data points and $S \sim D^m$ be a set of $m$ data points sampled from this distribution.
+%Then we define the true loss as
+%\begin{equation}
+    %L_\mathcal D(W) = \E_{(\x,y)\sim\mathcal D} \ell(W; \x, y)
+%\end{equation}
+%and the sample loss as
+%\begin{equation}
+    %L_S(W) = \frac 1 m \sum_{i=1}^m \ell(W; \x_i, y_i)
+    %.
+%\end{equation}
+%We refer to the difference between these two losses as the generalization error.
+%\begin{equation}
+    %\left\lvert L_\mathcal D(W) - L_S(W) \right\rvert.
+%\end{equation}
+%
+%Given a distribution of data points $\mathcal D$, the optimal parameter matrix is defined as
+%\begin{equation}
+    %\star W = \argmin_{W} \E_{(\x, y)} \ell(W; (\x, y))
+%\end{equation}
+%Given a dataset of $n$ points, we can estimate the parameter 
+%\begin{equation}
+    %\hat W = \argmin_{W} \frac1n\sum_{i=1}^n \ell(W; (\x_i, y_i))
+%\end{equation}
+%The main theoretical result for the cross entropy loss is that for a dataset with $n$ points,
+%the generalization error is $O(\sqrt{k/n})$.
+%There are many theorems that establish this result in different contexts.
+%The following is an example that relies on properties of SGD.
+%\begin{theorem}
+%\label{theorem:xentropy}
+%Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
+    %and that for each class $i\in[k]$, $\ltwo{\w_i}\le B$.
+%Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
+%\begin{equation}
+    %\E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt cB\rho}{\sqrt n}
+%\end{equation}
+%where $W^* = \argmin L_D(W)$.
+%\end{theorem}
 % \begin{proof}
@@
 %     \begin{align}
-%     {\| W \|^2_F}&=\sum_{i=1}^c{\| W_i\|^2}\\
-%                 &\le\sum_{i=1}^c{B^2}\\
+%     {\| W \|^2_F}&=\sum_{i=1}^k{\| W_i\|^2}\\
+%                 &\le\sum_{i=1}^k{B^2}\\
 %                 &\le cB^2\\
-%   \| W \|_F  &\le \sqrt c B 
+%   \| W \|_F  &\le \sqrt k B 
 %     \end{align}
@@
 
-There are many other loss functions that have been proposed for multilabel classification.
-In this section, we review these alternatives before presenting our proposed the tree loss.
-
-\subsection{Hierarchical Softmax}
-
-The tree loss is superficially related to the hierarchical softmax (HSM) because both losses are defined based on tree structures.
-\cite{morin2005hierarchical} introduced the HSM to speed up the computational time of neural network training,
-but the tree loss is used to improve sample efficiency rather than computational efficiency.
-\cite{mikolov2013distributed} introduce the word2vec model and experiment with using both the hierarchical softmax and cross entropy with negative sampling.
-They conclude that negative sampling has the best performance both computationally and statistically.
-Since the tree loss is a simple extension of the cross entropy loss,
-negative sampling can be used to speed up the cross entropy loss as well.
-\cite{bojanowski2017enriching} introduce the fastText extension of the word2vec model, which uses sub-word information to improve sample efficiency.
-They do not provide any theoretical justification for why their technique should improve sample efficiency,
-but their technique is computationally very similar to the tree loss,
-and so our technique may be able to provide the first theoretical justification for their work.
-
-HSM:
-\begin{equation}
-    \label{eq:xentropy}
-    \ell(W;(\x,y)) = - \log \prod_{k\in P_y}\frac {\exp(-\trans\w_k \x)}{j\in L_k \exp(-\trans \w_j \x)}
-\end{equation}
-where $P_y$ is path from root to node of Huffman Tree,
-$L_k$ are nodes on the level where $k$ are
-
-% \fixme{Read the papers mentioned above.  Verify that you agree with the things I wrote.  Then, write a detailed mathematical description of the HSM loss and contrast it with the cover tree loss.}
-
-% \fixme{Read 5-10 additional papers about the hierarchical softmax.
-For each paper, write a paragraph describing the paper's contributions and how it relates to the cover tree loss.
-For the final paper we will reference these papers.
-We will have to trim down the notes that you write for this task, but it's useful when writing the paper to have detailed notes about references.}
-
-The hierarchical softmax loss aims to improve computation efficiency. 
-\cite{Peng2017IncrementallyLT} introduce a training method incrementally train the hierarchical softmax function for neural network language models.
-They also provide a new stochastic gradient based method to update all the word vectors and their experimental results show the incremental training can save a lot of time.
-\cite{Jiang2017ExplorationOT} explore the tree-based hierarchical softmax method and reform its architecture, making it compatible with modern GPUs.
-\cite{Yang2017OptimizeHS} gives a theoretic analysis on how should organize the hierarchical tree by treating the tree structure as a parameter of the training objective function.
-They propose SemHuff, a new tree constructing scheme based on adjusting the Huffman tree with word similarity knowledge.
-Their experiments results also show that word embeddings trained with optimized hierarchical tree can give better results in various tasks.
-
-\cite{Mohammed2018EffectivenessOH} compare the performance of normal softmax and hierarchical softmax in large scale classification tasks. 
-Normal softmax is computationally expensive for large scale datasets with large number of possible outputs.
-Their experimental results show that normal softmax and hierarchical softmax underperforms on datasets with large number of labels.
-That is also one of our motivations of the tree loss function. 
-Compared to classic cross entropy loss function, the tree loss function performs better on datasets with large number of labels.
-Extreme multi-label classification is difficult, but organizing labels as a tree can handle this problem.
-
-% \cite{Peng2017IncrementallyLT} introduce a training method incrementally train the hierarchical softmax function for neural network language models. 
-% To be specific, the incremental training split the cost function to model old and update corpora separately and factorize the objective function for the hierarchical softmax. 
-% They also provide a new stochastic gradient based method to update all the word vectors and parameters and their theoretical analysis shows the mean square error of the parameter vectors can be bounded by a function of the number of changed words related to the parameter node which is similar to our idea of cover tree loss.
-% Their experimental results show the incremental training can save a lot of time.
-
-% \cite{Mohammed2018EffectivenessOH} compare the performance of normal softmax and hierarchical softmax in large scale classification tasks. 
-% Normal softmax is computationally expensive for large scale datasets with large number of possible outputs.
-% Their experimental results show that normal softmax and hierarchical softmax underperforms on datasets with large number of labels.
-% That is also one of our motivations of cover tree loss function. 
-% Compared to classic cross entropy loss function, cover tree loss function performs better on datasets with large number of labels.
-
-% Extreme multi-label classification is difficult, but organizing labels as a tree can handle this problem. 
-% Hierarchical softmax approach commonly used for multi-class problems.
-% \cite{Wydmuch2018ANG} investigate probabilistic label trees that have been recently devised for tackling extreme multi-label classification and show that probabilistic label trees are a no-regret multi-label generation of hierarchical softmax when precision $@k$ is used as a model evaluation metric.
-% They also show that their implementation of probabilistic label trees obtains significantly better results than hierarchical softmax with the pick-one-label heuristic.
-
-% Neural networks are widely used for computational linguistics.
-% These neural models leverage knowledge from massive corpora but they are extremely slow.
-% \cite{Jiang2017ExplorationOT} explore the tree-based hierarchical softmax method and reform its architecture, making it compatible
-% with modern GPUs and introducing a compact tree-based loss function.
-% Their tree-based loss function is the negative log-likelihood of the joint product of the probability of the route taken from the root to the corresponding leaf node. 
-% It is different from our cover tree loss function which parameterize the weight vectors.
-
-% \cite{Yang2017OptimizeHS} gives a theoretic analysis on how should organize the hierarchical tree by treating the tree structure as a parameter of the training objective function.
-% They propose SemHuff, a new tree constructing scheme based on adjusting the Huffman tree with word similarity knowledge.
-% Their experiments results also show that word embeddings trained with optimized hierarchical tree can give better results in various tasks.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%There are many other loss functions that have been proposed for multilabel classification.
+%In this section, we review these alternatives before presenting our proposed the tree loss.
 
@@
     %\\
-    %&\le \frac{4\rho^2}{\lambda T} ( 1 + \log T) + \frac{\lambda c B^2}{2}
+    %&\le \frac{4\rho^2}{\lambda T} ( 1 + \log T) + \frac{\lambda k B^2}{2}
     %.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Simloss}
-
-% \fixme{Write a detailed description of the sim loss}
-
-SimLoss \cite{Kobs2020SimLossCS} is similarity based loss function which incorporates class similarities to support the training of neural network classifiers.
-Cross entropy loss assumes only one class is correct and punishes every misclassification, while Simloss indicates classes have similarities and classifying a target as a similar class is better.
-When calculating the loss function, instead of only taking the probability vector at the target index Simloss also adds the product of similarity between target and other classes and probability vector at the corresponding class.
-Non zero values of similarity matrix lead to smaller losses when the network gives a high score to classes similar to the correct one. 
-It would allow the classifier to make less severe mistakes as it learns to predict similar classes.
-However, SimLoss does not have any theoretical justification to prove why it can outperform softmax cross entropy.
-SimLoss has a hyperparameter lower bound that controls the minimal class similarity that should have an impact on the network punishment.
-Any similarities below lower bound will be all zeros.
-It implies SimLoss would cost more time to fine tune.
-Our tree loss define a tree structure which can be obtained automatically and it is time-saving.
-\begin{align}
-    L_{Simloss}&=-\frac{1}{N}\log(\sum_{c=1}^{C}S_{y_i,c}\cdot p_i[c])\\
-    % L_{Simloss}=-\frac{1}{N}\log(\sum_{c=1}^{C}S_{y_i,c}\cdot\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)})
-    p_i&=\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)}
-\end{align}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% A simple way to reduce sample complexity when $c$ is large is to factor the parameter matrix as $W = VU$,
-% where $V : \R ^ {c \times e}$, $U : \R^{e \times d}$, and $e<\!<\!c$.
+% A simple way to reduce sample complexity when $k$ is large is to factor the parameter matrix as $W = VU$,
+% where $V : \R ^ {k \times e}$, $U : \R^{e \times d}$, and $e<\!<\!k$.
 % Then, each $\w_i = \vv_i U$, and the cross entropy softmax loss is
 % \begin{equation}
-%     \ell(VU;(\x,y)) = - \log \frac {\exp(-\trans\vv_y U \x)}{\sum_{j=1}^c \exp(-\trans \vv_j U \x)}
+%     \ell(VU;(\x,y)) = - \log \frac {\exp(-\trans\vv_y U \x)}{\sum_{j=1}^k \exp(-\trans \vv_j U \x)}
 %     .
@@
 
-% This factorization decreases the statistical complexity of the problem from $O(\sqrt{c/n})$ to $O(\sqrt{e/n})$.
-% Recall that $e$ is a hyperparameter that is selected to be much less than $c$ and should represent the "intrinsic" dimensionality of the weight matrix.
+% This factorization decreases the statistical complexity of the problem from $O(\sqrt{k/n})$ to $O(\sqrt{e/n})$.
+% Recall that $e$ is a hyperparameter that is selected to be much less than $k$ and should represent the "intrinsic" dimensionality of the weight matrix.
 % The following theorem proves this result formally.
@@
 % Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
-%     and that for each class $i\in[c]$, $\ltwo{\vv_i}\le 1$ and $\ltwo{\uu_i}\le B$.
+%     and that for each class $i\in[k]$, $\ltwo{\vv_i}\le 1$ and $\ltwo{\uu_i}\le B$.
 % Then the parameter vector $\bar W = V \bar U$ estimated from one epoch of SGD satisfies
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{The Tree Loss}
-
-Like the weight matrix factorization, the tree loss works by reparameterizing the weight matrix for the softmax cross entropy loss.
-The reparameterization is defined according to a \emph{label tree} structure that captures the similarity between labels.
-Every class is represented by a leaf node in the label tree,
-and internal nodes represent \emph{pseudo-classes} that group the existing classes into a logical hierarchy.
-At this point, we assume that the label tree structure is given a priori, and in Section \ref{sec:bias-var} we discuss methods for generating this structure and their tradeoffs.
-The following figure shows an example label tree for a classification problem with 9 classes.
-
-\begin{center}
-\begin{tikzpicture}
-    [ level distance=1.5cm
-    , level 1/.style={sibling distance=3cm}
-    , level 2/.style={sibling distance=1.5cm}
-    ]
-\node {\textit{pseudo1}}
-    child {node {\textit{pseudo2}}
-      child {node {\texttt{boat}}}
-      child {node {\texttt{plane}}}
-      child {node {\textit{pseudo3}}
-        child {node {\texttt{car}}}
-        child {node {\texttt{truck}}}
-        child {node {\texttt{van}}}
-        child {node {\texttt{motorcycle}}}
-      }
-      }
-    child {node {\texttt{building}}}
-    child {node {\textit{pseudo4}}
-      child {node {\texttt{cat}}}
-      child {node {\texttt{dog}}}
-    };
-\end{tikzpicture}
-\end{center}
-
-We parameterize the weight vectors from the label tree as follows.
-For each leaf node $i$ (equivalently for each class $i$),
-we let the sequence $P_i$ denote the path from the leaf node to the root.
-For example, using the label tree above,
-we have
-
-\begin{equation}
-\begin{split}
-    P_{\texttt{truck}} &= (\texttt{truck}, \textit{pseudo3}, \textit{pseudo2}, \textit{pseudo1} ) \\
-    P_{\texttt{cat}} &= (\texttt{cat}, \textit{pseudo4}, \textit{pseudo1} )
-\end{split}
-\end{equation}
-
-% \end{equation}
-
-Next, we associate a vector $\vv_i$ to each leaf and internal node $i$ in the tree structure.
-In particular, there is a there is a vector $\vv_i$ for each class and for each pseudo-class.
-Finally, we reparameterize the weights for the softmax cross entropy loss as the sum of the vectors along the paths.
-Specifically, we set the weight vector for class $j$ to be 
-\begin{equation}
-    \label{eq:covertree-reparam}
-    \w_j = \sum_{k\in P_j} \vv_k
-    .
-\end{equation}
-Substituting \eqref{eq:covertree-reparam} into \eqref{eq:xentropy} gives us the final tree loss
-\begin{equation}
-    \ell(V;(\x,y)) = - \log \frac {\exp(-\sum_{k\in P_y}\trans\vv_k \x)}{\sum_{j=1}^c \exp(- \sum_{k\in P_j}\trans\vv_k \x)}
-\end{equation}
-where $V=(\vv_1,...,\vv_k)$,
-and our goal is to minimize $\ell$ with respect to $V$.
-Note that this loss can easily be computed in libraries like pytorch or tensorflow with the standard cross entropy loss functions.
-The only change needed is to define the loss in terms of the sum of vectors $V$ instead of a variable tensor $W$.
-
-\subsection{Analysis}
-
-When analyzing stochastic gradient descent using the cross entropy loss,
-it is common to assume that the parameter space is bounded.
-Under the standard parameterization, we have that the weight vector for each class satisfies $\ltwo{\w_j} \le B$.
-It immediately follows that $\lF{W} \le \sqrt{c}B$,
-and from this and convergence results of SGD it follows that the generalization error is $O(\sqrt{k}B/n)$.
-(See Theorem \ref{theorem:xentropy} above.)
+\subsection{Our Results}
 
@@
     \begin{equation}
-        \lF{V} \le \tfrac12 Bq c^{(1 - 1/\log_2 q)}
+        \lF{V} \le \tfrac12 Bq k^{(1 - 1/\log_2 q)}
     \end{equation}
@@
     \end{equation}
-    which is independent of the number of classes $c$.
+    which is independent of the number of classes $k$.
 \end{lemma}
@@
         &=
-        \left(\frac q 2\right)^{\log_q n}\\
+        \left(\frac q 2\right)^{\log_q k}\\
         &=
-        \frac{n}{2^{\log_q n}}\\
+        \frac{k}{2^{\log_q k}}\\
         &=
-        \frac{n}{2^{{\log_2 n}/{\log_2 q}}}\\
+        \frac{k}{2^{{\log_2 k}/{\log_2 q}}}\\
         &=
-        \frac{n}{n^{1/\log_2 q}}\\
+        \frac{k}{k^{1/\log_2 q}}\\
         &=
-        n^{\left(1 - {1}/{\log_2 q}\right)}
+        k^{\left(1 - {1}/{\log_2 q}\right)}
         .
@@
 
-Substituting this Lemma into the SGD bounds gives us our main theorem:
+Substituting this Lemma into the SGD bounds gives us our main result:
 
@@
 % Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
-%     and that for each class $i\in[c]$, $\ltwo{\w_i}\le B$.
-\fixme{Add assumptions.}
-Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
-    and that for each class $i\in[c]$,  $\ltwo{\w _i} \le \frac{B}{2^{\level i}}$.
+%     and that for each class $i\in[k]$, $\ltwo{\w_i}\le B$.
+Assume that for all $i\in[n]$, $\ltwo{\x_i} \le \rho$,
+    and that for each class $i\in[k]$,  $\ltwo{\vv _i} \le \frac{B}{2^{\level i}}$.
 Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
@@
 \end{equation}
-which is independent of the number of classes $c$.
+which is independent of the number of classes $k$.
 \end{theorem}
@@
 %Then we build a ``cover tree'' from the class labels that respects the metric structure.
-%This cover tree will have exactly $c$ leaf nodes, one for each class label,
-%and $O(c)$ internal nodes.
+%This cover tree will have exactly $k$ leaf nodes, one for each class label,
+%and $O(k)$ internal nodes.
 %Why does this small change work?
@@
     %\label{eq:lFV-bound}
-    %\lF{V} \le (\ddim \log c) B.
+    %\lF{V} \le (\ddim \log k) B.
 %\end{equation}
@@
 %Formally, we can bound the Frobenius norm of the weight matrix $V$ by
-%which is significantly better than our bound on the weight matrix $W$ of only $\sqrt c B$.
+%which is significantly better than our bound on the weight matrix $W$ of only $\sqrt k B$.
 %Substituting \eqref{eq:lFV-bound} into Theorem 14.12 of Shalev-Shwartz and Ben-David gives us that if SGD is run for $T$ iterations to compute parameter estimate $\bar W$,
@@
 %\begin{equation}
-    %\E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt {\dim \mathcal L}B\rho\log c}{\sqrt T}
+    %\E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt {\dim \mathcal L}B\rho\log k}{\sqrt T}
 %\end{equation}
@@
 
-\subsection{Bias-variance tradeoff}
+\subsection{Limitations: the bias-variance tradeoff}
+
 \label{sec:bias-var}
@@
 \begin{align}
-    U \sim N^{c\times a} \qquad\text{and}\qquad
+    U \sim N^{k\times a} \qquad\text{and}\qquad
     A \sim N^{a\times d},
@@
 \end{equation}
-For all $i \in [c]$, the row $\w_i^*$ of $W^*$ corresponds to the parameter vector for class $i$ and has dimension $d$.
+For all $i \in [k]$, the row $\w_i^*$ of $W^*$ corresponds to the parameter vector for class $i$ and has dimension $d$.
 The variable $a$ controls the intrinsic dimensionality of the problem.
@@
 \begin{align}
-    y_i &\sim \text{Uniform}([c]), \text{and} \\
+    y_i &\sim \text{Uniform}([k]), \text{and} \\
     \x_{i} &\sim \mathcal N(\w^*_{y_i}; \sigma),
@@
             \includegraphics[width=\textwidth]{fig/images/accuracy_vs_n.png}
-            % \caption[Accuracy versus number of data points($d=64, \sigma=1.0, c=10$)]%
-            {{\small Accuracy versus number of data points($d=64, \sigma=1.0, c=10$)}}  
+            % \caption[Accuracy versus number of data points($d=64, \sigma=1.0, k=10$)]%
+            {{\small Accuracy versus number of data points($d=64, \sigma=1.0, k=10$)}}  
             \label{subfig.1}
@@
             \includegraphics[width=\textwidth]{fig/images/accuracy_vs_d.png}
-            % \caption[Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, c=10$)]%
-            {{\small Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, c=10$)}}
+            % \caption[Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, k=10$)]%
+            {{\small Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, k=10$)}}
             \label{subfig.2}
@@
             \includegraphics[width=\textwidth]{fig/images/accuracy_vs_sigma.png}
-            % \caption[Accuracy versus randomness($n=100, d=64, c=10$)]%
-            {{\small Accuracy versus randomness($n=100, d=64, c=10$)}}
+            % \caption[Accuracy versus randomness($n=100, d=64, k=10$)]%
+            {{\small Accuracy versus randomness($n=100, d=64, k=10$)}}
             \label{subfig.3}
@@
             \includegraphics[width=\textwidth]{fig/new_img/accuracy_vs_base.png}
-            {{\small Accuracy versus base of tree($n=1000, d=10, \sigma=1.0, c=100$)}}
+            {{\small Accuracy versus base of tree($n=1000, d=10, \sigma=1.0, k=100$)}}
             \label{subfig.1}
@@
             \includegraphics[width=\textwidth]{fig/new_img/height_vs_base.png}
-            {{\small Height versus base of tree($n=1000, d=10, \sigma=1.0, c=100$)}}   
+            {{\small Height versus base of tree($n=1000, d=10, \sigma=1.0, k=100$)}}   
             \label{subfig.2}
@@
             \includegraphics[width=\textwidth]{fig/new_img/loss_vs_structure.png}
-            % \caption[Accuracy versus randomness($n=100, d=64, c=10$)]%
-            {{\small Accuracy versus tree structure($n=1000, d=64, \sigma=1.0, c=100$)}}  
+            % \caption[Accuracy versus randomness($n=100, d=64, k=10$)]%
+            {{\small Accuracy versus tree structure($n=1000, d=64, \sigma=1.0, k=100$)}}  
             \label{subfig.3}
@@
         %     % \caption[Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)]%
-        %     {{\small Loss versus base of cover tree($n=1000, d=10, \sigma=1.0, c=100$)}}    
+        %     {{\small Loss versus base of cover tree($n=1000, d=10, \sigma=1.0, k=100$)}}    
         %     \label{subfig.4}
@@
 We do not focus on if we have state-of-the-art performance on specific models, but rather on the evaluation of the tree loss as a general loss function which can be applied on various tasks.
-These three tasks and datasets are typical examples for using softmax cross entropy loss.
+These three tasks and datasets are typical examples for using cross entropy loss.
 
@@
 We use properties of stochastic gradient descent to provide the theoretical justifications that the generalization error of the tree loss is better. 
-The tree loss works by re-parameterizing the parameter matrix for softmax cross entropy loss and can be easily implement. 
+The tree loss works by re-parameterizing the parameter matrix for cross entropy loss and can be easily implement. 
 We evaluate our tree loss on synthetic data and typically real world data. 

### 2021-10-13 paper/paper.tex
update figures

@@
 
-\begin{figure*}
-        \centering
-        \begin{subfigure}[b]{0.45\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{fig/images/accuracy_vs_n.png}
-            % \caption[Accuracy versus number of data points($d=64, \sigma=1.0, k=10$)]%
-            {{\small Accuracy versus number of data points($d=64, \sigma=1.0, k=10$)}}  
-            \label{subfig.1}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.45\textwidth}  
-            \centering 
-            \includegraphics[width=\textwidth]{fig/images/accuracy_vs_d.png}
-            % \caption[Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, k=10$)]%
-            {{\small Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, k=10$)}}
-            \label{subfig.2}
-        \end{subfigure}
-        \vskip\baselineskip
-        \begin{subfigure}[b]{0.45\textwidth}   
-            \centering 
-            \includegraphics[width=\textwidth]{fig/images/accuracy_vs_sigma.png}
-            % \caption[Accuracy versus randomness($n=100, d=64, k=10$)]%
-            {{\small Accuracy versus randomness($n=100, d=64, k=10$)}}
-            \label{subfig.3}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.45\textwidth}   
-            \centering 
-            \includegraphics[width=\textwidth]{fig/images/accuracy_vs_class.png}
-            % \caption[Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)]%
-            {{\small Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)}}   
-            \label{subfig.4}
-        \end{subfigure}
-        % \caption[ Figures of Synthetic Data Experiment ]
-        % {{\small Figures of Synthetic Data Experiment}}
-        \label{fig.1}
-    \end{figure*}
-
-\begin{figure*}
-        \centering
-        \begin{subfigure}[b]{0.45\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{fig/new_img/accuracy_vs_base.png}
-            {{\small Accuracy versus base of tree($n=1000, d=10, \sigma=1.0, k=100$)}}
-            \label{subfig.1}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.45\textwidth}  
-            \centering 
-            \includegraphics[width=\textwidth]{fig/new_img/height_vs_base.png}
-            {{\small Height versus base of tree($n=1000, d=10, \sigma=1.0, k=100$)}}   
-            \label{subfig.2}
-        \end{subfigure}
-        \vskip\baselineskip
-        \begin{subfigure}[b]{0.45\textwidth}   
-            \centering 
-            \includegraphics[width=\textwidth]{fig/new_img/loss_vs_structure.png}
-            % \caption[Accuracy versus randomness($n=100, d=64, k=10$)]%
-            {{\small Accuracy versus tree structure($n=1000, d=64, \sigma=1.0, k=100$)}}  
-            \label{subfig.3}
-        \end{subfigure}
-        \hfill
-        % \begin{subfigure}[b]{0.45\textwidth}   
-        %     \centering 
-        %     \includegraphics[width=\textwidth]{fig/new_img/loss_vs_base.png}
-        %     % \caption[Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)]%
-        %     {{\small Loss versus base of cover tree($n=1000, d=10, \sigma=1.0, k=100$)}}    
-        %     \label{subfig.4}
-        % \end{subfigure}
-        % \caption[ Figures of Synthetic Data Experiment ]
-        % {{\small Figures of Synthetic Data Experiment}} 
-        \label{fig.2}
-    \end{figure*}
+\begin{figure}[h]
+\vspace{.3in}
+\includegraphics[width=\linewidth]{fig/images/accuracy_vs_n.png}
+\vspace{.3in}
+\caption{\small Accuracy versus number of data points($d=64, \sigma=1.0, k=10$)}
+\label{accuracy_vs_n}
+\end{figure}
+
+\begin{figure}[h]
+\vspace{.3in}
+\includegraphics[width=\linewidth]{fig/images/accuracy_vs_d.png}
+\vspace{.3in}
+\caption{\small Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, k=10$)}
+\label{accuracy_vs_d}
+\end{figure}
+
+\begin{figure}[h]
+\vspace{.3in}
+\includegraphics[width=\linewidth]{fig/images/accuracy_vs_sigma.png}
+\vspace{.3in}
+\caption{\small Accuracy versus randomness($n=100, d=64, k=10$)}
+\label{accuracy_vs_sigma}
+\end{figure}
+
+\begin{figure}[h]
+\vspace{.3in}
+\includegraphics[width=\linewidth]{fig/images/accuracy_vs_class.png}
+\vspace{.3in}
+\caption{\small Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)}
+\label{accuracy_vs_class}
+\end{figure}
+
+\begin{figure}[h]
+\vspace{.3in}
+\includegraphics[width=\linewidth]{fig/new_img/accuracy_vs_base.png}
+\vspace{.3in}
+\caption{\small Accuracy versus base of tree($n=1000, d=10, \sigma=1.0, k=100$)}
+\label{accuracy_vs_base}
+\end{figure}
+
+\begin{figure}[h]
+\vspace{.3in}
+\includegraphics[width=\linewidth]{fig/new_img/height_vs_base.png}
+\vspace{.3in}
+\caption{\small Height versus base of tree($n=1000, d=10, \sigma=1.0, k=100$)}
+\label{height_vs_base}
+\end{figure}
+
+\begin{figure}[h]
+\vspace{.3in}
+\includegraphics[width=\linewidth]{fig/new_img/loss_vs_structure.png}
+\vspace{.3in}
+\caption{\small Accuracy versus tree structure($n=1000, d=64, \sigma=1.0, k=100$)}
+\label{accuracy_vs_structure}
+\end{figure}
 

### 2021-10-13 paper/paper.tex
update figures

@@
 \subsubsection{Results}
-From figure \ref{fig.1}, it is clear that the tree loss achieves the best performance. 
-The tree loss converges at a faster rate as number of data points and dimension of parameter matrix increase.
-If we increase the number of classes, the tree loss can keep a higher accuracy and the accuracy of SimLoss is higher than cross entropy loss and hierarchical softmax.
+It is clear that the tree loss achieves the best performance. 
+From figure \ref{accuracy_vs_n} and \ref{accuracy_vs_d}, the tree loss converges at a faster rate as number of data points and dimension of parameter matrix increase.
+Figure \ref{accuracy_vs_class} shows that if we increase the number of classes, the tree loss can keep a higher accuracy and the accuracy of SimLoss is higher than cross entropy loss and hierarchical softmax.
 It is as our expected, the tree loss can improve performance on large classes tasks.
-Besides, when we increase the noise in the dataset, the accuracy of all loss functions decrease, yet the tree loss decreases slower.
+From figure \ref{accuracy_vs_sigma}, we can see that when we increase the noise in the dataset, the accuracy of all loss functions decrease, yet the tree loss decreases slower.
 Among the four loss functions, hierarchical softmax hurts the performance obviously. 
@@
 There is a parameter 'base' which can control the height of tree.
-Figure \ref{subfig.2} shows that if we increase the value of base, the tree is shorter.
-As our expected, from figure \ref{subfig.1} we can see that a taller tree has higher accuracy. 
+Figure \ref{height_vs_base} shows that if we increase the value of base, the tree is shorter.
+As our expected, from figure \ref{accuracy_vs_base} we can see that a taller tree has higher accuracy. 
 We add a parameter randomness into the tree structure and the tree structure become more random as the randomness factor increase.
-As figure \ref{subfig.3} shows, when the tree structure become totally random, the performance of the tree loss is close to cross entropy loss.
+As figure \ref{accuracy_vs_structure} shows, when the tree structure become totally random, the performance of the tree loss is close to cross entropy loss.
 

### 2021-10-14 paper/paper.tex
cite paper
changes

--- 2021-10-13 paper/paper.tex
@@
 %\bibliographystyle{apalike}
-\usepackage[margin=1in]{geometry}
+%\usepackage[margin=1in]{geometry}
 \usepackage{amsmath}
@@
 \usepackage{bm}
-\usepackage{natbib}
+\usepackage[round]{natbib}
 \usepackage[inline]{enumitem}
@@
 
+\usepackage{array}
+\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
+\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
+\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
+\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}
+
 \usepackage{color}
@@
 
-\theoremstyle{definition}
+%\theoremstyle{definition}
+\newtheorem{assumption}{Assumption}
 \newtheorem{problem}{Problem}
@@
 
+\newcommand{\parent}[1]{\texttt{parent}({#1})}
+
 \renewcommand{\star}[1]{{#1}^{*}}
+\newcommand{\bad}[1]{{#1}^{\textit{bad}}}
 \newcommand{\trans}[1]{{#1}^{T}}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Tree Loss}
-
-\subsection{Problem Setting}
-
-Assume we are solving a standard multi-class classification problem with $k$ classes and $d$ input feature dimensions.
-The cross entropy loss (also called the logistic loss) is the standard loss function for this problem.
-It is defined to be
-\begin{equation}
-    \label{eq:xentropy}
-    \ell(W;(\x,y)) = - \log \frac {\exp(-\trans\w_y \x)}{\sum_{j=1}^k \exp(-\trans \w_j \x)}
-\end{equation}
-where for each class $i\in[k]$,
-$\w_i : \R^d$ is the parameter vector associated with class $i$;
-the variable $W : \R^{k \times d} = (\w_1; \w_2; ...; \w_k)$ is the full parameter matrix;
-$\x : \R^d$ is the feature vector;
-and $y \in [k]$ is the class label.
-
-\subsection{The Tree Loss}
-
-The tree loss works by reparameterizing the weight matrix for the cross entropy loss.
-Intuitively, our goal is to enforce that semantically similar labels will have similar weight vectors.
-
-The reparameterization is defined according to a \emph{label tree} structure that captures the similarity between labels.
-Every class is represented by a leaf node in the label tree,
-and internal nodes represent \emph{pseudo-classes} that group the existing classes into a logical hierarchy.
-At this point, we assume that the label tree structure is given a priori, and in Section \ref{sec:bias-var} we discuss methods for generating this structure and their tradeoffs.
-Figure \ref{fig:labeltree} shows an example label tree for a classification problem with 9 classes.
-
-\begin{figure}
+\begin{figure*}
 \resizebox{\columnwidth}{!}{
@@
     ]
+\node[draw, rounded corners=0.1in, inner sep=0.1in] at (-1.5in,0){\textbf{$U$-Tree}};
+\node {\texttt{truck}}
+    child {node {\texttt{boxer}}
+      child {node {\texttt{tiger}}}
+      child {node {\texttt{skunk}}}
+      child {node {\texttt{boxer}}
+        child {edge from parent[draw=none]} % Added
+        child {node {\texttt{bulldog}}}
+        child {node {\texttt{boxer}}}
+        child {node {\texttt{husky}}}
+        child {node {\texttt{sheepdog}}}
+      }
+      child {node {\texttt{bear}}}
+      child {edge from parent[draw=none]} % Added
+      }
+    child {node {\texttt{truck}}
+      child {edge from parent[draw=none]} % Added
+      child {node {\texttt{truck}}}
+      child {node {\texttt{bus}}}
+    }
+    child {node {\texttt{toaster}}}
+    ;
+
+\end{tikzpicture}
+}
+~~~
+\resizebox{\columnwidth}{!}{
+\begin{tikzpicture}
+    [ level distance=1.5cm
+    , level 1/.style={sibling distance=3cm}
+    , level 2/.style={sibling distance=1.5cm}
+    ]
+\node[draw, rounded corners=0.1in, inner sep=0.1in] at (-1.5in,0){\textbf{$V$-Tree}};
 \node {\textit{pseudo1}}
     child {node {\textit{pseudo2}}
-      child {node {\texttt{boat}}}
-      child {node {\texttt{plane}}}
+      child {node {\texttt{tiger}}}
+      child {node {\texttt{skunk}}}
       child {node {\textit{pseudo3}}
-        child {node {\texttt{car}}}
+        child {edge from parent[draw=none]} % Added
+        child {node {\texttt{bulldog}}}
+        child {node {\texttt{boxer}}}
+        child {node {\texttt{husky}}}
+        child {node {\texttt{sheepdog}}}
+      }
+      child {node {\texttt{bear}}}
+      child {edge from parent[draw=none]} % Added
+      }
+    child {node {\textit{pseudo4}}
+      child {edge from parent[draw=none]} % Added
       child {node {\texttt{truck}}}
-        child {node {\texttt{van}}}
-        child {node {\texttt{motorcycle}}}
-      }
-      }
-    child {node {\texttt{building}}}
-    child {node {\textit{pseudo4}}
-      child {node {\texttt{cat}}}
-      child {node {\texttt{dog}}}
-    };
+      child {node {\texttt{bus}}}
+    }
+    child {node {\texttt{toaster}}}
+    ;
+
 \end{tikzpicture}
 }
-    \caption{\fixme{caption}}
+    \caption{
+        Example label tree structures for a subset of 10 ImageNet classes.
+        The $U$-tree has class labels that repeat at multiple levels,
+        and the $V$-tree introduces ``pseudoclasses''.
+        The pseudoclass \textit{pseudo3} represents the class of ``dogs'',
+        and the pseudoclass \textit{pseudo2} represents the class of ``animals''.
+    }
     \label{fig:labeltree}
-\end{figure}
-
-We parameterize the weight vectors from the label tree as follows.
-For each leaf node $i$ (equivalently for each class $i$),
-we let the sequence $P_i$ denote the path from the leaf node to the root.
-For example, using the label tree above,
+\end{figure*}
+
+\section{The Tree Loss}
+
+This section first formally defines our problem setting,
+then formally defines the tree loss.
+We conclude with a comparison between the tree loss and related loss functions.
+
+\subsection{Problem Setting}
+
+We consider the multi-class classification setting with $k$ classes and $d$ input feature dimensions.
+The cross entropy loss is the standard loss function for this setting.
+It is defined to be
+\begin{equation}
+    \label{eq:xentropy}
+    \ell(W;(\x,y)) = - \log \frac {\exp(-\trans\w_y \x)}{\sum_{j=1}^k \exp(-\trans \w_j \x)}
+\end{equation}
+where for each class $i\in[k]$,
+$\w_i : \R^d$ is the parameter vector associated with class $i$;
+the variable $W : \R^{k \times d} = (\w_1; \w_2; ...; \w_k)$ is the full parameter matrix;
+$\x : \R^d$ is the input feature vector;
+and $y \in [k]$ is the input class label.
+
+\subsection{The Tree Loss}
+
+The tree loss reparameterizes the weight matrix used in the cross entropy loss in order to enforce that semantically similar labels will have similar weight vectors.
+The reparameterization is defined according to a \emph{label tree} structure that captures the similarity between labels.
+And we propose two variants of the tree loss called the $U$ and $V$ variants that use slightly different label tree structures.
+The main purpose of the $U$-tree structure is to simplify the analysis and exposition of the $V$-tree structure,
+and we show later in our theoretical results that the $V$-tree is strictly better than the $U$-tree.
+Figure \ref{fig:labeltree} shows examples of both.
+
+\subsubsection{The $U$-Tree Loss}
+
+In a $U$-tree, every node is a class and the class of all internal nodes matches the class of one of its children.
+For each class $i$, we define $\parent{i}$ to be the parent of the upper-most node for class $i$,
+and the $\texttt{parent}$ of the root is the 0 vector..
+For example, in the example of Figure \ref{fig:labeltree},
 we have
-
-\begin{equation}
+\begin{equation*}
 \begin{split}
-    P_{\texttt{truck}} &= (\texttt{truck}, \textit{pseudo3}, \textit{pseudo2}, \textit{pseudo1} ) \\
-    P_{\texttt{cat}} &= (\texttt{cat}, \textit{pseudo4}, \textit{pseudo1} )
+    \parent{\texttt{husky}} &= \texttt{boxer} \text{, and}\\
+    \parent{\texttt{bear}} &= \texttt{boxer} \text{, and}\\
+    \parent{\texttt{boxer}} &= \texttt{truck} .\\
 \end{split}
-\end{equation}
-
-% \end{equation}
-
-Next, we associate a vector $\vv_i$ to each leaf and internal node $i$ in the tree structure.
-In particular, there is a vector $\vv_i$ for each class and for each pseudo-class.
+\end{equation*}
+We associate for each class $i$ a new parameter vector $\uu_i$ and set
+\begin{equation}
+    \w_i = \w_{\parent{i}} - \uu_i,
+    \label{eq:uu}
+\end{equation}
+and we define the parameter matrix $U : \mathbb R^{k\times d}$ to be $(\uu_1;...;\uu_k)$.
+The $U$-tree loss is then defined by substituting \eqref{eq:uu} into \eqref{eq:xentropy} to get
+\begin{equation*}
+    \ell(U;(\x,y)) = - \log \frac {\exp(-(\trans\uu_{\parent{y}}-\trans\uu_y) \x)}{\sum_{j=1}^k \exp(-(\trans\uu_{\parent{j}}-\trans \uu_j) \x)}
+\end{equation*}
+We use the same $\ell$ notation for the standard cross entropy loss function and the $U$-Tree loss because the function is exactly the same;
+the only difference is how we represent the parameters.
+
+\subsubsection{The $V$-Tree Loss}
+
+The $V$-tree is constructed from the $U$-tree by replacing all non-leaf nodes with ``pseudoclasses''.
+Let $k'$ be the total number of nodes in the $V$-tree;
+so $k'$ equals $k$ plus the number of internal nodes.
+For each class $i$, we let the sequence $P_i$ denote the path from the leaf node to the root.
+For example, using the $V$-tree in Figure \ref{fig:labeltree},
+we have
+\begin{equation*}
+\begin{split}
+    P_{\texttt{sheepdog}} &= (\texttt{sheepdog}, \textit{pseudo3}, \textit{pseudo2}, \textit{pseudo1} ) \\
+    P_{\texttt{truck}} &= (\texttt{truck}, \textit{pseudo4}, \textit{pseudo1} )
+\end{split}
+\end{equation*}
+Next, we associate a vector $\vv_i$ to each node $i$ in the tree structure.
+In particular, there is a vector $\vv_i$ for each class and for each pseudo-class,
+so there are more parameter vectors for the $V$-tree loss than either the $U$-tree loss or the standard cross entropy loss.
+
 Finally, we reparameterize the weights for the cross entropy loss as the sum of the vectors along the paths.
-Specifically, we set the weight vector for class $j$ to be 
+Specifically, we set the weight vector for class $i$ to be 
 \begin{equation}
     \label{eq:covertree-reparam}
-    \w_j = \sum_{k\in P_j} \vv_k
+    \w_j = \sum_{j\in P_i} \vv_i
     .
 \end{equation}
-Substituting \eqref{eq:covertree-reparam} into \eqref{eq:xentropy} gives us the final tree loss
+The $V$-tree loss is defined by substituting \eqref{eq:covertree-reparam} into \eqref{eq:xentropy} to get
 \begin{equation}
     \ell(V;(\x,y)) = - \log \frac {\exp(-\sum_{k\in P_y}\trans\vv_k \x)}{\sum_{j=1}^k \exp(- \sum_{k\in P_j}\trans\vv_k \x)}
-\end{equation}
-where $V=(\vv_1,...,\vv_k)$,
-and our goal is to minimize $\ell$ with respect to $V$.
-Note that this loss can easily be computed in libraries like pytorch or tensorflow with the standard cross entropy loss functions.
+    .
+\end{equation}
+We continue to use the $\ell$ function to represent both the standard cross entropy loss and the $V$-tree loss function to emphasize that these are the same loss functions,
+just with different parameterizations of the weight matrix.
+
+\subsection{Intuition}
+
+The intuition behind the $V$-tree reparameterization is that whenever we perform a gradient update on a data point with class $i$,
+we will also be ``automatically'' updating the parameter vectors of similar classes.
+To see this, note that when we have a \texttt{sheepdog} data point,
+we will perform gradient updates on all $\vv_i$ in $P_\texttt{sheepdog}$; i.e. $\vv_{sheepdog}$, $\vv_{\textit{pseudo3}}$, $\vv_{\textit{pseudo2}}$, and $\vv_{\textit{pseudo1}}$.
+This will cause the $\w_{\texttt{husky}}$ and $\w_{\texttt{bear}}$ parameters (among many others) to update because they also depend on the pseudoclass vectors $\vv_{\textit{pseudo3}}$ and $\vv{_\textit{pseudo2}}$.
+Because $P_\texttt{husky}$ has a larger overlap with $P_\texttt{sheepdog}$ than $P_\texttt{bear}$,
+the parameters of this more similar class will be updated more heavily.
+
+\subsection{Implementation Notes}
+
+Both the $U$-tree and $V$-tree losses are easy to implement in practice using the built-in cross entropy loss function in libraries like PyTorch \citep{NEURIPS2019_9015} or Tensorflow \citep{tensorflow2015-whitepaper}.
 The only change needed is to define the loss in terms of the sum of vectors $V$ instead of a variable tensor $W$.
-
-\subsection{Related loss functions}
-
-Many alternatives to the cross entropy loss have been proposed.
-
-The tree loss is superficially related to the hierarchical softmax (HSM) because both losses are defined based on tree structures.
-\cite{morin2005hierarchical} introduced the HSM to speed up the computational time of neural network training,
-but the tree loss is used to improve sample efficiency rather than computational efficiency.
-
-\cite{mikolov2013distributed} introduce the word2vec model and experiment with using both the hierarchical softmax and cross entropy with negative sampling.
-They conclude that negative sampling has the best performance both computationally and statistically.
-Since the tree loss is a simple extension of the cross entropy loss,
-negative sampling can be used to speed up the cross entropy loss as well.
-
-\cite{bojanowski2017enriching} introduce the fastText extension of the word2vec model, which uses sub-word information to improve sample efficiency.
-They do not provide any theoretical justification for why their technique should improve sample efficiency,
-but their technique is computationally very similar to the tree loss,
-and so our technique may be able to provide the first theoretical justification for their work.
-
-HSM:
-\begin{equation}
-    \label{eq:xentropy}
-    \ell(W;(\x,y)) = - \log \prod_{k\in P_y}\frac {\exp(-\trans\w_k \x)}{j\in L_k \exp(-\trans \w_j \x)}
-\end{equation}
-where $P_y$ is path from root to node of Huffman Tree,
-$L_k$ are nodes on the level where $k$ are
-
-% \fixme{Read the papers mentioned above.  Verify that you agree with the things I wrote.  Then, write a detailed mathematical description of the HSM loss and contrast it with the cover tree loss.}
-
-% \fixme{Read 5-10 additional papers about the hierarchical softmax.
-For each paper, write a paragraph describing the paper's contributions and how it relates to the cover tree loss.
-For the final paper we will reference these papers.
-We will have to trim down the notes that you write for this task, but it's useful when writing the paper to have detailed notes about references.}
-
-The hierarchical softmax loss aims to improve computation efficiency. 
-\cite{Peng2017IncrementallyLT} introduce a training method incrementally train the hierarchical softmax function for neural network language models.
-They also provide a new stochastic gradient based method to update all the word vectors and their experimental results show the incremental training can save a lot of time.
-\cite{Jiang2017ExplorationOT} explore the tree-based hierarchical softmax method and reform its architecture, making it compatible with modern GPUs.
-\cite{Yang2017OptimizeHS} gives a theoretic analysis on how should organize the hierarchical tree by treating the tree structure as a parameter of the training objective function.
-They propose SemHuff, a new tree constructing scheme based on adjusting the Huffman tree with word similarity knowledge.
-Their experiments results also show that word embeddings trained with optimized hierarchical tree can give better results in various tasks.
-
-\cite{Mohammed2018EffectivenessOH} compare the performance of normal softmax and hierarchical softmax in large scale classification tasks. 
-Normal softmax is computationally expensive for large scale datasets with large number of possible outputs.
-Their experimental results show that normal softmax and hierarchical softmax underperforms on datasets with large number of labels.
-That is also one of our motivations of the tree loss function. 
-Compared to classic cross entropy loss function, the tree loss function performs better on datasets with large number of labels.
-Extreme multi-label classification is difficult, but organizing labels as a tree can handle this problem.
-
-% \fixme{Write a detailed description of the sim loss}
-
-SimLoss \cite{Kobs2020SimLossCS} is similarity based loss function which incorporates class similarities to support the training of neural network classifiers.
-Cross entropy loss assumes only one class is correct and punishes every misclassification, while Simloss indicates classes have similarities and classifying a target as a similar class is better.
-When calculating the loss function, instead of only taking the probability vector at the target index Simloss also adds the product of similarity between target and other classes and probability vector at the corresponding class.
-Non zero values of similarity matrix lead to smaller losses when the network gives a high score to classes similar to the correct one. 
-It would allow the classifier to make less severe mistakes as it learns to predict similar classes.
-However, SimLoss does not have any theoretical justification to prove why it can outperform cross entropy.
-SimLoss has a hyperparameter lower bound that controls the minimal class similarity that should have an impact on the network punishment.
-Any similarities below lower bound will be all zeros.
-It implies SimLoss would cost more time to fine tune.
-Our tree loss define a tree structure which can be obtained automatically and it is time-saving.
-\begin{align}
-    L_{Simloss}&=-\frac{1}{N}\log(\sum_{k=1}^{C}S_{y_i,k}\cdot p_i[k])\\
-    % L_{Simloss}=-\frac{1}{N}\log(\sum_{k=1}^{C}S_{y_i,k}\cdot\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)})
-    p_i&=\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)}
-\end{align}
+This ensures that the loss is implemented efficiently and is numerically stable.
+
+In practice, the $V$-tree loss is slightly slower than the standard cross entropy loss and $U$-tree losses due to the additional summation over the paths.
+In our experiments, we found this this to cause the $V$-tree loss to be about twice as slow.
 
@@
 
-It is well known that the cross entropy loss has generalization error $O(\sqrt{k/n})$.
-Our main theoretical result states that the tree loss significantly improves this generalization error down to $O(\sqrt{1/n})$.
-This is a shocking improvement since it implies that the generalization error is independent of the number of classes in our problem.
-
+It is well known that when using the standard cross entropy loss,
+SGD converges at a rate of $O(\sqrt{k/n})$.
+Our theoretical results asymptotically improve this convergence rate.
+
+With an appropriately constructed label tree,
+we show convergence at a rate of $O(\sqrt{\log k/n})$ or $O(\sqrt{k^{1-1/c}/n})$,
+where $c$ is a measure of difficulty of the problem.
+But what happens if the tree is poorly constructed?
+Remarkably, nothing bad.
+We also show that for arbitrarily bad label tree structures,
+the $U$ and $V$ losses maintain a $O(\sqrt{k/n})$ convergence rate.
+This suggests that there is essentially no downside to using the tree loss parameterizations.
+
+\fixme{
 Our analysis relies on simple properties of stochastic gradient descent,
 and we view the simplicity of our analysis as a major strength of the tree loss.
-In this section, we first review standard results of stochastic gradient needed for our analysis.
+In this section, we first review standard results of stochastic gradient descent needed for our analysis.
 Then we formally state and prove our main result.
-We conclude with a discussion about the bias-variance tradeoff.
+}
 
@@
 and it has many variations.
-Our analysis uses the results from \citet{shalev2014understanding} which are based off of a version of SGD that uses parameter averaging.
-All variants of SGD have similar results, however, and we refer the reader to the above reference for a detailed discussion of these variants and their algorithmic details.
-
-The main result we use is a bound on the convergence rate of SGD for convex Lipschitz functions.
+Our analysis uses the results from Chapter 14 of \citet{shalev2014understanding} which are based off of a version of SGD that uses parameter averaging.\footnote{
+Other variants of SGD have similar results,
+and our results are easy to generalize to other SGD variants.
+We refer the reader to \citet{shalev2014understanding} for a discussion of these variants.}
+In this section we recall these results,
+occasionally changing the names of variables to avoid conflicts with variable names used elsewhere in this paper.
+
+We assume we are optimizing a function $f : \Theta \to \mathbb R$,
+and that we are only given noisy samples of the function and its gradient.
+We let $\theta^{t}$ denote the parameter value at iteration $t$,
+and $\eta : \mathbb R$ be the step size.
+Then the parameter update for step $t$ is defined to be
+\begin{equation}
+    \theta^{(t+1)} = \theta^{(t)} - \eta \nabla f(\theta^{(t)}).
+\end{equation}
+When using parameter averaging, the final model parameters are defined to be
+\begin{equation}
+    \bar\theta = \frac1T \sum_{i=1}^T \theta^{(t)}
+    .
+\end{equation}
+Parameter averaging is not often used in practice because of the memory requirements,
+but we use it here due because theorems using parameter averaging are typically much easier to state and prove.
+Equivalent results without parameter averaging typically require and additional $\log T$ factor in their convergence rates\citep{}.
+
+The main result we rely on is a bound on the convergence rate of SGD for convex Lipschitz functions.
 We reproduce Theorem 14.8 of \citet{shalev2014understanding} in the theorem below.
@@
     \label{thm:sgd}
-    Let $B,\rho>0$.
-    Let $f$ be a convex function and let $\star W = \argmin_{W : \lF{W}\le B} f(W)$.
-    Assume that SGD is run for $T$ iterations with $\eta = \sqrt{\frac{B^2}{\rho^2 T}}$.
-    Assume that for all $t$, $\ltwo{\nabla f(W_t)} \le \rho$.
+    Let $\beta,\rho>0$.
+    Let $f$ be a convex function and let $\star \theta = \argmin_{\theta : \ltwo{\theta}\le \beta} f(\theta)$.
+    Assume that SGD is run for $T$ iterations with $\eta = \sqrt{\frac{\beta^2}{\rho^2 T}}$.
+    Assume that for all $t$, $\ltwo{\nabla f(\theta^{(t)})} \le \rho$.
     Then,
     \begin{equation}
-        \E f(\bar W) - f(\star W) \le \frac{B\rho}{\sqrt{T}}
+        \E f(\bar \theta) - f(\star \theta) \le \frac{\beta\rho}{\sqrt{T}}
         .
@@
 
-The following theorem bounds the generalization error of the cross entropy loss for multiclass classification problems.
-It is an immediate consequence of Theorem \ref{thm:sgd} above when $f$ is the cross entropy loss.
+\subsection{SGD and Statistical Learning}
+
+We now introduce more statistical learning theory notation,
+then apply Theorem \ref{thm:sgd} above to bound the rate of learning.
+
+Define the true loss of our learning problem as
+\begin{equation}
+    L_D(A) = \E_{(\x,y)\sim D} \ell(A; (\x, y))
+\end{equation}
+where $A \in \{W, U, V\}$ is a parameterization of the cross entropy loss.
+The optimal parameter vector is defined to be the minimum of the true loss:
+\begin{equation}
+    \star A = \argmin_{A} L_D(A).
+\end{equation}
+In order to apply Theorem \ref{thm:sgd} to a learning problem,
+we make the following assumption about our the size of our data points:
+\begin{assumption}
+    \label{ass:lip}
+    For each feature vector $\x$ in the data set, 
+        $\ltwo{\x} \le \rho$
+        .
+\end{assumption}
+Under this assumption, the cross entropy loss $\ell$ is $\rho$-Lipschitz for all parameterizations,
+and the true loss $L_D$ is therefore also $\rho$-Lipschitz.
+
+Applying Theorem \ref{thm:sgd} with $f=L_D$ gives
+\begin{corollary}
+    \label{ref:cor:A}
+    Under Assumption \ref{ass:lip}, we have that for any parameterization $A$ of the cross entropy loss,
+    \begin{equation}
+        \E L_D(\bar A) - L_D(\star A) \le \frac{\lF{\star A}\rho}{\sqrt n}.
+        \label{eq:Aconv}
+    \end{equation}
+\end{corollary}
+
+We can now bound the convergence of the standard cross entropy loss and the $U$ and $V$-tree losses by bounding the Frobenius norms of their parameter matrices.
+
+In order to recover the standard convergence rate of multiclass classification, we make the following assumption.
+\begin{assumption}
+    \label{ass:B}
+    For each class $i$, the optimal parameter vector $\star\w_i$ satisfies
+        $\ltwo{\star\w_i} \le B$
+        .
+\end{assumption}
+Note that this assumption is not limiting because the value of $B$ need not be known during the optimization procedure.
+
+It follows that
+\begin{equation}
+    \lF{\star W}^2 = \sum_{i=1}^k \ltwo{\star\w_i} \le kB^2.
+    \label{eq:starW}
+\end{equation}
+Substituting Eq \eqref{eq:starW} into \eqref{eq:Aconv} gives the following bound.
 
@@
 \label{theorem:xentropy}
-Assume that for all $i\in[n]$, $\ltwo{\x_i} \le \rho$,
-    and that for each class $i\in[k]$, $\ltwo{\w_i}\le B$.
-Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
-\begin{equation}
-    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt kB\rho}{\sqrt n}
-\end{equation}
-where $W^* = \argmin L_D(W)$.
+    Under assumptions \ref{ass:lip} and \ref{ass:B} above,
+then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
+\begin{equation}
+    \E L_D(\bar W) - L_D(W^*)
+    \le \frac {\sqrt kB\rho}{\sqrt n}
+    .
+\end{equation}
 \end{theorem}
-
-Intuitively, this theorem states that the generalization error of the cross entropy loss shrinks at the rate $O(\sqrt{k/n})$.
-
-%\begin{theorem}
-    %Let $B,\rho>0$.
-    %Let $f$ be a convex function and let $\star \w = \argmin_{\w : \ltwo{\w}\le B} f(\w)$.
-    %Assume that SGD is run for $T$ iterations with $\eta = \sqrt{\frac{B^2}{\rho^2 T}}$.
-    %Assume that for all $t$, $\ltwo{\nabla f(\w_t)} \le \rho$ with probability 1.
-    %Then,
+\fixme{
+It is important to note that this result above is an upper bound and not a lower bound.
+This $O(\sqrt{k/n})$ convergence rate matches the convergence rate implied by the Nataranj dimension \citep{}.
+We are not aware of any lower bounds for SGD in the Lipschitz setting.
+\citet{nguyen2018tight,jentzen2020lower} study the strongly convex case and find that the upper bounds match the lower bounds.
+}
+
+\subsection {Bad Tree Structures}
+
+\begin{lemma}
+    \ref{lemma:starV}
+    We have that for all $V$-trees derived from a $U$-tree,
+    \begin{equation}
+        \lF{\star V} \le \lF{\star U}.
+    \end{equation}
+\end{lemma}
+\begin{proof}
+    \fixme{}
+\end{proof}
+
+The following lemma shows that even for arbitrarily bad tree structures,
+the bound on the parameter spaces cannot be too bad.
+
+\begin{lemma}
+    \ref{lemma:starU}
+    Under assumption \ref{ass:B},
+    the following bound holds for all $U$-tree structures:
+    \begin{equation}
+        \lF{\star U} \le 2\sqrt{k}B.
+    \end{equation}
+\end{lemma}
+\begin{proof}
+    We have
+    \begin{align}
+        \lF{\star U}^2 
+        &= \sum_{i=1}^k \ltwo{\star\uu_i}^2 \\
+        &= \sum_{i=1}^k \ltwo{\star\w_i - \star\w_{\parent{i}}}^2 \\
+        &\le \sum_{i=1}^k \left(\ltwo{\star\w_i} + \ltwo{\star\w_{\parent{i}}} \right)^2 \\
+        &\le \sum_{i=1}^k (2B)^2 \\
+        &\le k (2B)^2
+        .
+    \end{align}
+\end{proof}
+
+\subsection{Good Tree Structures}
+
+\begin{assumption}
+We are given a distance metric $d$ over the labels such that for all labels $i$ and $j$,
+\begin{equation}
+    \frac 1 \lambda d(i,j)
+    \le \ltwo{\star \w_i - \star \w_j}
+    \le \lambda d(i, j).
+\end{equation}
+We denote by $c$ the doubling dimension of the metric $d$.
+\end{assumption}
+
+\begin{lemma}
+    \ref{lemma:main}
+    When $c\le1$, we have that
+    \begin{equation}
+        \lF{\star U} \le \tfrac{1}{\sqrt2}\lambda B \sqrt{\log_2 k}.
+        \label{eq:c<=1}
+    \end{equation}
+    When $c>1$, we have that
+    \begin{equation}
+        \lF{\star U} \le \sqrt{5}\lambda B \sqrt{k^{(1-1/c)}}.
+        \label{eq:c>1}
+    \end{equation}
+\end{lemma}
+\begin{proof}
+%Construct a cover tree over the distance metric $d$.
+%For each class $i$, define the vector
 %\begin{equation}
-        %\E f(\bar \w) - f(\star \w) \le \frac{B\rho}{\sqrt{T}}
+    %\uu_i =
+    %\begin{cases}
+        %\w_i & \text{if $i$ is the root of the cover tree} \\
+        %\w_i - \w_{\parent{i}} & \text{otherwise} \\
+    %\end{cases}
     %.
 %\end{equation}
-%\end{theorem}
-%
-%When analyzing stochastic gradient descent using the cross entropy loss,
-%it is common to assume that the parameter space is bounded.
-%Under the standard parameterization, we have that the weight vector for each class satisfies $\ltwo{\w_j} \le B$.
-%It immediately follows that $\lF{W} \le \sqrt{k}B$,
-%and from this and convergence results of SGD it follows that the generalization error is $O(\sqrt{k}B/n)$.
-%(See Theorem \ref{theorem:xentropy} above.)
-%
-%\begin{defn}
-    %A learning problem is called convex-lipschitz-bounded with parameters $\rho,B$ if
-    %\begin{enumerate}
-        %\item $\ltwo{\w} \le B$
-        %\item the loss
-    %\end{enumerate}
-%\end{defn}
-%
-%\begin{corollary}[Corollary 14.12 \citep{shalev2014understanding}]
-    %Consider a convex-Lipschitz-bounded learning problem with parameters $\rho, B$.
-    %Then for every $\epsilon>0$, if we run the SGD method for minimizing $L_\mathcal D(W)$ with a number of iterations
-        %$T \ge \frac{B^2\rho^2}{\epsilon^2}$
-    %and with
-        %$\eta = \sqrt{\frac{B^2}{\rho^2 T}}$
-    %then the output of SGD satisfies
+%Define the vector $\star\uu_i$ similarly by replacing all the $\w_i$ with $\star\w_i$ above.
+    First, we review some simple properties of the cover tree structure that will be needed in our proof.
+    Let $q$ denote the maximum number of children of any node in the cover tree.
+    A standard property of cover trees is that $q \le (4^c)$ \citep[Lemma 25]{izbickithesis}.
+    Let $Q_i$ denote the number of nodes at level $i$ in the cover tree.
+    Then we have that $|Q_i| \le q^i.$
+    Finally, let $r$ be the height of the cover tree.
+    Without loss of generality, we analyze the bound when the cover tree is perfectly balanced and so $r = \log_q k = \log_2 k / (2c)$.
+
+We have that
+\begin{align}
+    \lF{\star U}^2
+    &= \sum_{i=1}^k \ltwo{\star\uu_i}^2 \\
+    &= \sum_{i=0}^r \sum_{j\in Q_i} \ltwo{\star\uu_j}^2 \\
+    &= \sum_{i=0}^r \sum_{j\in Q_i} \ltwo{\star\w_j - \star\w_{\parent{j}}}^2 \\
+    &\le \sum_{i=0}^r \sum_{j\in Q_i} \lambda^2 d(j, \parent{j})^2 \\
+    &\le \sum_{i=0}^r \sum_{j\in Q_i} \lambda^2 (B/2^i)^2 \\
+    &\le \sum_{i=0}^r q^i \lambda^2 (B/2^i)^2 \\
+    &\le \sum_{i=0}^r \lambda^2 B^2 (q/4)^i 
+    \label{eq:precases}
+\end{align}
+We proceed by considering the case of $c\le1$ and $c>1$ separately.
+
+When $c\le1$, $q\le4$.
+Substituting into Eq \eqref{eq:precases}, we have
+\begin{align}
+    \lF{\star U}^2
+    &\le \sum_{i=0}^r \lambda^2 B^2 \\
+    &= (r+1) \lambda^2 B^2 \\
+    &= \frac{\log_2k}{2c} \lambda^2 B^2 \\
+    &\le \frac{\log_2k}{2} \lambda^2 B^2
+    .
+\end{align}
+This matches Eq \eqref{eq:c<=1} in the lemma's statement.
+
+When $c>$, then $q>4$.
+We first show the following equality.
+\begin{align}
+\left(\frac q 4\right)^r
+&=
+\left(\frac q 4\right)^{\log_q k}\\
+&=
+\frac{k}{4^{\log_q k}}\\
+&=
+\frac{k}{4^{{\log_4 k}/{\log_4 q}}}\\
+&=
+\frac{k}{k^{1/\log_4 q}}\\
+&=
+k^{\left(1 - {1}/{\log_4 q}\right)} \\
+&=
+k^{\left(1 - 1/c\right)}
+.
+\label{eq:lFU:frac}
+\end{align}
+Substituting into Eq \eqref{eq:precases}, we have
+\begin{align}
+    \lF{\star U}^2
+    &= \lambda^2B^2 \left(\frac{(q/4)^{r+1}-1}{q/4-1}\right) \\
+    \label{eq:lFU:4}
+    &= \lambda^2B^2 \left(\frac{(q/4)k^{(1-1/c)}-1}{q/4-1}\right) \\
+    &\le \lambda^2B^2 \left(\frac{(q/4)k^{(1-1/c)}}{q/4-1}\right) \\
+    &\le 5 \lambda^2B^2 k^{(1-1/c)}
+    \label{eq:lFU:5}
+\end{align}
+    Inequality \eqref{eq:lFU:5} follows because $\tfrac{q/4}{q/4-1} \le 5$ for integer values of $q>4$.
+\end{proof}
+
+%Substituting \eqref{eq:lFU:frac} info \eqref{eq:lFU:5} gives
+%\begin{align}
+    %\lF{U} \le \lambda B \sqrt{\frac{\log_2 k}{2c} + 1}\sqrt{k^{(1-1/c)}}
+%\end{align}
+%\begin{lemma}
+    %\label{lemma:technical}
+    %For all $a>1$ and $b>1$, we have that
     %\begin{equation}
-        %\E L_\mathcal D (\bar W) - L_\mathcal D(\star W) \le \epsilon
-    %\end{equation}
-%\end{corollary}
-%
-%\subsection{Background}
-
-%In this section, we first introduce more notation and definitions needed for our analysis,
-%then we recall a standard result of stochastic gradient descent.
-%We follow the notation of \citet{shalev2014understanding}'s textbook as closely as possible.
-%
-%Let $\mathcal D$ be a distribution over the input data points and $S \sim D^m$ be a set of $m$ data points sampled from this distribution.
-%Then we define the true loss as
-%\begin{equation}
-    %L_\mathcal D(W) = \E_{(\x,y)\sim\mathcal D} \ell(W; \x, y)
-%\end{equation}
-%and the sample loss as
-%\begin{equation}
-    %L_S(W) = \frac 1 m \sum_{i=1}^m \ell(W; \x_i, y_i)
-    %.
-%\end{equation}
-%We refer to the difference between these two losses as the generalization error.
-%\begin{equation}
-    %\left\lvert L_\mathcal D(W) - L_S(W) \right\rvert.
-%\end{equation}
-%
-%Given a distribution of data points $\mathcal D$, the optimal parameter matrix is defined as
-%\begin{equation}
-    %\star W = \argmin_{W} \E_{(\x, y)} \ell(W; (\x, y))
-%\end{equation}
-%Given a dataset of $n$ points, we can estimate the parameter 
-%\begin{equation}
-    %\hat W = \argmin_{W} \frac1n\sum_{i=1}^n \ell(W; (\x_i, y_i))
-%\end{equation}
-%The main theoretical result for the cross entropy loss is that for a dataset with $n$ points,
-%the generalization error is $O(\sqrt{k/n})$.
-%There are many theorems that establish this result in different contexts.
-%The following is an example that relies on properties of SGD.
-%\begin{theorem}
-%\label{theorem:xentropy}
-%Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
-    %and that for each class $i\in[k]$, $\ltwo{\w_i}\le B$.
-%Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
-%\begin{equation}
-    %\E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt cB\rho}{\sqrt n}
-%\end{equation}
-%where $W^* = \argmin L_D(W)$.
-%\end{theorem}
-% \begin{proof}
-%     \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David and the properties of the cross entropy loss from the last set of notes.}
-%     \begin{align}
-%     {\| W \|^2_F}&=\sum_{i=1}^k{\| W_i\|^2}\\
-%                 &\le\sum_{i=1}^k{B^2}\\
-%                 &\le cB^2\\
-%   \| W \|_F  &\le \sqrt k B 
-%     \end{align}
-% Then we get:
-%     \begin{equation}
-%     l(\bar W)-l(W^*)\le\frac {\sqrt cB\rho}{\sqrt n}
-%     \end{equation}
-%   Take expectation of both side of equation(3):
-%   \begin{equation}
-%     \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt cB\rho}{\sqrt n}
-% \end{equation}
-% \end{proof}
-
-%There are many other loss functions that have been proposed for multilabel classification.
-%In this section, we review these alternatives before presenting our proposed the tree loss.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Bounds using L2 regularization}
-%
-%Recall that when we apply L2 regularization,
-%we are minimizing the objective function
-%\begin{equation}
-    %f(W) = \tfrac 1 m \sum_{i=1}^m \loss(W; (\x_i,y_i)) + \tfrac\lambda2\lF{W}^2
-    %.
-%\end{equation}
-%This function is $\lambda$-strongly convex in $W$.
-%(Why?)
-%Then Theorem 14.11 tells us that after performing $T$ iterations of SGD, we have that
-%\begin{equation}
-    %\label{eq:f-bound}
-    %\E f(\bar W) - f(W^*) \le \frac{4\rho^2}{\lambda T} ( 1 + \log T)
-%\end{equation}
-%where $W^* = \argmin f(W)$.
-%If we substitute $f(W)=L_D(W)+\tfrac\lambda 2\lF{W}^2$ into Equation \ref{eq:f-bound} above,
-%then we get
-%\begin{align}
-    %\E L_D(\bar W) - L_D(W^*) 
-    %&\le \frac{4\rho^2}{\lambda T} ( 1 + \log T) + \tfrac\lambda2\lF{W^*}^2 - \tfrac\lambda2\lF{\bar W}^2
-    %\\
-    %&\le \frac{4\rho^2}{\lambda T} ( 1 + \log T) + \frac{\lambda k B^2}{2}
-    %.
-%\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsection{Weight matrix factorization}
-
-% A simple way to reduce sample complexity when $k$ is large is to factor the parameter matrix as $W = VU$,
-% where $V : \R ^ {k \times e}$, $U : \R^{e \times d}$, and $e<\!<\!k$.
-% Then, each $\w_i = \vv_i U$, and the cross entropy softmax loss is
-% \begin{equation}
-%     \ell(VU;(\x,y)) = - \log \frac {\exp(-\trans\vv_y U \x)}{\sum_{j=1}^k \exp(-\trans \vv_j U \x)}
-%     .
-% \end{equation}
-% Unfortunately, this new parameterization is not simultaneously convex in both $V$ and $U$;
-% therefore, to analyze this formulation, we will assume that $V$ is fixed and only $U$ is a learned parameter.
-% In practice, it is fine to set $V$ to be a random matrix (and there is good theory to justify this),
-% or to simultaneously learn both $V$ and $U$ despite the nonconvexity.
-
-% This factorization decreases the statistical complexity of the problem from $O(\sqrt{k/n})$ to $O(\sqrt{e/n})$.
-% Recall that $e$ is a hyperparameter that is selected to be much less than $k$ and should represent the "intrinsic" dimensionality of the weight matrix.
-% The following theorem proves this result formally.
-% \begin{theorem}
-% Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
-%     and that for each class $i\in[k]$, $\ltwo{\vv_i}\le 1$ and $\ltwo{\uu_i}\le B$.
-% Then the parameter vector $\bar W = V \bar U$ estimated from one epoch of SGD satisfies
-% \begin{equation}
-%     \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt eB\rho}{\sqrt n}
-% \end{equation}
-% where $W^* = \argmin L_D(W)$.
-% \end{theorem}
-% % \begin{proof}
-% %     \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David.}
-% %     \begin{align}
-% %     {\| U \|^2_F}&=\sum_{i=1}^e{\| U_i\|^2}\\
-% %                 &\le\sum_{i=1}^e{B^2}\\
-% %                 &\le eB^2\\
-% %   \| U \|_F  &\le \sqrt e B  \\
-% %   \| W \|_F  &\le \sqrt e B
-% %     \end{align}
-% %     Then we get:
-% %     \begin{equation}
-% %     l(\bar W)-l(W^*)\le\frac {\sqrt eB\rho}{\sqrt n}
-% %     \end{equation}
-% %   Take expectation of both side of equation(8):
-% %   \begin{equation}
-% %     \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt eB\rho}{\sqrt n}
-% % \end{equation}
-% % \end{proof}
-
-\subsection{Our Results}
-
-The key idea of the tree loss is that we can reduce the bound on the size of the parameter space,
-and this will result in the reduced sample complexity.
-Let $\level k$ denote the level of node $k$ in the label tree.
-Then we replace the constraints on the $\w_j$s with the following constraint on all $\vv_k$:
-\begin{equation}
-    \ltwo{\vv_k} \le \frac{B}{2^{\level k}}
-    .
-    \label{eq:tree-constraint}
-\end{equation}
-Notice that the original constraint \eqref{} immediately follows from the tree constraint \eqref{eq:tree-constraint} and the reparameterization \eqref{eq:covertree-reparam}.
-One way to interpret this is that we have ``factored out'' our bounds on the $\w_i$ into bounds on the smaller $\vv_k$ components,
-and because the $\vv_k$ vectors are shared between classes,
-we can reduce the overall bound.
-The following lemma bounds the Frobenius norm of the weight matrix $V$.
-
-\begin{lemma}
-    Assume that the label tree has at most $q$ nodes per level and $r$ levels.
-    Then,
-    \begin{equation}
-        \lF{V} \le \tfrac12 Bq k^{(1 - 1/\log_2 q)}
-    \end{equation}
-    In particular, if $q=2$, then
-    \begin{equation}
-        \lF{V} \le B,
-    \end{equation}
-    which is independent of the number of classes $k$.
-\end{lemma}
-\begin{proof}
-    We have the following chain of inequalities
-    \begin{align}
-        \lF{V} 
-        &\le \sum_{k\in \text{nodes of the level tree}} \ltwo{\vv_k}
-        \\
-        &= \sum_{i=0}^r \sum_{k\in \text{nodes at level $i$}} \ltwo{\vv_k}
-        \\
-        &\le \sum_{i=0}^r B\left(\frac {q} {2}\right)^i
-        \label{eq:lem:lFV:1}
-        \\
-        &=
-        B\left(\frac{1 - (q/2)^{r+1}}{1-q/2}\right)
-        \label{eq:lem:lFV:2}
-        \\
-        &\le
-        B(q/2)^{r+1}.
-        \label{eq:lem:lFV:3}
-    \end{align}
-    Line \eqref{eq:lem:lFV:1} follows from the fact that the number of nodes at level $i$ in the tree is upper bounded by $q^i$ and the the maximum L2 norm of a vector at level $i$ in the tree is $B/2^i$,so the sum of all vectors at level $i$ is bounded by $B(q/2)^i$.
-    Lines \eqref{eq:lem:lFV:2} and \eqref{eq:lem:lFV:3} are standard properties of geometric series.
-
-    Next, we show that
-    \begin{equation}
-    \begin{split}
-        \left(\frac q 2\right)^r
-        &=
-        \left(\frac q 2\right)^{\log_q k}\\
-        &=
-        \frac{k}{2^{\log_q k}}\\
-        &=
-        \frac{k}{2^{{\log_2 k}/{\log_2 q}}}\\
-        &=
-        \frac{k}{k^{1/\log_2 q}}\\
-        &=
-        k^{\left(1 - {1}/{\log_2 q}\right)}
-        .
-        \label{eq:lem:technical2}
-    \end{split}
-    \end{equation}
-    Substituting \eqref{eq:lem:technical2} into \eqref{eq:lem:lFV:3} gives the stated result.
-\end{proof}
-
-Substituting this Lemma into the SGD bounds gives us our main result:
-
-\begin{theorem}
-\label{theorem:xentropy}
-% Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
-%     and that for each class $i\in[k]$, $\ltwo{\w_i}\le B$.
-Assume that for all $i\in[n]$, $\ltwo{\x_i} \le \rho$,
-    and that for each class $i\in[k]$,  $\ltwo{\vv _i} \le \frac{B}{2^{\level i}}$.
-Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
-\begin{equation}
-    \E L_D(\bar W) - L_D(W^*) \le \frac {B\rho}{\sqrt n}
-    ,
-\end{equation}
-which is independent of the number of classes $k$.
-\end{theorem}
-%Let $\mathcal L$ be a metric space over the set of labels,
-%and $\ddim$ be the doubling dimension of $\mathcal L$.
-%Then we build a ``cover tree'' from the class labels that respects the metric structure.
-%This cover tree will have exactly $k$ leaf nodes, one for each class label,
-%and $O(k)$ internal nodes.
-%Why does this small change work?
-%Intuitively, classes that have a small distance from each other should have similar weight vectors.
-
-%\begin{lemma}
-    %Under the conditions defined above, we have
-%\begin{equation}
-    %\label{eq:lFV-bound}
-    %\lF{V} \le (\ddim \log k) B.
+        %\frac {1-a^b}{1-a} \le ba^b
     %\end{equation}
 %\end{lemma}
-%\begin{proof}
-%\end{proof}
-
-%Formally, we can bound the Frobenius norm of the weight matrix $V$ by
-%which is significantly better than our bound on the weight matrix $W$ of only $\sqrt k B$.
-%Substituting \eqref{eq:lFV-bound} into Theorem 14.12 of Shalev-Shwartz and Ben-David gives us that if SGD is run for $T$ iterations to compute parameter estimate $\bar W$,
-%then
-%\begin{equation}
-    %\E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt {\dim \mathcal L}B\rho\log k}{\sqrt T}
-%\end{equation}
-%where $W^* = \argmin L_D(W)$.
-
-\subsection{Limitations: the bias-variance tradeoff}
-
-\label{sec:bias-var}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+\includegraphics[width=\columnwidth,height=1.5in]{fig/images/accuracy_vs_n.png}
+\includegraphics[width=\columnwidth,height=1.5in]{fig/images/accuracy_vs_d.png}
+\includegraphics[width=\columnwidth,height=1.5in]{fig/images/accuracy_vs_class.png}
+\includegraphics[width=\columnwidth,height=1.5in]{fig/images/accuracy_vs_sigma.png}
+\caption{
+    Results of our Synthetic Experiments I.
+    The x-axis of each plot shows which problem parameter is being varied.
+    As our theory predicts, the Tree Loss outperforms the baseline loss functions in all data regimes.
+}
+\label{fig:synth:1}
+\end{figure*}
 
@@
 
-Let $N$ be the standard normal distribution.
-Then sample the matrices
+\subsubsection{Data Generation Procedure}
+\label{sec:exp:synth:problem}
+
+Let $\mathcal N$ be the standard normal distribution.
+Then sample the true parameter matrix
 \begin{align}
-    U \sim N^{k\times a} \qquad\text{and}\qquad
-    A \sim N^{a\times d},
+    \star W \sim \mathcal N^{k\times d}
+    .
 \end{align}
-and define the true parameter matrix to be
-\begin{equation}
-    W^* = UA.
-\end{equation}
 For all $i \in [k]$, the row $\w_i^*$ of $W^*$ corresponds to the parameter vector for class $i$ and has dimension $d$.
-The variable $a$ controls the intrinsic dimensionality of the problem.
-When $a$ is small, then many class labels will be similar to each other;
-but as $a$ increases, the class labels will have increasingly less structure.
-When $a$ is known in advance, then we can use weight matrix factorization and set $e=a$.
 
@@
 
-With our problem defined in this way, it is clear that
-\begin{equation}
-    \argmin_{W} \tfrac 1 n \ell(W; \x_i, y_i)
-\end{equation}
-converges to $W^*$ using the standard cross entropy loss and both the matrix factorization and tree reparameterizations.
-% \fixme{You should prove this for yourself.}
-% Figure \ref{fig:synthetic-results} shows that the cover tree loss converges at a faster rate.
-
-\begin{figure}[h]
-\vspace{.3in}
-\includegraphics[width=\linewidth]{fig/images/accuracy_vs_n.png}
-\vspace{.3in}
-\caption{\small Accuracy versus number of data points($d=64, \sigma=1.0, k=10$)}
-\label{accuracy_vs_n}
-\end{figure}
-
-\begin{figure}[h]
-\vspace{.3in}
-\includegraphics[width=\linewidth]{fig/images/accuracy_vs_d.png}
-\vspace{.3in}
-\caption{\small Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, k=10$)}
-\label{accuracy_vs_d}
-\end{figure}
-
-\begin{figure}[h]
-\vspace{.3in}
-\includegraphics[width=\linewidth]{fig/images/accuracy_vs_sigma.png}
-\vspace{.3in}
-\caption{\small Accuracy versus randomness($n=100, d=64, k=10$)}
-\label{accuracy_vs_sigma}
-\end{figure}
-
-\begin{figure}[h]
-\vspace{.3in}
-\includegraphics[width=\linewidth]{fig/images/accuracy_vs_class.png}
-\vspace{.3in}
-\caption{\small Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)}
-\label{accuracy_vs_class}
-\end{figure}
-
-\begin{figure}[h]
-\vspace{.3in}
-\includegraphics[width=\linewidth]{fig/new_img/accuracy_vs_base.png}
-\vspace{.3in}
-\caption{\small Accuracy versus base of tree($n=1000, d=10, \sigma=1.0, k=100$)}
-\label{accuracy_vs_base}
-\end{figure}
-
-\begin{figure}[h]
-\vspace{.3in}
-\includegraphics[width=\linewidth]{fig/new_img/height_vs_base.png}
-\vspace{.3in}
-\caption{\small Height versus base of tree($n=1000, d=10, \sigma=1.0, k=100$)}
-\label{height_vs_base}
-\end{figure}
-
-\begin{figure}[h]
-\vspace{.3in}
-\includegraphics[width=\linewidth]{fig/new_img/loss_vs_structure.png}
-\vspace{.3in}
-\caption{\small Accuracy versus tree structure($n=1000, d=64, \sigma=1.0, k=100$)}
-\label{accuracy_vs_structure}
-\end{figure}
-
-\subsubsection{Results}
+With our problem defined in this way, it is clear that the empirical risk minimizer
+\begin{equation}
+    \hat W = \argmin_{W} \tfrac 1 n \ell(W; \x_i, y_i)
+\end{equation}
+converges to $W^*$.
+
+\subsubsection{Experiment I: Data Regimes}
+
+In this experiment, we investigate the tree loss's performance in a wide range of settings as we vary the number of data points ($n$), the number of dimensions ($d$), number of class labels ($k$), and the Bayes error ($\sigma$) of our problem.
+First, we construct a standard experimental setting with $n=100$, $d=64$, $k=10$, and $\sigma=1$.
+Then, for each of these parameters, we investigate the effect of that parameter's performance on the problem by varying it over a large range.
+For each value in the range, we:
+(1) randomly sample 50 problems using the procedure described in Section \ref{sec:exp:synth:problem};
+(2) for each problem, we:
+(2a) sample a training set with $n$ data points and a test set with 10000 data points;
+(2b) train 4 models on the training set using the standard cross entropy loss, tree loss, simloss, and hierarchical softmax;
+(2c) report the average accuracy accross the sampled test sets.
+
+Figure \ref{fig:synth:1} shows the results of these experiments.
+As our theory suggests, the tree loss outperforms all other losses in all regimes.
+Consider the top-left plot.
+As the number of data points $n$ gets large,
+then all of the models have accuracies that converge to 1;
+for most problems, however, the number of data points will not be sufficiently large to drive the generalization error to 0,
+and the fewer data points that the problem has,
+the better the tree loss performs compared to other losses.
+
+\fixme{
 From figure \ref{fig.1}, it is clear that the tree loss achieves the best performance. 
@@
 We would not apply hierarchical softmax on real world data experiment in terms of computation.
-
-There is a parameter 'base' which can control the height of tree.
-Figure \ref{subfig.2} shows that if we increase the value of base, the tree is shorter.
-As our expected, from figure \ref{subfig.1} we can see that a taller tree has higher accuracy. 
-We add a parameter randomness into the tree structure and the tree structure become more random as the randomness factor increase.
-As figure \ref{subfig.3} shows, when the tree structure become totally random, the performance of the tree loss is close to cross entropy loss.
-
-\subsubsection{Alternative synthetic experiments}
-
-In multi-label classification, it is common for the classes to be unbalanced.
-We would like to show that the tree loss works well for unbalanced data.
-A good way to do that is to change the distribution that $y_i$ is drawn from,
-and a geometric distribution is a likely good alternative.
-
-The tree loss can work well even when the weight matrix has non-linear intrinsic structure.
-We should adapt the $\w*_i$ vectors to sit on a manifold instead of a hyperplane to demonstrate this fact.
-
-\subsection{Real world data}
-% \fixme{Write a description of the experiment.}
-In this experiment, we will compare the tree loss with softmax corss entropy and simloss on some real world data.
-We conduct image classification tasks on CIFAR-100 dataset and ImageNet dataset and emoji prediction task on twitter dataset.
-Our goal is to investigate the effects of changing the loss function on our example experiments.
-We do not focus on if we have state-of-the-art performance on specific models, but rather on the evaluation of the tree loss as a general loss function which can be applied on various tasks.
-These three tasks and datasets are typical examples for using cross entropy loss.
-
-\subsubsection{CIFAR-100 Data}
-We use CIFAR-100 dataset which has 100 classes for image classification.
-We also get word embeddings from a word2vec model pretrained on Google News \cite{Mikolov2013EfficientEO} of class names and construct tree structure and calculate similarity between classes from word embeddings.
-Four class names do not yield a word embedding and are therefore eliminated.
-
-To evaluate our tree loss, we rely on three metrics: accuracy (Acc.) which focus on correct predictions and similarity accuracy (Similarity Acc.) which focus on the similarity of predicted and target class and superclass accuracy (SA).
-Every example in CIFAR-100 dataset has a main class and a superclass.
-Superclass accuracy is the fraction of examples that are correctly put into the corresponding superclass.
-We take ResNet20 model \cite{He2016DeepRL} and SGD optimizer with a learning rate 0.1 and a batch size of 1021. 
-We stop early to get the highest accuracy on validation set.
-
-\begin{table}[]
-\caption{Test results with early stopping on CIFAR-100 dataset. Best values are written in bold.} \label{cifar100}
-\begin{center}
-\begin{tabular}{@{}cccc@{}}
-\toprule
-\multirow{2}{*}{Loss} & \multicolumn{3}{c}{Test}    \\ \cmidrule(l){2-4} 
-                      & Acc. & Similarity Acc. & SA \\ \cmidrule(r){1-1}
-Tree Loss       & \textbf{52.78}     &  \textbf{65.90}               &  \textbf{62.55}  \\
-Cross Entropy         &  51.87    &   65.58              &  62.14  \\
-SimLoss               &    52.43  &    65.82             & 62.34  \\\bottomrule
-\end{tabular}
-\end{center}
-\end{table}
-
-\subsubsection{ImageNet Data}
-ImageNet dataset \cite{Russakovsky2015ImageNetLS} has 1000 classes and many of the classes are similar and related, we consider the internal class structure has a impact on performance of loss function.
-We use class names to get class representations from a pretrained FastText model.
-We take ResNet50 model \cite{He2016DeepRL} trained on 1.28 mollion training images and evaluated on the 50k validation images and SGD optimizer with a learning rate 0.01.
-We use top1 accuracy and top5 accuracy to evaluate our loss functions.
-
-\begin{table}[]
-\caption{Validation results on ImageNet dataset. Best values are written in bold.} \label{imagenet}
-\begin{center}
-\begin{tabular}{@{}ccc@{}}
-\toprule
-\multirow{2}{*}{Loss} & \multicolumn{2}{c}{Validation} \\ \cmidrule(l){2-3} 
-                      & Top1 Acc.      & Top5 Acc.     \\ \cmidrule(r){1-1}
-Tree Loss       & \textbf{76.52} & \textbf{92.92} \\
-Cross Entropy         & 75.30          & 92.36         \\
-SimLoss               & 76.24          & 92.83         \\ \bottomrule
-\end{tabular}
-\end{center}
-\end{table}
+}
+
+\subsubsection{Experiment II: Parameter Norms}
+
+Corollary \ref{ref:cor:A} suggests that the norm of the parameter matrix is what controls convergence rate of SGD,
+and the proof of our main result in Theorem \ref{} relies on bounding this norm.
+In this experiment, we directly measure the norm of the parameter matrices and show that $\lF{V}$ is significantly less than the $lF{W}$,
+justifying the good convergence rates we observed in Synthetic Experiment I above.
+We set $n=1000$, $d=10$, and $\sigma=1$, and vary the number of classes $k$.
+Figure \ref{fig:synth:norm} shows that $\lF{\star V}$ grows much slower than $\lF{\star W}$.
+Notice in particular that $\lF{\star W}$ grows at the rate $O(\sqrt{k})$ and $\lF{\star V}$ grows at a rate strictly less than $o(\sqrt{k})$ as our theory predicts.
+
+\begin{figure}
+\includegraphics[width=\columnwidth,height=1.5in]{fig/images/class_v_norm.png}
+\caption{As we increase the number of classes $k$,
+    $\lF{\star V}$ grows significantly slower than $\lF{\star W}$.
+    Since the convergence rate of SGD is proportional to $\lF{\cdot}$ (by Corollary \ref{ref:cor:A}),
+    the tree loss converges faster than the standard cross entropy loss. 
+    }
+\label{fig:synth:norm}
+\end{figure}
+
+\subsubsection{Experiment III: Tree Shapes}
+
+In this experiment, we study how the shape of our tree structure impacts performance.
+We set $n=1000$, $d=10$, $k=100$, and $\sigma=1$.
+We use a relatively large number of classes $k$ compared to our standard problem in Section \ref{sec:synth:1} above in order to ensure that we have enough classes to generate meaningfully different tree structures.
+The basic trends we observe are consistent for all other values of $n$, $d$, and $\sigma$.
+
+Recall that the cover tree has a parameter \texttt{base} which controls the rate of expansion between layers of the tree.
+As seen in Figure \ref{fig:ct:height}, reducing \texttt{base} increases the height of the tree and increasing \texttt{base} reduces the height of the tree.
+This will affect the performance of our tree loss because taller trees result in more parameter sharing.
+Figure \ref{fig:ct:acc} plots the accuracy of the tree loss as a function of the \texttt{base} hyperparameter.
+Across all ranges, the tree loss outperforms the cross entropy loss.
+Interestingly, the tree loss's accuracy is maximized when $\texttt{base}\approx1.3$.
+The original cover tree paper \citep{beygelzimer2006cover} also found that a \texttt{base} of 1.3 resulted in the fastest nearest neighbor queries.
+It's unclear why 1.3 has this good quality,
+but the fact that this constant results in good computational performance for nearest neighbor queries and good statistical performance in the tree loss, two rather different use cases, suggests that there is something fundamental going on here that we don't yet fully understand.
+
+\begin{figure}
+            \includegraphics[width=\columnwidth,height=1.5in]{fig/new_img/height_vs_base.png}
+            \caption{The height of a cover tree varies inversely with it's \texttt{base} hyperparameter.}
+            \label{fig:ct:height}
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=\columnwidth,height=1.5in]{fig/new_img/accuracy_vs_base.png}
+            \caption
+            {The tree loss outperforms the standard cross entropy loss for all values of \texttt{base}, but the performance is maximized when $\texttt{base}\approx1.3$.}
+            \label{fig:ct:acc}
+\end{figure}
+
+\subsubsection{Experiment IV: Metric Quality}
+\label{sec:synth:eps}
+
+Recall that our theoretical results state that the convergence rate of SGD depends on a factor $\lambda$ that measures how well our metric over the class labels is able to predict the distances between the true parameter vectors.
+In this experiment, we study the effect of this $\lambda$ parameter on prediction accuracy.
+
+We fix the following problem hyperparameters:
+$n=100$, $d=64$, $k=10$, and $\sigma=1$.
+Then we construct a bad parameter matrix $\bad W$ using the same procedure we used to construct the optimal parameter matrix;
+that is,
+\begin{equation}
+    \bad W \sim \mathcal N ^ {k\times d}
+    .
+\end{equation}
+Each row $\bad \w_i$ of $\bad W$ is now a $d$ dimensional random vector that has absolutely no relation to the true parameter vector.
+Next, we define a family of ``$\epsilon$-bad'' parameter vectors that mix between the perfectly bad and perfectly good parameter vectors:
+\begin{equation}
+    \w^\epsilon_i = (1-\epsilon) \w^*_i + \epsilon \bad\w_i.
+\end{equation}
+Finally, we define our $\epsilon$-bad distance metric as
+\begin{equation}
+    d_\epsilon(i,j) = \ltwo{\w_i^\epsilon - \w_j^\epsilon}
+\end{equation}
+and build our cover tree structure using $d_\epsilon$.
+When $\epsilon=0$, this cover tree structure will be the ideal structure and $\lambda$ will be equal to 1;
+when $\epsilon=1$, this cover tree structure will be maximally bad, and $\lambda$ will be large.
+
+Figure \ref{fig:synth:eps} shows the performance of the tree loss as a function of $\epsilon$.
+Remarkably, the tree loss outperforms the standard cross entropy loss even when using a perfectly bad tree structure (i.e. when $\epsilon=1$).
+This surprising empirical finding actually agrees with our theoretical results in two ways.
+First, Lemmas \ref{lemma:starV} and \ref{lemma:starU} together imply that that $\lF{\star V} = O(\lF{\star W})$,
+and so no tree structure can perform asymptotically worse than the standard cross entropy loss.
+Second, when $\epsilon=1$ and we have a perfectly random tree structure,
+the distance $d_\epsilon$ can still be embedded into the ideal metric $d$ with some large (but finite!) $\lambda$.
+Asymptotically, Lemma \ref{lemma:main} then implies that SGD converges at the rate $O(\sqrt{k^{1-1/c}})$,
+which is less than the convergence rate of the standard cross entropy loss.
+\fixme{replace lemma with theorem}
+
+\begin{figure}
+\includegraphics[width=\columnwidth,height=1.5in]{fig/new_img/loss_vs_structure.png}
+\caption{
+As $\epsilon\to1$, the quality of our metric for generating the tree structure decreases.
+But even with a perfectly random tree structure,
+the tree loss still outperforms the cross entropy loss.
+}  
+\label{fig:synth:eps}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Real World Data}
+
+\begin{table*}
+    \centering
+    \input{fig/real_world.tex}
+    \caption{Experimental results on real world datasets.  For all accuracy measures, larger numbers are better.  The tree loss achieves the best results in all cases.}
+    \label{table:results}
+\end{table*}
+
+We now validate the tree loss on real world image (CIFAR100, ImageNet) and text (Twitter) data.
+For each dataset, we report standard top-k accuracy scores,
+and the less well known \emph{superclass accuracy} (SA) score.
+SA is a generalization of the top-1 accuracy proposed by the simloss paper \citep{Kobs2020SimLossCS}.
+The idea is that misclassifying a \texttt{sheepdog} as a \texttt{husky} should be penalized less than misclassifying a \texttt{sheepdog} as a \texttt{bus} because the \texttt{sheepdog} and \texttt{husky} classes are more similar to each other.
+
+Table \ref{table:results} shows that on each of these datasets and for each metric,
+the tree loss outperforms the baseline cross entropy loss and simloss.\footnote{We do not evaluate against the hierarchical softmax on these datasets for computational reasons.
+The results on the synthetic data, however, suggest that the hierarchical softmax would have performed poorly.}
+The remainder of this section describes the experimental procedures for each dataset in detail.
+
+\subsubsection{CIFAR100}
+
+CIFAR100 is a standard image dataset with 100 classes \citep{krizhevsky2009learning}.
+It is more difficult than MNIST and CIFAR-10,
+but small and so less computationally demanding than ImageNet.
+
+We follow the procedure used in the SimLoss paper \citep{Kobs2020SimLossCS} in this experiment.
+We generate our distance metric over the class labels using a word2vec model \citep{Mikolov2013EfficientEO} pretrained on GoogleNews.
+The distance between class labels is defined to be the distance between their corresponding word2vec embeddings.
+There are 4 class labels with no corresponding word2vec embedding,
+and so following the simloss paper we discard these classes.
+
+We train 3 ResNet20 models on CIFAR100 \citep{He2016DeepRL} using hyperparameters specified in the original paper.
+The only difference between the three models is the final layer:
+one model uses the standard cross entropy loss, one uses the tree loss, and one uses the simloss.
+The results shown in Table \ref{table:results} shows that the tree loss significantly outperforms the other losses.
+
+\subsubsection{ImageNet}
+
+ImageNet is the gold-standard dataset for image classification tasks \citep{Russakovsky2015ImageNetLS}.
+It has 1000 class labels and 1.2 million images.
+
+We generate our distance metric over the image labels using a pretrained fastText model \citep{bojanowski2017enriching}.
+We use fastText rather than word2vec because many of the class labels contain words not in the word2vec models' vocabulary;
+since fastText is naturally able to handle out-of-vocabulary words,
+there is not need to discard class labels like we did for CIFAR100.
+Many ImageNet class label names contain multiple words,
+and for these classes we generate the embedding with a simple average of the fastText embedding over all words.
+
+We again train a ResNet50 model \citep{He2016DeepRL} using standard hyperparameters, replacing only the last layer of the model.
+As with CIFAR100, Table \ref{table:results} shows that the tree loss significantly outperforms the other losses.
+Since the publication of ResNet50 in 2016,
+there have been many newer network architectures with better performance on ImageNet \citep[e.g.][]{howard2017mobilenets,huang2017densely,pmlr-v97-tan19a}.
+We unfortunately did not have sufficient computational resources to train these more modern models with the tree loss,
+and we emphasize that we are not trying to compete directly with these network architectures to achieve state-of-the-art performance.
+Instead, our goal is to show that for a given network architecture,
+replacing the cross entropy loss with the tree loss results in improved performance.
 
@@
 
-We apply the tree loss on emoji prediction in twitter dataset. 
-Emojis are popular to express emotions in text messages and tweets are a wildely used social media over the world. 
-We trained the multilingual BERT model on tweets to predict which emoji corresponds to a piece of text is best for measuring the emotional content in the text. 
-Our 1660 target emojis are defined by emo2vec \cite{Eisner2016emoji2vecLE}.
-
-We collect all tweets \cite{Izbicki2019GeolocatingTI} in any languages sent from anywhere in the world and filter the tweets with target emojis. 
-For each tweet, we replace all user mentions with a special token \texttt{\text{<}mention\text{>}} and all URLS with a special token \texttt{\text{<}url\text{>}} and delete all emojis. 
-We keep all hashtags and duplicate the tweet once for each emoji if a tweet has multiple emojis. 
-Then we split the dataset into training validadtion and testing sets by user id to ensure each user appears in only one set in order to prevent data leakage.
-
-We take the multilingual BERT model \cite{Feng2020LanguageagnosticBS} pretrained on data from 109 distinct languages which achieves state-of-the-art performance on a wide variety of natural language tasks.
-We get the embeddings of 1660 target emojis defined by emo2vec.
-
-\begin{table}[h]
-\small
-\caption{Validation and test results of emoji prediction task on twitter dataset. Best values are written in bold.} \label{twitter}
-\begin{center}
-\begin{tabular}{@{}lcccc@{}}
-\toprule
-\multicolumn{1}{c}{\multirow{2}{*}{Loss}} & \multicolumn{2}{c}{VALIDATION} & \multicolumn{2}{c}{TEST}       \\ \cmidrule(l){2-5} 
-\multicolumn{1}{c}{}                      & Acc.       & SA       & Acc.      & SA             \\ \cmidrule(r){1-1}
-Tree Loss                           &   \textbf{20.81}    &   \textbf{50.26}  &  \textbf{20.96}    &   \textbf{50.45}        \\
-Cross Entropy                             &   19.90    &   48.27  &  19.95    &   48.33        \\
-SimLoss                                   &   19.91    &   48.25  &  19.96    &   48.32         \\ \bottomrule
-\end{tabular}
-\end{center}
-\end{table}
-
-\subsubsection{Results}
-We evaluate the tree loss on image data(CIFAR100, ImageNet) and text data(Twitter) and the tree loss outperforms cross entropy loss and Simloss on metrics.
-Table \ref{cifar100} shows the results of three loss functions for the test set of the CIFAR-100 dataset.
-Similarity accuracy and superclass accuracy pay attention to more similar classes and the tree loss get higher accuracy.
-Table \ref{imagenet} shows the results for the valdidation set of ImageNet dataset.
-ImageNet has 1000 classes and many classes are semantically  similar.
-The tree loss incorporates the similarities to training and get a higher top1 accuracy and top5 accuracy.
-The emojis of Twitter dataset is typically unbalanced and the tree loss works well for unbalanced data.
-Table \ref{twitter} shows the results for validation set and test set of twitter dataset.
-The tree loss achieve the best performance on accuracy and similarity accuracy.
+We now consider the problem of predicting the emotions of twitter text.
+This is a very different domain than the image problems considered above,
+and demonstrates that the tree loss works across many domains.
+We use the dataset collected by \citep{stoikos2020multilingual} for analyzing emotional response to Covid19 on Twitter.
+This dataset contains all geolocated tweets written in any language sent over the 6 month period between 1 January 2020 and 1 July 2020.
+Tweets in the dataset are preprocessed to have all emojis, usernames, and urls removed from the text,
+and then the goal is to predict the emoji given only the remaining text.
+Since most emojis represent emotions,
+the task of emoji prediction serves as a proxy for emotion prediction.
+
+We generate our distance metric over the class labels using the pretrained emoji2vec model \citep{Eisner2016emoji2vecLE},
+which associates each emoji with a vector embedding.
+We then follow the procedure in \citet{stoikos2020multilingual} to train multilingual BERT models \citep{Feng2020LanguageagnosticBS} with the last layers replaced by the three different loss functions.
+Table \ref{table:results} shows the tree loss significantly outperforming the baseline models.
+%Furthermore, the original BERTmoticon model proposed in \citet{stoikos2020multilingual} is only able to predict 80 emoji categories and ignores all other emoji,
+%a restriction they found necessary due to the sample complexity of including more emoji in the classsification problem.
+%But our model using the tree loss is able to predict over 1600 different emoji and still achieves better accuracy than the original BERTmoticon.
 
 \section{Conclusion}
-In this paper, we have presented the tree loss, a drop-in replacement for the cross entropy loss that incorporated class relations. 
-We use properties of stochastic gradient descent to provide the theoretical justifications that the generalization error of the tree loss is better. 
-The tree loss works by re-parameterizing the parameter matrix for cross entropy loss and can be easily implement. 
-We evaluate our tree loss on synthetic data and typically real world data. 
-From the results of experiments, we found the tree loss improve the performance significantly and  help with predicting more similar classes if the model misclassified an example. 
-In our analysis, since the tree loss can obtain background knowledge of classes, it works well for tasks with many classes and data with unbalanced classes.
+The tree loss is a drop-in replacement for the cross entropy loss for multiclass classification problems.
+It can take advantage of background knowledge about the underlying class structure in order to improve the convergence rate of SGD.
+
+Both our theoretical and empirical results show that the tree loss improves performance over the cross entropy loss in a wide range of circumstances.
+Remarkably, we observe that the tree loss improves performance even when our assumptions about the underlying class structure are perfectly wrong (see Section \ref{sec:synth:eps}).
+We therefore suggest that you replace the cross entropy loss with the tree loss on all of your multiclass problems.
+%there are no downsides there is essentially no downside to using the tree loss as a drop-in replacement for the cross entropy loss.
+%Even if you have no a-priori knowledge about the class structure,
+%and are forced to use a random tree,
+%the tree loss can still improve classification accuracy.
 
@@
 
+\appendix
+\section{Related loss functions}
+
+Many alternatives to the cross entropy loss have been proposed.
+
+The tree loss is superficially related to the hierarchical softmax (HSM) because both losses are defined based on tree structures.
+\cite{morin2005hierarchical} introduced the HSM to speed up the computational time of neural network training,
+but the tree loss is used to improve sample efficiency rather than computational efficiency.
+
+\cite{mikolov2013distributed} introduce the word2vec model and experiment with using both the hierarchical softmax and cross entropy with negative sampling.
+They conclude that negative sampling has the best performance both computationally and statistically.
+Since the tree loss is a simple extension of the cross entropy loss,
+negative sampling can be used to speed up the cross entropy loss as well.
+
+\cite{bojanowski2017enriching} introduce the fastText extension of the word2vec model, which uses sub-word information to improve sample efficiency.
+They do not provide any theoretical justification for why their technique should improve sample efficiency,
+but their technique is computationally very similar to the tree loss,
+and so our technique may be able to provide the first theoretical justification for their work.
+
+HSM:
+\begin{equation}
+    \label{eq:xentropy}
+    \ell(W;(\x,y)) = - \log \prod_{k\in P_y}\frac {\exp(-\trans\w_k \x)}{j\in L_k \exp(-\trans \w_j \x)}
+\end{equation}
+where $P_y$ is path from root to node of Huffman Tree,
+$L_k$ are nodes on the level where $k$ are
+
+The hierarchical softmax loss aims to improve computation efficiency. 
+\cite{Peng2017IncrementallyLT} introduce a training method incrementally train the hierarchical softmax function for neural network language models.
+They also provide a new stochastic gradient based method to update all the word vectors and their experimental results show the incremental training can save a lot of time.
+\cite{Jiang2017ExplorationOT} explore the tree-based hierarchical softmax method and reform its architecture, making it compatible with modern GPUs.
+\cite{Yang2017OptimizeHS} gives a theoretic analysis on how should organize the hierarchical tree by treating the tree structure as a parameter of the training objective function.
+They propose SemHuff, a new tree constructing scheme based on adjusting the Huffman tree with word similarity knowledge.
+Their experiments results also show that word embeddings trained with optimized hierarchical tree can give better results in various tasks.
+
+\cite{Mohammed2018EffectivenessOH} compare the performance of normal softmax and hierarchical softmax in large scale classification tasks. 
+Normal softmax is computationally expensive for large scale datasets with large number of possible outputs.
+Their experimental results show that normal softmax and hierarchical softmax underperforms on datasets with large number of labels.
+That is also one of our motivations of the tree loss function. 
+Compared to classic cross entropy loss function, the tree loss function performs better on datasets with large number of labels.
+Extreme multi-label classification is difficult, but organizing labels as a tree can handle this problem.
+
+% \fixme{Write a detailed description of the sim loss}
+
+SimLoss \cite{Kobs2020SimLossCS} is similarity based loss function which incorporates class similarities to support the training of neural network classifiers.
+Cross entropy loss assumes only one class is correct and punishes every misclassification, while Simloss indicates classes have similarities and classifying a target as a similar class is better.
+When calculating the loss function, instead of only taking the probability vector at the target index Simloss also adds the product of similarity between target and other classes and probability vector at the corresponding class.
+Non zero values of similarity matrix lead to smaller losses when the network gives a high score to classes similar to the correct one. 
+It would allow the classifier to make less severe mistakes as it learns to predict similar classes.
+However, SimLoss does not have any theoretical justification to prove why it can outperform cross entropy.
+SimLoss has a hyperparameter lower bound that controls the minimal class similarity that should have an impact on the network punishment.
+Any similarities below lower bound will be all zeros.
+It implies SimLoss would cost more time to fine tune.
+Our tree loss define a tree structure which can be obtained automatically and it is time-saving.
+\begin{align}
+    L_{Simloss}&=-\frac{1}{N}\log(\sum_{k=1}^{C}S_{y_i,k}\cdot p_i[k])\\
+    % L_{Simloss}=-\frac{1}{N}\log(\sum_{k=1}^{C}S_{y_i,k}\cdot\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)})
+    p_i&=\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)}
+\end{align}
+
 \end{document}

### 2021-10-14 paper/regularization.tex
changes

--- 2021-10-13 paper/paper.tex
@@
-\documentclass[twoside]{article}
+\documentclass[10pt]{article}
 
-\usepackage{aistats2022}
-% If your paper is accepted, change the options for the package
-% aistats2022 as follows:
-%
-%\usepackage[accepted]{aistats2022}
-%
-% This option will print headings for the title of your paper and
-% headings for the authors names, plus a copyright note at the end of
-% the first column of the first page.
-
-% If you set papersize explicitly, activate the following three lines:
-%\special{papersize = 8.5in, 11in}
-%\setlength{\pdfpageheight}{11in}
-%\setlength{\pdfpagewidth}{8.5in}
-
-% If you use natbib package, activate the following three lines:
-%\usepackage[round]{natbib}
-%\renewcommand{\bibname}{References}
-%\renewcommand{\bibsection}{\subsubsection*{\bibname}}
-
-% If you use BibTeX in apalike style, activate the following line:
-%\bibliographystyle{apalike}
 \usepackage[margin=1in]{geometry}
@@
 \usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{mwe}
+\usepackage{subfigure}
 
@@
 \newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}
 \newtheorem{fact}{Fact}
@@
 
-\renewcommand{\star}[1]{{#1}^{*}}
 \newcommand{\trans}[1]{{#1}^{T}}
 \newcommand{\loss}{\ell}
+\newcommand{\Loss}{\mathcal{L}}
 \newcommand{\aaa}{\mathbf a}
@@
 
-\newcommand{\ignore}[1]{}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% If your paper is accepted and the title of your paper is very long,
-% the style will print as headings an error message. Use the following
-% command to supply a shorter title of your paper so that it can be
-% used as headings.
-%
-%\runningtitle{I use this title instead because the last one was very long}
-
-% If your paper is accepted and the number of authors is large, the
-% style will print as headings an error message. Use the following
-% command to supply a shorter version of the authors names so that
-% they can be used as headings (for example, use only the surnames)
-%
-%\runningauthor{Surname 1, Surname 2, Surname 3, ...., Surname n}
-
-\twocolumn[
-
-\aistatstitle{The Tree Loss: Improving Generalization with Many Classes}
-
-\aistatsauthor{ Yujie Wang \And Michael Izbicki  }
-
-\aistatsaddress{ Claremont Graduate University \And  Claremont McKenna College } ]
-
-\begin{abstract}
-    %Multiclass logistic regression has generalization error $O(\sqrt{k/n})$, where $k$ is the number of classes and $n$ the number of data points.
-
-    Multiclass classification problems often have many semantically similar classes.
-    For example, 90 of ImageNet's 1000 classes are for different breeds of dog.
-    We should expect that these semantically similar classes will have similar parameter vectors,
-    but the standard cross entropy loss does not enforce this constraint.
-    %These classes are semantically similar to each other,
-    %and so we expect their learned parameter vectors to also be similar.
-    %Unfortunately, the standard cross entropy loss function does not enforce this constraint.
-    %It has generalization error $O(\sqrt{k/n})$, where $k$ is the number of classes and $n$ the number of data points.
-
-    We introduce the tree loss as a drop-in replacement for the cross entropy loss.
-    The tree loss re-parameterizes the parameter matrix in order to guarantee that semantically similar classes will have similar parameter vectors.
-    Using simple properties of stochastic gradient descent,
-    we show that the tree loss's generalization error is asymptotically better than the cross entropy loss's.
-    We then validate these theoretical results on synthetic data, image data (CIFAR100, ImageNet), and text data (Twitter).
-
-    %Whereas The standard cross entropy loss function has generalization error $O(\sqrt{k/n})$,
-    %where $k$ is the number of classes and $n$ the number of data points.
-
-%Softmax Cross Entropy loss function treats every class equally while classes often have an internal structure. 
-%We introduce cover tree loss function which takes advantage of this internal class structure.
-%The cover tree loss works by reparameterizing the weight matrix for the cross entropy loss.
-%Compare to cross entropy which has generalization error $O(\sqrt{k/n})$, the generalization error of cover tree loss is $O(\sqrt{1/n})$ which is independent of the number of classes. 
-%We provide the theoretical justification and conduct extensive experiments on fully synthetic data and real world data. 
-%For real world data, we take CIFAR100 dataset, IMAGENET dataset and TWITTER dataset.
-%The cover tree loss outperforms than cross entropy loss function on metrics.
-\end{abstract}
+\begin{center}
+\Huge
+Tree Regularization
+\end{center}
 
@@
 
-When people do a multi-class classification task, the standard loss function is cross entropy.
-The mechanism of cross entropy loss function is to maximize the assigned target class probability and punishes every misclassification equally, independent of some other information about the predicted class.
-However, classes often have an internal structure. 
-For example, dog and cat belong to same 'parent': animal and many transportations have same 'parent' while they have different brothers.
-Take the internal structure in the training procedure would allow the classifier to make less sever mistakes as it learns to predict similar classes.
-In terms of theoretical result, the parameter matrix of cross entropy loss is bounded by $\sqrt{k}B$ (where $k$ is the number of classes) and for $n$ data points, the generalization error is $O(\sqrt{k/n})$ which is dependent on $k$.
+This note introduces \emph{tree regularization}.
+For multi-class learning problems, tree regularization achieves a generalization error of $O(\sqrt{\log k / m})$ which is comparable to the tree loss's error of $O(\sqrt{1/m})$.
+Tree regularization has several advantages over the tree loss, however:
+\begin{enumerate}
+    \item
+        It can work with any loss function.
+        For example, we can apply tree regularization to multiple regression, multi-label prediction, and objection detection problems.
+    \item
+        The optimal tree structure can be learned at training time and the problem remains convex.
+    \item
+        The analysis works for all optimization algorithms, not just stochastic gradient descent.
+\end{enumerate}
 
-In this paper, we introduce the tree loss which take advantage of the internal structure bewtween classes.
-The idea of the tree loss is that we use tree structure to reduce the bound of the size of the parameter space and then the generalization error of the tree loss is $O(\sqrt{1/n})$ which is independent of $k$.
-In the tree loss, we take a tree structure which defined by similarity between classes to re-parameterize the weight matrix for the cross entropy loss.
-We incorporate class similarities with loss function to make the model learn more information about classes.
-It can benefit the tasks on unbalanced datasets.
-Take a emoji prediction task as an example, people often use emojis in tweets.
-However, some emojis are popular and some emojis are rarely used.
-This leads to an unbalanced tweets data and there is not enough training data for unpopular emojis.
-The tree loss can learn more information and work well for unbalanced data.
+\section{Notation}
+Many regularized learning problems take the form
+\begin{equation}
+    \argmin_{W} \Loss(Z ; W) + \lambda R(W)^2
+\end{equation}
+where
+$Z = \{z_1, ..., z_m\}$ is the training set,
+$W$ is the model parameters,
+\begin{equation}
+    \Loss(Z ; W) = \frac 1m \sum_{i=1}^m \loss(z_i; W)
+\end{equation}
+and $R : W \to \R^+$ is a regularization function.
 
-Our contributions are as below:
-\begin{itemize}
-    \item [1] 
-    We introduce the tree loss which take advantage of internal structure between all classes.
-    \item [2] 
-    We provide theoretical justification that the generalization error of the tree loss is independent of the number of classes.
-    \item [3]
-    We evaluate our tree loss on experiments. One is experiment on fully synthetic data which is designed to be convex. The another one is on real world data: CIFAR100, IMAGENET and TWITTER dataset.
+We assume that the parameters $W$ are given in matrix as a $k \times d$ matrix.
+In the multi-class prediction problem,
+each row $i$ is a $d$ dimensional vector that represents the parameter matrix for class $i$.
 
-\end{itemize}
+\section{Tree Regularization}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Tree Loss}
-
-\subsection{Problem Setting}
-
-Assume we are solving a standard multi-class classification problem with $k$ classes and $d$ input feature dimensions.
-The cross entropy loss (also called the logistic loss) is the standard loss function for this problem.
-It is defined to be
+The Tree Regularizer is defined to be
 \begin{equation}
-    \label{eq:xentropy}
-    \ell(W;(\x,y)) = - \log \frac {\exp(-\trans\w_y \x)}{\sum_{j=1}^k \exp(-\trans \w_j \x)}
-\end{equation}
-where for each class $i\in[k]$,
-$\w_i : \R^d$ is the parameter vector associated with class $i$;
-the variable $W : \R^{k \times d} = (\w_1; \w_2; ...; \w_k)$ is the full parameter matrix;
-$\x : \R^d$ is the feature vector;
-and $y \in [k]$ is the class label.
-
-\subsection{The Tree Loss}
-
-The tree loss works by reparameterizing the weight matrix for the cross entropy loss.
-Intuitively, our goal is to enforce that semantically similar labels will have similar weight vectors.
-
-The reparameterization is defined according to a \emph{label tree} structure that captures the similarity between labels.
-Every class is represented by a leaf node in the label tree,
-and internal nodes represent \emph{pseudo-classes} that group the existing classes into a logical hierarchy.
-At this point, we assume that the label tree structure is given a priori, and in Section \ref{sec:bias-var} we discuss methods for generating this structure and their tradeoffs.
-Figure \ref{fig:labeltree} shows an example label tree for a classification problem with 9 classes.
-
-\begin{figure}
-    \resizebox{\columnwidth}{!}{
-\begin{tikzpicture}
-    [ level distance=1.5cm
-    , level 1/.style={sibling distance=3cm}
-    , level 2/.style={sibling distance=1.5cm}
-    ]
-\node {\textit{pseudo1}}
-    child {node {\textit{pseudo2}}
-      child {node {\texttt{boat}}}
-      child {node {\texttt{plane}}}
-      child {node {\textit{pseudo3}}
-        child {node {\texttt{car}}}
-        child {node {\texttt{truck}}}
-        child {node {\texttt{van}}}
-        child {node {\texttt{motorcycle}}}
-      }
-      }
-    child {node {\texttt{building}}}
-    child {node {\textit{pseudo4}}
-      child {node {\texttt{cat}}}
-      child {node {\texttt{dog}}}
-    };
-\end{tikzpicture}
-}
-    \caption{\fixme{caption}}
-    \label{fig:labeltree}
-\end{figure}
-
-We parameterize the weight vectors from the label tree as follows.
-For each leaf node $i$ (equivalently for each class $i$),
-we let the sequence $P_i$ denote the path from the leaf node to the root.
-For example, using the label tree above,
-we have
-
-\begin{equation}
-\begin{split}
-    P_{\texttt{truck}} &= (\texttt{truck}, \textit{pseudo3}, \textit{pseudo2}, \textit{pseudo1} ) \\
-    P_{\texttt{cat}} &= (\texttt{cat}, \textit{pseudo4}, \textit{pseudo1} )
-\end{split}
+    R(W, V, A) 
+    = \sum_{i} \left\lVert \w_i - \sum_{j}A_{i,j} \vv_j \right\lVert
+    = \sum_{i} \left\lVert \w_i - A_i V \right\lVert
 \end{equation}
 
-% \end{equation}
-
-Next, we associate a vector $\vv_i$ to each leaf and internal node $i$ in the tree structure.
-In particular, there is a vector $\vv_i$ for each class and for each pseudo-class.
-Finally, we reparameterize the weights for the cross entropy loss as the sum of the vectors along the paths.
-Specifically, we set the weight vector for class $j$ to be 
-\begin{equation}
-    \label{eq:covertree-reparam}
-    \w_j = \sum_{k\in P_j} \vv_k
-    .
-\end{equation}
-Substituting \eqref{eq:covertree-reparam} into \eqref{eq:xentropy} gives us the final tree loss
-\begin{equation}
-    \ell(V;(\x,y)) = - \log \frac {\exp(-\sum_{k\in P_y}\trans\vv_k \x)}{\sum_{j=1}^k \exp(- \sum_{k\in P_j}\trans\vv_k \x)}
-\end{equation}
-where $V=(\vv_1,...,\vv_k)$,
-and our goal is to minimize $\ell$ with respect to $V$.
-Note that this loss can easily be computed in libraries like pytorch or tensorflow with the standard cross entropy loss functions.
-The only change needed is to define the loss in terms of the sum of vectors $V$ instead of a variable tensor $W$.
-
-\subsection{Related loss functions}
-
-Many alternatives to the cross entropy loss have been proposed.
-
-The tree loss is superficially related to the hierarchical softmax (HSM) because both losses are defined based on tree structures.
-\cite{morin2005hierarchical} introduced the HSM to speed up the computational time of neural network training,
-but the tree loss is used to improve sample efficiency rather than computational efficiency.
-
-\cite{mikolov2013distributed} introduce the word2vec model and experiment with using both the hierarchical softmax and cross entropy with negative sampling.
-They conclude that negative sampling has the best performance both computationally and statistically.
-Since the tree loss is a simple extension of the cross entropy loss,
-negative sampling can be used to speed up the cross entropy loss as well.
-
-\cite{bojanowski2017enriching} introduce the fastText extension of the word2vec model, which uses sub-word information to improve sample efficiency.
-They do not provide any theoretical justification for why their technique should improve sample efficiency,
-but their technique is computationally very similar to the tree loss,
-and so our technique may be able to provide the first theoretical justification for their work.
-
-HSM:
-\begin{equation}
-    \label{eq:xentropy}
-    \ell(W;(\x,y)) = - \log \prod_{k\in P_y}\frac {\exp(-\trans\w_k \x)}{j\in L_k \exp(-\trans \w_j \x)}
-\end{equation}
-where $P_y$ is path from root to node of Huffman Tree,
-$L_k$ are nodes on the level where $k$ are
-
-% \fixme{Read the papers mentioned above.  Verify that you agree with the things I wrote.  Then, write a detailed mathematical description of the HSM loss and contrast it with the cover tree loss.}
-
-% \fixme{Read 5-10 additional papers about the hierarchical softmax.
-For each paper, write a paragraph describing the paper's contributions and how it relates to the cover tree loss.
-For the final paper we will reference these papers.
-We will have to trim down the notes that you write for this task, but it's useful when writing the paper to have detailed notes about references.}
-
-The hierarchical softmax loss aims to improve computation efficiency. 
-\cite{Peng2017IncrementallyLT} introduce a training method incrementally train the hierarchical softmax function for neural network language models.
-They also provide a new stochastic gradient based method to update all the word vectors and their experimental results show the incremental training can save a lot of time.
-\cite{Jiang2017ExplorationOT} explore the tree-based hierarchical softmax method and reform its architecture, making it compatible with modern GPUs.
-\cite{Yang2017OptimizeHS} gives a theoretic analysis on how should organize the hierarchical tree by treating the tree structure as a parameter of the training objective function.
-They propose SemHuff, a new tree constructing scheme based on adjusting the Huffman tree with word similarity knowledge.
-Their experiments results also show that word embeddings trained with optimized hierarchical tree can give better results in various tasks.
-
-\cite{Mohammed2018EffectivenessOH} compare the performance of normal softmax and hierarchical softmax in large scale classification tasks. 
-Normal softmax is computationally expensive for large scale datasets with large number of possible outputs.
-Their experimental results show that normal softmax and hierarchical softmax underperforms on datasets with large number of labels.
-That is also one of our motivations of the tree loss function. 
-Compared to classic cross entropy loss function, the tree loss function performs better on datasets with large number of labels.
-Extreme multi-label classification is difficult, but organizing labels as a tree can handle this problem.
-
-% \fixme{Write a detailed description of the sim loss}
-
-SimLoss \cite{Kobs2020SimLossCS} is similarity based loss function which incorporates class similarities to support the training of neural network classifiers.
-Cross entropy loss assumes only one class is correct and punishes every misclassification, while Simloss indicates classes have similarities and classifying a target as a similar class is better.
-When calculating the loss function, instead of only taking the probability vector at the target index Simloss also adds the product of similarity between target and other classes and probability vector at the corresponding class.
-Non zero values of similarity matrix lead to smaller losses when the network gives a high score to classes similar to the correct one. 
-It would allow the classifier to make less severe mistakes as it learns to predict similar classes.
-However, SimLoss does not have any theoretical justification to prove why it can outperform cross entropy.
-SimLoss has a hyperparameter lower bound that controls the minimal class similarity that should have an impact on the network punishment.
-Any similarities below lower bound will be all zeros.
-It implies SimLoss would cost more time to fine tune.
-Our tree loss define a tree structure which can be obtained automatically and it is time-saving.
-\begin{align}
-    L_{Simloss}&=-\frac{1}{N}\log(\sum_{k=1}^{C}S_{y_i,k}\cdot p_i[k])\\
-    % L_{Simloss}=-\frac{1}{N}\log(\sum_{k=1}^{C}S_{y_i,k}\cdot\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)})
-    p_i&=\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)}
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Theoretical Results}
-
-It is well known that the cross entropy loss has generalization error $O(\sqrt{k/n})$.
-Our main theoretical result states that the tree loss significantly improves this generalization error down to $O(\sqrt{1/n})$.
-This is a shocking improvement since it implies that the generalization error is independent of the number of classes in our problem.
-
-Our analysis relies on simple properties of stochastic gradient descent,
-and we view the simplicity of our analysis as a major strength of the tree loss.
-In this section, we first review standard results of stochastic gradient needed for our analysis.
-Then we formally state and prove our main result.
-We conclude with a discussion about the bias-variance tradeoff.
-
-\subsection{SGD Background}
-
-SGD is a standard algorithm for optimizing convex losses,
-and it has many variations.
-Our analysis uses the results from \citet{shalev2014understanding} which are based off of a version of SGD that uses parameter averaging.
-All variants of SGD have similar results, however, and we refer the reader to the above reference for a detailed discussion of these variants and their algorithmic details.
-
-The main result we use is a bound on the convergence rate of SGD for convex Lipschitz functions.
-We reproduce Theorem 14.8 of \citet{shalev2014understanding} in the theorem below.
-
-\begin{theorem}
-    \label{thm:sgd}
-    Let $B,\rho>0$.
-    Let $f$ be a convex function and let $\star W = \argmin_{W : \lF{W}\le B} f(W)$.
-    Assume that SGD is run for $T$ iterations with $\eta = \sqrt{\frac{B^2}{\rho^2 T}}$.
-    Assume that for all $t$, $\ltwo{\nabla f(W_t)} \le \rho$.
-    Then,
-    \begin{equation}
-        \E f(\bar W) - f(\star W) \le \frac{B\rho}{\sqrt{T}}
-        .
-    \end{equation}
-\end{theorem}
-
-The following theorem bounds the generalization error of the cross entropy loss for multiclass classification problems.
-It is an immediate consequence of Theorem \ref{thm:sgd} above when $f$ is the cross entropy loss.
-
-\begin{theorem}
-\label{theorem:xentropy}
-Assume that for all $i\in[n]$, $\ltwo{\x_i} \le \rho$,
-    and that for each class $i\in[k]$, $\ltwo{\w_i}\le B$.
-Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
-\begin{equation}
-    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt kB\rho}{\sqrt n}
-\end{equation}
-where $W^* = \argmin L_D(W)$.
-\end{theorem}
-
-Intuitively, this theorem states that the generalization error of the cross entropy loss shrinks at the rate $O(\sqrt{k/n})$.
-
-%\begin{theorem}
-    %Let $B,\rho>0$.
-    %Let $f$ be a convex function and let $\star \w = \argmin_{\w : \ltwo{\w}\le B} f(\w)$.
-    %Assume that SGD is run for $T$ iterations with $\eta = \sqrt{\frac{B^2}{\rho^2 T}}$.
-    %Assume that for all $t$, $\ltwo{\nabla f(\w_t)} \le \rho$ with probability 1.
-    %Then,
-    %\begin{equation}
-        %\E f(\bar \w) - f(\star \w) \le \frac{B\rho}{\sqrt{T}}
-        %.
-    %\end{equation}
-%\end{theorem}
-%
-%When analyzing stochastic gradient descent using the cross entropy loss,
-%it is common to assume that the parameter space is bounded.
-%Under the standard parameterization, we have that the weight vector for each class satisfies $\ltwo{\w_j} \le B$.
-%It immediately follows that $\lF{W} \le \sqrt{k}B$,
-%and from this and convergence results of SGD it follows that the generalization error is $O(\sqrt{k}B/n)$.
-%(See Theorem \ref{theorem:xentropy} above.)
-%
-%\begin{defn}
-    %A learning problem is called convex-lipschitz-bounded with parameters $\rho,B$ if
-    %\begin{enumerate}
-        %\item $\ltwo{\w} \le B$
-        %\item the loss
-    %\end{enumerate}
-%\end{defn}
-%
-%\begin{corollary}[Corollary 14.12 \citep{shalev2014understanding}]
-    %Consider a convex-Lipschitz-bounded learning problem with parameters $\rho, B$.
-    %Then for every $\epsilon>0$, if we run the SGD method for minimizing $L_\mathcal D(W)$ with a number of iterations
-        %$T \ge \frac{B^2\rho^2}{\epsilon^2}$
-    %and with
-        %$\eta = \sqrt{\frac{B^2}{\rho^2 T}}$
-    %then the output of SGD satisfies
-    %\begin{equation}
-        %\E L_\mathcal D (\bar W) - L_\mathcal D(\star W) \le \epsilon
-    %\end{equation}
-%\end{corollary}
-%
-%\subsection{Background}
-
-%In this section, we first introduce more notation and definitions needed for our analysis,
-%then we recall a standard result of stochastic gradient descent.
-%We follow the notation of \citet{shalev2014understanding}'s textbook as closely as possible.
-%
-%Let $\mathcal D$ be a distribution over the input data points and $S \sim D^m$ be a set of $m$ data points sampled from this distribution.
-%Then we define the true loss as
-%\begin{equation}
-    %L_\mathcal D(W) = \E_{(\x,y)\sim\mathcal D} \ell(W; \x, y)
-%\end{equation}
-%and the sample loss as
-%\begin{equation}
-    %L_S(W) = \frac 1 m \sum_{i=1}^m \ell(W; \x_i, y_i)
-    %.
-%\end{equation}
-%We refer to the difference between these two losses as the generalization error.
-%\begin{equation}
-    %\left\lvert L_\mathcal D(W) - L_S(W) \right\rvert.
-%\end{equation}
-%
-%Given a distribution of data points $\mathcal D$, the optimal parameter matrix is defined as
-%\begin{equation}
-    %\star W = \argmin_{W} \E_{(\x, y)} \ell(W; (\x, y))
-%\end{equation}
-%Given a dataset of $n$ points, we can estimate the parameter 
-%\begin{equation}
-    %\hat W = \argmin_{W} \frac1n\sum_{i=1}^n \ell(W; (\x_i, y_i))
-%\end{equation}
-%The main theoretical result for the cross entropy loss is that for a dataset with $n$ points,
-%the generalization error is $O(\sqrt{k/n})$.
-%There are many theorems that establish this result in different contexts.
-%The following is an example that relies on properties of SGD.
-%\begin{theorem}
-%\label{theorem:xentropy}
-%Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
-    %and that for each class $i\in[k]$, $\ltwo{\w_i}\le B$.
-%Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
-%\begin{equation}
-    %\E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt cB\rho}{\sqrt n}
-%\end{equation}
-%where $W^* = \argmin L_D(W)$.
-%\end{theorem}
-% \begin{proof}
-%     \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David and the properties of the cross entropy loss from the last set of notes.}
-%     \begin{align}
-%     {\| W \|^2_F}&=\sum_{i=1}^k{\| W_i\|^2}\\
-%                 &\le\sum_{i=1}^k{B^2}\\
-%                 &\le cB^2\\
-%   \| W \|_F  &\le \sqrt k B 
-%     \end{align}
-% Then we get:
-%     \begin{equation}
-%     l(\bar W)-l(W^*)\le\frac {\sqrt cB\rho}{\sqrt n}
-%     \end{equation}
-%   Take expectation of both side of equation(3):
-%   \begin{equation}
-%     \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt cB\rho}{\sqrt n}
-% \end{equation}
-% \end{proof}
-
-%There are many other loss functions that have been proposed for multilabel classification.
-%In this section, we review these alternatives before presenting our proposed the tree loss.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Bounds using L2 regularization}
-%
-%Recall that when we apply L2 regularization,
-%we are minimizing the objective function
-%\begin{equation}
-    %f(W) = \tfrac 1 m \sum_{i=1}^m \loss(W; (\x_i,y_i)) + \tfrac\lambda2\lF{W}^2
-    %.
-%\end{equation}
-%This function is $\lambda$-strongly convex in $W$.
-%(Why?)
-%Then Theorem 14.11 tells us that after performing $T$ iterations of SGD, we have that
-%\begin{equation}
-    %\label{eq:f-bound}
-    %\E f(\bar W) - f(W^*) \le \frac{4\rho^2}{\lambda T} ( 1 + \log T)
-%\end{equation}
-%where $W^* = \argmin f(W)$.
-%If we substitute $f(W)=L_D(W)+\tfrac\lambda 2\lF{W}^2$ into Equation \ref{eq:f-bound} above,
-%then we get
-%\begin{align}
-    %\E L_D(\bar W) - L_D(W^*) 
-    %&\le \frac{4\rho^2}{\lambda T} ( 1 + \log T) + \tfrac\lambda2\lF{W^*}^2 - \tfrac\lambda2\lF{\bar W}^2
-    %\\
-    %&\le \frac{4\rho^2}{\lambda T} ( 1 + \log T) + \frac{\lambda k B^2}{2}
-    %.
-%\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsection{Weight matrix factorization}
-
-% A simple way to reduce sample complexity when $k$ is large is to factor the parameter matrix as $W = VU$,
-% where $V : \R ^ {k \times e}$, $U : \R^{e \times d}$, and $e<\!<\!k$.
-% Then, each $\w_i = \vv_i U$, and the cross entropy softmax loss is
-% \begin{equation}
-%     \ell(VU;(\x,y)) = - \log \frac {\exp(-\trans\vv_y U \x)}{\sum_{j=1}^k \exp(-\trans \vv_j U \x)}
-%     .
-% \end{equation}
-% Unfortunately, this new parameterization is not simultaneously convex in both $V$ and $U$;
-% therefore, to analyze this formulation, we will assume that $V$ is fixed and only $U$ is a learned parameter.
-% In practice, it is fine to set $V$ to be a random matrix (and there is good theory to justify this),
-% or to simultaneously learn both $V$ and $U$ despite the nonconvexity.
-
-% This factorization decreases the statistical complexity of the problem from $O(\sqrt{k/n})$ to $O(\sqrt{e/n})$.
-% Recall that $e$ is a hyperparameter that is selected to be much less than $k$ and should represent the "intrinsic" dimensionality of the weight matrix.
-% The following theorem proves this result formally.
-% \begin{theorem}
-% Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
-%     and that for each class $i\in[k]$, $\ltwo{\vv_i}\le 1$ and $\ltwo{\uu_i}\le B$.
-% Then the parameter vector $\bar W = V \bar U$ estimated from one epoch of SGD satisfies
-% \begin{equation}
-%     \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt eB\rho}{\sqrt n}
-% \end{equation}
-% where $W^* = \argmin L_D(W)$.
-% \end{theorem}
-% % \begin{proof}
-% %     \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David.}
-% %     \begin{align}
-% %     {\| U \|^2_F}&=\sum_{i=1}^e{\| U_i\|^2}\\
-% %                 &\le\sum_{i=1}^e{B^2}\\
-% %                 &\le eB^2\\
-% %   \| U \|_F  &\le \sqrt e B  \\
-% %   \| W \|_F  &\le \sqrt e B
-% %     \end{align}
-% %     Then we get:
-% %     \begin{equation}
-% %     l(\bar W)-l(W^*)\le\frac {\sqrt eB\rho}{\sqrt n}
-% %     \end{equation}
-% %   Take expectation of both side of equation(8):
-% %   \begin{equation}
-% %     \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt eB\rho}{\sqrt n}
-% % \end{equation}
-% % \end{proof}
-
-\subsection{Our Results}
-
-The key idea of the tree loss is that we can reduce the bound on the size of the parameter space,
-and this will result in the reduced sample complexity.
-Let $\level k$ denote the level of node $k$ in the label tree.
-Then we replace the constraints on the $\w_j$s with the following constraint on all $\vv_k$:
-\begin{equation}
-    \ltwo{\vv_k} \le \frac{B}{2^{\level k}}
-    .
-    \label{eq:tree-constraint}
-\end{equation}
-Notice that the original constraint \eqref{} immediately follows from the tree constraint \eqref{eq:tree-constraint} and the reparameterization \eqref{eq:covertree-reparam}.
-One way to interpret this is that we have ``factored out'' our bounds on the $\w_i$ into bounds on the smaller $\vv_k$ components,
-and because the $\vv_k$ vectors are shared between classes,
-we can reduce the overall bound.
-The following lemma bounds the Frobenius norm of the weight matrix $V$.
-
-\begin{lemma}
-    Assume that the label tree has at most $q$ nodes per level and $r$ levels.
-    Then,
-    \begin{equation}
-        \lF{V} \le \tfrac12 Bq k^{(1 - 1/\log_2 q)}
-    \end{equation}
-    In particular, if $q=2$, then
-    \begin{equation}
-        \lF{V} \le B,
-    \end{equation}
-    which is independent of the number of classes $k$.
-\end{lemma}
-\begin{proof}
-    We have the following chain of inequalities
-    \begin{align}
-        \lF{V} 
-        &\le \sum_{k\in \text{nodes of the level tree}} \ltwo{\vv_k}
-        \\
-        &= \sum_{i=0}^r \sum_{k\in \text{nodes at level $i$}} \ltwo{\vv_k}
-        \\
-        &\le \sum_{i=0}^r B\left(\frac {q} {2}\right)^i
-        \label{eq:lem:lFV:1}
-        \\
-        &=
-        B\left(\frac{1 - (q/2)^{r+1}}{1-q/2}\right)
-        \label{eq:lem:lFV:2}
-        \\
-        &\le
-        B(q/2)^{r+1}.
-        \label{eq:lem:lFV:3}
-    \end{align}
-    Line \eqref{eq:lem:lFV:1} follows from the fact that the number of nodes at level $i$ in the tree is upper bounded by $q^i$ and the the maximum L2 norm of a vector at level $i$ in the tree is $B/2^i$,so the sum of all vectors at level $i$ is bounded by $B(q/2)^i$.
-    Lines \eqref{eq:lem:lFV:2} and \eqref{eq:lem:lFV:3} are standard properties of geometric series.
-
-    Next, we show that
-    \begin{equation}
-    \begin{split}
-        \left(\frac q 2\right)^r
-        &=
-        \left(\frac q 2\right)^{\log_q k}\\
-        &=
-        \frac{k}{2^{\log_q k}}\\
-        &=
-        \frac{k}{2^{{\log_2 k}/{\log_2 q}}}\\
-        &=
-        \frac{k}{k^{1/\log_2 q}}\\
-        &=
-        k^{\left(1 - {1}/{\log_2 q}\right)}
-        .
-        \label{eq:lem:technical2}
-    \end{split}
-    \end{equation}
-    Substituting \eqref{eq:lem:technical2} into \eqref{eq:lem:lFV:3} gives the stated result.
-\end{proof}
-
-Substituting this Lemma into the SGD bounds gives us our main result:
-
-\begin{theorem}
-\label{theorem:xentropy}
-% Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
-%     and that for each class $i\in[k]$, $\ltwo{\w_i}\le B$.
-Assume that for all $i\in[n]$, $\ltwo{\x_i} \le \rho$,
-    and that for each class $i\in[k]$,  $\ltwo{\vv _i} \le \frac{B}{2^{\level i}}$.
-Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
-\begin{equation}
-    \E L_D(\bar W) - L_D(W^*) \le \frac {B\rho}{\sqrt n}
-    ,
-\end{equation}
-which is independent of the number of classes $k$.
-\end{theorem}
-%Let $\mathcal L$ be a metric space over the set of labels,
-%and $\ddim$ be the doubling dimension of $\mathcal L$.
-%Then we build a ``cover tree'' from the class labels that respects the metric structure.
-%This cover tree will have exactly $k$ leaf nodes, one for each class label,
-%and $O(k)$ internal nodes.
-%Why does this small change work?
-%Intuitively, classes that have a small distance from each other should have similar weight vectors.
-
-%\begin{lemma}
-    %Under the conditions defined above, we have
-%\begin{equation}
-    %\label{eq:lFV-bound}
-    %\lF{V} \le (\ddim \log k) B.
-%\end{equation}
-%\end{lemma}
-%\begin{proof}
-%\end{proof}
-
-%Formally, we can bound the Frobenius norm of the weight matrix $V$ by
-%which is significantly better than our bound on the weight matrix $W$ of only $\sqrt k B$.
-%Substituting \eqref{eq:lFV-bound} into Theorem 14.12 of Shalev-Shwartz and Ben-David gives us that if SGD is run for $T$ iterations to compute parameter estimate $\bar W$,
-%then
-%\begin{equation}
-    %\E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt {\dim \mathcal L}B\rho\log k}{\sqrt T}
-%\end{equation}
-%where $W^* = \argmin L_D(W)$.
-
-\subsection{Limitations: the bias-variance tradeoff}
-
-\label{sec:bias-var}
-
-\section{Experiments}
-
-\subsection{Synthetic data}
-
-In this experiment we will demonstrate the tree loss's effectiveness on a simple multiclass logistic regression problem.
-The problem will be specifically designed to be convex and have low intrinsic dimension in the class labels in order to illustrate the advantages of the cover tree loss.
-
-Let $N$ be the standard normal distribution.
-Then sample the matrices
-\begin{align}
-    U \sim N^{k\times a} \qquad\text{and}\qquad
-    A \sim N^{a\times d},
-\end{align}
-and define the true parameter matrix to be
-\begin{equation}
-    W^* = UA.
-\end{equation}
-For all $i \in [k]$, the row $\w_i^*$ of $W^*$ corresponds to the parameter vector for class $i$ and has dimension $d$.
-The variable $a$ controls the intrinsic dimensionality of the problem.
-When $a$ is small, then many class labels will be similar to each other;
-but as $a$ increases, the class labels will have increasingly less structure.
-When $a$ is known in advance, then we can use weight matrix factorization and set $e=a$.
-
-For each data point $i\in[n]$,
-we sample the data point according to the following rules:
-\begin{align}
-    y_i &\sim \text{Uniform}([k]), \text{and} \\
-    \x_{i} &\sim \mathcal N(\w^*_{y_i}; \sigma),
-\end{align}
-where $\sigma$ controls the noise in the dataset.
-Increasing $\sigma$ adds noise and makes classes harder to distinguish,
-whereas decreasing $\sigma$ reduces noise and makes the classes easier to distinguish.
-
-With our problem defined in this way, it is clear that
-\begin{equation}
-    \argmin_{W} \tfrac 1 n \ell(W; \x_i, y_i)
-\end{equation}
-converges to $W^*$ using the standard cross entropy loss and both the matrix factorization and tree reparameterizations.
-% \fixme{You should prove this for yourself.}
-% Figure \ref{fig:synthetic-results} shows that the cover tree loss converges at a faster rate.
-
-\begin{figure}[h]
-\vspace{.3in}
-\includegraphics[width=\linewidth]{fig/images/accuracy_vs_n.png}
-\vspace{.3in}
-\caption{\small Accuracy versus number of data points($d=64, \sigma=1.0, k=10$)}
-\label{accuracy_vs_n}
-\end{figure}
-
-\begin{figure}[h]
-\vspace{.3in}
-\includegraphics[width=\linewidth]{fig/images/accuracy_vs_d.png}
-\vspace{.3in}
-\caption{\small Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, k=10$)}
-\label{accuracy_vs_d}
-\end{figure}
-
-\begin{figure}[h]
-\vspace{.3in}
-\includegraphics[width=\linewidth]{fig/images/accuracy_vs_sigma.png}
-\vspace{.3in}
-\caption{\small Accuracy versus randomness($n=100, d=64, k=10$)}
-\label{accuracy_vs_sigma}
-\end{figure}
-
-\begin{figure}[h]
-\vspace{.3in}
-\includegraphics[width=\linewidth]{fig/images/accuracy_vs_class.png}
-\vspace{.3in}
-\caption{\small Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)}
-\label{accuracy_vs_class}
-\end{figure}
-
-\begin{figure}[h]
-\vspace{.3in}
-\includegraphics[width=\linewidth]{fig/new_img/accuracy_vs_base.png}
-\vspace{.3in}
-\caption{\small Accuracy versus base of tree($n=1000, d=10, \sigma=1.0, k=100$)}
-\label{accuracy_vs_base}
-\end{figure}
-
-\begin{figure}[h]
-\vspace{.3in}
-\includegraphics[width=\linewidth]{fig/new_img/height_vs_base.png}
-\vspace{.3in}
-\caption{\small Height versus base of tree($n=1000, d=10, \sigma=1.0, k=100$)}
-\label{height_vs_base}
-\end{figure}
-
-\begin{figure}[h]
-\vspace{.3in}
-\includegraphics[width=\linewidth]{fig/new_img/loss_vs_structure.png}
-\vspace{.3in}
-\caption{\small Accuracy versus tree structure($n=1000, d=64, \sigma=1.0, k=100$)}
-\label{accuracy_vs_structure}
-\end{figure}
-
-\subsubsection{Results}
-From figure \ref{fig.1}, it is clear that the tree loss achieves the best performance. 
-The tree loss converges at a faster rate as number of data points and dimension of parameter matrix increase.
-If we increase the number of classes, the tree loss can keep a higher accuracy and the accuracy of SimLoss is higher than cross entropy loss and hierarchical softmax.
-It is as our expected, the tree loss can improve performance on large classes tasks.
-Besides, when we increase the noise in the dataset, the accuracy of all loss functions decrease, yet the tree loss decreases slower.
-Among the four loss functions, hierarchical softmax hurts the performance obviously. 
-We would not apply hierarchical softmax on real world data experiment in terms of computation.
-
-There is a parameter 'base' which can control the height of tree.
-Figure \ref{subfig.2} shows that if we increase the value of base, the tree is shorter.
-As our expected, from figure \ref{subfig.1} we can see that a taller tree has higher accuracy. 
-We add a parameter randomness into the tree structure and the tree structure become more random as the randomness factor increase.
-As figure \ref{subfig.3} shows, when the tree structure become totally random, the performance of the tree loss is close to cross entropy loss.
-
-\subsubsection{Alternative synthetic experiments}
-
-In multi-label classification, it is common for the classes to be unbalanced.
-We would like to show that the tree loss works well for unbalanced data.
-A good way to do that is to change the distribution that $y_i$ is drawn from,
-and a geometric distribution is a likely good alternative.
-
-The tree loss can work well even when the weight matrix has non-linear intrinsic structure.
-We should adapt the $\w*_i$ vectors to sit on a manifold instead of a hyperplane to demonstrate this fact.
-
-\subsection{Real world data}
-% \fixme{Write a description of the experiment.}
-In this experiment, we will compare the tree loss with softmax corss entropy and simloss on some real world data.
-We conduct image classification tasks on CIFAR-100 dataset and ImageNet dataset and emoji prediction task on twitter dataset.
-Our goal is to investigate the effects of changing the loss function on our example experiments.
-We do not focus on if we have state-of-the-art performance on specific models, but rather on the evaluation of the tree loss as a general loss function which can be applied on various tasks.
-These three tasks and datasets are typical examples for using cross entropy loss.
-
-\subsubsection{CIFAR-100 Data}
-We use CIFAR-100 dataset which has 100 classes for image classification.
-We also get word embeddings from a word2vec model pretrained on Google News \cite{Mikolov2013EfficientEO} of class names and construct tree structure and calculate similarity between classes from word embeddings.
-Four class names do not yield a word embedding and are therefore eliminated.
-
-To evaluate our tree loss, we rely on three metrics: accuracy (Acc.) which focus on correct predictions and similarity accuracy (Similarity Acc.) which focus on the similarity of predicted and target class and superclass accuracy (SA).
-Every example in CIFAR-100 dataset has a main class and a superclass.
-Superclass accuracy is the fraction of examples that are correctly put into the corresponding superclass.
-We take ResNet20 model \cite{He2016DeepRL} and SGD optimizer with a learning rate 0.1 and a batch size of 1021. 
-We stop early to get the highest accuracy on validation set.
-
-\begin{table}[]
-\caption{Test results with early stopping on CIFAR-100 dataset. Best values are written in bold.} \label{cifar100}
-\begin{center}
-\begin{tabular}{@{}cccc@{}}
-\toprule
-\multirow{2}{*}{Loss} & \multicolumn{3}{c}{Test}    \\ \cmidrule(l){2-4} 
-                      & Acc. & Similarity Acc. & SA \\ \cmidrule(r){1-1}
-Tree Loss       & \textbf{52.78}     &  \textbf{65.90}               &  \textbf{62.55}  \\
-Cross Entropy         &  51.87    &   65.58              &  62.14  \\
-SimLoss               &    52.43  &    65.82             & 62.34  \\\bottomrule
-\end{tabular}
-\end{center}
-\end{table}
-
-\subsubsection{ImageNet Data}
-ImageNet dataset \cite{Russakovsky2015ImageNetLS} has 1000 classes and many of the classes are similar and related, we consider the internal class structure has a impact on performance of loss function.
-We use class names to get class representations from a pretrained FastText model.
-We take ResNet50 model \cite{He2016DeepRL} trained on 1.28 mollion training images and evaluated on the 50k validation images and SGD optimizer with a learning rate 0.01.
-We use top1 accuracy and top5 accuracy to evaluate our loss functions.
-
-\begin{table}[]
-\caption{Validation results on ImageNet dataset. Best values are written in bold.} \label{imagenet}
-\begin{center}
-\begin{tabular}{@{}ccc@{}}
-\toprule
-\multirow{2}{*}{Loss} & \multicolumn{2}{c}{Validation} \\ \cmidrule(l){2-3} 
-                      & Top1 Acc.      & Top5 Acc.     \\ \cmidrule(r){1-1}
-Tree Loss       & \textbf{76.52} & \textbf{92.92} \\
-Cross Entropy         & 75.30          & 92.36         \\
-SimLoss               & 76.24          & 92.83         \\ \bottomrule
-\end{tabular}
-\end{center}
-\end{table}
-
-\subsubsection{Twitter Data}
-
-We apply the tree loss on emoji prediction in twitter dataset. 
-Emojis are popular to express emotions in text messages and tweets are a wildely used social media over the world. 
-We trained the multilingual BERT model on tweets to predict which emoji corresponds to a piece of text is best for measuring the emotional content in the text. 
-Our 1660 target emojis are defined by emo2vec \cite{Eisner2016emoji2vecLE}.
-
-We collect all tweets \cite{Izbicki2019GeolocatingTI} in any languages sent from anywhere in the world and filter the tweets with target emojis. 
-For each tweet, we replace all user mentions with a special token \texttt{\text{<}mention\text{>}} and all URLS with a special token \texttt{\text{<}url\text{>}} and delete all emojis. 
-We keep all hashtags and duplicate the tweet once for each emoji if a tweet has multiple emojis. 
-Then we split the dataset into training validadtion and testing sets by user id to ensure each user appears in only one set in order to prevent data leakage.
-
-We take the multilingual BERT model \cite{Feng2020LanguageagnosticBS} pretrained on data from 109 distinct languages which achieves state-of-the-art performance on a wide variety of natural language tasks.
-We get the embeddings of 1660 target emojis defined by emo2vec.
-
-\begin{table}[h]
-\small
-\caption{Validation and test results of emoji prediction task on twitter dataset. Best values are written in bold.} \label{twitter}
-\begin{center}
-\begin{tabular}{@{}lcccc@{}}
-\toprule
-\multicolumn{1}{c}{\multirow{2}{*}{Loss}} & \multicolumn{2}{c}{VALIDATION} & \multicolumn{2}{c}{TEST}       \\ \cmidrule(l){2-5} 
-\multicolumn{1}{c}{}                      & Acc.       & SA       & Acc.      & SA             \\ \cmidrule(r){1-1}
-Tree Loss                           &   \textbf{20.81}    &   \textbf{50.26}  &  \textbf{20.96}    &   \textbf{50.45}        \\
-Cross Entropy                             &   19.90    &   48.27  &  19.95    &   48.33        \\
-SimLoss                                   &   19.91    &   48.25  &  19.96    &   48.32         \\ \bottomrule
-\end{tabular}
-\end{center}
-\end{table}
-
-\subsubsection{Results}
-We evaluate the tree loss on image data(CIFAR100, ImageNet) and text data(Twitter) and the tree loss outperforms cross entropy loss and Simloss on metrics.
-Table \ref{cifar100} shows the results of three loss functions for the test set of the CIFAR-100 dataset.
-Similarity accuracy and superclass accuracy pay attention to more similar classes and the tree loss get higher accuracy.
-Table \ref{imagenet} shows the results for the valdidation set of ImageNet dataset.
-ImageNet has 1000 classes and many classes are semantically  similar.
-The tree loss incorporates the similarities to training and get a higher top1 accuracy and top5 accuracy.
-The emojis of Twitter dataset is typically unbalanced and the tree loss works well for unbalanced data.
-Table \ref{twitter} shows the results for validation set and test set of twitter dataset.
-The tree loss achieve the best performance on accuracy and similarity accuracy.
-
-\section{Conclusion}
-In this paper, we have presented the tree loss, a drop-in replacement for the cross entropy loss that incorporated class relations. 
-We use properties of stochastic gradient descent to provide the theoretical justifications that the generalization error of the tree loss is better. 
-The tree loss works by re-parameterizing the parameter matrix for cross entropy loss and can be easily implement. 
-We evaluate our tree loss on synthetic data and typically real world data. 
-From the results of experiments, we found the tree loss improve the performance significantly and  help with predicting more similar classes if the model misclassified an example. 
-In our analysis, since the tree loss can obtain background knowledge of classes, it works well for tasks with many classes and data with unbalanced classes.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{plainnat}
-\bibliography{paper}
-% \begin{abstract}
-%   The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
-%   both left and right-hand margins. Use 10~point type, with a vertical
-%   spacing of 11~points. The \textbf{Abstract} heading must be centered,
-%   bold, and in point size 12. Two line spaces precede the
-%   Abstract. The Abstract must be limited to one paragraph.
-% \end{abstract}
-
-% \section{GENERAL FORMATTING INSTRUCTIONS}
-
-% The camera-ready versions of the accepted papers are 8 pages,
-% plus any additional pages needed for references.
-
-% Papers are in 2 columns with the overall line width of 6.75~inches (41~picas).
-% Each column is 3.25~inches wide (19.5~picas).  The space
-% between the columns is .25~inches wide (1.5~picas).  The left margin is 0.88~inches (5.28~picas).
-% Use 10~point type with a vertical spacing of
-% 11~points. Please use US Letter size paper instead of A4.
-
-% Paper title is 16~point, caps/lc, bold, centered between 2~horizontal rules.
-% Top rule is 4~points thick and bottom rule is 1~point thick.
-% Allow 1/4~inch space above and below title to rules.
-
-% Author descriptions are center-justified, initial caps.  The lead
-% author is to be listed first (left-most), and the Co-authors are set
-% to follow.  If up to three authors, use a single row of author
-% descriptions, each one center-justified, and all set side by side;
-% with more authors or unusually long names or institutions, use more
-% rows.
-
-% Use one-half line space between paragraphs, with no indent.
-
-% \section{FIRST LEVEL HEADINGS}
-
-% First level headings are all caps, flush left, bold, and in point size
-% 12. Use one line space before the first level heading and one-half line space
-% after the first level heading.
-
-% \subsection{Second Level Heading}
-
-% Second level headings are initial caps, flush left, bold, and in point
-% size 10. Use one line space before the second level heading and one-half line
-% space after the second level heading.
-
-% \subsubsection{Third Level Heading}
-
-% Third level headings are flush left, initial caps, bold, and in point
-% size 10. Use one line space before the third level heading and one-half line
-% space after the third level heading.
-
-% \paragraph{Fourth Level Heading}
-
-% Fourth level headings must be flush left, initial caps, bold, and
-% Roman type.  Use one line space before the fourth level heading, and
-% place the section text immediately after the heading with no line
-% break, but an 11 point horizontal space.
-
-% %%%
-% \subsection{Citations, Figure, References}
-
-% \subsubsection{Citations in Text}
-
-% Citations within the text should include the author's last name and
-% year, e.g., (Cheesman, 1985). 
-% %Apart from including the author's last name and year, citations can follow any style, as long as the style is consistent throughout the paper.  
-% Be sure that the sentence reads
-% correctly if the citation is deleted: e.g., instead of ``As described
-% by (Cheesman, 1985), we first frobulate the widgets,'' write ``As
-% described by Cheesman (1985), we first frobulate the widgets.''
-
-% The references listed at the end of the paper can follow any style as long as it is used consistently.
-
-% %Be sure to avoid
-% %accidentally disclosing author identities through citations.
-
-% \subsubsection{Footnotes}
-
-% Indicate footnotes with a number\footnote{Sample of the first
-%   footnote.} in the text. Use 8 point type for footnotes. Place the
-% footnotes at the bottom of the column in which their markers appear,
-% continuing to the next column if required. Precede the footnote
-% section of a column with a 0.5 point horizontal rule 1~inch (6~picas)
-% long.\footnote{Sample of the second footnote.}
-
-% \subsubsection{Figures}
-
-% All artwork must be centered, neat, clean, and legible.  All lines
-% should be very dark for purposes of reproduction, and art work should
-% not be hand-drawn.  Figures may appear at the top of a column, at the
-% top of a page spanning multiple columns, inline within a column, or
-% with text wrapped around them, but the figure number and caption
-% always appear immediately below the figure.  Leave 2 line spaces
-% between the figure and the caption. The figure caption is initial caps
-% and each figure should be numbered consecutively.
-
-% Make sure that the figure caption does not get separated from the
-% figure. Leave extra white space at the bottom of the page rather than
-% splitting the figure and figure caption.
-% \begin{figure}[h]
-% \vspace{.3in}
-% \centerline{\fbox{This figure intentionally left non-blank}}
-% \vspace{.3in}
-% \caption{Sample Figure Caption}
-% \end{figure}
-
-% \subsubsection{Tables}
-
-% All tables must be centered, neat, clean, and legible. Do not use hand-drawn tables.
-% Table number and title always appear above the table.
-% See Table~\ref{sample-table}.
-
-% Use one line space before the table title, one line space after the table title,
-% and one line space after the table. The table title must be
-% initial caps and each table numbered consecutively.
-
-% \begin{table}[h]
-% \caption{Sample Table Title} \label{sample-table}
-% \begin{center}
-% \begin{tabular}{ll}
-% \textbf{PART}  &\textbf{DESCRIPTION} \\
-% \hline \\
-% Dendrite         &Input terminal \\
-% Axon             &Output terminal \\
-% Soma             &Cell body (contains cell nucleus) \\
-% \end{tabular}
-% \end{center}
-% \end{table}
-
-% \section{SUPPLEMENTARY MATERIAL}
-
-% If you need to include additional appendices during submission, you can include them in the supplementary material file.
-% You can submit a single file of additional supplementary material which may be either a pdf file (such as proof details) or a zip file for other formats/more files (such as code or videos). 
-% Note that reviewers are under no obligation to examine your supplementary material. 
-% If you have only one supplementary pdf file, please upload it as is; otherwise gather everything to the single zip file.
-
-% You must use \texttt{aistats2022.sty} as a style file for your supplementary pdf file and follow the same formatting instructions as in the main paper. 
-% The only difference is that it must be in a \emph{single-column} format.
-% You can use \texttt{supplement.tex} in our starter pack as a starting point.
-% Alternatively, you may append the supplementary content to the main paper and split the final PDF into two separate files.
-
-% \section{SUBMISSION INSTRUCTIONS}
-
-% To submit your paper to AISTATS 2022, please follow these instructions.
-
-% \begin{enumerate}
-%     \item Download \texttt{aistats2022.sty}, \texttt{fancyhdr.sty}, and \texttt{sample\_paper.tex} provided in our starter pack. 
-%     Please, do not modify the style files as this might result in a formatting violation.
-
-%     \item Use \texttt{sample\_paper.tex} as a starting point.
-%     \item Begin your document with
-%     \begin{flushleft}
-%     \texttt{\textbackslash documentclass[twoside]\{article\}}\\
-%     \texttt{\textbackslash usepackage\{aistats2022\}}
-%     \end{flushleft}
-%     The \texttt{twoside} option for the class article allows the
-%     package \texttt{fancyhdr.sty} to include headings for even and odd
-%     numbered pages.
-%     \item When you are ready to submit the manuscript, compile the latex file to obtain the pdf file.
-%     \item Check that the content of your submission, \emph{excluding} references, is limited to \textbf{8 pages}. The number of pages containing references alone is not limited.
-%     \item Upload the PDF file along with other supplementary material files to the CMT website.
-% \end{enumerate}
-
-% \subsection{Camera-ready Papers}
-
-% %For the camera-ready paper, if you are using \LaTeX, please make sure
-% %that you follow these instructions.  
-% % (If you are not using \LaTeX,
-% %please make sure to achieve the same effect using your chosen
-% %typesetting package.)
-
-% If your papers are accepted, you will need to submit the camera-ready version. Please make sure that you follow these instructions:
-% \begin{enumerate}
-%     %\item Download \texttt{fancyhdr.sty} -- the
-%     %\texttt{aistats2022.sty} file will make use of it.
-%     \item Change the beginning of your document to
-%     \begin{flushleft}
-%     \texttt{\textbackslash documentclass[twoside]\{article\}}\\
-%     \texttt{\textbackslash usepackage[accepted]\{aistats2022\}}
-%     \end{flushleft}
-%     The option \texttt{accepted} for the package
-%     \texttt{aistats2022.sty} will write a copyright notice at the end of
-%     the first column of the first page. This option will also print
-%     headings for the paper.  For the \emph{even} pages, the title of
-%     the paper will be used as heading and for \emph{odd} pages the
-%     author names will be used as heading.  If the title of the paper
-%     is too long or the number of authors is too large, the style will
-%     print a warning message as heading. If this happens additional
-%     commands can be used to place as headings shorter versions of the
-%     title and the author names. This is explained in the next point.
-%     \item  If you get warning messages as described above, then
-%     immediately after $\texttt{\textbackslash
-%     begin\{document\}}$, write
-%     \begin{flushleft}
-%     \texttt{\textbackslash runningtitle\{Provide here an alternative
-%     shorter version of the title of your paper\}}\\
-%     \texttt{\textbackslash runningauthor\{Provide here the surnames of
-%     the authors of your paper, all separated by commas\}}
-%     \end{flushleft}
-%     Note that the text that appears as argument in \texttt{\textbackslash
-%       runningtitle} will be printed as a heading in the \emph{even}
-%     pages. The text that appears as argument in \texttt{\textbackslash
-%       runningauthor} will be printed as a heading in the \emph{odd}
-%     pages.  If even the author surnames do not fit, it is acceptable
-%     to give a subset of author names followed by ``et al.''
-
-%     %\item Use the file sample\_paper.tex as an example.
-
-%     \item The camera-ready versions of the accepted papers are 8
-%       pages, plus any additional pages needed for references.
-
-%     \item If you need to include additional appendices,
-%       you can include them in the supplementary
-%       material file.
-
-%     \item Please, do not change the layout given by the above
-%       instructions and by the style file.
-
-% \end{enumerate}
-
-% \subsubsection*{Acknowledgements}
-% All acknowledgments go at the end of the paper, including thanks to reviewers who gave useful comments, to colleagues who contributed to the ideas, and to funding agencies and corporate sponsors that provided financial support.
-% To preserve the anonymity, please include acknowledgments \emph{only} in the camera-ready papers.
-
-% \subsubsection*{References}
-
-% References follow the acknowledgements.  Use an unnumbered third level
-% heading for the references section.  Please use the same font
-% size for references as for the body of the paper---remember that
-% references do not count against your page length total.
-
-% \begin{thebibliography}{}
-% \setlength{\itemindent}{-\leftmargin}
-% \makeatletter\renewcommand{\@biblabel}[1]{}\makeatother
-% \bibitem{} J.~Alspector, B.~Gupta, and R.~B.~Allen (1989).
-%     \newblock Performance of a stochastic learning microchip.
-%     \newblock In D. S. Touretzky (ed.),
-%     \textit{Advances in Neural Information Processing Systems 1}, 748--760.
-%     San Mateo, Calif.: Morgan Kaufmann.
-
-% \bibitem{} F.~Rosenblatt (1962).
-%     \newblock \textit{Principles of Neurodynamics.}
-%     \newblock Washington, D.C.: Spartan Books.
-
-% \bibitem{} G.~Tesauro (1989).
-%     \newblock Neurogammon wins computer Olympiad.
-%     \newblock \textit{Neural Computation} \textbf{1}(3):321--323.
-% \end{thebibliography}
+The idea of the convergence proof is to show that any loss function that is $\rho$-Lipschitz with respect to the L2 norm is $\rho/k$ Lipschitz with respect to the tree regularizer (for fixed $V$,$A$ and near the optimal solution).
+Then applying the exercise at the end of the chapter solves the problem.
 

### 2021-10-14 paper/paper.tex
changes

@@
 
-\newcommand{\fixme}[1]{\noindent{\color{red}\textbf{FIXME:}  {#1}}}
+%\newcommand{\fixme}[1]{\noindent{\color{red}\textbf{FIXME:}  {#1}}}
+\newcommand{\fixme}[1]{}
 \newcommand{\fixmemike}[1]{\noindent{\color{blue}\textbf{FIXME (Mike):}  {#1}}}
@@
 \begin{abstract}
-    %Multiclass logistic regression has generalization error $O(\sqrt{k/n})$, where $k$ is the number of classes and $n$ the number of data points.
-
-    Multiclass classification problems often have many semantically similar classes.
+    %Multi-class logistic regression has generalization error $O(\sqrt{k/n})$, where $k$ is the number of classes and $n$ the number of data points.
+
+    Multi-class classification problems often have many semantically similar classes.
     For example, 90 of ImageNet's 1000 classes are for different breeds of dog.
@@
 \section{Introduction}
+
+%Binary classification is perhaps the oldest and most important problem in statistical learning theory.
+%The classic VC theory \citep{vapnik2015uniform} shows that for linear problems in $d$ dimensions and $n$ data points,
+%the generalization error decays at a rate of $O(\sqrt{d/n})$.
+%Multi-class classification is a natural generalization of the binary case,
+%and \citet{natarajan1989learning} generalized the VC theory to show that for a $k$-class problem, the generalization error decays as $O(\sqrt{kd/n})$.
+%This bound is tight in the sense that for any given hypothesis class,
+%there exists a data distribution whose generalization error will decay as $\Omega(\sqrt{kd/n})$.
+%Chapter 29 of \citet{shalev2014understanding} provides a modern overview of these results.
+
+The cross entropy loss is the most widely used loss function for multi-class classification problems,
+and stochastic gradient descent (SGD) is the most common algorithm for optimizing this loss.
+Standard results show that generalization error decays at a rate of $O(\sqrt{kd/n})$,
+where $k$ is the number of class labels, $d$ is the number of feature dimensions, and $n$ is the number of data points.
+These results (which we review later) make no assumptions about the underlying distribution of classes.
+
+In this paper,
+we assume that the class labels have an underlying metric structure,
+and we introduce the tree loss for exploiting this structure.
+The tree loss is the first multi-class loss function with provably better generalization error than the cross entropy loss.
+We show that if the class label metric has doubling dimension $c$,
+then SGD applied to the tree loss will converge at a rate of $O(\sqrt{d \log k/n})$ when $c\le 1$ or $O(\sqrt{k^{1-1/c}d/n})$ when $c\ge 1$.
+These improvements are most dramatic for small $c$,
+and our empirical results show that many real world classification problems have a label structure with small $c$.
+
+Our paper is organized as follows.
+We begin in Section \ref{sec:related} by discussing limitations of related loss functions and how the tree loss will address those limitations.
+Section \ref{sec:tree} then formally defines the tree loss.
+We emphasize that the tree loss is simply a reparameterization of the standard cross entropy loss,
+and so it is easy to implement in common machine learning libraries.
+Section \ref{sec:theory} reviews standard results on the convergence of stochastic gradient descent,
+and uses those results to prove the convergence bounds for the tree loss.
+Finally, Section \ref{sec:experiment} conducts experiments on synthetic, real world image (CIFAR100, ImageNet) and text (Twitter) data.
+We show that in practice, the tree loss essentially always outperforms the cross entropy loss.
+
+\section{Related Work}
+\label{sec:related}
+
+Previous work on multi-class loss functions have focused on improving either the statistical or computational performance.
+Statistical work includes loss functions designed for hierarchichally structured labels \citep{cesa2006incremental,wu2017hierarchical},
+loss functions for improving top-$k$ accuracy \citep{lapin2016loss},
+or focusing on noisy labels \citep{sukhbaatar2014training,zhang2018generalized}.
+The work most similar to ours is the simloss \citep{Kobs2020SimLossCS},
+which also makes a metric assumptions about the class label structure.
+Our work improves on all of this statistical work by being the first to provide convergence bounds that improve on the bounds of the cross entropy loss.
+
+Other work focuses on improving the speed of multiclass classification.
+The hierarchical softmax \citep{morin2005hierarchical} is a particularly well studied variant of the cross entropy loss with many variations \citep[e.g.][]{Peng2017IncrementallyLT,Jiang2017ExplorationOT,Yang2017OptimizeHS,Mohammed2018EffectivenessOH}.
+It is easily confused with our tree loss because both loss functions involve a tree structure.
+The difference, however, is that the hierarchical softmax focuses on improving runtime performance,
+and most variants actually sacrifice statistical performance to do so.
+The tree loss, in contrast maintains the runtime performance of the standard cross entropy loss but improves the statistical performance.
+Our empirical results in Section \ref{sec:experiment} show that the tree loss has much better statistical performance than the hierarchical softmax.
+Other variations of the cross entropy loss include negative sampling, as used in the celebrated word2vec model \citep{mikolov2013distributed}. 
+Like with the hierarchical softmax, negative sampling makes no attempt to improve statistical performance.
+
+\ignore{
+%Hierarchical classification \citep{cesa2006incremental}
+%Hierarchical but without success \citep{wu2017hierarchical}
+%
+%Focus on top-$k$ accuracy rather than top-1 accuracy \citep{lapin2016loss}
+%
+%Requires custom training procedure \citep{liu2017easy}
+%
+%Noisy labels \citep{sukhbaatar2014training,zhang2018generalized}
 
@@
 \end{itemize}
+}
 
@@
 \section{The Tree Loss}
+\label{sec:tree}
 
@@
 \section{Theoretical Results}
+\label{sec:theory}
 
@@
 \begin{lemma}
-    \ref{lemma:starV}
+    \label{lemma:starV}
     We have that for all $V$-trees derived from a $U$-tree,
@@
 \end{lemma}
+\fixme{
 \begin{proof}
-    \fixme{}
 \end{proof}
+}
 
@@
 \begin{lemma}
-    \ref{lemma:starU}
+    \label{lemma:starU}
     Under assumption \ref{ass:B},
@@
 \begin{lemma}
-    \ref{lemma:main}
+    \label{lemma:main}
     When $c\le1$, we have that
@@
 \end{lemma}
+
+\fixme{
 \begin{proof}
-%Construct a cover tree over the distance metric $d$.
-%For each class $i$, define the vector
-%\begin{equation}
-    %\uu_i =
-    %\begin{cases}
-        %\w_i & \text{if $i$ is the root of the cover tree} \\
-        %\w_i - \w_{\parent{i}} & \text{otherwise} \\
-    %\end{cases}
-    %.
-%\end{equation}
-%Define the vector $\star\uu_i$ similarly by replacing all the $\w_i$ with $\star\w_i$ above.
     First, we review some simple properties of the cover tree structure that will be needed in our proof.
@@
 \end{proof}
+}
 
@@
 \section{Experiments}
+\label{sec:experiment}
 
@@
     \input{fig/real_world.tex}
-    \caption{Experimental results on real world datasets.  For all accuracy measures, larger numbers are better.  The tree loss achieves the best results in all cases.}
+    \caption{Experimental results on real world datasets.  For all performance measures, larger numbers are better.  The tree loss achieves the best results in all cases.}
     \label{table:results}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 \bibliographystyle{plainnat}
@@
 
+\ignore{
 \appendix
@@
 
+}
 \end{document}

### 2021-10-14 paper/paper.tex
changes

@@
 \newcommand{\level}[1]{\texttt{level}({#1})}
+\newcommand{\depth}[1]{\texttt{depth}({#1})}
 
@@
 
-%\newcommand{\fixme}[1]{\noindent{\color{red}\textbf{FIXME:}  {#1}}}
-\newcommand{\fixme}[1]{}
+\newcommand{\fixme}[1]{\noindent{\color{red}\textbf{FIXME:}  {#1}}}
+%\newcommand{\fixme}[1]{}
 \newcommand{\fixmemike}[1]{\noindent{\color{blue}\textbf{FIXME (Mike):}  {#1}}}
@@
 
-\section{The Tree Loss}
+\section{Problem Setting}
 \label{sec:tree}
-
-This section first formally defines our problem setting,
-then formally defines the tree loss.
-We conclude with a comparison between the tree loss and related loss functions.
-
-\subsection{Problem Setting}
 
@@
 
-\subsection{The Tree Loss}
-
-The tree loss reparameterizes the weight matrix used in the cross entropy loss in order to enforce that semantically similar labels will have similar weight vectors.
-The reparameterization is defined according to a \emph{label tree} structure that captures the similarity between labels.
-And we propose two variants of the tree loss called the $U$ and $V$ variants that use slightly different label tree structures.
-The main purpose of the $U$-tree structure is to simplify the analysis and exposition of the $V$-tree structure,
-and we show later in our theoretical results that the $V$-tree is strictly better than the $U$-tree.
-Figure \ref{fig:labeltree} shows examples of both.
-
-\subsubsection{The $U$-Tree Loss}
-
-In a $U$-tree, every node is a class and the class of all internal nodes matches the class of one of its children.
-For each class $i$, we define $\parent{i}$ to be the parent of the upper-most node for class $i$,
-and the $\texttt{parent}$ of the root is the 0 vector..
-For example, in the example of Figure \ref{fig:labeltree},
+The cross entropy loss has no constraints on the weight matrix that cause similar classes to have similar parameter vectors.
+The tree loss fixes this problem, resulting in faster convergence and better generalization.
+
+\section{The Tree Loss}
+
+The main idea of the tree loss is that similar classes should be forced to ``share'' some of their parameters.
+%This sharing causes parameter updates in SGD to also update the parameters of similar classes,
+%resulting in improved generalization.
+The tree loss refactors the cross entropy loss's weight matrix in order to enforce this sharing.
+
+We propose two variants of the tree loss which enforce this sharing in different ways.
+We begin by introducing the $U$-tree loss,
+which is simpler to explain and analyze.
+Then, we introduce the $V$-tree loss,
+which improves on the $U$-tree loss and is the loss we suggest using in practice.
+Whenever we refer to the tree loss without a qualifier,
+we mean the $V$-tree loss.
+
+%Our analysis in Section \ref{sec:theory} will require a metric structure over the class labels.
+%This metric structure is not needed to explain the construction of the tree loss itself,
+%however, so we defer this explanation until later.
+
+%The tree loss reparameterizes the weight matrix used in the cross entropy loss in order to enforce that semantically similar labels will have similar weight vectors.
+%The reparameterization is defined according to a \emph{label tree} structure that captures the similarity between labels.
+%And we propose two variants of the tree loss called the $U$ and $V$ variants that use slightly different label tree structures.
+%The main purpose of the $U$-tree structure is to simplify the analysis and exposition of the $V$-tree structure,
+%and we show later in our theoretical results that the $V$-tree is strictly better than the $U$-tree.
+%Figure \ref{fig:labeltree} shows examples of both.
+
+\subsection{The $U$-Tree Loss}
+
+Explaining our new $U$-tree parameterization requires introducing some notation.
+
+We define a $U$-tree over the class labels to be a tree where each leaf node is represented by a label,
+and each internal node shares a label with a child node.
+Figure \ref{fig:labeltree} (left) shows an example $U$-tree structure.
+The definition of a $U$-tree is motivated by the cover tree data structure \citep{beygelzimer2006cover},
+which generates $U$-tree structures given a metric over the class labels.
+
+%In a $U$-tree, every node is a class and the class of all internal nodes matches the class of one of its children.
+For each class $i$, we let the sequence $P_i$ denote the path from the leaf node to the root with duplicates removed.
+For example, using the $U$-tree in Figure \ref{fig:labeltree},
 we have
@@
 \begin{split}
-    \parent{\texttt{husky}} &= \texttt{boxer} \text{, and}\\
-    \parent{\texttt{bear}} &= \texttt{boxer} \text{, and}\\
-    \parent{\texttt{boxer}} &= \texttt{truck} .\\
+    P_{\texttt{bear}} &= (\texttt{bear}, \texttt{boxer}, \texttt{truck}) \\
+    P_{\texttt{sheepdog}} &= (\texttt{sheepdog}, \texttt{boxer}, \texttt{truck}) \\
+    P_{\texttt{truck}} &= (\texttt{truck})
 \end{split}
 \end{equation*}
-We associate for each class $i$ a new parameter vector $\uu_i$ and set
-\begin{equation}
-    \w_i = \w_{\parent{i}} - \uu_i,
+For each class $i$, we define $\parent{i}$ to be the first node in $P_i$ not equal to $i$.
+In other words, $\parent{i}$ is the parent of the upper-most node for class $i$.
+%For example, using the $U$-tree structure in Figure \ref{fig:labeltree},
+%we have
+%\begin{equation*}
+%\begin{split}
+    %\parent{\texttt{husky}} &= \texttt{boxer} \text{, and}\\
+    %\parent{\texttt{bear}} &= \texttt{boxer} \text{, and}\\
+    %\parent{\texttt{boxer}} &= \texttt{truck} .\\
+%\end{split}
+%\end{equation*}
+
+We are now ready to introduce the $U$-tree parameterization.
+Intuitively, we will represent each parameter as the difference between itself and it's parent in the $U$-tree.
+We associate for each class $i$ a new parameter vector $\uu_i$ defined to be
+\begin{equation}
+    \uu_i =
+    \begin{cases}
+        \w_i                    & \text{if $i$ is the root} \\
+        \w_{\parent{i}} - \w_i  & \text{otherwise}
+    \end{cases}
+    ,
+\end{equation}
+and we define the parameter matrix $U : \mathbb R^{k\times d}$ to be $(\uu_1;\uu_2;...;\uu_k)$.
+We can recursively rewrite the original parameter vectors in terms of this new parameterization as
+\begin{equation}
+    \w_i = \sum_{j\in P_i} \uu_i
+    .
     \label{eq:uu}
 \end{equation}
-and we define the parameter matrix $U : \mathbb R^{k\times d}$ to be $(\uu_1;...;\uu_k)$.
 The $U$-tree loss is then defined by substituting \eqref{eq:uu} into \eqref{eq:xentropy} to get
 \begin{equation*}
-    \ell(U;(\x,y)) = - \log \frac {\exp(-(\trans\uu_{\parent{y}}-\trans\uu_y) \x)}{\sum_{j=1}^k \exp(-(\trans\uu_{\parent{j}}-\trans \uu_j) \x)}
+    %\ell(U;(\x,y)) = - \log \frac {\exp(-(\trans\uu_{\parent{y}}-\trans\uu_y) \x)}{\sum_{j=1}^k \exp(-(\trans\uu_{\parent{j}}-\trans \uu_j) \x)}
+\ell(U;(\x,y)) = - \log \frac {\exp(-\sum_{j\in P_y}\trans\uu_j \x)}{\sum_{i=1}^k \exp(- \sum_{j\in P_i}\trans\uu_j \x)}
 \end{equation*}
 We use the same $\ell$ notation for the standard cross entropy loss function and the $U$-Tree loss because the function is exactly the same;
-the only difference is how we represent the parameters.
-
-\subsubsection{The $V$-Tree Loss}
+the only difference is how we represent the parameters during the training procedure.
+
+\subsection{The $V$-Tree Loss}
 
 The $V$-tree is constructed from the $U$-tree by replacing all non-leaf nodes with ``pseudoclasses''.
-Let $k'$ be the total number of nodes in the $V$-tree;
-so $k'$ equals $k$ plus the number of internal nodes.
-For each class $i$, we let the sequence $P_i$ denote the path from the leaf node to the root.
-For example, using the $V$-tree in Figure \ref{fig:labeltree},
-we have
+Let $k'$ denote the total number of classes plus the total number of pseudoclasses.
+%so $k'$ equals $k$ plus the number of internal nodes.
+%For each class $i$, we let the sequence $P_i$ denote the path from the leaf node to the root.
+%For example, using the $V$-tree in Figure \ref{fig:labeltree},
+%we have
+
+We let $P_i$ be defined as the path from leaf node $i$ to the root as before,
+but note that there are now no duplicates to remove and so the paths are longer.
+For example,
 \begin{equation*}
 \begin{split}
+    P_{\texttt{bear}} &= (\texttt{bear}, \textit{pseudo2}, \textit{pseudo1}) \\
     P_{\texttt{sheepdog}} &= (\texttt{sheepdog}, \textit{pseudo3}, \textit{pseudo2}, \textit{pseudo1} ) \\
@@
 \end{equation*}
-Next, we associate a vector $\vv_i$ to each node $i$ in the tree structure.
-In particular, there is a vector $\vv_i$ for each class and for each pseudo-class,
-so there are more parameter vectors for the $V$-tree loss than either the $U$-tree loss or the standard cross entropy loss.
-
-Finally, we reparameterize the weights for the cross entropy loss as the sum of the vectors along the paths.
-Specifically, we set the weight vector for class $i$ to be 
-\begin{equation}
-    \label{eq:covertree-reparam}
-    \w_j = \sum_{j\in P_i} \vv_i
-    .
-\end{equation}
-The $V$-tree loss is defined by substituting \eqref{eq:covertree-reparam} into \eqref{eq:xentropy} to get
+%Next, we associate a vector $\vv_i$ to each node $i$ in the tree structure.
+%In particular, there is a vector $\vv_i$ for each class and for each pseudo-class,
+%so there are more parameter vectors for the $V$-tree loss than either the $U$-tree loss or the standard cross entropy loss.
+The $\vv_i$ and $V$ parameters are now defined analogously to the $\uu_i$ and $U$ parameters, but over the $V$-tree structure instead of the $U$-tree structure.
+An important distinction between the $V$ and $U$ parameter matrices is that they will have different shapes.
+The $U$ matrix has shape $k \times d$, which is the same as the $W$ matrix,
+but the $V$ matrix has shape $k' \times d$,
+which is potentially a factor of up to 2 times larger.
+
+%Finally, we reparameterize the weights for the cross entropy loss as the sum of the vectors along the paths.
+%Specifically, we set the weight vector for class $i$ to be 
+%\begin{equation}
+    %\label{eq:covertree-reparam}
+    %\w_j = \sum_{j\in P_i} \vv_i
+    %.
+%\end{equation}
+%The $V$-tree loss is defined by substituting \eqref{eq:covertree-reparam} into \eqref{eq:xentropy} to get
+The $V$-tree loss is defined by using the $V$ matrix to parameterize the cross entropy loss, giving
 \begin{equation}
@@
 
+This reparameterization is reminiscent of the way that fastText \citep{bojanowski2017enriching} reparameterizes the word2vec \citep{Mikolov2013EfficientEO} model to improve statistical efficiency.
+Two notable difference, however, are that fastText is a domain-specific adaptation and provides no theoretical guarantees;
+our tree loss works on any domain and provides theoretical guarantees.
+
 \subsection{Implementation Notes}
@@
 Both the $U$-tree and $V$-tree losses are easy to implement in practice using the built-in cross entropy loss function in libraries like PyTorch \citep{NEURIPS2019_9015} or Tensorflow \citep{tensorflow2015-whitepaper}.
-The only change needed is to define the loss in terms of the sum of vectors $V$ instead of a variable tensor $W$.
-This ensures that the loss is implemented efficiently and is numerically stable.
-
-In practice, the $V$-tree loss is slightly slower than the standard cross entropy loss and $U$-tree losses due to the additional summation over the paths.
-In our experiments, we found this this to cause the $V$-tree loss to be about twice as slow.
+%The only change needed is to pass in a variable representing the $U$/$V$ parameter matrices to the cross entropy loss function
+The only change needed is to represent the $W$ parameter matrix in your code as an appropriate sum over the $U$ or $V$ parameter matrices.
+The magic of automatic differentiation will then take care of the rest and ensure that the underlying $U$ or $V$ matrix is optimized.
+Our TreeLoss library\footnote{URL blinded for peer review.} provides easy-to-use functions for generating these matrices,
+and so modifying code to work with the tree loss is a 1 line code change.
+
+In practice, the tree loss is slightly slower than the standard cross entropy loss due to the additional summation over the paths.
+In our experiments, we observed an approximately 2x slowdown.
 
@@
 SGD converges at a rate of $O(\sqrt{k/n})$.
-Our theoretical results asymptotically improve this convergence rate.
-
-With an appropriately constructed label tree,
-we show convergence at a rate of $O(\sqrt{\log k/n})$ or $O(\sqrt{k^{1-1/c}/n})$,
-where $c$ is a measure of difficulty of the problem.
+The tree loss's parameter sharing scheme asymptotically improves this convergence rate.
+
+We assume that the class labels have a metric structure and let $c$ denote the doubling dimension of this metric.
+This $c$ is a measure of the difficulty of our problem,
+with larger $c$ implying more complex metrics and a more difficult learning problem.
+This is captured in our convergence rates,
+which show show that the tree loss converges at a rate of $O(\sqrt{\log k/n})$ for $c\le1$ or $O(\sqrt{k^{1-1/c}/n})$ for $c>1$.
+
 But what happens if the tree is poorly constructed?
@@
 
-\fixme{
-Our analysis relies on simple properties of stochastic gradient descent,
-and we view the simplicity of our analysis as a major strength of the tree loss.
-In this section, we first review standard results of stochastic gradient descent needed for our analysis.
-Then we formally state and prove our main result.
-}
+Our analysis relies on standard properties of stochastic gradient descent.
+In this section, we first review these results,
+then we formally state and prove our main result.
 
@@
 Other variants of SGD have similar results,
-and our results are easy to generalize to other SGD variants.
-We refer the reader to \citet{shalev2014understanding} for a discussion of these variants.}
-In this section we recall these results,
-occasionally changing the names of variables to avoid conflicts with variable names used elsewhere in this paper.
-
-We assume we are optimizing a function $f : \Theta \to \mathbb R$,
-and that we are only given noisy samples of the function and its gradient.
-We let $\theta^{t}$ denote the parameter value at iteration $t$,
+and we refer the reader to \citet{shalev2014understanding} for a discussion of these variants.}
+In this section we review these results.
+We follow the notation of \citet{shalev2014understanding} as closely as possible,
+but we occasionally change the names of variables to avoid conflicts with variable names used elsewhere in this paper.\footnote{
+    Specifically, we replace all Latin variables with Greek alternatives.
+    We use $\theta$ instead of $\w$, $\nu$ instead of $\vv$, and $\beta$ instead of $B$.
+    The Greek letters $\rho$ and $\eta$ have the same meaning in both documents.
+}
+
+SGD is an iterative procedure for optimizing a function $f : \Theta \to \mathbb R$ given only noisy samples of the function's gradient.
+We let $\theta^{(t)}$ denote the parameter value at iteration $t$,
 and $\eta : \mathbb R$ be the step size.
+Let $\nu_t$ be a noisy gradient of $f$ satisfying
+\begin{equation}
+    \E[\nu_t | \theta^{(t)}] = \nabla f(\theta^{(t)}).
+\end{equation}
 Then the parameter update for step $t$ is defined to be
 \begin{equation}
-    \theta^{(t+1)} = \theta^{(t)} - \eta \nabla f(\theta^{(t)}).
+    \theta^{(t+1)} = \theta^{(t)} - \eta \nabla \nu_t
+    .
 \end{equation}
@@
 \end{equation}
-Parameter averaging is not often used in practice because of the memory requirements,
-but we use it here due because theorems using parameter averaging are typically much easier to state and prove.
-Equivalent results without parameter averaging typically require and additional $\log T$ factor in their convergence rates\citep{}.
+Parameter averaging is not often used in practice because it has a large memory overhead,
+but it is widely used in theoretical analysis of SGD.
+Theorems using parameter averaging are typically much easier to state and prove,
+and equivalent results without parameter averaging typically require an additional $\log T$ factor in their convergence rates \citep{rakhlin2011making}.
 
@@
     Let $\beta,\rho>0$.
-    Let $f$ be a convex function and let $\star \theta = \argmin_{\theta : \ltwo{\theta}\le \beta} f(\theta)$.
+    Let $f$ be a convex, $\rho$-Lipschitz function and let $\star \theta = \argmin_{\theta : \ltwo{\theta}\le \beta} f(\theta)$.
     Assume that SGD is run for $T$ iterations with $\eta = \sqrt{\frac{\beta^2}{\rho^2 T}}$.
-    Assume that for all $t$, $\ltwo{\nabla f(\theta^{(t)})} \le \rho$.
+    %Assume that for all $t$, $\ltwo{\nabla f(\theta^{(t)})} \le \rho$.
     Then,
@@
 We now introduce more statistical learning theory notation,
-then apply Theorem \ref{thm:sgd} above to bound the rate of learning.
+and apply Theorem \ref{thm:sgd} above to bound the rate of learning.
 
@@
 In order to apply Theorem \ref{thm:sgd} to a learning problem,
-we make the following assumption about our the size of our data points:
+we make the following assumption about the size of our data points.
 \begin{assumption}
@@
 \end{assumption}
+%For standard data distributions (e.g. any sub-normal distribution),
+%$\rho$ is upper bounded by $O(\sqrt{d})$.
 Under this assumption, the cross entropy loss $\ell$ is $\rho$-Lipschitz for all parameterizations,
@@
 
-Applying Theorem \ref{thm:sgd} with $f=L_D$ gives
-\begin{corollary}
+We use SGD to optimize $L_D$.
+We let $f=L_D$, and $\theta = A$,
+so $\nu_t$ is the gradient of $\ell$ on the $t$th data point.
+Applying Theorem \ref{thm:sgd} gives the following convergence bound.
+\begin{lemma}
     \label{ref:cor:A}
-    Under Assumption \ref{ass:lip}, we have that for any parameterization $A$ of the cross entropy loss,
+    Under Assumption \ref{ass:lip},
+    we have that for any parameterization $A$ of the cross entropy loss,
+    SGD converges at the rate
     \begin{equation}
@@
     \end{equation}
-\end{corollary}
-
-We can now bound the convergence of the standard cross entropy loss and the $U$ and $V$-tree losses by bounding the Frobenius norms of their parameter matrices.
-
-In order to recover the standard convergence rate of multiclass classification, we make the following assumption.
+\end{lemma}
+
+We emphasize that this convergence rate above is both computational and statistical.
+The expression on the left hand side of \eqref{eq:Aconv} is equivalent to the expected generalization error of the parameter $\bar A$,
+and so we use the terms ``convergence rate'' and ``generalization error'' essentially interchangeably.
+
+The important intuition of Lemma \ref{ref:cor:A} is that the generalization error of the cross entropy loss depends on the Frobenious norm of the optimal parameter matrix.
+We can therefore compare the convergence of the standard parameterization with the $U$/$V$-tree parameterizations by comparing these norms.
+
+Our next task is to recover the standard convergence rate of multi-class classification, and so we will now bound $\lF{\star W}$.
+We make the following assumption.
 \begin{assumption}
@@
 \end{assumption}
-Note that this assumption is not limiting because the value of $B$ need not be known during the optimization procedure.
-
+%Note that this assumption is not limiting because the value of $B$ need not be known during the optimization procedure.
+%
 It follows that
@@
 Substituting Eq \eqref{eq:starW} into \eqref{eq:Aconv} gives the following bound.
-
-\begin{theorem}
+\begin{corollary}
 \label{theorem:xentropy}
-    Under assumptions \ref{ass:lip} and \ref{ass:B} above,
-then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
+    Under assumptions \ref{ass:lip} and \ref{ass:B},
+    then the generalization error of the standard cross entropy parameterization when trained with SGD is
 \begin{equation}
@@
 \end{equation}
-\end{theorem}
-\fixme{
+\end{corollary}
+
+\ignore{
 It is important to note that this result above is an upper bound and not a lower bound.
@@
 
-\subsection {Bad Tree Structures}
-
-\begin{lemma}
-    \label{lemma:starV}
-    We have that for all $V$-trees derived from a $U$-tree,
-    \begin{equation}
-        \lF{\star V} \le \lF{\star U}.
-    \end{equation}
-\end{lemma}
-\fixme{
-\begin{proof}
-\end{proof}
-}
-
-The following lemma shows that even for arbitrarily bad tree structures,
-the bound on the parameter spaces cannot be too bad.
-
+\subsection{Bounding the Tree Loss}
+
+We now bound the Frobenius norm of $\star U$ in order to bound the generalization of the $U$-tree loss.
+By construction, $\lF{\star V} \le \lF{\star U}$,
+so this will also bound the convergence rates of the $V$-tree loss.
+
+The analysis is divided into two parts.
+First, we make no assumptions that the $U$-tree structure is good,
+and we show that even in the worst case $\lF{\star U} = O(\lF{\star W})$.
+This implies that using the tree loss cannot significantly hurt our performance.
 \begin{lemma}
@@
 \end{proof}
-
-\subsection{Good Tree Structures}
-
+Now we consider the more important case of when we have a useful $U$-tree structure that meaningfully captures the similarity between classes.
+This idea is captured in the following assumption.
 \begin{assumption}
-We are given a distance metric $d$ over the labels such that for all labels $i$ and $j$,
+    \label{ass:metric}
+    Let $\lambda >= 1$, and $d$ be a distance metric over the labels such that for all labels $i$ and $j$,
 \begin{equation}
@@
 \end{equation}
-We denote by $c$ the doubling dimension of the metric $d$.
+We denote by $c$ the doubling dimension of the metric $d$,
+and we assume that the $U$-tree structure is built using a cover tree \citep{beygelzimer2006cover}.
 \end{assumption}
+
+The Cover Tree was originally designed for speeding up nearest neighbor queries in arbitrary metric spaces.
+The definition is rather technical, so we do not restate it here.
+Instead, we mention only two important properties of the cover tree.
+First, it can be constructed in time $O(k)$,
+so building the cover tree is a cheap operation that has no meaningful impact on training performance.
+It also only has to be done in the initialization step of the learning process, and not on every iteration.
+Second, the cover tree construction has a hyperparameter which we call \texttt{base}.
+This hyperparameter controls the fanout and depth of the tree because at any node $i$ at depth $\depth{i}$ in the tree,
+the cover tree maintains the invariant that $d(i, \parent{i}) \le \texttt{base}^{-\depth{i}}$.
+Increasing the $\texttt{base}$ hyperparameter results in shorter, fatter trees,
+and decreasing it results in taller, narrower trees.
+Our analysis follows the convention of setting $\texttt{base}=2$,
+but we show in the experiments below that good performance is achieved for a wide range of base values.
+
+The following Lemma uses Assumption \ref{ass:metric} and properties of the cover tree to bound the norm of $\lF{\star U}$.
+It is our main technical result and the proof is deferred to the appendix.
 
@@
     \label{lemma:main}
-    When $c\le1$, we have that
-    \begin{equation}
-        \lF{\star U} \le \tfrac{1}{\sqrt2}\lambda B \sqrt{\log_2 k}.
+    Under Assumptions \ref{ass:B} and \ref{ass:metric},
+    when $c\le1$, we have that
+    \begin{equation}
+        \lF{\star U} \le \tfrac{1}{\sqrt2}\lambda B \sqrt{\log_2 k},
         \label{eq:c<=1}
     \end{equation}
-    When $c>1$, we have that
+    and when $c>1$, we have that
     \begin{equation}
@@
 
-\fixme{
-\begin{proof}
-    First, we review some simple properties of the cover tree structure that will be needed in our proof.
-    Let $q$ denote the maximum number of children of any node in the cover tree.
-    A standard property of cover trees is that $q \le (4^c)$ \citep[Lemma 25]{izbickithesis}.
-    Let $Q_i$ denote the number of nodes at level $i$ in the cover tree.
-    Then we have that $|Q_i| \le q^i.$
-    Finally, let $r$ be the height of the cover tree.
-    Without loss of generality, we analyze the bound when the cover tree is perfectly balanced and so $r = \log_q k = \log_2 k / (2c)$.
-
-We have that
-\begin{align}
-    \lF{\star U}^2
-    &= \sum_{i=1}^k \ltwo{\star\uu_i}^2 \\
-    &= \sum_{i=0}^r \sum_{j\in Q_i} \ltwo{\star\uu_j}^2 \\
-    &= \sum_{i=0}^r \sum_{j\in Q_i} \ltwo{\star\w_j - \star\w_{\parent{j}}}^2 \\
-    &\le \sum_{i=0}^r \sum_{j\in Q_i} \lambda^2 d(j, \parent{j})^2 \\
-    &\le \sum_{i=0}^r \sum_{j\in Q_i} \lambda^2 (B/2^i)^2 \\
-    &\le \sum_{i=0}^r q^i \lambda^2 (B/2^i)^2 \\
-    &\le \sum_{i=0}^r \lambda^2 B^2 (q/4)^i 
-    \label{eq:precases}
-\end{align}
-We proceed by considering the case of $c\le1$ and $c>1$ separately.
-
-When $c\le1$, $q\le4$.
-Substituting into Eq \eqref{eq:precases}, we have
-\begin{align}
-    \lF{\star U}^2
-    &\le \sum_{i=0}^r \lambda^2 B^2 \\
-    &= (r+1) \lambda^2 B^2 \\
-    &= \frac{\log_2k}{2c} \lambda^2 B^2 \\
-    &\le \frac{\log_2k}{2} \lambda^2 B^2
-    .
-\end{align}
-This matches Eq \eqref{eq:c<=1} in the lemma's statement.
-
-When $c>$, then $q>4$.
-We first show the following equality.
-\begin{align}
-\left(\frac q 4\right)^r
-&=
-\left(\frac q 4\right)^{\log_q k}\\
-&=
-\frac{k}{4^{\log_q k}}\\
-&=
-\frac{k}{4^{{\log_4 k}/{\log_4 q}}}\\
-&=
-\frac{k}{k^{1/\log_4 q}}\\
-&=
-k^{\left(1 - {1}/{\log_4 q}\right)} \\
-&=
-k^{\left(1 - 1/c\right)}
-.
-\label{eq:lFU:frac}
-\end{align}
-Substituting into Eq \eqref{eq:precases}, we have
-\begin{align}
-    \lF{\star U}^2
-    &= \lambda^2B^2 \left(\frac{(q/4)^{r+1}-1}{q/4-1}\right) \\
-    \label{eq:lFU:4}
-    &= \lambda^2B^2 \left(\frac{(q/4)k^{(1-1/c)}-1}{q/4-1}\right) \\
-    &\le \lambda^2B^2 \left(\frac{(q/4)k^{(1-1/c)}}{q/4-1}\right) \\
-    &\le 5 \lambda^2B^2 k^{(1-1/c)}
-    \label{eq:lFU:5}
-\end{align}
-    Inequality \eqref{eq:lFU:5} follows because $\tfrac{q/4}{q/4-1} \le 5$ for integer values of $q>4$.
-\end{proof}
-}
+We note that embedding techniques can be used to reduce the intrinsic dimension of the metric ($c$) at the expense of increasing the metric's distortion,
+but we make no attempt to optimize this tradeoff in this paper.
+
+We now state our main result.
+It is an immediate consequence of the fact that $\lF{\star V} \le \lF{\star U}$ and Lemmas \ref{ref:cor:A} and \ref{lemma:main}.
+\begin{corollary}
+    \label{cor:main}
+    Under assumptions \ref{ass:lip}, \ref{ass:B}, and \ref{ass:metric},
+    when $c\le1$, the generalization error of the tree loss is bounded by
+\begin{equation}
+    \E L_D(\bar V) - L_D(V^*)
+    \le \frac {\lambda B\rho \sqrt{\log_2 k}}{\sqrt 2n}
+    .
+\end{equation}
+    When $c>1$, the generalization error of the tree loss is bounded by
+\begin{equation}
+    \E L_D(\bar V) - L_D(V^*)
+    \le \frac {\lambda B\rho \sqrt{5 k^{(1-1/c)}}}{\sqrt n}
+    .
+\end{equation}
+\end{corollary}
+These convergence rates are asymptotically better than the convergence rates for the standard parameterization of the cross entropy loss.
 
@@
 
+We evaluate the tree loss on 4 synthetic and 3 real world experiments.
+We compare the tree loss to the standard cross entropy loss, the recently proposed simloss \citep{Kobs2020SimLossCS}, and the confusingly similar hierarchical softmax \citep{morin2005hierarchical}.
+The results confirm our theoretical findings from Section \ref{sec:theory} and demonstrate that the tree loss significantly improves the performance of these baseline losses in a wide range of scenarios.
+
 \subsection{Synthetic data}
 
-In this experiment we will demonstrate the tree loss's effectiveness on a simple multiclass logistic regression problem.
-The problem will be specifically designed to be convex and have low intrinsic dimension in the class labels in order to illustrate the advantages of the cover tree loss.
+Experiments on synthetic data let us control various hyperparameters of the dataset in order to see how the tree loss behaves in a wide range of scenarios.
+The next subsection introduces our data generation procedure,
+and then subsequent subsections describe 4 different experiments baed on this procedure.
 
@@
 
+Our data generation procedure has 4 key hyperparameters:
+the number of data points $n$, the number of feature dimensions $d$, the number of classes $k$, and a randomness parameter $\sigma$.
+
 Let $\mathcal N$ be the standard normal distribution.
-Then sample the true parameter matrix
+Then sample the true parameter matrix as
 \begin{align}
@@
 For all $i \in [k]$, the row $\w_i^*$ of $W^*$ corresponds to the parameter vector for class $i$ and has dimension $d$.
+Standard results on random matrices show that $\lF{\star W} = O(\sqrt{kd})$ with high probability, as assumed by our theory.
 
@@
     y_i &\sim \text{Uniform}([k]), \text{and} \\
-    \x_{i} &\sim \mathcal N(\w^*_{y_i}; \sigma),
+    \x_{i} &\sim \mathcal N(\w^*_{y_i}; \sigma).
 \end{align}
-where $\sigma$ controls the noise in the dataset.
-Increasing $\sigma$ adds noise and makes classes harder to distinguish,
-whereas decreasing $\sigma$ reduces noise and makes the classes easier to distinguish.
-
-With our problem defined in this way, it is clear that the empirical risk minimizer
-\begin{equation}
-    \hat W = \argmin_{W} \tfrac 1 n \ell(W; \x_i, y_i)
-\end{equation}
-converges to $W^*$.
+
+Observe that larger $\sigma$ values result in
+more noise in the data points,
+making the classes harder to distinguish,
+and increasing the bayes error of the problem.
+Also observe that for any two classes $i$ and $j$,
+the distance between the two classes $\ltwo{\star\w_i - \star\w_j} = O(\sqrt{d})$.
+This implies that as $d$ increases,
+the separation between data points from different classes will also increase,
+reducing the bayes error of the problem.
+
+%With our problem defined in this way, it is clear that the empirical risk minimizer
+%\begin{equation}
+    %\hat W = \argmin_{W} \tfrac 1 n \ell(W; \x_i, y_i)
+%\end{equation}
+%converges to $W^*$.
 
@@
 
-In this experiment, we investigate the tree loss's performance in a wide range of settings as we vary the number of data points ($n$), the number of dimensions ($d$), number of class labels ($k$), and the Bayes error ($\sigma$) of our problem.
-First, we construct a standard experimental setting with $n=100$, $d=64$, $k=10$, and $\sigma=1$.
-Then, for each of these parameters, we investigate the effect of that parameter's performance on the problem by varying it over a large range.
+Our first experiment investigates the tree loss's performance in a wide range of statistical settings controlled by the dataset hyperparameters ($n$, $d$, $k$, and $\sigma$).
+We use a baseline experimental setting with $n=100$, $d=64$, $k=10$, and $\sigma=1$.
+For each of the hyperparameters, we investigate the effect of that hyperparameter's performance on the problem by varying it over a large range.
 For each value in the range, we:
-(1) randomly sample 50 problems using the procedure described in Section \ref{sec:exp:synth:problem};
-(2) for each problem, we:
-(2a) sample a training set with $n$ data points and a test set with 10000 data points;
+(1) randomly sample 50 different $\star W$ using the procedure described in Section \ref{sec:exp:synth:problem};
+(2) for each $\star W$, we:
+(2a) sample a training set with $n$ data points and a test set with 10000 data points\footnote{The size of the test set is fixed and large to ensure that our results have high statistical significance.};
 (2b) train 4 models on the training set using the standard cross entropy loss, tree loss, simloss, and hierarchical softmax;
-(2c) report the average accuracy accross the sampled test sets.
-
+(2c) report the average accuracy across the sampled test sets.
 Figure \ref{fig:synth:1} shows the results of these experiments.
 As our theory suggests, the tree loss outperforms all other losses in all regimes.
+
 Consider the top-left plot.
-As the number of data points $n$ gets large,
-then all of the models have accuracies that converge to 1;
-for most problems, however, the number of data points will not be sufficiently large to drive the generalization error to 0,
-and the fewer data points that the problem has,
-the better the tree loss performs compared to other losses.
-
-\fixme{
+This plot has a low bayes error, and so all the variation in performance we see is due to the generalization error of the models.
+As the number of data points $n$ grows large,
+then all models generalize well and have accuracies that converge to 1 (except the hierarchical softmax, which is designed for speed not statistical performance).
+In other words, as $n$ grows large, its influence on the cross entropy's convergence rate of $O(\sqrt{k/n})$ dominates the influence of $k$.
+When the number of data points is small (as it typically is in the real world),
+then the dependence on $k$ becomes more important.
+The tree loss's dependence of $O(\sqrt{k^{1-1/c}/n})$ is strictly better than the cross entropy loss's,
+explaining the observed improved performance.
+A similar effect explain's our model's observed improved performance in the bottom-left plot as $k$ varies.
+
+Now consider the top-right plot.
+The bayes error of our problem setup is inversely related to the problem dimension $d$ (see observations in Section \ref{sec:exp:synth:problem}),
+so this plot compares the different loss's performance on different probablem difficulties.
+On maximally easy (large $d$) and hard (small $d$) problems,
+then the tree loss performs similarly to the other loss functions because the performance is dominated by the bayes error and no improvement is possible.
+The main advantage of the tree loss is in the mid-difficulty problems.
+In this regime, performance is dominated by the generalization ability of the different losses,
+and the tree loss's improved generalization results in noticable improvements.
+The bottom-right plot tells a similar story but controls the difficulty of the problem directly by tuning the randomness $\sigma$.
+
+\ignore{
 From figure \ref{fig.1}, it is clear that the tree loss achieves the best performance. 
@@
 This surprising empirical finding actually agrees with our theoretical results in two ways.
-First, Lemmas \ref{lemma:starV} and \ref{lemma:starU} together imply that that $\lF{\star V} = O(\lF{\star W})$,
+First, Lemma \ref{lemma:starU} implies that that $\lF{\star V} = O(\lF{\star W})$,
 and so no tree structure can perform asymptotically worse than the standard cross entropy loss.
@@
 the distance $d_\epsilon$ can still be embedded into the ideal metric $d$ with some large (but finite!) $\lambda$.
-Asymptotically, Lemma \ref{lemma:main} then implies that SGD converges at the rate $O(\sqrt{k^{1-1/c}})$,
+Asymptotically, Corollary \ref{cor:main} then implies that SGD converges at the rate $O(\sqrt{k^{1-1/c}})$,
 which is less than the convergence rate of the standard cross entropy loss.
-\fixme{replace lemma with theorem}
 
@@
 }
+
+\clearpage
+\appendix
+
+\section{Theoretical Results}
+\label{sec:theory}
+
+It is well known that when using the standard cross entropy loss,
+SGD converges at a rate of $O(\sqrt{k/n})$.
+The tree loss's parameter sharing scheme asymptotically improves this convergence rate.
+
+We assume that the class labels have a metric structure and let $c$ denote the doubling dimension of this metric.
+This $c$ is a measure of the difficulty of our problem,
+with larger $c$ implying more complex metrics and a more difficult learning problem.
+This is captured in our convergence rates,
+which show show that the tree loss converges at a rate of $O(\sqrt{\log k/n})$ for $c\le1$ or $O(\sqrt{k^{1-1/c}/n})$ for $c>1$.
+
+But what happens if the tree is poorly constructed?
+Remarkably, nothing bad.
+We also show that for arbitrarily bad label tree structures,
+the $U$ and $V$ losses maintain a $O(\sqrt{k/n})$ convergence rate.
+This suggests that there is essentially no downside to using the tree loss parameterizations.
+
+Our analysis relies on standard properties of stochastic gradient descent.
+In this section, we first review these results,
+then we formally state and prove our main result.
+
+\subsection{SGD Background}
+
+SGD is a standard algorithm for optimizing convex losses,
+and it has many variations.
+Our analysis uses the results from Chapter 14 of \citet{shalev2014understanding} which are based off of a version of SGD that uses parameter averaging.\footnote{
+Other variants of SGD have similar results,
+and we refer the reader to \citet{shalev2014understanding} for a discussion of these variants.}
+In this section we review these results.
+We follow the notation of \citet{shalev2014understanding} as closely as possible,
+but we occasionally change the names of variables to avoid conflicts with variable names used elsewhere in this paper.\footnote{
+    Specifically, we replace all Latin variables with Greek alternatives.
+    We use $\theta$ instead of $\w$, $\nu$ instead of $\vv$, and $\beta$ instead of $B$.
+    The Greek letters $\rho$ and $\eta$ have the same meaning in both documents.
+}
+
+SGD is an iterative procedure for optimizing a function $f : \Theta \to \mathbb R$ given only noisy samples of the function's gradient.
+We let $\theta^{(t)}$ denote the parameter value at iteration $t$,
+and $\eta : \mathbb R$ be the step size.
+Let $\nu_t$ be a noisy gradient of $f$ satisfying
+\begin{equation}
+    \E[\nu_t | \theta^{(t)}] = \nabla f(\theta^{(t)}).
+\end{equation}
+Then the parameter update for step $t$ is defined to be
+\begin{equation}
+    \theta^{(t+1)} = \theta^{(t)} - \eta \nabla \nu_t
+    .
+\end{equation}
+When using parameter averaging, the final model parameters are defined to be
+\begin{equation}
+    \bar\theta = \frac1T \sum_{i=1}^T \theta^{(t)}
+    .
+\end{equation}
+Parameter averaging is not often used in practice because it has a large memory overhead,
+but it is widely used in theoretical analysis of SGD.
+Theorems using parameter averaging are typically much easier to state and prove,
+and equivalent results without parameter averaging typically require an additional $\log T$ factor in their convergence rates \citep{rakhlin2011making}.
+
+The main result we rely on is a bound on the convergence rate of SGD for convex Lipschitz functions.
+We reproduce Theorem 14.8 of \citet{shalev2014understanding} in the theorem below.
+
+\begin{theorem}
+    \label{thm:sgd}
+    Let $\beta,\rho>0$.
+    Let $f$ be a convex, $\rho$-Lipschitz function and let $\star \theta = \argmin_{\theta : \ltwo{\theta}\le \beta} f(\theta)$.
+    Assume that SGD is run for $T$ iterations with $\eta = \sqrt{\frac{\beta^2}{\rho^2 T}}$.
+    %Assume that for all $t$, $\ltwo{\nabla f(\theta^{(t)})} \le \rho$.
+    Then,
+    \begin{equation}
+        \E f(\bar \theta) - f(\star \theta) \le \frac{\beta\rho}{\sqrt{T}}
+        .
+    \end{equation}
+\end{theorem}
+
+\subsection{SGD and Statistical Learning}
+
+We now introduce more statistical learning theory notation,
+and apply Theorem \ref{thm:sgd} above to bound the rate of learning.
+
+Define the true loss of our learning problem as
+\begin{equation}
+    L_D(A) = \E_{(\x,y)\sim D} \ell(A; (\x, y))
+\end{equation}
+where $A \in \{W, U, V\}$ is a parameterization of the cross entropy loss.
+The optimal parameter vector is defined to be the minimum of the true loss:
+\begin{equation}
+    \star A = \argmin_{A} L_D(A).
+\end{equation}
+In order to apply Theorem \ref{thm:sgd} to a learning problem,
+we make the following assumption about the size of our data points.
+\begin{assumption}
+    \label{ass:lip}
+    For each feature vector $\x$ in the data set, 
+        $\ltwo{\x} \le \rho$
+        .
+\end{assumption}
+%For standard data distributions (e.g. any sub-normal distribution),
+%$\rho$ is upper bounded by $O(\sqrt{d})$.
+Under this assumption, the cross entropy loss $\ell$ is $\rho$-Lipschitz for all parameterizations,
+and the true loss $L_D$ is therefore also $\rho$-Lipschitz.
+
+We use SGD to optimize $L_D$.
+We let $f=L_D$, and $\theta = A$,
+so $\nu_t$ is the gradient of $\ell$ on the $t$th data point.
+Applying Theorem \ref{thm:sgd} gives the following convergence bound.
+\begin{lemma}
+    \label{ref:cor:A}
+    Under Assumption \ref{ass:lip},
+    we have that for any parameterization $A$ of the cross entropy loss,
+    SGD converges at the rate
+    \begin{equation}
+        \E L_D(\bar A) - L_D(\star A) \le \frac{\lF{\star A}\rho}{\sqrt n}.
+        \label{eq:Aconv}
+    \end{equation}
+\end{lemma}
+
+We emphasize that this convergence rate above is both computational and statistical.
+The expression on the left hand side of \eqref{eq:Aconv} is equivalent to the expected generalization error of the parameter $\bar A$,
+and so we use the terms ``convergence rate'' and ``generalization error'' essentially interchangeably.
+
+The important intuition of Lemma \ref{ref:cor:A} is that the generalization error of the cross entropy loss depends on the Frobenious norm of the optimal parameter matrix.
+We can therefore compare the convergence of the standard parameterization with the $U$/$V$-tree parameterizations by comparing these norms.
+
+Our next task is to recover the standard convergence rate of multi-class classification, and so we will now bound $\lF{\star W}$.
+We make the following assumption.
+\begin{assumption}
+    \label{ass:B}
+    For each class $i$, the optimal parameter vector $\star\w_i$ satisfies
+        $\ltwo{\star\w_i} \le B$
+        .
+\end{assumption}
+%Note that this assumption is not limiting because the value of $B$ need not be known during the optimization procedure.
+%
+It follows that
+\begin{equation}
+    \lF{\star W}^2 = \sum_{i=1}^k \ltwo{\star\w_i} \le kB^2.
+    \label{eq:starW}
+\end{equation}
+Substituting Eq \eqref{eq:starW} into \eqref{eq:Aconv} gives the following bound.
+\begin{corollary}
+\label{theorem:xentropy}
+    Under assumptions \ref{ass:lip} and \ref{ass:B},
+    then the generalization error of the standard cross entropy parameterization when trained with SGD is
+\begin{equation}
+    \E L_D(\bar W) - L_D(W^*)
+    \le \frac {\sqrt kB\rho}{\sqrt n}
+    .
+\end{equation}
+\end{corollary}
+
+\ignore{
+It is important to note that this result above is an upper bound and not a lower bound.
+This $O(\sqrt{k/n})$ convergence rate matches the convergence rate implied by the Nataranj dimension \citep{}.
+We are not aware of any lower bounds for SGD in the Lipschitz setting.
+\citet{nguyen2018tight,jentzen2020lower} study the strongly convex case and find that the upper bounds match the lower bounds.
+}
+
+\subsection{Bounding the Tree Loss}
+
+We now bound the Frobenius norm of $\star U$ in order to bound the generalization of the $U$-tree loss.
+By construction, $\lF{\star V} \le \lF{\star U}$,
+so this will also bound the convergence rates of the $V$-tree loss.
+
+The analysis is divided into two parts.
+First, we make no assumptions that the $U$-tree structure is good,
+and we show that even in the worst case $\lF{\star U} = O(\lF{\star W})$.
+This implies that using the tree loss cannot significantly hurt our performance.
+\begin{lemma}
+    \label{lemma:starU}
+    Under assumption \ref{ass:B},
+    the following bound holds for all $U$-tree structures:
+    \begin{equation}
+        \lF{\star U} \le 2\sqrt{k}B.
+    \end{equation}
+\end{lemma}
+\begin{proof}
+    We have
+    \begin{align}
+        \lF{\star U}^2 
+        &= \sum_{i=1}^k \ltwo{\star\uu_i}^2 \\
+        &= \sum_{i=1}^k \ltwo{\star\w_i - \star\w_{\parent{i}}}^2 \\
+        &\le \sum_{i=1}^k \left(\ltwo{\star\w_i} + \ltwo{\star\w_{\parent{i}}} \right)^2 \\
+        &\le \sum_{i=1}^k (2B)^2 \\
+        &\le k (2B)^2
+        .
+    \end{align}
+\end{proof}
+Now we consider the more important case of when we have a useful $U$-tree structure that meaningfully captures the similarity between classes.
+This idea is captured in the following assumption.
+\begin{assumption}
+    \label{ass:metric}
+    Let $\lambda >= 1$, and $d$ be a distance metric over the labels such that for all labels $i$ and $j$,
+\begin{equation}
+    \frac 1 \lambda d(i,j)
+    \le \ltwo{\star \w_i - \star \w_j}
+    \le \lambda d(i, j).
+\end{equation}
+We denote by $c$ the doubling dimension of the metric $d$,
+and we assume that the $U$-tree structure is built using a cover tree \citep{beygelzimer2006cover}.
+\end{assumption}
+
+The Cover Tree was originally designed for speeding up nearest neighbor queries in arbitrary metric spaces.
+The definition is rather technical, so we do not restate it here.
+Instead, we mention only two important properties of the cover tree.
+First, it can be constructed in time $O(k)$,
+so building the cover tree is a cheap operation that has no meaningful impact on training performance.
+It also only has to be done in the initialization step of the learning process, and not on every iteration.
+Second, the cover tree construction has a hyperparameter which we call \texttt{base}.
+This hyperparameter controls the fanout and depth of the tree because at any node $i$ at depth $\depth{i}$ in the tree,
+the cover tree maintains the invariant that $d(i, \parent{i}) \le \texttt{base}^{-\depth{i}}$.
+Increasing the $\texttt{base}$ hyperparameter results in shorter, fatter trees,
+and decreasing it results in taller, narrower trees.
+Our analysis follows the convention of setting $\texttt{base}=2$,
+but we show in the experiments below that good performance is achieved for a wide range of base values.
+
+The following Lemma uses Assumption \ref{ass:metric} and properties of the cover tree to bound the norm of $\lF{\star U}$.
+It is our main technical result and the proof is deferred to the appendix.
+
+\begin{lemma}
+    \label{lemma:main}
+    Under Assumptions \ref{ass:B} and \ref{ass:metric},
+    when $c\le1$, we have that
+    \begin{equation}
+        \lF{\star U} \le \tfrac{1}{\sqrt2}\lambda B \sqrt{\log_2 k},
+        \label{eq:c<=1}
+    \end{equation}
+    and when $c>1$, we have that
+    \begin{equation}
+        \lF{\star U} \le \sqrt{5}\lambda B \sqrt{k^{(1-1/c)}}.
+        \label{eq:c>1}
+    \end{equation}
+\end{lemma}
+
+\begin{proof}
+    First, we review some simple properties of the cover tree structure that will be needed in our proof.
+    Let $q$ denote the maximum number of children of any node in the cover tree.
+    A standard property of cover trees is that $q \le (4^c)$ \citep[Lemma 25]{izbickithesis}.
+    Let $Q_i$ denote the number of nodes at level $i$ in the cover tree.
+    Then we have that $|Q_i| \le q^i.$
+    Finally, let $r$ be the height of the cover tree.
+    Without loss of generality, we analyze the bound when the cover tree is perfectly balanced and so $r = \log_q k = \log_2 k / (2c)$.
+
+We have that
+\begin{align}
+    \lF{\star U}^2
+    &= \sum_{i=1}^k \ltwo{\star\uu_i}^2 \\
+    &= \sum_{i=0}^r \sum_{j\in Q_i} \ltwo{\star\uu_j}^2 \\
+    &= \sum_{i=0}^r \sum_{j\in Q_i} \ltwo{\star\w_j - \star\w_{\parent{j}}}^2 \\
+    &\le \sum_{i=0}^r \sum_{j\in Q_i} \lambda^2 d(j, \parent{j})^2 \\
+    &\le \sum_{i=0}^r \sum_{j\in Q_i} \lambda^2 (B/2^i)^2 \\
+    &\le \sum_{i=0}^r q^i \lambda^2 (B/2^i)^2 \\
+    &\le \sum_{i=0}^r \lambda^2 B^2 (q/4)^i 
+    \label{eq:precases}
+\end{align}
+We proceed by considering the case of $c\le1$ and $c>1$ separately.
+
+When $c\le1$, $q\le4$.
+Substituting into Eq \eqref{eq:precases}, we have
+\begin{align}
+    \lF{\star U}^2
+    &\le \sum_{i=0}^r \lambda^2 B^2 \\
+    &= (r+1) \lambda^2 B^2 \\
+    &= \frac{\log_2k}{2c} \lambda^2 B^2 \\
+    &\le \frac{\log_2k}{2} \lambda^2 B^2
+    .
+\end{align}
+This matches Eq \eqref{eq:c<=1} in the lemma's statement.
+
+When $c>$, then $q>4$.
+We first show the following equality.
+\begin{align}
+\left(\frac q 4\right)^r
+&=
+\left(\frac q 4\right)^{\log_q k}\\
+&=
+\frac{k}{4^{\log_q k}}\\
+&=
+\frac{k}{4^{{\log_4 k}/{\log_4 q}}}\\
+&=
+\frac{k}{k^{1/\log_4 q}}\\
+&=
+k^{\left(1 - {1}/{\log_4 q}\right)} \\
+&=
+k^{\left(1 - 1/c\right)}
+.
+\label{eq:lFU:frac}
+\end{align}
+Substituting into Eq \eqref{eq:precases}, we have
+\begin{align}
+    \lF{\star U}^2
+    &= \lambda^2B^2 \left(\frac{(q/4)^{r+1}-1}{q/4-1}\right) \\
+    \label{eq:lFU:4}
+    &= \lambda^2B^2 \left(\frac{(q/4)k^{(1-1/c)}-1}{q/4-1}\right) \\
+    &\le \lambda^2B^2 \left(\frac{(q/4)k^{(1-1/c)}}{q/4-1}\right) \\
+    &\le 5 \lambda^2B^2 k^{(1-1/c)}
+    \label{eq:lFU:5}
+\end{align}
+    Inequality \eqref{eq:lFU:5} follows because $\tfrac{q/4}{q/4-1} \le 5$ for integer values of $q>4$.
+\end{proof}
+We note that embedding techniques can be used to reduce the intrinsic dimension of the metric ($c$) at the expense of increasing the metric's distortion,
+but we make no attempt to optimize this tradeoff in this paper.
+
+We now state our main result.
+It is an immediate consequence of the fact that $\lF{\star V} \le \lF{\star U}$ and Lemmas \ref{ref:cor:A} and \ref{lemma:main}.
+\begin{corollary}
+    \label{cor:main}
+    Under assumptions \ref{ass:lip}, \ref{ass:B}, and \ref{ass:metric},
+    when $c\le1$, the generalization error of the tree loss is bounded by
+\begin{equation}
+    \E L_D(\bar V) - L_D(V^*)
+    \le \frac {\lambda B\rho \sqrt{\log_2 k}}{\sqrt 2n}
+    .
+\end{equation}
+    When $c>1$, the generalization error of the tree loss is bounded by
+\begin{equation}
+    \E L_D(\bar V) - L_D(V^*)
+    \le \frac {\lambda B\rho \sqrt{5 k^{(1-1/c)}}}{\sqrt n}
+    .
+\end{equation}
+\end{corollary}
+These convergence rates are asymptotically better than the convergence rates for the standard parameterization of the cross entropy loss.
+
 \end{document}

### 2021-10-15 paper/paper.tex
changes
upload

@@
 and stochastic gradient descent (SGD) is the most common algorithm for optimizing this loss.
-Standard results show that generalization error decays at a rate of $O(\sqrt{kd/n})$,
-where $k$ is the number of class labels, $d$ is the number of feature dimensions, and $n$ is the number of data points.
+Standard results show that the generalization error decays at a rate of $O(\sqrt{k/n})$,
+where $k$ is the number of class labels,
+and $n$ is the number of data points.
 These results (which we review later) make no assumptions about the underlying distribution of classes.
@@
 and we introduce the tree loss for exploiting this structure.
-The tree loss is the first multi-class loss function with provably better generalization error than the cross entropy loss.
-We show that if the class label metric has doubling dimension $c$,
-then SGD applied to the tree loss will converge at a rate of $O(\sqrt{d \log k/n})$ when $c\le 1$ or $O(\sqrt{k^{1-1/c}d/n})$ when $c\ge 1$.
-These improvements are most dramatic for small $c$,
-and our empirical results show that many real world classification problems have a label structure with small $c$.
+The doubling dimension $c$ of a metric space is a common measure of the complexity of the metric,
+and we show that SGD applied to the tree loss will converge at a rate of $O(\sqrt{\log k/n})$ when $c\le 1$ or $O(\sqrt{k^{1-1/c}/n})$ when $c\ge 1$.
+These improvements are obviously most dramatic for small $c$,
+and many most dramatic for small $c$,
+but the tree loss is the first multi-class loss function with provably better generalization error than the cross entropy loss in any regime.
 
 Our paper is organized as follows.
-We begin in Section \ref{sec:related} by discussing limitations of related loss functions and how the tree loss will address those limitations.
-Section \ref{sec:tree} then formally defines the tree loss.
+We begin in Section \ref{sec:related} by discussing limitations of related loss functions and how the tree loss addresses those limitations.
+Section \ref{sec:problem} then formally defines the problem setting, and Section \ref{sec:tree} formally defines the tree loss.
 We emphasize that the tree loss is simply a reparameterization of the standard cross entropy loss,
@@
 Finally, Section \ref{sec:experiment} conducts experiments on synthetic, real world image (CIFAR100, ImageNet) and text (Twitter) data.
-We show that in practice, the tree loss essentially always outperforms the cross entropy loss.
-
-\section{Related Work}
-\label{sec:related}
-
-Previous work on multi-class loss functions have focused on improving either the statistical or computational performance.
-Statistical work includes loss functions designed for hierarchichally structured labels \citep{cesa2006incremental,wu2017hierarchical},
-loss functions for improving top-$k$ accuracy \citep{lapin2016loss},
-or focusing on noisy labels \citep{sukhbaatar2014training,zhang2018generalized}.
-The work most similar to ours is the simloss \citep{Kobs2020SimLossCS},
-which also makes a metric assumptions about the class label structure.
-Our work improves on all of this statistical work by being the first to provide convergence bounds that improve on the bounds of the cross entropy loss.
-
-Other work focuses on improving the speed of multiclass classification.
-The hierarchical softmax \citep{morin2005hierarchical} is a particularly well studied variant of the cross entropy loss with many variations \citep[e.g.][]{Peng2017IncrementallyLT,Jiang2017ExplorationOT,Yang2017OptimizeHS,Mohammed2018EffectivenessOH}.
-It is easily confused with our tree loss because both loss functions involve a tree structure.
-The difference, however, is that the hierarchical softmax focuses on improving runtime performance,
-and most variants actually sacrifice statistical performance to do so.
-The tree loss, in contrast maintains the runtime performance of the standard cross entropy loss but improves the statistical performance.
-Our empirical results in Section \ref{sec:experiment} show that the tree loss has much better statistical performance than the hierarchical softmax.
-Other variations of the cross entropy loss include negative sampling, as used in the celebrated word2vec model \citep{mikolov2013distributed}. 
-Like with the hierarchical softmax, negative sampling makes no attempt to improve statistical performance.
-
-\ignore{
-%Hierarchical classification \citep{cesa2006incremental}
-%Hierarchical but without success \citep{wu2017hierarchical}
-%
-%Focus on top-$k$ accuracy rather than top-1 accuracy \citep{lapin2016loss}
-%
-%Requires custom training procedure \citep{liu2017easy}
-%
-%Noisy labels \citep{sukhbaatar2014training,zhang2018generalized}
-
-When people do a multi-class classification task, the standard loss function is cross entropy.
-The mechanism of cross entropy loss function is to maximize the assigned target class probability and punishes every misclassification equally, independent of some other information about the predicted class.
-However, classes often have an internal structure. 
-For example, dog and cat belong to same 'parent': animal and many transportations have same 'parent' while they have different brothers.
-Take the internal structure in the training procedure would allow the classifier to make less sever mistakes as it learns to predict similar classes.
-In terms of theoretical result, the parameter matrix of cross entropy loss is bounded by $\sqrt{k}B$ (where $k$ is the number of classes) and for $n$ data points, the generalization error is $O(\sqrt{k/n})$ which is dependent on $k$.
-
-In this paper, we introduce the tree loss which take advantage of the internal structure bewtween classes.
-The idea of the tree loss is that we use tree structure to reduce the bound of the size of the parameter space and then the generalization error of the tree loss is $O(\sqrt{1/n})$ which is independent of $k$.
-In the tree loss, we take a tree structure which defined by similarity between classes to re-parameterize the weight matrix for the cross entropy loss.
-We incorporate class similarities with loss function to make the model learn more information about classes.
-It can benefit the tasks on unbalanced datasets.
-Take a emoji prediction task as an example, people often use emojis in tweets.
-However, some emojis are popular and some emojis are rarely used.
-This leads to an unbalanced tweets data and there is not enough training data for unpopular emojis.
-The tree loss can learn more information and work well for unbalanced data.
-
-Our contributions are as below:
-\begin{itemize}
-    \item [1] 
-    We introduce the tree loss which take advantage of internal structure between all classes.
-    \item [2] 
-    We provide theoretical justification that the generalization error of the tree loss is independent of the number of classes.
-    \item [3]
-    We evaluate our tree loss on experiments. One is experiment on fully synthetic data which is designed to be convex. The another one is on real world data: CIFAR100, IMAGENET and TWITTER dataset.
-
-\end{itemize}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We show that in practice, the tree loss essentially always outperforms other multi-class loss functions.
+
 \begin{figure*}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Related Work}
+\label{sec:related}
+
+Previous work on multi-class loss functions has focused on improving either the statistical or computational performance.
+Statistical work includes loss functions designed for hierarchichally structured labels \citep{cesa2006incremental,wu2017hierarchical},
+loss functions for improving top-$k$ accuracy \citep{lapin2016loss},
+or focusing on noisy labels \citep{sukhbaatar2014training,zhang2018generalized}.
+The work most similar to ours is the simloss \citep{Kobs2020SimLossCS},
+which also makes a metric assumptions about the class label structure.
+Our work improves on all of this statistical work by being the first to provide convergence bounds that improve on the bounds of the cross entropy loss.
+
+Other work focuses on improving the speed of multiclass classification.
+The hierarchical softmax \citep{morin2005hierarchical} is a particularly well studied variant of the cross entropy loss with many variations \citep[e.g.][]{Peng2017IncrementallyLT,Jiang2017ExplorationOT,Yang2017OptimizeHS,Mohammed2018EffectivenessOH}.
+It is easily confused with our tree loss because both loss functions involve a tree structure.
+The difference, however, is that the hierarchical softmax focuses on improving runtime performance,
+and most variants actually sacrifice statistical performance to do so.
+The tree loss, in contrast, maintains the runtime performance of the standard cross entropy loss but improves the statistical performance.
+%Our empirical results in Section \ref{sec:experiment} show that the tree loss has much better statistical performance than the hierarchical softmax.
+%Other variations of the cross entropy loss include negative sampling, as used in the celebrated word2vec model \citep{mikolov2013distributed}. 
+%Like with the hierarchical softmax, negative sampling makes no attempt to improve statistical performance.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Problem Setting}
-\label{sec:tree}
+\label{sec:problem}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{The Tree Loss}
+\label{sec:tree}
 
@@
 
-It is well known that when using the standard cross entropy loss,
-SGD converges at a rate of $O(\sqrt{k/n})$.
-The tree loss's parameter sharing scheme asymptotically improves this convergence rate.
-
-We assume that the class labels have a metric structure and let $c$ denote the doubling dimension of this metric.
-This $c$ is a measure of the difficulty of our problem,
-with larger $c$ implying more complex metrics and a more difficult learning problem.
-This is captured in our convergence rates,
-which show show that the tree loss converges at a rate of $O(\sqrt{\log k/n})$ for $c\le1$ or $O(\sqrt{k^{1-1/c}/n})$ for $c>1$.
-
-But what happens if the tree is poorly constructed?
-Remarkably, nothing bad.
-We also show that for arbitrarily bad label tree structures,
-the $U$ and $V$ losses maintain a $O(\sqrt{k/n})$ convergence rate.
-This suggests that there is essentially no downside to using the tree loss parameterizations.
-
-Our analysis relies on standard properties of stochastic gradient descent.
-In this section, we first review these results,
-then we formally state and prove our main result.
-
-\subsection{SGD Background}
-
-SGD is a standard algorithm for optimizing convex losses,
-and it has many variations.
-Our analysis uses the results from Chapter 14 of \citet{shalev2014understanding} which are based off of a version of SGD that uses parameter averaging.\footnote{
-Other variants of SGD have similar results,
-and we refer the reader to \citet{shalev2014understanding} for a discussion of these variants.}
-In this section we review these results.
-We follow the notation of \citet{shalev2014understanding} as closely as possible,
-but we occasionally change the names of variables to avoid conflicts with variable names used elsewhere in this paper.\footnote{
-    Specifically, we replace all Latin variables with Greek alternatives.
-    We use $\theta$ instead of $\w$, $\nu$ instead of $\vv$, and $\beta$ instead of $B$.
-    The Greek letters $\rho$ and $\eta$ have the same meaning in both documents.
-}
-
-SGD is an iterative procedure for optimizing a function $f : \Theta \to \mathbb R$ given only noisy samples of the function's gradient.
-We let $\theta^{(t)}$ denote the parameter value at iteration $t$,
-and $\eta : \mathbb R$ be the step size.
-Let $\nu_t$ be a noisy gradient of $f$ satisfying
-\begin{equation}
-    \E[\nu_t | \theta^{(t)}] = \nabla f(\theta^{(t)}).
-\end{equation}
-Then the parameter update for step $t$ is defined to be
-\begin{equation}
-    \theta^{(t+1)} = \theta^{(t)} - \eta \nabla \nu_t
-    .
-\end{equation}
-When using parameter averaging, the final model parameters are defined to be
-\begin{equation}
-    \bar\theta = \frac1T \sum_{i=1}^T \theta^{(t)}
-    .
-\end{equation}
-Parameter averaging is not often used in practice because it has a large memory overhead,
-but it is widely used in theoretical analysis of SGD.
-Theorems using parameter averaging are typically much easier to state and prove,
-and equivalent results without parameter averaging typically require an additional $\log T$ factor in their convergence rates \citep{rakhlin2011making}.
-
-The main result we rely on is a bound on the convergence rate of SGD for convex Lipschitz functions.
-We reproduce Theorem 14.8 of \citet{shalev2014understanding} in the theorem below.
-
-\begin{theorem}
-    \label{thm:sgd}
-    Let $\beta,\rho>0$.
-    Let $f$ be a convex, $\rho$-Lipschitz function and let $\star \theta = \argmin_{\theta : \ltwo{\theta}\le \beta} f(\theta)$.
-    Assume that SGD is run for $T$ iterations with $\eta = \sqrt{\frac{\beta^2}{\rho^2 T}}$.
-    %Assume that for all $t$, $\ltwo{\nabla f(\theta^{(t)})} \le \rho$.
-    Then,
-    \begin{equation}
-        \E f(\bar \theta) - f(\star \theta) \le \frac{\beta\rho}{\sqrt{T}}
-        .
-    \end{equation}
-\end{theorem}
-
-\subsection{SGD and Statistical Learning}
-
-We now introduce more statistical learning theory notation,
-and apply Theorem \ref{thm:sgd} above to bound the rate of learning.
-
+We use standard properties of stochastic gradient descent to bound the generalization error of the tree loss.
+In this section we formally state our main results,
+but we do not review the details about stochastic gradient descent or prove the results.
+Appendix \ref{appendix:theory} reviews stochastic gradient descent in detail and uses the results to prove the theorems below.
+
+To state our results, we first must introduce some learning theory notation.
 Define the true loss of our learning problem as
@@
 where $A \in \{W, U, V\}$ is a parameterization of the cross entropy loss.
-The optimal parameter vector is defined to be the minimum of the true loss:
+The optimal parameter vector is defined to be the minimum of the true loss
 \begin{equation}
@@
 \end{equation}
-In order to apply Theorem \ref{thm:sgd} to a learning problem,
-we make the following assumption about the size of our data points.
+%and we let $\bar A$ denote the parameter matrix learned by running SGD.
+The key idea of our technique is that $\lF{\star A}$ bounds the generalization error SGD with parameterization $A$,
+and we prove bounds on $\lF{\star W}$, $\lF{\star U}$, and $\lF{\star V}$.
+This idea is formalized in the following assumption and lemma.
+
 \begin{assumption}
@@
 \end{assumption}
-%For standard data distributions (e.g. any sub-normal distribution),
-%$\rho$ is upper bounded by $O(\sqrt{d})$.
-Under this assumption, the cross entropy loss $\ell$ is $\rho$-Lipschitz for all parameterizations,
-and the true loss $L_D$ is therefore also $\rho$-Lipschitz.
-
-We use SGD to optimize $L_D$.
-We let $f=L_D$, and $\theta = A$,
-so $\nu_t$ is the gradient of $\ell$ on the $t$th data point.
-Applying Theorem \ref{thm:sgd} gives the following convergence bound.
 \begin{lemma}
@@
 and so we use the terms ``convergence rate'' and ``generalization error'' essentially interchangeably.
-
-The important intuition of Lemma \ref{ref:cor:A} is that the generalization error of the cross entropy loss depends on the Frobenious norm of the optimal parameter matrix.
-We can therefore compare the convergence of the standard parameterization with the $U$/$V$-tree parameterizations by comparing these norms.
 
@@
 \end{assumption}
-%Note that this assumption is not limiting because the value of $B$ need not be known during the optimization procedure.
-%
 It follows that
@@
 
-\ignore{
-It is important to note that this result above is an upper bound and not a lower bound.
-This $O(\sqrt{k/n})$ convergence rate matches the convergence rate implied by the Nataranj dimension \citep{}.
-We are not aware of any lower bounds for SGD in the Lipschitz setting.
-\citet{nguyen2018tight,jentzen2020lower} study the strongly convex case and find that the upper bounds match the lower bounds.
-}
-
-\subsection{Bounding the Tree Loss}
-
-We now bound the Frobenius norm of $\star U$ in order to bound the generalization of the $U$-tree loss.
-By construction, $\lF{\star V} \le \lF{\star U}$,
-so this will also bound the convergence rates of the $V$-tree loss.
-
+Next, we bound $\lF{\star U}$ and $\lF{\star V}$ in order to bound the generalization error of the $U$/$V$ parameterizations.
 The analysis is divided into two parts.
@@
     \begin{equation}
-        \lF{\star U} \le 2\sqrt{k}B.
+        \lF{\star V} \le \lF{\star U} \le 2\sqrt{k}B.
     \end{equation}
 \end{lemma}
-\begin{proof}
-    We have
-    \begin{align}
-        \lF{\star U}^2 
-        &= \sum_{i=1}^k \ltwo{\star\uu_i}^2 \\
-        &= \sum_{i=1}^k \ltwo{\star\w_i - \star\w_{\parent{i}}}^2 \\
-        &\le \sum_{i=1}^k \left(\ltwo{\star\w_i} + \ltwo{\star\w_{\parent{i}}} \right)^2 \\
-        &\le \sum_{i=1}^k (2B)^2 \\
-        &\le k (2B)^2
-        .
-    \end{align}
-\end{proof}
 Now we consider the more important case of when we have a useful $U$-tree structure that meaningfully captures the similarity between classes.
@@
 The following Lemma uses Assumption \ref{ass:metric} and properties of the cover tree to bound the norm of $\lF{\star U}$.
-It is our main technical result and the proof is deferred to the appendix.
-
+It is our most difficult technical result.
 \begin{lemma}
@@
 We now state our main result.
-It is an immediate consequence of the fact that $\lF{\star V} \le \lF{\star U}$ and Lemmas \ref{ref:cor:A} and \ref{lemma:main}.
+It is an immediate consequence Lemmas \ref{ref:cor:A}, \ref{lemma:starU} and \ref{lemma:main}.
 \begin{corollary}
@@
 
-%Substituting \eqref{eq:lFU:frac} info \eqref{eq:lFU:5} gives
-%\begin{align}
-    %\lF{U} \le \lambda B \sqrt{\frac{\log_2 k}{2c} + 1}\sqrt{k^{(1-1/c)}}
-%\end{align}
-%\begin{lemma}
-    %\label{lemma:technical}
-    %For all $a>1$ and $b>1$, we have that
-    %\begin{equation}
-        %\frac {1-a^b}{1-a} \le ba^b
-    %\end{equation}
-%\end{lemma}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{figure*}
+    \centering
+
 \includegraphics[width=\columnwidth,height=1.5in]{fig/images/accuracy_vs_n.png}
 \includegraphics[width=\columnwidth,height=1.5in]{fig/images/accuracy_vs_d.png}
+
 \includegraphics[width=\columnwidth,height=1.5in]{fig/images/accuracy_vs_class.png}
@@
 \caption{
-    Results of our Synthetic Experiments I.
+    Results of Synthetic Experiment I.
     The x-axis of each plot shows which problem parameter is being varied.
@@
 \subsubsection{Experiment I: Data Regimes}
+\label{sec:synth:1}
 
@@
 \includegraphics[width=\columnwidth,height=1.5in]{fig/images/class_v_norm.png}
-\caption{As we increase the number of classes $k$,
+\caption{
+    Results of Synthetic Experiment II.
+    As we increase $k$,
     $\lF{\star V}$ grows significantly slower than $\lF{\star W}$.
-    Since the convergence rate of SGD is proportional to $\lF{\cdot}$ (by Corollary \ref{ref:cor:A}),
+    Since the convergence rate of SGD is proportional to $\lF{\cdot}$ (by Lemma \ref{ref:cor:A}),
     the tree loss converges faster than the standard cross entropy loss. 
@@
 We set $n=1000$, $d=10$, $k=100$, and $\sigma=1$.
-We use a relatively large number of classes $k$ compared to our standard problem in Section \ref{sec:synth:1} above in order to ensure that we have enough classes to generate meaningfully different tree structures.
+We use a relatively large number of classes $k$ compared to the standard problem in Section \ref{sec:synth:1} above in order to ensure that we have enough classes to generate meaningfully different tree structures.
 The basic trends we observe are consistent for all other values of $n$, $d$, and $\sigma$.
@@
 Recall that the cover tree has a parameter \texttt{base} which controls the rate of expansion between layers of the tree.
-As seen in Figure \ref{fig:ct:height}, reducing \texttt{base} increases the height of the tree and increasing \texttt{base} reduces the height of the tree.
+%As seen in Figure \ref{fig:ct:height},
+Reducing \texttt{base} increases the height of the tree and increasing \texttt{base} reduces the height of the tree.
 This will affect the performance of our tree loss because taller trees result in more parameter sharing.
@@
 
-\begin{figure}
-            \includegraphics[width=\columnwidth,height=1.5in]{fig/new_img/height_vs_base.png}
-            \caption{The height of a cover tree varies inversely with it's \texttt{base} hyperparameter.}
-            \label{fig:ct:height}
-\end{figure}
+%\begin{figure}
+            %\includegraphics[width=\columnwidth,height=1.5in]{fig/new_img/height_vs_base.png}
+            %\caption{The height of a cover tree varies inversely with it's \texttt{base} hyperparameter.}
+            %\label{fig:ct:height}
+%\end{figure}
 
@@
 \caption
-            {The tree loss outperforms the standard cross entropy loss for all values of \texttt{base}, but the performance is maximized when $\texttt{base}\approx1.3$.}
+{
+    Results of Synthetic Experiment III.
+    The tree loss outperforms the standard cross entropy loss for all values of \texttt{base}.
+    %but the performance is maximized when $\texttt{base}\approx1.3$.
+}
 \label{fig:ct:acc}
@@
 \caption{
-As $\epsilon\to1$, the quality of our metric for generating the tree structure decreases.
-But even with a perfectly random tree structure,
-the tree loss still outperforms the cross entropy loss.
+Results for Synthetic Experiment IV.
+As $\epsilon\to1$, 
+the tree structure becomes perfectly random.
+The tree loss still outperforms the cross entropy loss in this worst-case scenario.
+    %the quality of our metric for generating the tree structure decreases.
+%But even with a perfectly random tree structure,
+%the tree loss still outperforms the cross entropy loss.
 }  
@@
 It can take advantage of background knowledge about the underlying class structure in order to improve the convergence rate of SGD.
-
-Both our theoretical and empirical results show that the tree loss improves performance over the cross entropy loss in a wide range of circumstances.
-Remarkably, we observe that the tree loss improves performance even when our assumptions about the underlying class structure are perfectly wrong (see Section \ref{sec:synth:eps}).
-We therefore suggest that you replace the cross entropy loss with the tree loss on all of your multiclass problems.
-%there are no downsides there is essentially no downside to using the tree loss as a drop-in replacement for the cross entropy loss.
-%Even if you have no a-priori knowledge about the class structure,
-%and are forced to use a random tree,
-%the tree loss can still improve classification accuracy.
+Both theoretical and empirical results suggest there is no disadvantage for using the tree loss,
+but potentially large advantages.
+
+%Both our theoretical and empirical results show that the tree loss improves performance over the cross entropy loss in a wide range of circumstances.
+%Remarkably, we observe that the tree loss improves performance even when our assumptions about the underlying class structure are perfectly wrong (see Section \ref{sec:synth:eps}).
+%We therefore suggest that you replace the cross entropy loss with the tree loss on all of your multiclass problems.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\ignore{
 \clearpage
@@
 \section{Theoretical Results}
-\label{sec:theory}
+\label{appendix:theory}
 
@@
 These convergence rates are asymptotically better than the convergence rates for the standard parameterization of the cross entropy loss.
+}
 

### 2021-12-03 TreeLoss/loss.py
update emoji embedding

@@ -42,13 +42,13 @@ class CoverTreeLoss(torch.nn.Module):
         self.new2index = new2index
 
     @staticmethod
-    def tree_structure(c, m, base):
+    def tree_structure(c, m):
         '''
         m: embeddings of existed classes
         This function constructs cover tree structure.
         '''
         distance = cosine
-        tree = CoverTree(m, distance, leafsize=1, base=base)
+        tree = CoverTree(m, distance, leafsize=1)
         # _print(tree)
         new_index = path(tree)
 
@@ -70,7 +70,7 @@ class CoverTreeLoss(torch.nn.Module):
         new2index = dict()
         for i in range(len(new_index)):
             new2index[new_index[i][len(new_index[i])-1]] = new_index[i]
-        return new2index, length, tree
+        return new2index, length
 
     def forward(self,
                 weights: torch.Tensor,

### 2021-12-03 TreeLoss/utilities.py

@@ -7,7 +7,7 @@ import os
 import torch
 from sklearn.metrics.pairwise import cosine_similarity
 from .cover_tree import CoverTree
-from transformers import BertModel, BertTokenizer
+# from transformers import BertModel, BertTokenizer
 from tqdm import tqdm
 import math
 
@@ -221,37 +221,37 @@ def adjust_learning_rate(optimizer, epoch, init_lr):
         param_group['lr'] = lr
 
 
-class AttrEncoder(object):
-    def __init__(self, max_len, device) -> None:
-        super().__init__()
-        self.tokenizer = BertTokenizer.from_pretrained('bert-base-uncased')
-        self.model = BertModel.from_pretrained('bert-base-uncased')
-        self.device = device
-        self.model.to(self.device)
-        self.model.eval()
-        self.max_len = max_len
-        self.batch_size = 128
+# class AttrEncoder(object):
+#     def __init__(self, max_len, device) -> None:
+#         super().__init__()
+#         self.tokenizer = BertTokenizer.from_pretrained('bert-base-uncased')
+#         self.model = BertModel.from_pretrained('bert-base-uncased')
+#         self.device = device
+#         self.model.to(self.device)
+#         self.model.eval()
+#         self.max_len = max_len
+#         self.batch_size = 128
 
-    def encoding(self, attr_list):
-        repr_matrix = []
+#     def encoding(self, attr_list):
+#         repr_matrix = []
 
-        with torch.no_grad():
+#         with torch.no_grad():
 
-            for i in tqdm(range(0, len(attr_list), self.batch_size), desc='Encoding Attributes ', ncols=150):
+#             for i in tqdm(range(0, len(attr_list), self.batch_size), desc='Encoding Attributes ', ncols=150):
 
-                attr_batch = attr_list[i: i+self.batch_size]
-                inputs = self.tokenizer(attr_batch, return_tensors="pt", padding=True, truncation=True, max_length=self.max_len)
+#                 attr_batch = attr_list[i: i+self.batch_size]
+#                 inputs = self.tokenizer(attr_batch, return_tensors="pt", padding=True, truncation=True, max_length=self.max_len)
 
-                for k, v in inputs.items():
-                    inputs[k] = v.to(self.device)
+#                 for k, v in inputs.items():
+#                     inputs[k] = v.to(self.device)
 
-                outputs = self.model(**inputs)
-                last_hidden_state = outputs[0]
-                attr_feature = last_hidden_state[:, 0]
[…]

### 2021-12-03 experiments/synthetic/create_figure_1a.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for n in 16 32 64 128 256 512 1024 2048 4096 8192; do
-        python3 run_experiment.py --exp_num=$num --loss=HSM --n=$n --experiment=loss_vs_n
+        python3 new_exp.py --exp_num=$num --loss=HSM --n=$n --experiment=loss_vs_n
     done
 done

### 2021-12-03 experiments/synthetic/create_figure_1b.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for d in 2 4 8 16 32 64 128 256 512 1024; do
-        python3 run_experiment.py --exp_num=$num --loss=HSM --d=$d --experiment=loss_vs_d 
+        python3 new_exp.py --exp_num=$num --loss=HSM --d=$d --experiment=loss_vs_d 
     done
 done

### 2021-12-03 experiments/synthetic/create_figure_1c.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for sigma in 1.0 2.0 3.0 4.0 5.0 6.0 7.0 8.0 9.0 10.0; do
-        python3 run_experiment.py --exp_num=$num --sigma=$sigma --loss=HSM --experiment=loss_vs_sigma
+        python3 new_exp.py --exp_num=$num --sigma=$sigma --loss=HSM --experiment=loss_vs_sigma
     done
 done

### 2021-12-03 experiments/synthetic/create_figure_1d.sh

@@ -3,6 +3,6 @@
 for num in {1..50};
 do
     for c in 10 20 30 40 50 60 70 80 90 100; do
-        python3 run_experiment.py --exp_num=$num --loss=HSM --c=$c --experiment=loss_vs_c
+        python3 new_exp.py --exp_num=$num --loss=simloss --lower_bound=0.9 --c=$c --experiment=loss_vs_c
     done
 done

### 2021-12-03 experiments/synthetic/figure.py

@@ -1,0 +1,75 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+f_tree1 = open(f'1_tree_100_1000.txt', 'r')
+f_tree2 = open(f'2_tree_100_1000.txt', 'r')
+f_tree3 = open(f'3_tree_100_1000.txt', 'r')
+f_tree4 = open(f'4_tree_100_1000.txt', 'r')
+f_tree5 = open(f'5_tree_100_1000.txt', 'r')
+f_xentropy = open('1_xentropy_100_1000.txt','r')
+
+accuracy_tree = []
+accuracy_xentropy = []
+for line in f_tree1:
+    line = line.strip()
+    if len(line)>1:
+        acc_start = line.find('Accuracy:')
+        acc_end  = acc_start + len('Accuracy:')
+
+        acc = float(line[acc_end:].strip())
+
+        accuracy_tree.append(acc)
+for line in f_tree2:
+    line = line.strip()
+    if len(line)>1:
+        acc_start = line.find('Accuracy:')
+        acc_end  = acc_start + len('Accuracy:')
+
+        acc = float(line[acc_end:].strip())
+
+        accuracy_tree.append(acc)
+for line in f_tree3:
+    line = line.strip()
+    if len(line)>1:
+        acc_start = line.find('Accuracy:')
+        acc_end  = acc_start + len('Accuracy:')
+
+        acc = float(line[acc_end:].strip())
+
+        accuracy_tree.append(acc)
+for line in f_tree4:
+    line = line.strip()
+    if len(line)>1:
+        acc_start = line.find('Accuracy:')
+        acc_end  = acc_start + len('Accuracy:')
+
+        acc = float(line[acc_end:].strip())
+
+        accuracy_tree.append(acc)
+for line in f_tree5:
+    line = line.strip()
+    if len(line)>1:
+        acc_start = line.find('Accuracy:')
+        acc_end  = acc_start + len('Accuracy:')
+
+        acc = float(line[acc_end:].strip())
+
+        accuracy_tree.append(acc)
+for line in f_xentropy:
+    line = line.strip()
+    if len(line)>1:
+        acc_start = line.find('Accuracy:')
+        acc_end  = acc_start + len('Accuracy:')
+
+        acc = float(line[acc_end:].strip())
+
+        accuracy_xentropy.append(acc)
+
[…]

### 2021-12-03 experiments/synthetic/new_exp.py

@@ -1,0 +1,176 @@
+
+import sys
+sys.path.append('../..')
+
+import logging
+import os
+import argparse
+parser = argparse.ArgumentParser(description='synthetic data experiment')
+
+parser_data = parser.add_argument_group(
+        title='data generation',
+        description='the variable names for these arguments match exactly the variable names used in the paper'
+        )
+parser_data.add_argument('--exp_num', type=int, default=1)
+parser_data.add_argument('--a', type=int, default=5)
+parser_data.add_argument('--c', type=int, default=100)
+parser_data.add_argument('--n', type=int, default=1000)
+parser_data.add_argument('--d', type=int, default=64)
+parser_data.add_argument('--sigma', type=float, default=1.0)
+parser_data.add_argument('--seed', type=int, default=666)
+parser_data.add_argument('--test', type=int, default=10000)
+
+parser_model = parser.add_argument_group(
+        title='model hyperparameters',
+        description="it's recommended to always use scientific notation for hyperparameter values since we really care about the order of magnitude",
+        )
+parser_model.add_argument('--lr', type=float, default=1e-4, metavar='LR') 
+parser_model.add_argument('--momentum', type=float, default=0.9)
+parser_model.add_argument('--weight_decay', type=float, default=3e-4)
+parser_model.add_argument('--loss', choices=['tree','xentropy','simloss', 'HSM'], default='xentropy')
+parser.add_argument('--lower_bound', type=float, default=0.5)
+
+parser_debug = parser.add_argument_group(title='debug')
+parser_model.add_argument('--experiment', choices=['loss_vs_n','loss_vs_d', 'loss_vs_sigma', 'loss_vs_c', 'loss_vs_structure'], required=True)
+args = parser.parse_args()
+
+import random
+import numpy as np
+import math
+import os
+import torch
+import torch.nn as nn
+import torch.optim as optim
+import torch.nn.functional as F
+from torch.utils.tensorboard import SummaryWriter
+from TreeLoss.utilities import set_seed, gen_sim
+from TreeLoss.loss import CoverTreeLoss, SimLoss, HSM
+
[…]

### 2021-12-03 experiments/synthetic/para.sh

@@ -1,4 +1,4 @@
 for num in {10..1000};
 do
-    python3 para_exp.py --c=$num
+    python3 para_exp_2.py --c=$num
 done

### 2021-12-03 experiments/synthetic/para_exp_2.py

@@ -60,7 +60,7 @@ from TreeLoss.cover_tree import CoverTree
 from TreeLoss.utilities import set_seed, gen_sim, level
 from TreeLoss.loss import CoverTreeLoss, SimLoss, HSM
 import matplotlib.pyplot as plt
-
+from numpy import linalg as LA
 # set the seed
 logging.debug('set_seed('+str(args.seed)+')')
 set_seed(args.exp_num*10)
@@ -160,6 +160,8 @@ def para_figure(W_norm, height):
 
 
 W_norm = torch.norm(W)
-V_norm = torch.norm(V)
-with open('norm.txt', 'a') as f:
+V = V.detach().cpu().numpy()
+V_ = V @ f
+V_norm = LA.norm(V_)
+with open('norm_.txt', 'a') as f:
     f.write(f'W_norm: {W_norm} \t V_norm: {V_norm} \n')

### 2021-12-03 experiments/synthetic/para_figure.py

@@ -2,7 +2,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 import math
 
-f = open('norm.txt', 'r')
+f = open('norm_.txt', 'r')
 
 W = []
 V = []
@@ -28,4 +28,4 @@ l2, = plt.plot(classes, V)
 plt.legend(handles=[l1,l2],labels=[r'$|{W}|$', r'$|{V}|$'], fontsize=15)
 plt.xlabel('Number of Classes($k$)', fontsize=15)
 plt.ylabel('Norm of Vector', fontsize=15)
-plt.savefig('class_v_norm.png', dpi=300)
+plt.savefig('class_v_norm_.png', dpi=300)

### 2021-12-03 experiments/synthetic/plot_figure.py

@@ -7,15 +7,20 @@ import matplotlib.pyplot as plt
 import numpy as np
 import math
 
-f_tree = open(f'{args.experiment}_tree_original.txt', 'r')
-f_xentropy = open(f'{args.experiment}_xentropy_original.txt', 'r')
-f_simloss_1 = open(f'{args.experiment}_simloss_original.txt', 'r')
-f_simloss_2 = open(f'{args.experiment}_simloss_original_0.6.txt', 'r')
-f_simloss_3 = open(f'{args.experiment}_simloss_original_0.7.txt', 'r')
-f_simloss_4 = open(f'{args.experiment}_simloss_original_0.8.txt', 'r')
-f_simloss_5 = open(f'{args.experiment}_simloss_original_0.9.txt', 'r')
-f_simloss = [f_simloss_1, f_simloss_2, f_simloss_3, f_simloss_4, f_simloss_5]
-f_HSM = open(f'{args.experiment}_HSM_original.txt', 'r')
+# f_tree = open(f'{args.experiment}_tree_original.txt', 'r')
+# f_xentropy = open(f'{args.experiment}_xentropy_original.txt', 'r')
+# f_simloss_1 = open(f'{args.experiment}_simloss_original.txt', 'r')
+# f_simloss_2 = open(f'{args.experiment}_simloss_original_0.6.txt', 'r')
+# f_simloss_3 = open(f'{args.experiment}_simloss_original_0.7.txt', 'r')
+# f_simloss_4 = open(f'{args.experiment}_simloss_original_0.8.txt', 'r')
+# f_simloss_5 = open(f'{args.experiment}_simloss_original_0.9.txt', 'r')
+# f_simloss = [f_simloss_1, f_simloss_2, f_simloss_3, f_simloss_4, f_simloss_5]
+# f_HSM = open(f'{args.experiment}_HSM_original.txt', 'r')
+
+f_tree = open(f'{args.experiment}_tree_0.0001.txt','r')
+f_xentropy = open(f'{args.experiment}_xentropy_0.0001.txt', 'r')
+f_simloss = open(f'{args.experiment}_simloss_0.0001.txt', 'r')
+f_HSM = open(f'{args.experiment}_HSM_0.0001.txt', 'r')
 
 loss_tree_all = []
 W_err_tree_all = []
@@ -94,51 +99,89 @@ for num in range(10):
     W_err_xentropy.append(np.mean(W_err_mid))
[…]

### 2021-12-03 experiments/synthetic/proj_exp.py

@@ -1,22 +1,9 @@
-#!/usr/bin/python3
 
-# this is a temporary hack to allow importing the files in the TreeLoss folder when the library is not yet installed
 import sys
 sys.path.append('../..')
 
 import logging
 import os
-LOGLEVEL = os.environ.get('LOGLEVEL', 'WARNING').upper()
-logging.basicConfig(
-    level=LOGLEVEL,
-    format='%(asctime)s.%(msecs)03d %(levelname)s %(module)s - %(funcName)s: %(message)s',
-    datefmt='%Y-%m-%d %H:%M:%S',
-    )
-
-################################################################################
-# command line arguments
-################################################################################
-logging.info('processing command line arguments')
 import argparse
 parser = argparse.ArgumentParser(description='synthetic data experiment')
 
@@ -25,17 +12,16 @@ parser_data = parser.add_argument_group(
         description='the variable names for these arguments match exactly the variable names used in the paper'
         )
 parser_data.add_argument('--exp_num', type=int, default=1)
+parser_data.add_argument('--num', type=int, default=1)
 parser_data.add_argument('--a', type=int, default=5)
-parser_data.add_argument('--c', type=int, default=100)
+parser_data.add_argument('--k', type=int, default=100)
+parser_data.add_argument('--d_', type=int, default=5)
 parser_data.add_argument('--n', type=int, default=1000)
-parser_data.add_argument('--d', type=int, default=10)
+parser_data.add_argument('--d', type=int, default=1000)
 parser_data.add_argument('--sigma', type=float, default=1.0)
 parser_data.add_argument('--seed', type=int, default=666)
-parser_data.add_argument('--base', type=float, default=1.1)
-parser_data.add_argument('--batch', type=int, default=1000)
-parser_data.add_argument('--epoch', type=int, default=1)
-
-
+parser_data.add_argument('--test', type=int, default=10000)
+parser_data.add_argument('--batch', type=int, default=10000)
 
 parser_model = parser.add_argument_group(
         title='model hyperparameters',
[…]

### 2021-12-03 experiments/synthetic/projection.sh

@@ -1,0 +1,9 @@
+
+#!/bin/bash
+
+# for num in {1..50};
+# do
+for d_ in {5..1000}; do
+    python3 proj_exp.py --k=1000 --loss=xentropy --d_=$d_ --experiment=loss_vs_d_
+done
+# done

### 2021-12-03 experiments/synthetic/projection_1.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+# for num in {1..50};
+# do
+for a in {5..200}; do
+    python3 proj_exp.py --num=1 --loss=tree --a=$a --experiment=loss_vs_d_
+done
+# done

### 2021-12-03 experiments/synthetic/projection_2.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+# for num in {1..50};
+# do
+for d_ in {201..400}; do
+    python3 proj_exp.py --num=2 --k=1000 --loss=tree --d_=$d_ --experiment=loss_vs_d_
+done
+# done

### 2021-12-03 experiments/synthetic/projection_3.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+# for num in {1..50};
+# do
+for d_ in {401..600}; do
+    python3 proj_exp.py --num=3 --k=1000 --loss=tree --d_=$d_ --experiment=loss_vs_d_
+done
+# done

### 2021-12-03 experiments/synthetic/projection_4.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+# for num in {1..50};
+# do
+for d_ in {601..800}; do
+    python3 proj_exp.py --num=4 --k=1000 --loss=tree --d_=$d_ --experiment=loss_vs_d_
+done
+# done

### 2021-12-03 experiments/synthetic/projection_5.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+# for num in {1..50};
+# do
+for d_ in {801..1000}; do
+    python3 proj_exp.py --num=5 --k=1000 --loss=tree --d_=$d_ --experiment=loss_vs_d_
+done
+# done

### 2021-12-03 experiments/synthetic/tree_figure.py

@@ -1,14 +1,14 @@
 import argparse
 parser = argparse.ArgumentParser(description='create tree figures')
-parser.add_argument('--experiment', choices=['loss_vs_structure', 'base_experiment', 'para_norm'], required=True)
+parser.add_argument('--experiment', choices=['loss_vs_structure', 'base_experiment', 'para_norm', 'loss_vs_d_'], required=True)
 # parser.add_argument('--loss', choices=['xentropy', 'tree', 'simloss', 'HSM'], required=True)
 args = parser.parse_args()
 
 import matplotlib.pyplot as plt
 import numpy as np
 
-f_tree = open(f'{args.experiment}_tree_50.txt', 'r')
-f_xentropy = open(f'{args.experiment}_xentropy_50.txt', 'r')
+f_tree = open(f'{args.experiment}_tree_100.txt', 'r')
+f_xentropy = open(f'{args.experiment}_xentropy_100.txt', 'r')
 # f_simloss = open(f'{args.experiment}_simloss.txt', 'r')
 # f_HSM = open(f'{args.experiment}_HSM.txt', 'r')
 
@@ -317,4 +317,34 @@ if args.experiment == 'base_experiment':
     plt.ylabel('Loss')
     plt.savefig('loss_vs_base.png', dpi=300)
 
-    
+if args.experiment == 'loss_vs_d_':
+    acc_tree = []
+    acc_xentropy = []
+    for line in f_tree:
+        line = line.strip()
+        if len(line)>1:
+            acc_start = line.find('Accuracy:')
+            acc_end  = acc_start + len('Accuracy:')
+
+            acc = float(line[acc_end:].strip())
+
+            acc_tree.append(acc)
+
+    for line in f_xentropy:
+        line = line.strip()
+        if len(line)>1:
+            acc_start = line.find('Accuracy:')
+            acc_end  = acc_start + len('Accuracy:')
+
+            acc = float(line[acc_end:].strip())
+
+            acc_xentropy.append(acc)
+
+    classes = np.arange(10,1001)
+    plt.figure(0, figsize=(10,5))
+    l1, = plt.plot(classes, acc_tree)
+    l2, = plt.plot(classes, acc_xentropy)
+    plt.legend(handles=[l1,l2],labels=['Tree Loss', 'Cross Entropy Loss'], fontsize=15)
+    plt.xlabel('$d$', fontsize=15)
+    plt.ylabel('Accuracy', fontsize=15)
+    plt.savefig('accuracy_vs_d__.png', dpi=300)

### 2021-12-03 experiments/synthetic/projection_1.sh
update emoji embedding

@@ -1,8 +1,0 @@
-#!/bin/bash
-
-# for num in {1..50};
-# do
-for a in {5..200}; do
-    python3 proj_exp.py --num=1 --loss=tree --a=$a --experiment=loss_vs_d_
-done
-# done

### 2021-12-03 experiments/synthetic/projection_2.sh

@@ -1,8 +1,0 @@
-#!/bin/bash
-
-# for num in {1..50};
-# do
-for d_ in {201..400}; do
-    python3 proj_exp.py --num=2 --k=1000 --loss=tree --d_=$d_ --experiment=loss_vs_d_
-done
-# done

### 2021-12-03 experiments/synthetic/projection_3.sh

@@ -1,8 +1,0 @@
-#!/bin/bash
-
-# for num in {1..50};
-# do
-for d_ in {401..600}; do
-    python3 proj_exp.py --num=3 --k=1000 --loss=tree --d_=$d_ --experiment=loss_vs_d_
-done
-# done

### 2021-12-03 experiments/synthetic/projection_4.sh

@@ -1,8 +1,0 @@
-#!/bin/bash
-
-# for num in {1..50};
-# do
-for d_ in {601..800}; do
-    python3 proj_exp.py --num=4 --k=1000 --loss=tree --d_=$d_ --experiment=loss_vs_d_
-done
-# done

### 2021-12-03 experiments/synthetic/projection_5.sh

@@ -1,8 +1,0 @@
-#!/bin/bash
-
-# for num in {1..50};
-# do
-for d_ in {801..1000}; do
-    python3 proj_exp.py --num=5 --k=1000 --loss=tree --d_=$d_ --experiment=loss_vs_d_
-done
-# done

### 2022-01-18 paper/paper.tex

@@
 These improvements are obviously most dramatic for small $c$,
-and many most dramatic for small $c$,
-but the tree loss is the first multi-class loss function with provably better generalization error than the cross entropy loss in any regime.
+and the tree loss outperforms the cross entropy loss best in this regime.
+The tree loss is the first multi-class loss function with provably better generalization error than the cross entropy loss in any regime.
 
@@
 The work most similar to ours is the simloss \citep{Kobs2020SimLossCS},
-which also makes a metric assumptions about the class label structure.
+which also makes a metric assumption about the class label structure.
 Our work improves on all of this statistical work by being the first to provide convergence bounds that improve on the bounds of the cross entropy loss.
@@
 Other work focuses on improving the speed of multiclass classification.
-The hierarchical softmax \citep{morin2005hierarchical} is a particularly well studied variant of the cross entropy loss with many variations \citep[e.g.][]{Peng2017IncrementallyLT,Jiang2017ExplorationOT,Yang2017OptimizeHS,Mohammed2018EffectivenessOH}.
+The hierarchical softmax \citep{morin2005hierarchical} is a particularly well studied modification of the cross entropy loss with many variations \citep[e.g.][]{Peng2017IncrementallyLT,Jiang2017ExplorationOT,Yang2017OptimizeHS,Mohammed2018EffectivenessOH}.
 It is easily confused with our tree loss because both loss functions involve a tree structure.
@@
 The cross entropy loss has no constraints on the weight matrix that cause similar classes to have similar parameter vectors.
-The tree loss fixes this problem, resulting in faster convergence and better generalization.
+The tree loss adds these constraints,
+resulting in faster convergence and better generalization.
 
@@
 We are now ready to introduce the $U$-tree parameterization.
-Intuitively, we will represent each parameter as the difference between itself and it's parent in the $U$-tree.
+%Intuitively, we will represent each parameter as the difference between itself and it's parent in the $U$-tree.
 We associate for each class $i$ a new parameter vector $\uu_i$ defined to be
@@
 This reparameterization is reminiscent of the way that fastText \citep{bojanowski2017enriching} reparameterizes the word2vec \citep{Mikolov2013EfficientEO} model to improve statistical efficiency.
-Two notable difference, however, are that fastText is a domain-specific adaptation and provides no theoretical guarantees;
+Two notable differences, however, are that fastText is a domain-specific adaptation and provides no theoretical guarantees;
 our tree loss works on any domain and provides theoretical guarantees.
@@
 In our experiments, we observed an approximately 2x slowdown.
+Modifications to the cross entropy loss that improve runtime (such as the hierarchical softmax or negative sampling) could also be used to improve the runtime of the tree loss,
+but we do not explore this possibility in depth in this paper.
 
@@
 but we do not review the details about stochastic gradient descent or prove the results.
-Appendix \ref{appendix:theory} reviews stochastic gradient descent in detail and uses the results to prove the theorems below.
+The Appendix reviews stochastic gradient descent in detail and uses the results to prove the theorems below.
 
@@
 where $A \in \{W, U, V\}$ is a parameterization of the cross entropy loss.
-The optimal parameter vector is defined to be the minimum of the true loss
-\begin{equation}
-    \star A = \argmin_{A} L_D(A).
-\end{equation}
-%and we let $\bar A$ denote the parameter matrix learned by running SGD.
-The key idea of our technique is that $\lF{\star A}$ bounds the generalization error SGD with parameterization $A$,
-and we prove bounds on $\lF{\star W}$, $\lF{\star U}$, and $\lF{\star V}$.
-This idea is formalized in the following assumption and lemma.
-
+We define $\bar A$ to be the result of running SGD on $n$ data points to optimize parameterization $A$,
+and 
+\begin{equation}
+    \star A = \argmin_{A} L_D(A)
+\end{equation}
+to be the optimal parameterization.
+Our goal is to bound the generalization error
+\begin{equation}
+    \E L_D(\bar A) - L_D(\star A).
+\end{equation}
+
+In order to bound this error, we make the following standard assumption about our data.
 \begin{assumption}
@@
 \end{assumption}
+This assumption is equivalent to stating that $L_D$ (or $\ell$) is $\rho$-Lipschitz.
+
+Now our key observation is that $\lF{\star A}$ bounds the generalization error,
+as formalized in the following lemma.
 \begin{lemma}
@@
     we have that for any parameterization $A$ of the cross entropy loss,
-    SGD converges at the rate
     \begin{equation}
@@
 
-We emphasize that this convergence rate above is both computational and statistical.
-The expression on the left hand side of \eqref{eq:Aconv} is equivalent to the expected generalization error of the parameter $\bar A$,
-and so we use the terms ``convergence rate'' and ``generalization error'' essentially interchangeably.
-
-Our next task is to recover the standard convergence rate of multi-class classification, and so we will now bound $\lF{\star W}$.
+%We emphasize that this convergence rate above is both computational and statistical.
+%The expression on the left hand side of \eqref{eq:Aconv} is equivalent to the expected generalization error of the parameter $\bar A$,
+%and so we use the terms ``convergence rate'' and ``generalization error'' essentially interchangeably.
+
+We will next show how to use Lemma \ref{ref:cor:A} to recover the standard convergence rate of multi-class classification by bounding $\lF{\star W}$.
 We make the following assumption.
@@
     Under assumption \ref{ass:B},
-    the following bound holds for all $U$-tree structures:
+    the following bound holds for all $U$/$V$-tree structures:
     \begin{equation}
@@
 \end{lemma}
-Now we consider the more important case of when we have a useful $U$-tree structure that meaningfully captures the similarity between classes.
-This idea is captured in the following assumption.
+Now we consider the more important case of when we have a tree structure that meaningfully captures the similarity between classes.
+This idea is captured in our final assumption.
 \begin{assumption}
@@
 \end{assumption}
+
+The $\lambda$ parameter above measures the quality of our metric.
+When $\lambda=1$, the metric $d$ is good and perfectly predicts the distance between parameter vectors;
+when $\lambda$ is large, the metric $d$ is bad.
 
@@
 First, it can be constructed in time $O(k)$,
-so building the cover tree is a cheap operation that has no meaningful impact on training performance.
-It also only has to be done in the initialization step of the learning process, and not on every iteration.
-Second, the cover tree construction has a hyperparameter which we call \texttt{base}.
+so building the $U$-tree structure is a cheap operation that has no meaningful impact on training performance.
+%It also only has to be done once when initializing the optimization,
+%and not on every iteration.
+Second, the cover tree has a hyperparameter which we call \texttt{base}.
 This hyperparameter controls the fanout and depth of the tree because at any node $i$ at depth $\depth{i}$ in the tree,
@@
 
-We note that embedding techniques can be used to reduce the intrinsic dimension of the metric ($c$) at the expense of increasing the metric's distortion,
+We note that embedding techniques can be used to reduce the intrinsic dimension of the metric ($c$) at the expense of increasing the metric's distortion ($\lambda$),
 but we make no attempt to optimize this tradeoff in this paper.
@@
 
-\includegraphics[width=\columnwidth,height=1.5in]{fig/images/accuracy_vs_n.png}
-\includegraphics[width=\columnwidth,height=1.5in]{fig/images/accuracy_vs_d.png}
-
-\includegraphics[width=\columnwidth,height=1.5in]{fig/images/accuracy_vs_class.png}
-\includegraphics[width=\columnwidth,height=1.5in]{fig/images/accuracy_vs_sigma.png}
+\includegraphics[width=\columnwidth,height=1.45in]{fig/images/accuracy_vs_n.png}
+\includegraphics[width=\columnwidth,height=1.45in]{fig/images/accuracy_vs_d.png}
+
+\includegraphics[width=\columnwidth,height=1.45in]{fig/images/accuracy_vs_class.png}
+\includegraphics[width=\columnwidth,height=1.45in]{fig/images/accuracy_vs_sigma.png}
 \caption{
@@
 We evaluate the tree loss on 4 synthetic and 3 real world experiments.
-We compare the tree loss to the standard cross entropy loss, the recently proposed simloss \citep{Kobs2020SimLossCS}, and the confusingly similar hierarchical softmax \citep{morin2005hierarchical}.
+We compare the tree loss to the standard cross entropy loss, the recently proposed simloss \citep{Kobs2020SimLossCS}, and the hierarchical softmax \citep{morin2005hierarchical}.
 The results confirm our theoretical findings from Section \ref{sec:theory} and demonstrate that the tree loss significantly improves the performance of these baseline losses in a wide range of scenarios.
@@
 \end{align}
-For all $i \in [k]$, the row $\w_i^*$ of $W^*$ corresponds to the parameter vector for class $i$ and has dimension $d$.
+%For all $i \in [k]$, the row $\w_i^*$ of $W^*$ corresponds to the parameter vector for class $i$ and has dimension $d$.
 Standard results on random matrices show that $\lF{\star W} = O(\sqrt{kd})$ with high probability, as assumed by our theory.
@@
 \end{align}
-
 Observe that larger $\sigma$ values result in
@@
 (2a) sample a training set with $n$ data points and a test set with 10000 data points\footnote{The size of the test set is fixed and large to ensure that our results have high statistical significance.};
-(2b) train 4 models on the training set using the standard cross entropy loss, tree loss, simloss, and hierarchical softmax;
-(2c) report the average accuracy across the sampled test sets.
+(2b) train a separate model for each of our loss functions;
+(2c) report the average test accuracy across 50 samples from step (1).
 Figure \ref{fig:synth:1} shows the results of these experiments.
@@
 As the number of data points $n$ grows large,
-then all models generalize well and have accuracies that converge to 1 (except the hierarchical softmax, which is designed for speed not statistical performance).
-In other words, as $n$ grows large, its influence on the cross entropy's convergence rate of $O(\sqrt{k/n})$ dominates the influence of $k$.
-When the number of data points is small (as it typically is in the real world),
+its influence on the standard cross entropy's convergence rate of $O(\sqrt{k/n})$ dominates,
+and the model generalizes well.
+%then all models generalize well. % and have accuracies that converge to 1 (except the hierarchical softmax, which is designed for speed not statistical performance).
+%In other words, as $n$ grows large, its influence on the cross entropy's convergence rate of $O(\sqrt{k/n})$ dominates the influence of $k$.
+When the number of data points is small, %(as it typically is in the real world),
 then the dependence on $k$ becomes more important.
@@
 The bayes error of our problem setup is inversely related to the problem dimension $d$ (see observations in Section \ref{sec:exp:synth:problem}),
-so this plot compares the different loss's performance on different probablem difficulties.
+so this plot compares performance on different problem difficulties.
 On maximally easy (large $d$) and hard (small $d$) problems,
@@
 In this regime, performance is dominated by the generalization ability of the different losses,
-and the tree loss's improved generalization results in noticable improvements.
+and the tree loss's improved generalization results in noticeable improvements.
 The bottom-right plot tells a similar story but controls the difficulty of the problem directly by tuning the randomness $\sigma$.
@@
 
-Corollary \ref{ref:cor:A} suggests that the norm of the parameter matrix is what controls convergence rate of SGD,
-and the proof of our main result in Theorem \ref{} relies on bounding this norm.
-In this experiment, we directly measure the norm of the parameter matrices and show that $\lF{V}$ is significantly less than the $lF{W}$,
+Lemma \ref{ref:cor:A} suggests that the norm of the parameter matrix is what controls convergence rate of SGD,
+and the proof of our main result in Corollary \ref{cor:main} relies on bounding this norm.
+In this experiment, we directly measure the norm of the parameter matrices and show that $\lF{V}$ is significantly less than $\lF{W}$,
 justifying the good convergence rates we observed in Synthetic Experiment I above.
@@
 We set $n=1000$, $d=10$, $k=100$, and $\sigma=1$.
-We use a relatively large number of classes $k$ compared to the standard problem in Section \ref{sec:synth:1} above in order to ensure that we have enough classes to generate meaningfully different tree structures.
+We use a relatively large number of classes $k$ compared to the standard problem in Section \ref{sec:synth:1} above in order to ensure that we have enough classes to generate meaningfully complex tree structures.
 The basic trends we observe are consistent for all other values of $n$, $d$, and $\sigma$.
@@
 The original cover tree paper \citep{beygelzimer2006cover} also found that a \texttt{base} of 1.3 resulted in the fastest nearest neighbor queries.
-It's unclear why 1.3 has this good quality,
-but the fact that this constant results in good computational performance for nearest neighbor queries and good statistical performance in the tree loss, two rather different use cases, suggests that there is something fundamental going on here that we don't yet fully understand.
+We do not know of a good theoretical explanation for this phenomenon.
+%It's unclear why 1.3 has this good quality,
+%but the fact that this constant results in good computational performance for nearest neighbor queries and good statistical performance in the tree loss, two rather different use cases, suggests that there is something fundamental going on here that we don't yet fully understand.
 
@@
 Each row $\bad \w_i$ of $\bad W$ is now a $d$ dimensional random vector that has absolutely no relation to the true parameter vector.
-Next, we define a family of ``$\epsilon$-bad'' parameter vectors that mix between the perfectly bad and perfectly good parameter vectors:
+Next, we define a family of ``$\epsilon$-bad'' parameter vectors that mix between the bad and optimal parameter vectors:
 \begin{equation}
@@
 We now validate the tree loss on real world image (CIFAR100, ImageNet) and text (Twitter) data.
-For each dataset, we report standard top-k accuracy scores,
+For each dataset, we report standard top-1 accuracy scores,
 and the less well known \emph{superclass accuracy} (SA) score.
@@
 Table \ref{table:results} shows that on each of these datasets and for each metric,
-the tree loss outperforms the baseline cross entropy loss and simloss.\footnote{We do not evaluate against the hierarchical softmax on these datasets for computational reasons.
+the tree loss outperforms the baseline cross entropy loss and simloss.\footnote{We do not evaluate against the hierarchical softmax due to limited computational resources.
 The results on the synthetic data, however, suggest that the hierarchical softmax would have performed poorly.}
@@
 CIFAR100 is a standard image dataset with 100 classes \citep{krizhevsky2009learning}.
-It is more difficult than MNIST and CIFAR-10,
+It is more difficult than MNIST and CIFAR10,
 but small and so less computationally demanding than ImageNet.
-
-We follow the procedure used in the SimLoss paper \citep{Kobs2020SimLossCS} in this experiment.
-We generate our distance metric over the class labels using a word2vec model \citep{Mikolov2013EfficientEO} pretrained on GoogleNews.
+In this experiment, we exactly follow the procedure used in the SimLoss paper \citep{Kobs2020SimLossCS}, 
+and find that under their experimental conditions,
+the tree loss has the best performance.
+
+First, we generate our distance metric over the class labels using a word2vec model \citep{Mikolov2013EfficientEO} pretrained on GoogleNews.
 The distance between class labels is defined to be the distance between their corresponding word2vec embeddings.
@@
 We generate our distance metric over the image labels using a pretrained fastText model \citep{bojanowski2017enriching}.
-We use fastText rather than word2vec because many of the class labels contain words not in the word2vec models' vocabulary;
+We use fastText rather than word2vec because many of the class labels contain words not in the word2vec model's vocabulary;
 since fastText is naturally able to handle out-of-vocabulary words,
-there is not need to discard class labels like we did for CIFAR100.
+there is no need to discard class labels like we did for CIFAR100.
 Many ImageNet class label names contain multiple words,
@@
 and demonstrates that the tree loss works across many domains.
-We use the dataset collected by \citep{stoikos2020multilingual} for analyzing emotional response to Covid19 on Twitter.
-This dataset contains all geolocated tweets written in any language sent over the 6 month period between 1 January 2020 and 1 July 2020.
+We use the dataset collected by \citet{stoikos2020multilingual} for analyzing emotional response to Covid19 on Twitter.
+This dataset contains all geolocated tweets written in any language sent over the 6 month period between 1 January 2020 and 1 July 2020 that mention certain Covid19 keywords.
 Tweets in the dataset are preprocessed to have all emojis, usernames, and urls removed from the text,
@@
 \bibliography{paper}
-% \begin{abstract}
-%   The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
-%   both left and right-hand margins. Use 10~point type, with a vertical
-%   spacing of 11~points. The \textbf{Abstract} heading must be centered,
-%   bold, and in point size 12. Two line spaces precede the
-%   Abstract. The Abstract must be limited to one paragraph.
-% \end{abstract}
-
-% \section{GENERAL FORMATTING INSTRUCTIONS}
-
-% The camera-ready versions of the accepted papers are 8 pages,
-% plus any additional pages needed for references.
-
-% Papers are in 2 columns with the overall line width of 6.75~inches (41~picas).
-% Each column is 3.25~inches wide (19.5~picas).  The space
-% between the columns is .25~inches wide (1.5~picas).  The left margin is 0.88~inches (5.28~picas).
-% Use 10~point type with a vertical spacing of
-% 11~points. Please use US Letter size paper instead of A4.
-
-% Paper title is 16~point, caps/lc, bold, centered between 2~horizontal rules.
-% Top rule is 4~points thick and bottom rule is 1~point thick.
-% Allow 1/4~inch space above and below title to rules.
-
-% Author descriptions are center-justified, initial caps.  The lead
-% author is to be listed first (left-most), and the Co-authors are set
-% to follow.  If up to three authors, use a single row of author
-% descriptions, each one center-justified, and all set side by side;
-% with more authors or unusually long names or institutions, use more
-% rows.
-
-% Use one-half line space between paragraphs, with no indent.
-
-% \section{FIRST LEVEL HEADINGS}
-
-% First level headings are all caps, flush left, bold, and in point size
-% 12. Use one line space before the first level heading and one-half line space
-% after the first level heading.
-
-% \subsection{Second Level Heading}
-
-% Second level headings are initial caps, flush left, bold, and in point
-% size 10. Use one line space before the second level heading and one-half line
-% space after the second level heading.
-
-% \subsubsection{Third Level Heading}
-
-% Third level headings are flush left, initial caps, bold, and in point
-% size 10. Use one line space before the third level heading and one-half line
-% space after the third level heading.
-
-% \paragraph{Fourth Level Heading}
-
-% Fourth level headings must be flush left, initial caps, bold, and
-% Roman type.  Use one line space before the fourth level heading, and
-% place the section text immediately after the heading with no line
-% break, but an 11 point horizontal space.
-
-% %%%
-% \subsection{Citations, Figure, References}
-
-% \subsubsection{Citations in Text}
-
-% Citations within the text should include the author's last name and
-% year, e.g., (Cheesman, 1985). 
-% %Apart from including the author's last name and year, citations can follow any style, as long as the style is consistent throughout the paper.  
-% Be sure that the sentence reads
-% correctly if the citation is deleted: e.g., instead of ``As described
-% by (Cheesman, 1985), we first frobulate the widgets,'' write ``As
-% described by Cheesman (1985), we first frobulate the widgets.''
-
-% The references listed at the end of the paper can follow any style as long as it is used consistently.
-
-% %Be sure to avoid
-% %accidentally disclosing author identities through citations.
-
-% \subsubsection{Footnotes}
-
-% Indicate footnotes with a number\footnote{Sample of the first
-%   footnote.} in the text. Use 8 point type for footnotes. Place the
-% footnotes at the bottom of the column in which their markers appear,
-% continuing to the next column if required. Precede the footnote
-% section of a column with a 0.5 point horizontal rule 1~inch (6~picas)
-% long.\footnote{Sample of the second footnote.}
-
-% \subsubsection{Figures}
-
-% All artwork must be centered, neat, clean, and legible.  All lines
-% should be very dark for purposes of reproduction, and art work should
-% not be hand-drawn.  Figures may appear at the top of a column, at the
-% top of a page spanning multiple columns, inline within a column, or
-% with text wrapped around them, but the figure number and caption
-% always appear immediately below the figure.  Leave 2 line spaces
-% between the figure and the caption. The figure caption is initial caps
-% and each figure should be numbered consecutively.
-
-% Make sure that the figure caption does not get separated from the
-% figure. Leave extra white space at the bottom of the page rather than
-% splitting the figure and figure caption.
-% \begin{figure}[h]
-% \vspace{.3in}
-% \centerline{\fbox{This figure intentionally left non-blank}}
-% \vspace{.3in}
-% \caption{Sample Figure Caption}
-% \end{figure}
-
-% \subsubsection{Tables}
-
-% All tables must be centered, neat, clean, and legible. Do not use hand-drawn tables.
-% Table number and title always appear above the table.
-% See Table~\ref{sample-table}.
-
-% Use one line space before the table title, one line space after the table title,
-% and one line space after the table. The table title must be
-% initial caps and each table numbered consecutively.
-
-% \begin{table}[h]
-% \caption{Sample Table Title} \label{sample-table}
-% \begin{center}
-% \begin{tabular}{ll}
-% \textbf{PART}  &\textbf{DESCRIPTION} \\
-% \hline \\
-% Dendrite         &Input terminal \\
-% Axon             &Output terminal \\
-% Soma             &Cell body (contains cell nucleus) \\
-% \end{tabular}
-% \end{center}
-% \end{table}
-
-% \section{SUPPLEMENTARY MATERIAL}
-
-% If you need to include additional appendices during submission, you can include them in the supplementary material file.
-% You can submit a single file of additional supplementary material which may be either a pdf file (such as proof details) or a zip file for other formats/more files (such as code or videos). 
-% Note that reviewers are under no obligation to examine your supplementary material. 
-% If you have only one supplementary pdf file, please upload it as is; otherwise gather everything to the single zip file.
-
-% You must use \texttt{aistats2022.sty} as a style file for your supplementary pdf file and follow the same formatting instructions as in the main paper. 
-% The only difference is that it must be in a \emph{single-column} format.
-% You can use \texttt{supplement.tex} in our starter pack as a starting point.
-% Alternatively, you may append the supplementary content to the main paper and split the final PDF into two separate files.
-
-% \section{SUBMISSION INSTRUCTIONS}
-
-% To submit your paper to AISTATS 2022, please follow these instructions.
-
-% \begin{enumerate}
-%     \item Download \texttt{aistats2022.sty}, \texttt{fancyhdr.sty}, and \texttt{sample\_paper.tex} provided in our starter pack. 
-%     Please, do not modify the style files as this might result in a formatting violation.
-
-%     \item Use \texttt{sample\_paper.tex} as a starting point.
-%     \item Begin your document with
-%     \begin{flushleft}
-%     \texttt{\textbackslash documentclass[twoside]\{article\}}\\
-%     \texttt{\textbackslash usepackage\{aistats2022\}}
-%     \end{flushleft}
-%     The \texttt{twoside} option for the class article allows the
-%     package \texttt{fancyhdr.sty} to include headings for even and odd
-%     numbered pages.
-%     \item When you are ready to submit the manuscript, compile the latex file to obtain the pdf file.
-%     \item Check that the content of your submission, \emph{excluding} references, is limited to \textbf{8 pages}. The number of pages containing references alone is not limited.
-%     \item Upload the PDF file along with other supplementary material files to the CMT website.
-% \end{enumerate}
-
-% \subsection{Camera-ready Papers}
-
-% %For the camera-ready paper, if you are using \LaTeX, please make sure
-% %that you follow these instructions.  
-% % (If you are not using \LaTeX,
-% %please make sure to achieve the same effect using your chosen
-% %typesetting package.)
-
-% If your papers are accepted, you will need to submit the camera-ready version. Please make sure that you follow these instructions:
-% \begin{enumerate}
-%     %\item Download \texttt{fancyhdr.sty} -- the
-%     %\texttt{aistats2022.sty} file will make use of it.
-%     \item Change the beginning of your document to
-%     \begin{flushleft}
-%     \texttt{\textbackslash documentclass[twoside]\{article\}}\\
-%     \texttt{\textbackslash usepackage[accepted]\{aistats2022\}}
-%     \end{flushleft}
-%     The option \texttt{accepted} for the package
-%     \texttt{aistats2022.sty} will write a copyright notice at the end of
-%     the first column of the first page. This option will also print
-%     headings for the paper.  For the \emph{even} pages, the title of
-%     the paper will be used as heading and for \emph{odd} pages the
-%     author names will be used as heading.  If the title of the paper
-%     is too long or the number of authors is too large, the style will
-%     print a warning message as heading. If this happens additional
-%     commands can be used to place as headings shorter versions of the
-%     title and the author names. This is explained in the next point.
-%     \item  If you get warning messages as described above, then
-%     immediately after $\texttt{\textbackslash
-%     begin\{document\}}$, write
-%     \begin{flushleft}
-%     \texttt{\textbackslash runningtitle\{Provide here an alternative
-%     shorter version of the title of your paper\}}\\
-%     \texttt{\textbackslash runningauthor\{Provide here the surnames of
-%     the authors of your paper, all separated by commas\}}
-%     \end{flushleft}
-%     Note that the text that appears as argument in \texttt{\textbackslash
-%       runningtitle} will be printed as a heading in the \emph{even}
-%     pages. The text that appears as argument in \texttt{\textbackslash
-%       runningauthor} will be printed as a heading in the \emph{odd}
-%     pages.  If even the author surnames do not fit, it is acceptable
-%     to give a subset of author names followed by ``et al.''
-
-%     %\item Use the file sample\_paper.tex as an example.
-
-%     \item The camera-ready versions of the accepted papers are 8
-%       pages, plus any additional pages needed for references.
-
-%     \item If you need to include additional appendices,
-%       you can include them in the supplementary
-%       material file.
-
-%     \item Please, do not change the layout given by the above
-%       instructions and by the style file.
-
-% \end{enumerate}
-
-% \subsubsection*{Acknowledgements}
-% All acknowledgments go at the end of the paper, including thanks to reviewers who gave useful comments, to colleagues who contributed to the ideas, and to funding agencies and corporate sponsors that provided financial support.
-% To preserve the anonymity, please include acknowledgments \emph{only} in the camera-ready papers.
-
-% \subsubsection*{References}
-
-% References follow the acknowledgements.  Use an unnumbered third level
-% heading for the references section.  Please use the same font
-% size for references as for the body of the paper---remember that
-% references do not count against your page length total.
-
-% \begin{thebibliography}{}
-% \setlength{\itemindent}{-\leftmargin}
-% \makeatletter\renewcommand{\@biblabel}[1]{}\makeatother
-% \bibitem{} J.~Alspector, B.~Gupta, and R.~B.~Allen (1989).
-%     \newblock Performance of a stochastic learning microchip.
-%     \newblock In D. S. Touretzky (ed.),
-%     \textit{Advances in Neural Information Processing Systems 1}, 748--760.
-%     San Mateo, Calif.: Morgan Kaufmann.
-
-% \bibitem{} F.~Rosenblatt (1962).
-%     \newblock \textit{Principles of Neurodynamics.}
-%     \newblock Washington, D.C.: Spartan Books.
-
-% \bibitem{} G.~Tesauro (1989).
-%     \newblock Neurogammon wins computer Olympiad.
-%     \newblock \textit{Neural Computation} \textbf{1}(3):321--323.
-% \end{thebibliography}
-
-\ignore{
-\appendix
-\section{Related loss functions}
-
-Many alternatives to the cross entropy loss have been proposed.
-
-The tree loss is superficially related to the hierarchical softmax (HSM) because both losses are defined based on tree structures.
-\cite{morin2005hierarchical} introduced the HSM to speed up the computational time of neural network training,
-but the tree loss is used to improve sample efficiency rather than computational efficiency.
-
-\cite{mikolov2013distributed} introduce the word2vec model and experiment with using both the hierarchical softmax and cross entropy with negative sampling.
-They conclude that negative sampling has the best performance both computationally and statistically.
-Since the tree loss is a simple extension of the cross entropy loss,
-negative sampling can be used to speed up the cross entropy loss as well.
-
-\cite{bojanowski2017enriching} introduce the fastText extension of the word2vec model, which uses sub-word information to improve sample efficiency.
-They do not provide any theoretical justification for why their technique should improve sample efficiency,
-but their technique is computationally very similar to the tree loss,
-and so our technique may be able to provide the first theoretical justification for their work.
-
-HSM:
-\begin{equation}
-    \label{eq:xentropy}
-    \ell(W;(\x,y)) = - \log \prod_{k\in P_y}\frac {\exp(-\trans\w_k \x)}{j\in L_k \exp(-\trans \w_j \x)}
-\end{equation}
-where $P_y$ is path from root to node of Huffman Tree,
-$L_k$ are nodes on the level where $k$ are
-
-The hierarchical softmax loss aims to improve computation efficiency. 
-\cite{Peng2017IncrementallyLT} introduce a training method incrementally train the hierarchical softmax function for neural network language models.
-They also provide a new stochastic gradient based method to update all the word vectors and their experimental results show the incremental training can save a lot of time.
-\cite{Jiang2017ExplorationOT} explore the tree-based hierarchical softmax method and reform its architecture, making it compatible with modern GPUs.
-\cite{Yang2017OptimizeHS} gives a theoretic analysis on how should organize the hierarchical tree by treating the tree structure as a parameter of the training objective function.
-They propose SemHuff, a new tree constructing scheme based on adjusting the Huffman tree with word similarity knowledge.
-Their experiments results also show that word embeddings trained with optimized hierarchical tree can give better results in various tasks.
-
-\cite{Mohammed2018EffectivenessOH} compare the performance of normal softmax and hierarchical softmax in large scale classification tasks. 
-Normal softmax is computationally expensive for large scale datasets with large number of possible outputs.
-Their experimental results show that normal softmax and hierarchical softmax underperforms on datasets with large number of labels.
-That is also one of our motivations of the tree loss function. 
-Compared to classic cross entropy loss function, the tree loss function performs better on datasets with large number of labels.
-Extreme multi-label classification is difficult, but organizing labels as a tree can handle this problem.
-
-% \fixme{Write a detailed description of the sim loss}
-
-SimLoss \cite{Kobs2020SimLossCS} is similarity based loss function which incorporates class similarities to support the training of neural network classifiers.
-Cross entropy loss assumes only one class is correct and punishes every misclassification, while Simloss indicates classes have similarities and classifying a target as a similar class is better.
-When calculating the loss function, instead of only taking the probability vector at the target index Simloss also adds the product of similarity between target and other classes and probability vector at the corresponding class.
-Non zero values of similarity matrix lead to smaller losses when the network gives a high score to classes similar to the correct one. 
-It would allow the classifier to make less severe mistakes as it learns to predict similar classes.
-However, SimLoss does not have any theoretical justification to prove why it can outperform cross entropy.
-SimLoss has a hyperparameter lower bound that controls the minimal class similarity that should have an impact on the network punishment.
-Any similarities below lower bound will be all zeros.
-It implies SimLoss would cost more time to fine tune.
-Our tree loss define a tree structure which can be obtained automatically and it is time-saving.
-\begin{align}
-    L_{Simloss}&=-\frac{1}{N}\log(\sum_{k=1}^{C}S_{y_i,k}\cdot p_i[k])\\
-    % L_{Simloss}=-\frac{1}{N}\log(\sum_{k=1}^{C}S_{y_i,k}\cdot\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)})
-    p_i&=\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)}
-\end{align}
-
-}
 
@@
 
-\ignore{
 \clearpage
@@
 
-\section{Theoretical Results}
+\setcounter{lemma}{0}
+\setcounter{assumption}{0}
+\setcounter{corollary}{0}
+\setcounter{theorem}{0}
+
+\section{Theoretical Results (Supplement)}
 \label{appendix:theory}
+
+This appendix is an expanded explanation of our theoretical results from Section \ref{sec:theory} in the main paper.
+We begin with a short background explaining the standard properties of stochastic gradient descent that our proofs rely on,
+then we restate our theoretical results from before along with detailed proofs.
+
+\ignore{
+\subsection{Summary}
 
@@
 then we formally state and prove our main result.
+}
 
@@
     Under assumption \ref{ass:B},
-    the following bound holds for all $U$-tree structures:
-    \begin{equation}
-        \lF{\star U} \le 2\sqrt{k}B.
+    the following bound holds for all tree structures:
+    \begin{equation}
+        \lF{\star V} \le \lF{\star U} \le 2\sqrt{k}B.
     \end{equation}
@@
 \begin{proof}
+    %The leftmost inequality follows because every $U$ parameterization can be represented by a $V$ parameterization with certain rows set to 0
     We have
@@
 These convergence rates are asymptotically better than the convergence rates for the standard parameterization of the cross entropy loss.
-}
 

### 2022-02-01 paper/slides/background-ml2.tex
colloquium checkpoint

\begin{frame}
\frametitle{Machine Learning Review: What is Generalization Error?}

Standard Experimental Design:
\begin{itemize}
\item Split data into training/test set
\item Train model on training set
\item Evaluate model on the test set
\end{itemize}

%\includegraphics[width=\textwidth]{img/llustration-of-the-underfitting-overfitting-issue-on-a-simple-regression-case-Data}

\includegraphics[width=\textwidth]{img/over-under-fit}

{
\fontsize{4}{4}
{\tiny Image source:} \url{https://scikit-learn.org/stable/auto_examples/model_selection/plot_underfitting_overfitting.html}
}
\end{frame}

### 2022-02-01 paper/slides/conclusion.tex
colloquium checkpoint

\begin{frame}{Summary}

Theory predicts the following generalization errors:
\begin{itemize}
\item cross entropy is $O(\sqrt{k/n})$
\item tree loss is $\begin{cases}O(\sqrt{\log k/n})&c<=1\\O(\sqrt{k^{1-1/c}/n})&c>1\end{cases}$% if $c<=1$ else $O(\sqrt{k^{1-1/c}/n})$
\end{itemize}

\vspace{0.1in}
We hypothesize the optimal is $O(\sqrt{c/n})$

\vspace{0.1in}
Experiments:
\begin{itemize}
\item tree loss outperforms cross entropy loss:
\begin{itemize}
\item in all regimes of ablation study
\item even for bad trees! (lemma proves this is always true)
\end{itemize}
\item good performance on real world problems
\begin{itemize}
\item still working on gettint SOTA on ImageNet...
\end{itemize}
\end{itemize}

\vspace{0.1in}
\textbf{Tree Loss is easy to implement! Code available!}

\url{https://github.com/cora1021/TreeLoss}
\end{frame}

### 2022-02-01 paper/slides/covertree/cdoub.tex
colloquium checkpoint

\newcommand{\radius}{r}
\newcommand{\dispersion}{d}
\newcommand{\distf}{d}
\newcommand{\dpdim}{\text{dpdim}}
\newcommand{\dpnum}{\text{ep}}

\begin{frame}[fragile]{The doubling constant is a better dimension}

An \textbf{$r$-covering} of a set $X$ is a subset of $X$ such that all pairwise distances are greater than $r$. %$\{x_1,x_2,...x_M\} \subset X$ such that $\dist{x_i}{x_j} > r$ for all distinct $i,j$.

The \textbf{$r$-packing number} $M_r (X)$ is the cardinality of the largest $r$-packing.

The \textbf{doubling constant} of a set $X$ is 
\begin{equation}
\cdoub(X) = \sup_{p\in X,r>0} M_r( B(p,2r))
.
\end{equation}

\vspace{0.15in}
\hrule
\vspace{0.15in}

%The double-packing dimension is defined to be the base 2 logarithm of the double-packing number.
%That is,
%\begin{equation}
%\dpdim(\set X) = \lg \dpnum(\set X)
%.
%\end{equation}
\begin{tabular}{m{4cm}m{7cm} }
\resizebox{!}{3.5cm}{
\begin{tikzpicture}[dot/.style={circle,inner sep=2pt,fill,name=#1},
    extended line/.style={shorten >=-#1,shorten <=-#1},
    extended line/.default=1cm]

% draw the grid
\draw[->] (0,-0.25) -- (0,5.25) ;
\draw[->] (-0.25,0) -- (5.25,0) ;
\foreach \i in {1,...,5} {
    \draw[dotted] (-0.25,\i) -- (5.25,\i);
    \draw[dotted] (\i,-0.25) -- (\i,5.25);
}

\draw[line width=2pt,<->] (-0.25,4.125) -- (5.25,1.375);

\uncover<1> {
    %\node at (2.6,3.2) { \textcolor{red}{\Large r} };
    %\path[draw=red,dotted,line width=1pt] (2,3) -- (2.8,3.8);
    \path[draw=red,line width=2pt] (2,3) circle (2.2);

    %\path[draw=red,fill=red] (2,3) circle (0.1);
    %\path[draw=red,line width=2pt] (2,3) circle (1.1);

    \path[draw=blue,fill=blue] (1.5,3.25) circle (0.1);
    \path[draw=blue,line width=2pt] (1.5,3.25) circle (1.1);

    \path[draw=blue,fill=blue] (2.75,2.625) circle (0.1);
    \path[draw=blue,line width=2pt] (2.75,2.625) circle (1.1);

    \path[draw=blue,fill=blue] (4,2) circle (0.1);
    \path[draw=blue,line width=2pt] (4,2) circle (1.1);
    \path[draw=blue,fill=blue] (0.5,3.75) circle (0.1);
    \path[draw=blue,line width=2pt] (0.5,3.75) circle (1.1);
}

\uncover<2> {
    %\node at (2.6,3.2) { \textcolor{red}{\Large r} };
    %\path[draw=red,dotted,line width=1pt] (2,2) -- (2.8,3.8);
    \path[draw=blue,fill=blue] (2,2) circle (0.1);
    \path[draw=blue,line width=2pt] (2,2) circle (0.7);
    \path[draw=red,line width=2pt] (2,2) circle (1.4);

    \path[draw=blue,fill=blue] (1.5,3.25) circle (0.1);
    \path[draw=blue,line width=2pt] (1.5,3.25) circle (0.7);
    \path[draw=blue,fill=blue] (3.2,2.4) circle (0.1);
    \path[draw=blue,line width=2pt] (3.2,2.4) circle (0.7);
    \path[draw=blue,fill=blue] (2.35,2.825) circle (0.1);
    \path[draw=blue,line width=2pt] (2.35,2.825) circle (0.7);
}

%\node[text width=8cm, align=left] at (10,3.5) {
    %\Large
%
%
    %%with the Euclidean distance.
%};

\end{tikzpicture}
}
&
\uncover<1> {
    \textbf{Property 1:}
    Accurately captures the dimension of Euclidean space.
    Specifically,

    \begin{equation}
    \log_2 \dpnum(\mathbb R^n) = O(n)
    \end{equation}

    %In the metric space $\mathbb{R}^n$,
    %$$
    %c
    %= \frac{\pi(2r)^2}{\pi r^2}
    %= 4
    %$$
    %Define the \textbf{expansion-packing dimension} as $\log_2 \dpnum(X)$.
%
    %Then the expansion dimension of $\mathbb{R}^n$ is $O(n)$.
}
\\ &
\vspace{-1.5in}
\uncover<2> {
    \textbf{Property 2:}
    Robust to perturbations in the set $X$.
    For any set $X$ and point $x$, we have that
    \begin{equation}
    \dpnum(X\cup\{x\}) \le \dpnum(X)+1
    \end{equation}
}
%\\ &
%\vspace{-1.75in}
%\uncover<3> {
    %\textbf{Example 3:}
    %In the subspace of $\mathbb{R}^2$ given by
    %$$
    %%\mathcal{X} = \{ (x,y) : y = -0.5x+4 \}
    %\{ (x,y) : y = -0.5x+4 \} \cup \{(2,2)\}
    %$$
    %we have
    %$
    %c
    %%= \frac{\infty}{0}
    %= \infty
    %$
    %%so the expansion dimension is also $\infty$.
%}
\end{tabular}
\end{frame}

### 2022-02-01 paper/slides/covertree/contributions-ancestor-simple.tex
colloquium checkpoint

\begin{frame}[fragile]{The nearest ancestor cover tree}

\definecolor{lightred}{rgb}{1,0.8,0.8}
\definecolor{lightgreen}{rgb}{0.8,1,0.8}
\begin{center}
\begin{tikzpicture}
    [ draw
    , every node/.style={minimum size=10mm,fill=white}
    , level/.style={sibling distance = 23mm/#1, level distance=12mm}
    %,    level distance = 1.5cm}
    , sibling distance=8mm
    ]
\draw (-2.3,0) -- (8.6,0)[dotted];
\draw (-2.3,-12mm) -- (8.6,-12mm)[dotted];
\draw (-2.3,-24mm) -- (8.6,-24mm)[dotted];
\node[shape=circle,draw] at (0,0) {10}
    child { node[circle,draw] {8}
        child { node[circle,draw] {7}  }
        child { node[circle,draw,fill=lightred,line width=1pt] {11} }
        }
    child { node[circle,draw] {12}
        child { node[circle,draw,fill=lightred,line width=1pt] {9}  }
        child { node[circle,draw] {13} }
        }
    ;
\node[shape=circle,draw] at (5,0) {10}
    child { node[circle,draw] {8}
        child { node[circle,draw] {7}  }
        child { node[circle,draw,fill=lightgreen,line width=1pt] {9} }
        }
    child { node[circle,draw] {12}
        child { node[circle,draw,fill=lightgreen,line width=1pt] {11}  }
        child { node[circle,draw] {13} }
        }
    ;
\node[fill=none] at (8,3mm) {level 3};
\node[fill=none] at (8,-9mm) {level 2};
\node[fill=none] at (8,-21mm) {level 1};
\end{tikzpicture}
\end{center}

\uncover<1> {
A \textbf{nearest ancestor cover tree} is a simplified cover tree where every point $p$ satisfies the additional invariant that if $q_1$ is an ancestor of $p$ and $q_2$ is a sibling of $q_1$, then
$$
d(p,q_1) \le d(p,q_2)
$$
}

%\vspace{0.15in}
%Insertion requires rebalancing.
\uncover<2> {
\vspace{-1.1in}
Insertions require rebalancing.

\vspace{0.15in}
No runtime guarantees on the rebalance step.

\vspace{0.15in}
In practice, queries are much faster and construction is only slightly slower.
}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{Comparing cover trees on \emph{construction} time}
\centering
\graphicspath{{slides/covertree/paperimg/}}
\input{slides/covertree/paperimg/numdist_insert}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    \node at (0.45in,0.6in) {\small\rotatebox{90}{}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{Comparing cover trees on \emph{construction and query} time}
\centering
\graphicspath{{slides/covertree/paperimg/}}
\input{slides/covertree/paperimg/numdist}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    \node at (0.45in,0.6in) {\small\rotatebox{90}{}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{All of the cover trees scale similarly}

This experiment uses the protein data and the random walk graph kernel.
\vspace{0.15in}

{
\centering
\graphicspath{{slides/covertree/paperimg/}}
\input{slides/covertree/paperimg/protein-simple}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    %\node at (0.6in,0.7in) {\small\rotatebox{90}{ dotted lines: construction only}};
    %\node at (0.75in,0.81in) {\small\rotatebox{90}{ solid lines: construction and query}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
}

\end{frame}

### 2022-02-01 paper/slides/covertree/contributions-ancestor.tex
colloquium checkpoint

--- 2022-02-01 paper/slides/covertree/contributions-ancestor-simple.tex
@@
 
-\uncover<1> {
 A \textbf{nearest ancestor cover tree} is a simplified cover tree where every point $p$ satisfies the additional invariant that if $q_1$ is an ancestor of $p$ and $q_2$ is a sibling of $q_1$, then
@@
 $$
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{frame}[fragile]{Inserting into a nearest ancestor cover tree}
+Inserting into a nearest ancestor cover tree can require rebalancing.
+\begin{center}
+\begin{tikzpicture}
+    [ draw
+    , every node/.style={minimum size=10mm,fill=white}
+    , level/.style={sibling distance = 23mm/#1, level distance=12mm}
+    %,    level distance = 1.5cm}
+    , sibling distance=8mm
+    ]
+\draw (-2.3,0) -- (8.6,0)[dotted];
+\draw (-2.3,-12mm) -- (8.6,-12mm)[dotted];
+\draw (-2.3,-24mm) -- (8.6,-24mm)[dotted];
+
+\uncover<1> {
+\node[shape=circle,draw] at (2.5,0) {10}
+    child { node[circle,draw] {8}
+        child [color=white] {}
+        child { node[circle,draw] {11} }
+        }
+    child [ color=white ] { %node[circle,draw] {12}
+        %child { node[circle,draw,fill=lightred,line width=1pt] {9}  }
+        %child { node[circle,draw] {13} }
+        }
+    ;
 }
 
-%\vspace{0.15in}
-%Insertion requires rebalancing.
 \uncover<2> {
-\vspace{-1.1in}
-Insertions require rebalancing.
+\node[shape=circle,draw] at (2.5,0) {10}
+    child { node[circle,draw] {8}
+        child [color=white] {}
+        child { node[circle,fill=lightred,draw] {11} }
+        }
+    child  { node[circle,draw] {12}
+        %child { node[circle,draw,fill=lightred,line width=1pt] {9}  }
+        %child { node[circle,draw] {13} }
+        }
+    ;
+}
+
+\uncover<3> {
+\node[shape=circle,draw] at (2.5,0) {10}
+    child { node[circle,draw] {8}
+        child [color=white] {}
+        child [color=white] {}
+        }
+    child  { node[circle,draw] {12}
+        child { node[circle,fill=lightgreen,draw] {11} }
+        child [color=white] {}
+        %child { node[circle,draw,fill=lightred,line width=1pt] {9}  }
+        %child { node[circle,draw] {13} }
+        }
+    ;
+}
+\node[fill=none] at (8,3mm) {level 3};
+\node[fill=none] at (8,-9mm) {level 2};
+\node[fill=none] at (8,-21mm) {level 1};
+\end{tikzpicture}
+\end{center}
 
 \vspace{0.15in}
-No runtime guarantees on the rebalance step.
+No runtime bounds on the rebalancing step.
 
 \vspace{0.15in}
-In practice, queries are much faster and construction is only slightly slower.
-}
+In practice, queries are faster but construction is slower.
 \end{frame}
@@
 \centering
-\graphicspath{{slides/covertree/paperimg/}}
-\input{slides/covertree/paperimg/numdist_insert}
+\graphicspath{{covertree/paperimg/}}
+\input{covertree/paperimg/numdist_insert}
 \begin{tikzpicture}
@@
 \centering
-\graphicspath{{slides/covertree/paperimg/}}
-\input{slides/covertree/paperimg/numdist}
+\graphicspath{{covertree/paperimg/}}
+\input{covertree/paperimg/numdist}
 \begin{tikzpicture}
@@
 \centering
-\graphicspath{{slides/covertree/paperimg/}}
-\input{slides/covertree/paperimg/protein-simple}
+\graphicspath{{covertree/paperimg/}}
+\input{covertree/paperimg/protein-simple}
 \begin{tikzpicture}

### 2022-02-01 paper/slides/covertree/contributions-merge.tex
colloquium checkpoint

\begin{frame}[fragile]{Merging cover trees}

Merging cover trees gives us a parallel tree construction algorithm

\vspace{0.15in}

Sometimes, merging cover trees is \textbf{easy}:

\begin{center}
\begin{tikzpicture}
    [ draw
    , every node/.style={minimum size=10mm,fill=white}
    , level/.style={sibling distance = 23mm/#1, level distance=12mm}
    %,    level distance = 1.5cm}
    , sibling distance=8mm
    ]
\draw (-2.3,0) -- (8.6,0)[dotted];
\draw (-2.3,-12mm) -- (8.6,-12mm)[dotted];
\draw (-2.3,-24mm) -- (8.6,-24mm)[dotted];
\node[shape=circle,draw] at (0,0) {10}
    child { node[circle,draw] {8}
        child { node[circle,draw] {7}  }
        child { node[circle,draw] {9} }
        }
    child [color=white] {}
    %child { node[circle,draw] {12}
        %child { node[circle,draw] {9}  }
        %child { node[circle,draw] {13} }
        %}
    ;
\node[shape=circle,draw,fill=lightgreen] at (5,-12mm) {12}
    %child { node[circle,draw] {8}
        %child { node[circle,draw] {7}  }
        %child { node[circle,draw,fill=lightgreen,line width=1pt] {9} }
        %}
    %child { node[circle,draw] {12}
        child { node[circle,draw] {11}  }
        child { node[circle,draw] {13} }
        %}
    ;
\node[fill=none] at (8,3mm) {level 3};
\node[fill=none] at (8,-9mm) {level 2};
\node[fill=none] at (8,-21mm) {level 1};
\end{tikzpicture}
\end{center}

\vspace{0.1in}
No runtime bound on the merge operation, but it is fast in practice

%\vspace{0.1in}
%But, if the runtime is $o(n)$, then we get an algorithm for tree construction that takes time $O(n)$
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{Merging cover trees}

Merging cover trees gives us a parallel tree construction algorithm

\vspace{0.15in}

Sometimes, merging cover trees is \textbf{hard}:

\begin{center}
\begin{tikzpicture}
    [ draw
    , every node/.style={minimum size=10mm,fill=white}
    , level/.style={sibling distance = 23mm/#1, level distance=12mm}
    %,    level distance = 1.5cm}
    , sibling distance=8mm
    ]
\draw (-2.3,0) -- (8.6,0)[dotted];
\draw (-2.3,-12mm) -- (8.6,-12mm)[dotted];
\draw (-2.3,-24mm) -- (8.6,-24mm)[dotted];
\node[shape=circle,draw] at (0,0) {10}
    child { node[circle,draw] {8}
        child { node[circle,draw] {7}  }
        child { node[circle,draw] {9} }
        }
    child [color=white] {}
    %child { node[circle,draw] {12}
        %child { node[circle,draw] {9}  }
        %child { node[circle,draw] {13} }
        %}
    ;
\node[shape=circle,draw,fill=lightred] at (5,-12mm) {11.5}
    %child { node[circle,draw] {8}
        %child { node[circle,draw] {7}  }
        %child { node[circle,draw,fill=lightgreen,line width=1pt] {9} }
        %}
    %child { node[circle,draw] {12}
        child { node[circle,draw] {11}  }
        child { node[circle,draw] {13} }
        %}
    ;
\node[fill=none] at (8,3mm) {level 3};
\node[fill=none] at (8,-9mm) {level 2};
\node[fill=none] at (8,-21mm) {level 1};
\end{tikzpicture}
\end{center}

\vspace{0.1in}
No runtime bound on the merge operation, but it is fast in practice

%\vspace{0.1in}
%But, if the runtime is $o(n)$, then we get an algorithm for tree construction that takes time $O(n)$
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{The effect of parallel tree \emph{construction} on small datasets}
\begin{center}
\graphicspath{{slides/covertree/paperimg/}}
\input{slides/covertree/paperimg/parallel-ancestor-build}
\begin{tikzpicture}
    \node[draw,fill=blue,minimum width=0.05in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,0.63in) {\small\rotatebox{90}{Our cover tree}};
    \node[minimum width=0.05in,minimum height=0.3in] at (0.45in,0) {};
    \node at (0.45in,0.61in) {\small\rotatebox{90}{}};
    \node at (0,-0.475in) {};
\end{tikzpicture}
\end{center}

\vspace{0.1in}
Experiments run on an Amazon AWS instance with 16 true cores
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{Parallel tree construction really matters on larger data sets}

%on small datasets with cheap metrics, parallel construction is less useful

\vspace{0.1in}
On large datasets with an expensive metric, parallelism is more useful

\vspace{0.15in}
Yahoo! Flickr dataset with 1.5 million images and earth mover distance

%\vspace{0.2in}
\vspace{0.15in}
\begin{center}
\Large
\begin{tabular}{ccccc}
\hline
num cores
 & \multicolumn{2}{c}{simplified tree} & \multicolumn{2}{c}{nearest ancestor tree} \\
%& \multicolumn{2}{c}{construction} & \multicolumn{2}{c}{construction} \\ %\cline{2-5}
& time & speedup & time & speedup \\
\hline
\hline
1  & 70.7 min & 1.0 & 210.9 min& 1.0\\
2  & 36.6 min & 1.9 & 94.2 min & 2.2\\
4  & 18.5 min & 3.8 & 48.5 min & 4.3\\
8  & 10.2 min & 6.9 & 25.3 min & 8.3\\
16 & 6.7 min & 10.5 & 12.0 min & 17.6\\
\hline
\end{tabular}
\end{center}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{The effect of parallel tree \emph{construction and query}}
\begin{center}
\graphicspath{{slides/covertree/paperimg/}}
\input{slides/covertree/paperimg/parallel}
\definecolor{colorOrig}{RGB}{102,51,0}
\definecolor{colorMlpack}{RGB}{204,153,0}
\begin{tikzpicture}
    \node[draw,fill=colorOrig,minimum width=0.05in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.79in) {\small\rotatebox{90}{Reference cover tree}};
    \node[draw,fill=colorMlpack,minimum width=0.05in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.80in) {\small\rotatebox{90}{MLPack's cover tree}};
    \node[draw,fill=blue,minimum width=0.05in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,0.63in) {\small\rotatebox{90}{Our cover tree}};
    \node[minimum width=0.05in,minimum height=0.3in] at (0.45in,0) {};
    \node at (0.45in,0.61in) {\small\rotatebox{90}{}};
    \node at (0,-0.475in) {};
\end{tikzpicture}
\end{center}

\vspace{0.1in}
Experiments run on an Amazon AWS instance with 16 true cores
\end{frame}

### 2022-02-01 paper/slides/covertree/contributions-simplified.tex
colloquium checkpoint

\begin{frame}[fragile]{The simplified cover tree}

\begin{center}
\begin{tikzpicture}
    [ draw
    , every node/.style={minimum size=10mm,fill=white}
    , level/.style={sibling distance = 23mm/#1, level distance=12mm}
    %,    level distance = 1.5cm}
    , sibling distance=8mm
    ]
\draw (-2.3,0) -- (8.6,0)[dotted];
\draw (-2.3,-12mm) -- (8.6,-12mm)[dotted];
\draw (-2.3,-24mm) -- (8.6,-24mm)[dotted];
\node[shape=circle,draw] at (2.5,0) {10}
    child { node[circle,draw] {8}
        child { node[circle,draw] {7}  }
        child { node[circle,draw] {9} }
        }
    child { node[circle,draw] {12}
        %child { node[circle,draw,fill=lightred,line width=1pt] {9}  }
        %child { node[circle,draw] {13} }
        }
    ;
%\node[shape=circle,draw] at (5,0) {10}
    %child { node[circle,draw] {8}
        %child { node[circle,draw] {7}  }
        %child { node[circle,draw,fill=lightgreen,line width=1pt] {9} }
        %}
    %child { node[circle,draw] {12}
        %child { node[circle,draw,fill=lightgreen,line width=1pt] {11}  }
        %child { node[circle,draw] {13} }
        %}
    %;
\node[fill=none] at (8,3mm) {level 3};
\node[fill=none] at (8,-9mm) {level 2};
\node[fill=none] at (8,-21mm) {level 1};
\end{tikzpicture}
\end{center}

\uncover<1> {
%\vspace{0.15in}
\textbf{The covering invariant.}
For every node $p$, define the function $\covdist p = \exprad p^{\level p}$.
For each child $q$ of $p$
$$
\dist p q \le \covdist p
$$

\vspace{0.15in}
\textbf{The separating invariant.}
For every node $p$, define the function $\sepdist p = \exprad p^{\level p-1}$.
For all distinct children $q_1$ and $q_2$ of $p$
$$
\dist{q_1}{q_2} \ge \sepdist p
$$
}

\uncover<2> {
\vspace{-1.70in}
Advantages of the simplified cover tree:
\vspace{0.05in}
\begin{itemize}
\item Maintains all runtime guarantees of the original cover tree.
\vspace{0.05in}

\item Significantly easier to understand and implement.

%\vspace{0.05in}
The original cover tree was described in terms of an infinitely large tree, only a subset of which actually gets implemented.

\vspace{0.05in}
\item Requires exactly $n$ nodes instead of $O(n)$ nodes.

%\vspace{0.05in}
Fewer nodes means a faster constant factor for all algorithms. %insertions and queries are faster.
\end{itemize}
\vspace{1.3in}
}

\end{frame}

\begin{frame}[fragile]{The simplified cover tree}

\centering
\graphicspath{{slides/covertree/paperimg/}}
\input{slides/covertree/paperimg/nodes}

\end{frame}

### 2022-02-01 paper/slides/covertree/contributions.tex
colloquium checkpoint

\begin{frame}[fragile]{My contributions}

\large

I made cover trees faster in practice:
\begin{itemize}

\item Two new cover tree variants:

\begin{itemize}
\item The simplified cover tree

\item The nearest ancestor cover tree
\end{itemize}
\large

\item A cache efficient memory layout for the cover tree

\item A method for parallel tree construction
\end{itemize}

\vspace{0.15in}
I'll demonstrate the improvements empirically
\begin{itemize}
\item Experiments use the \emph{all-nearest-neighbor} query method
\item Datasets:
\begin{itemize}
\item Benchmark data sets using the Euclidean distance
\item The protein data bank using random walk distance
\item Flickr 1.5 million image data set using earth mover's distance
\end{itemize}
\end{itemize}

\end{frame}

### 2022-02-01 paper/slides/covertree/dimension.tex
colloquium checkpoint

\begin{frame}[fragile]{The expansion constant $\cexp$ is a type of dimension}

The \textbf{expansion constant} is defined as:
$$
\cexp = \sup_{p\in X, r\ge0} \left(
    \frac{|B(p,2r)|}{|B(p,r)|}
      \right)
$$
where
$$
B(p,r) = \{q \in X : d(p,q) \le r \}
$$
is the ball of radius $r$ centered at point $p$.
\vspace{0.15in}

\hrule
\vspace{0.15in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tikzpicture}

    %\node[text width=12cm] at (3,0) {\textbf{Example 1:} $X =$ regularly spaced points in $\R^d$, $\log\cexp=\Theta(d)$};
    %\foreach \i in {1,...,20} {
    %\foreach \j in {1,...,13} {
        %\node[draw=blue,minimum size=0.5mm,inner sep=0pt,outer sep=0pt,shape=circle,fill=blue] at (0.2*\i,-0.2*\j-0.3) {};
    %}}
%
    %\path[draw=red,fill=red]   (2,-1.7) circle (0.05);
    %\path[draw=red,very thick] (2,-1.7) circle (0.5);
    %\path[draw=red,very thick] (2,-1.7) circle (1);

    \node[text width=12cm] at (3,0) {\textbf{Example 2:} $X = \{ 2^{-i} \}_{i=1}^n$, then $\log\cexp = \Theta(\log n)$ };

    %\node[draw=blue,minimum size=0.5mm,inner sep=0pt,outer sep=0pt,shape=circle,fill=blue] at (-2,-1.5) {};
    \node[draw=blue,minimum size=1mm,inner sep=0pt,outer sep=0pt,shape=circle,fill=blue] at (2,-1.5) {};
    \node[draw=blue,minimum size=1mm,inner sep=0pt,outer sep=0pt,shape=circle,fill=blue] at (4,-1.5) {};
    \node[draw=blue,minimum size=1mm,inner sep=0pt,outer sep=0pt,shape=circle,fill=blue] at (5,-1.5) {};
    \node[draw=blue,minimum size=1mm,inner sep=0pt,outer sep=0pt,shape=circle,fill=blue] at (5.5,-1.5) {};
    \node[draw=blue,minimum size=1mm,inner sep=0pt,outer sep=0pt,shape=circle,fill=blue] at (5.75,-1.5) {};
    \node[draw=blue,minimum size=1mm,inner sep=0pt,outer sep=0pt,shape=circle,fill=blue] at (5.825,-1.5) {};

    \path[draw=red,fill=red]   (2,-1.5) circle (0.05);

    \draw [red,thick,domain=-150:-210] plot ({2+1.9*cos(\x)}, {-1.5+1.9*sin(\x)});
    \draw [red,thick,domain=-30:30] plot ({2+1.9*cos(\x)}, {-1.5+1.9*sin(\x)});

    \draw [red,thick,domain=-015:015] plot ({2+4.0*cos(\x)}, {-1.5+4.0*sin(\x)});
    \draw [red,thick,domain=-165:-195] plot ({2+4.0*cos(\x)}, {-1.5+4.0*sin(\x)});
    %\draw [red,thick,domain=-15:15] plot ({-2+3.9*cos(\x)}, {-1.5+3.9*sin(\x)});
    %\draw [red,thick,domain=-7.5:7.5] plot ({-2+8.0*cos(\x)}, {-1.5+8.0*sin(\x)});
\end{tikzpicture}

\end{frame}

### 2022-02-01 paper/slides/covertree/dimensions.tex
colloquium checkpoint

\begin{frame}[fragile]{dimensions of arbitrary metric spaces}

\textbf{vector space dimension $(d)$}: what we're used to, only applies to $\mathbb{R}^d$
\vspace{0.05in}

\hspace{0.2in}...

\vspace{0.05in}
\textbf{Hausdorff dimension $(h)$}: the ``ideal'' generalization of dimensions to any metric space; can handle fractional dimensions, and is often associated with fractals
\begin{center}
\includegraphics[width=6cm]{covertree/gb-hausdorff.png}
\end{center}

%dimension of the ``fractall'' coastline of Britain is about 1.25

\textbf{open problem}: create a data structure that lets us query nearest neighbors in time $O(h \log n)$; is it even possible?
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{dimensions of arbitrary metric spaces}

Given a metric space $X$ with distance $d : X \times X \to \mathbb{R}$, define
\vspace{0.15in}

\textbf{ball of radius $r$ centered at point $p$ }:
$$
B(p,r) = \{q \in X : d(p,q) \le r \}
$$
%\vspace{0.15in}

%\textbf{expansion constant $(c)$}: the smallest value $c \ge 2$ such that
%$$
%|B(p,2r)| \le c|B(p,r)|
%$$
%for every $p$ in the metric space $X$ and $r\ge0$.

\textbf{expansion constant}:
$$
c = \sup_{p\in X, r\ge0} \left\{
    \frac{|B(p,2r)|}{|B(p,r)|}
      \right\}
$$

\hrule

\vspace{0.15in}
properties of the expansion constant:
\begin{enumerate}
\item dimension $(=\log c)$ of $\mathbb{R}^n$ is $O(n)$
\item roughly captures the ``intrinsic dimensionality'' of $X$
\item adding a single new point to $X$ can increase $c$ by an arbitrary amount;

there are subsets of $\mathbb{R}^2$ with $c=\infty$
\end{enumerate}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{data structures: bounds with arbitrary metric}

\begin{center}
\includegraphics[width=12cm]{covertree/runtimes}
\end{center}

Karger and Ruhl, Symposium on the Theory of Computing, 2002

\vspace{0.15in}
Krauthgamer and Lee, Symposium on Discrete Algorithms, 2004

\vspace{0.15in}
Beygelzimer, Kakade, and Langford, ICML, 2006

\vspace{0.15in}
\textbf{open problem}: construct a data structure in time $O(c^{O(1)}n)$ for some dimensionality $c$; is it even possible?
\vspace{0.15in}

\end{frame}

### 2022-02-01 paper/slides/covertree/experiment-protein.tex
colloquium checkpoint

--- 2022-02-01 paper/slides/covertree/contributions-ancestor-simple.tex
@@
-\begin{frame}[fragile]{The nearest ancestor cover tree}
-
-\definecolor{lightred}{rgb}{1,0.8,0.8}
-\definecolor{lightgreen}{rgb}{0.8,1,0.8}
-\begin{center}
-\begin{tikzpicture}
-    [ draw
-    , every node/.style={minimum size=10mm,fill=white}
-    , level/.style={sibling distance = 23mm/#1, level distance=12mm}
-    %,    level distance = 1.5cm}
-    , sibling distance=8mm
-    ]
-\draw (-2.3,0) -- (8.6,0)[dotted];
-\draw (-2.3,-12mm) -- (8.6,-12mm)[dotted];
-\draw (-2.3,-24mm) -- (8.6,-24mm)[dotted];
-\node[shape=circle,draw] at (0,0) {10}
-    child { node[circle,draw] {8}
-        child { node[circle,draw] {7}  }
-        child { node[circle,draw,fill=lightred,line width=1pt] {11} }
-        }
-    child { node[circle,draw] {12}
-        child { node[circle,draw,fill=lightred,line width=1pt] {9}  }
-        child { node[circle,draw] {13} }
-        }
-    ;
-\node[shape=circle,draw] at (5,0) {10}
-    child { node[circle,draw] {8}
-        child { node[circle,draw] {7}  }
-        child { node[circle,draw,fill=lightgreen,line width=1pt] {9} }
-        }
-    child { node[circle,draw] {12}
-        child { node[circle,draw,fill=lightgreen,line width=1pt] {11}  }
-        child { node[circle,draw] {13} }
-        }
-    ;
-\node[fill=none] at (8,3mm) {level 3};
-\node[fill=none] at (8,-9mm) {level 2};
-\node[fill=none] at (8,-21mm) {level 1};
-\end{tikzpicture}
-\end{center}
-
-\uncover<1> {
-A \textbf{nearest ancestor cover tree} is a simplified cover tree where every point $p$ satisfies the additional invariant that if $q_1$ is an ancestor of $p$ and $q_2$ is a sibling of $q_1$, then
-$$
-d(p,q_1) \le d(p,q_2)
-$$
-}
-
-%\vspace{0.15in}
-%Insertion requires rebalancing.
-\uncover<2> {
-\vspace{-1.1in}
-Insertions require rebalancing.
-
-\vspace{0.15in}
-No runtime guarantees on the rebalance step.
-
-\vspace{0.15in}
-In practice, queries are much faster and construction is only slightly slower.
-}
-\end{frame}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{frame}[fragile]{Comparing cover trees on \emph{construction} time}
-\centering
+\begin{frame}[fragile]{Experiment: protein data bank data}
+
+%This experiment uses the protein data and the random walk graph kernel.
+\vspace{0.1in}
+Protein distance measured using the random walk graph kernel
+\vspace{0.1in}
+
+{
+\begin{center}
 \graphicspath{{slides/covertree/paperimg/}}
-\input{slides/covertree/paperimg/numdist_insert}
+\input{slides/covertree/paperimg/protein-pres}
 \begin{tikzpicture}
@@
     \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
-    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
-    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
-    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
-    \node at (0.45in,0.6in) {\small\rotatebox{90}{}};
-    \node at (0,-0.5in) {};
-\end{tikzpicture}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}[fragile]{Comparing cover trees on \emph{construction and query} time}
-\centering
-\graphicspath{{slides/covertree/paperimg/}}
-\input{slides/covertree/paperimg/numdist}
-\begin{tikzpicture}
-    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
-    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
-    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
-    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
-    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
-    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
-    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
-    \node at (0.45in,0.6in) {\small\rotatebox{90}{}};
-    \node at (0,-0.5in) {};
-\end{tikzpicture}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}[fragile]{All of the cover trees scale similarly}
-
-This experiment uses the protein data and the random walk graph kernel.
-\vspace{0.15in}
-
-{
-\centering
-\graphicspath{{slides/covertree/paperimg/}}
-\input{slides/covertree/paperimg/protein-simple}
-\begin{tikzpicture}
-    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
-    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
-    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
-    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
-    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
-    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
-    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
+    %\node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
+    %\node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
+    %\node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
     %\node at (0.6in,0.7in) {\small\rotatebox{90}{ dotted lines: construction only}};
@@
 \end{tikzpicture}
+\end{center}
 }

### 2022-02-01 paper/slides/covertree/experimental-setup.tex
colloquium checkpoint

\begin{frame}{Experimental setup}
\Large

Three data sources:
\begin{itemize}
\item Protein dataset with the random walk graph distance
\item Yahoo! 1.5 million creative common images with the earth movers distance
\item MLPack benchmarks with Euclidean distance
    %\begin{itemize}
    %\item Selected the 8 largest datasets
    %\item Maximum size
    %\end{itemize}
\end{itemize}

\vspace{0.15in}
Benchmarking procedure:
\begin{itemize}
\item Construct a cover tree on the dataset
\item For each data point in the dataset, find the nearest neighbor
\item AWS instance with 16 true cores
\end{itemize}

\end{frame}

### 2022-02-01 paper/slides/covertree/img-allcovertree.tex
colloquium checkpoint

\documentclass[tikz]{standalone}
\usetikzlibrary{patterns}
\begin{document}

\definecolor{lightred}{RGB}{255,200,200}
\definecolor{lightgreen}{RGB}{200,255,200}
\definecolor{lightblue}{RGB}{200,200,255}
\definecolor{darkred}{RGB}{127,0,0}
\definecolor{darkgreen}{RGB}{0,127,0}
\definecolor{darkblue}{RGB}{0,0,127}

\definecolor{lightgray}{RGB}{205,210,255}
\definecolor{lightgray2}{RGB}{235,240,255}

\begin{tikzpicture}
    [ draw
    , every node/.style={line width=1pt, minimum size=10mm,fill=lightgray}
    , level 1/.style={sibling distance = 30mm, level distance=20mm}
    , level 2/.style={sibling distance = 24mm, level distance=12mm}
    , level 3/.style={sibling distance = 12mm, level distance=12mm}
    , level 4/.style={sibling distance = 12mm, level distance=20mm}
    , dash/.style={edge from parent/.style={gray,thin,draw}}
    , norm/.style={edge from parent/.style={black,very thick,draw}}
    , funk/.style={preaction={fill=white},pattern=north west lines,pattern color=lightgray,draw=gray,circle,thin}
    %,    level distance = 1.5cm}
    , sibling distance=8mm
    ]
\draw (-4.3,  0mm) -- (18,  0mm)[dotted];
\draw (-4.3,-20mm) -- (18,-20mm)[dotted];
\draw (-4.3,-32mm) -- (18,-32mm)[dotted];
\draw (-4.3,-44mm) -- (18,-44mm)[dotted];
\draw (-4.3,-64mm) -- (18,-64mm)[dotted];
%\node[circle,draw=gray,thin,pattern=north west lines,pattern color=lightgray] at (0,0) {10}
\node[funk] at (0,0) {10}
    child[dash] {
        node[shape=circle,draw] (b1) {10}
        child[norm] { node[circle,draw=black,very thick] {8}
            child[norm] { node[circle,draw] {7}         child[dash] { node[funk] (a) {7} } }
            child[dash] { node[funk] {8}  child[dash] { node[funk] {8} } }
            child[opacity=0] { node[opacity=0] {} }
            }
        child[norm] { node[circle,draw=black] (b2) {10}
            child[norm] { node[circle,draw,fill=lightred] {8.5}         child[dash] { node[funk] {8.5} } }
            child[dash] { node[funk] {10} child[dash] { node[funk] {10}} }
            child[norm] { node[circle,draw,fill=lightred] (c1) {11.5}        child[dash] { node[funk] {11.5}} }
            }
        child[norm] { node[circle,draw=black] {12}
            child[opacity=0] { node[opacity=0] {} }
            child[dash] { node[funk] {12} child[dash] { node[funk] {12}} }
            child[norm] { node[circle,draw] {13}        child[dash] { node[funk] {13}} }
            }
        }
    ;

\node[opacity=0] at (8,0) {}
    child[norm,opacity=0] { node[opacity=1,shape=circle,draw] {10}
        child[opacity=1] { node[circle,draw] {8}
            child { node[circle,draw] {7}  }
            child { node[circle,draw,fill=lightred,line width=1pt] (c2) {11.5} }
            }
        child[opacity=1] { node[circle,draw] {12}
            child { node[circle,draw,fill=lightred,line width=1pt] {8.5}  }
            child { node[circle,draw] {13} }
            }
        }
    ;

\node[opacity=0] at (14.5,0) {}
    child[norm,opacity=0] { node[opacity=1,shape=circle,draw] {10}
        child[opacity=1] { node[circle,draw] {8}
            child { node[circle,draw] {7}  }
            child { node[circle,draw,fill=lightgreen,line width=1pt] {8.5} }
            }
        child[opacity=1] { node[circle,draw] {12}
            child { node[circle,draw,fill=lightgreen,line width=1pt] (d1) {11.5}  }
            child { node[circle,draw] {13} }
            }
        }
    ;

\node[fill=none] at (19,0mm) {level $\infty$};
\node[fill=none] at (19,-10mm) {$\vdots$};
\node[fill=none] at (19,-20mm) {level 2};
\node[fill=none] at (19,-32mm) {level 1};
\node[fill=none] at (19,-44mm) {level 0};
\node[fill=none] at (19,-54mm) {$\vdots$};
\node[fill=none] at (19,-64mm) {level $-\infty$};

\node[fill=none] at (-2,-0.70) {\textbf{original}};
\node[fill=none] at (-2,-1.05) {\textbf{cover tree}};

\node[fill=none] at (8,-0.70) {\textbf{simplified}};
\node[fill=none] at (8,-1.05) {\textbf{cover tree}};

\node[fill=none] at (14.5,-0.70) {\textbf{nearest ancestor}};
\node[fill=none] at (14.5,-1.05) {\textbf{cover tree}};

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\node[fill=none] at (0,-8) {\parbox{2.5in}{
    these ``implicit'' nodes are needed to describe the original cover tree,
    but they don't actually get implemented
    }};
\draw[->,out=180,in=270] (-3.5,-8) to (a);

\node[fill=none] at (3.5,-1.5) {\parbox{2in}{
    once a value appears in the tree, it must be in every lower level
    }};
\draw[->,out=180,in=45] (0.75,-1.5) to (b1);
%\draw[->,out=225,in=45] (0.75,-1.65) to (b2);

\node[fill=none] at (8,-5.75) {\parbox{2.3in}{
    nodes can be placed suboptimally even in one dimension
    }};
\draw[->,out=180,in=315] (4.85,-5.75) to (c1);
\draw[->,out=80,in=270] (7.25,-5.35) to (c2);

\node[fill=none] at (14,-7.25) {\parbox{3in}{
    in one dimension, nearest ancestor trees behave like balanced binary search trees
    }};
\draw[->,out=80,in=270] (14.25,-6.8) to (d1);

\end{tikzpicture}
\end{document}

### 2022-02-01 paper/slides/covertree/img-originalcovertree.tex
colloquium checkpoint

\documentclass[tikz]{standalone}
\begin{document}

\definecolor{lightred}{RGB}{255,200,200}
\definecolor{lightgreen}{RGB}{200,255,200}
\definecolor{lightblue}{RGB}{200,200,255}
\definecolor{darkred}{RGB}{127,0,0}
\definecolor{darkgreen}{RGB}{0,127,0}
\definecolor{darkblue}{RGB}{0,0,127}

\definecolor{lightgray}{RGB}{205,210,255}

\begin{tikzpicture}
    [ draw
    , every node/.style={line width=1pt, minimum size=10mm,fill=lightgray}
    , level 1/.style={sibling distance = 30mm, level distance=20mm}
    , level 2/.style={sibling distance = 30mm, level distance=12mm}
    , level 3/.style={sibling distance = 12mm, level distance=12mm}
    , level 4/.style={sibling distance = 12mm, level distance=20mm}
    , dash/.style={edge from parent/.style={gray,thin,draw}}
    , norm/.style={edge from parent/.style={black,very thick,draw}}
    %,    level distance = 1.5cm}
    , sibling distance=8mm
    ]
\draw (-4.3,0mm) -- (5,0mm)[dotted];
\draw (-4.3,-20mm) -- (5,-20mm)[dotted];
\draw (-4.3,-32mm) -- (5,-32mm)[dotted];
\draw (-4.3,-44mm) -- (5,-44mm)[dotted];
\draw (-4.3,-64mm) -- (5,-64mm)[dotted];
\node[circle,draw=gray,thin] at (0,0) {10}
    child[dash] {
        node[shape=circle,draw] {10}
        child[norm] { node[circle,draw=black,very thick] {8}
            child[norm] { node[circle,draw] {7}         child[dash] { node[circle,draw=gray,thin] {7} } }
            child[dash] { node[circle,draw=gray,thin] {8}  child[dash] { node[circle,draw=gray,thin] {8} } }
            }
        child[norm] { node[circle,draw=black] {10}
            child[norm] { node[circle,draw] {9}         child[dash] { node[circle,draw=gray,thin] {9} } }
            child[dash] { node[circle,draw=gray,thin] {10} child[dash] { node[circle,draw=gray,thin] {10}} }
            child[norm] { node[circle,draw] {11}        child[dash] { node[circle,draw=gray,thin] {11}} }
            }
        child[norm] { node[circle,draw=black] {12}
            child[dash] { node[circle,draw=gray,thin] {12} child[dash] { node[circle,draw=gray,thin] {12}} }
            child[norm] { node[circle,draw] {13}        child[dash] { node[circle,draw=gray,thin] {13}} }
            }
        }
    ;
\node[fill=none] at (6,0mm) {level $\infty$};
\node[fill=none] at (6,-10mm) {$\vdots$};
\node[fill=none] at (6,-20mm) {level 2};
\node[fill=none] at (6,-32mm) {level 1};
\node[fill=none] at (6,-44mm) {level 0};
\node[fill=none] at (6,-54mm) {$\vdots$};
\node[fill=none] at (6,-64mm) {level $-\infty$};
\end{tikzpicture}
\end{document}

### 2022-02-01 paper/slides/covertree/img-simplifiedcovertree2.tex
colloquium checkpoint

--- 2022-02-01 paper/slides/covertree/contributions-ancestor-simple.tex
@@
-\begin{frame}[fragile]{The nearest ancestor cover tree}
+\documentclass[tikz]{standalone}
+\begin{document}
 
-\definecolor{lightred}{rgb}{1,0.8,0.8}
-\definecolor{lightgreen}{rgb}{0.8,1,0.8}
-\begin{center}
+\definecolor{lightred}{RGB}{255,200,200}
+\definecolor{lightgreen}{RGB}{200,255,200}
+\definecolor{lightblue}{RGB}{200,200,255}
+\definecolor{darkred}{RGB}{127,0,0}
+\definecolor{darkgreen}{RGB}{0,127,0}
+\definecolor{darkblue}{RGB}{0,0,127}
+
 \begin{tikzpicture}
@@
 \end{tikzpicture}
-\end{center}
-
-\uncover<1> {
-A \textbf{nearest ancestor cover tree} is a simplified cover tree where every point $p$ satisfies the additional invariant that if $q_1$ is an ancestor of $p$ and $q_2$ is a sibling of $q_1$, then
-$$
-d(p,q_1) \le d(p,q_2)
-$$
-}
-
-%\vspace{0.15in}
-%Insertion requires rebalancing.
-\uncover<2> {
-\vspace{-1.1in}
-Insertions require rebalancing.
-
-\vspace{0.15in}
-No runtime guarantees on the rebalance step.
-
-\vspace{0.15in}
-In practice, queries are much faster and construction is only slightly slower.
-}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}[fragile]{Comparing cover trees on \emph{construction} time}
-\centering
-\graphicspath{{slides/covertree/paperimg/}}
-\input{slides/covertree/paperimg/numdist_insert}
-\begin{tikzpicture}
-    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
-    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
-    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
-    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
-    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
-    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
-    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
-    \node at (0.45in,0.6in) {\small\rotatebox{90}{}};
-    \node at (0,-0.5in) {};
-\end{tikzpicture}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}[fragile]{Comparing cover trees on \emph{construction and query} time}
-\centering
-\graphicspath{{slides/covertree/paperimg/}}
-\input{slides/covertree/paperimg/numdist}
-\begin{tikzpicture}
-    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
-    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
-    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
-    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
-    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
-    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
-    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
-    \node at (0.45in,0.6in) {\small\rotatebox{90}{}};
-    \node at (0,-0.5in) {};
-\end{tikzpicture}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}[fragile]{All of the cover trees scale similarly}
-
-This experiment uses the protein data and the random walk graph kernel.
-\vspace{0.15in}
-
-{
-\centering
-\graphicspath{{slides/covertree/paperimg/}}
-\input{slides/covertree/paperimg/protein-simple}
-\begin{tikzpicture}
-    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
-    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
-    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
-    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
-    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
-    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
-    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
-    %\node at (0.6in,0.7in) {\small\rotatebox{90}{ dotted lines: construction only}};
-    %\node at (0.75in,0.81in) {\small\rotatebox{90}{ solid lines: construction and query}};
-    \node at (0,-0.5in) {};
-\end{tikzpicture}
-}
-
-\end{frame}
+\end{document}

### 2022-02-01 paper/slides/covertree/knn.tex
colloquium checkpoint

%\begin{frame}[fragile]{Why care about faster nearest neighbor queries?}
\begin{frame}[fragile]{Why care about cover trees?}
% image from: http://scikit-learn.org/0.11/auto_examples/neighbors/plot_classification.html

They speed up nearest neighbor queries, e.g. in
 $k$-nn classification:

\begin{center}
\includegraphics[width=5.5cm]{covertree/knn.png}
\end{center}
%source: scikit learn

But neighbor queries are used in many other algorithms too:
\begin{itemize}
\item Localized support vector machines (Segata \& Blanzieri, 2010)
\item Dimensionality reduction (Lisitsyn \emph{et. al.}, 2013)
\item Reinforcement learning (Tziortziotis \emph{et. al.}, 2014)
\end{itemize}

\vspace{0.05in}
{\tiny image from: \url{http://scikit-learn.org}}

\end{frame}

### 2022-02-01 paper/slides/covertree/metrics-image.tex
colloquium checkpoint

\begin{frame}[fragile]{Metrics for images}
\includegraphics[width=6cm]{slides/covertree/imagehistogram2.png}
\includegraphics[width=6cm]{slides/covertree/imagehistogram3b.jpg}

\vspace{0.15in}
There are \emph{lots} of distance metrics for images.
Histogram metrics follow the two step process:
\begin{itemize}
\item generate histograms (usually of colors)
\item define a distance between histograms
\end{itemize}

Earth mover's distance is a popular but slow metric.
It runs in time $O(b^3 \log b)$, where $b$ is the size of the histogram.
(Rubner \emph{et. al.}, 1998)

\vspace{0.05in}
{\tiny
images from: \url{http://billmill.org/the_histogram.html}
}
\end{frame}

%\begin{frame}[fragile]{metrics for images}
%\includegraphics[width=12cm]{slides/covertree/emd.png}
%
%\end{frame}

### 2022-02-01 paper/slides/covertree/metrics-protein.tex
colloquium checkpoint

\begin{frame}[fragile]{Metrics for proteins}

\vspace{-0.3in}
\begin{center}
\begin{tikzpicture}
%\node at (0,0) {\includegraphics[width=4cm]{slides/covertree/xrayprotein}};
\node at (0,0) {\includegraphics[width=4cm]{img-presentation/Lignin1_0}};
\node at (6,0) {\includegraphics[width=4cm]{slides/covertree/ProteinGraphs}};

\draw[->,line width=4pt] (2.75,0) -- (3.75,0);
\end{tikzpicture}
\end{center}

\vspace{-0.2in}

%The protein databank contains information on $\sim$100,000 proteins
%
%\vspace{0.1in}
Protein structure (and hence function) can be modeled as a graph

\vspace{0.1in}
The random walk graph kernel is a commonly used protein metric

\vspace{0.1in}
This is an \emph{expensive} metric, taking time $O(v^3)$

\vspace{0.1in}
(Vishwanathan \emph{et. al.}, 2010)

\vspace{0.15in}
{\tiny
images from: \url{http://www.lunenfeld.ca}, and \url{http://vishgraph.mbu.iisc.ernet.in/GraProStr/}
}

\end{frame}

### 2022-02-01 paper/slides/covertree/runtimes-graphs.tex
colloquium checkpoint

--- 2022-02-01 paper/slides/covertree/contributions-merge.tex
@@
-\begin{frame}[fragile]{Merging cover trees}
-
-Merging cover trees gives us a parallel tree construction algorithm
-
-\vspace{0.15in}
-
-Sometimes, merging cover trees is \textbf{easy}:
-
+\begin{frame}[fragile]{Cover tree performance comparisons}
 \begin{center}
-\begin{tikzpicture}
-    [ draw
-    , every node/.style={minimum size=10mm,fill=white}
-    , level/.style={sibling distance = 23mm/#1, level distance=12mm}
-    %,    level distance = 1.5cm}
-    , sibling distance=8mm
-    ]
-\draw (-2.3,0) -- (8.6,0)[dotted];
-\draw (-2.3,-12mm) -- (8.6,-12mm)[dotted];
-\draw (-2.3,-24mm) -- (8.6,-24mm)[dotted];
-\node[shape=circle,draw] at (0,0) {10}
-    child { node[circle,draw] {8}
-        child { node[circle,draw] {7}  }
-        child { node[circle,draw] {9} }
-        }
-    child [color=white] {}
-    %child { node[circle,draw] {12}
-        %child { node[circle,draw] {9}  }
-        %child { node[circle,draw] {13} }
-        %}
-    ;
-\node[shape=circle,draw,fill=lightgreen] at (5,-12mm) {12}
-    %child { node[circle,draw] {8}
-        %child { node[circle,draw] {7}  }
-        %child { node[circle,draw,fill=lightgreen,line width=1pt] {9} }
-        %}
-    %child { node[circle,draw] {12}
-        child { node[circle,draw] {11}  }
-        child { node[circle,draw] {13} }
-        %}
-    ;
-\node[fill=none] at (8,3mm) {level 3};
-\node[fill=none] at (8,-9mm) {level 2};
-\node[fill=none] at (8,-21mm) {level 1};
-\end{tikzpicture}
-\end{center}
-
-\vspace{0.1in}
-No runtime bound on the merge operation, but it is fast in practice
-
-%\vspace{0.1in}
-%But, if the runtime is $o(n)$, then we get an algorithm for tree construction that takes time $O(n)$
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}[fragile]{Merging cover trees}
-
-Merging cover trees gives us a parallel tree construction algorithm
-
-\vspace{0.15in}
-
-Sometimes, merging cover trees is \textbf{hard}:
-
-\begin{center}
-\begin{tikzpicture}
-    [ draw
-    , every node/.style={minimum size=10mm,fill=white}
-    , level/.style={sibling distance = 23mm/#1, level distance=12mm}
-    %,    level distance = 1.5cm}
-    , sibling distance=8mm
-    ]
-\draw (-2.3,0) -- (8.6,0)[dotted];
-\draw (-2.3,-12mm) -- (8.6,-12mm)[dotted];
-\draw (-2.3,-24mm) -- (8.6,-24mm)[dotted];
-\node[shape=circle,draw] at (0,0) {10}
-    child { node[circle,draw] {8}
-        child { node[circle,draw] {7}  }
-        child { node[circle,draw] {9} }
-        }
-    child [color=white] {}
-    %child { node[circle,draw] {12}
-        %child { node[circle,draw] {9}  }
-        %child { node[circle,draw] {13} }
-        %}
-    ;
-\node[shape=circle,draw,fill=lightred] at (5,-12mm) {11.5}
-    %child { node[circle,draw] {8}
-        %child { node[circle,draw] {7}  }
-        %child { node[circle,draw,fill=lightgreen,line width=1pt] {9} }
-        %}
-    %child { node[circle,draw] {12}
-        child { node[circle,draw] {11}  }
-        child { node[circle,draw] {13} }
-        %}
-    ;
-\node[fill=none] at (8,3mm) {level 3};
-\node[fill=none] at (8,-9mm) {level 2};
-\node[fill=none] at (8,-21mm) {level 1};
-\end{tikzpicture}
-\end{center}
-
-\vspace{0.1in}
-No runtime bound on the merge operation, but it is fast in practice
-
-%\vspace{0.1in}
-%But, if the runtime is $o(n)$, then we get an algorithm for tree construction that takes time $O(n)$
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}[fragile]{The effect of parallel tree \emph{construction} on small datasets}
-\begin{center}
-\graphicspath{{slides/covertree/paperimg/}}
-\input{slides/covertree/paperimg/parallel-ancestor-build}
-\begin{tikzpicture}
-    \node[draw,fill=blue,minimum width=0.05in,minimum height=0.3in] at (0.3in,0) {};
-    \node at (0.3in,0.63in) {\small\rotatebox{90}{Our cover tree}};
-    \node[minimum width=0.05in,minimum height=0.3in] at (0.45in,0) {};
-    \node at (0.45in,0.61in) {\small\rotatebox{90}{}};
-    \node at (0,-0.475in) {};
-\end{tikzpicture}
-\end{center}
-
-\vspace{0.1in}
-Experiments run on an Amazon AWS instance with 16 true cores
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}[fragile]{Parallel tree construction really matters on larger data sets}
-
-%on small datasets with cheap metrics, parallel construction is less useful
-
-\vspace{0.1in}
-On large datasets with an expensive metric, parallelism is more useful
-
-\vspace{0.15in}
-Yahoo! Flickr dataset with 1.5 million images and earth mover distance
-
-%\vspace{0.2in}
-\vspace{0.15in}
-\begin{center}
-\Large
-\begin{tabular}{ccccc}
-\hline
-num cores
- & \multicolumn{2}{c}{simplified tree} & \multicolumn{2}{c}{nearest ancestor tree} \\
-%& \multicolumn{2}{c}{construction} & \multicolumn{2}{c}{construction} \\ %\cline{2-5}
-& time & speedup & time & speedup \\
-\hline
-\hline
-1  & 70.7 min & 1.0 & 210.9 min& 1.0\\
-2  & 36.6 min & 1.9 & 94.2 min & 2.2\\
-4  & 18.5 min & 3.8 & 48.5 min & 4.3\\
-8  & 10.2 min & 6.9 & 25.3 min & 8.3\\
-16 & 6.7 min & 10.5 & 12.0 min & 17.6\\
-\hline
-\end{tabular}
-\end{center}
-
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}[fragile]{The effect of parallel tree \emph{construction and query}}
-\begin{center}
-\graphicspath{{slides/covertree/paperimg/}}
+\graphicspath{{covertree/paperimg/}}
 \input{slides/covertree/paperimg/parallel}

### 2022-02-01 paper/slides/experiments-image.tex
colloquium checkpoint

\begin{frame}{Experiments: Real World}

\resizebox{\columnwidth}{!}{
\input{fig/real_world.tex}
}

    \vspace{0.2in}
Experimental Details:

\begin{itemize}
    \item CIFAR100/ImageNet: Image data, 100/1000 classes, ResNet features \citep{He2016DeepRL}

    \item Twitter: Text data, 80 classes, BERT features \citep{stoikos2020multilingual}

        \begin{itemize}
            \item predict the emoji (detailed sentiment) of a tweet about coronavirus
        \end{itemize}
\end{itemize}

\end{frame}

### 2022-02-01 paper/slides/knuth.tex
colloquium checkpoint

\begin{frame}
\frametitle{(Content Warning) Proof Culture in Machine Learning}
\pause
\begin{tikzpicture}
\node at (0,0) {\includegraphics[width=2in]{img/knuth}};
\node at (6,0) {\parbox{2.4in}{
    \Large
Beware of bugs in the above code; I have only proved it correct, not tried it.

\vspace{0.2in}
-- Donald Knuth
}};
\end{tikzpicture}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{(Content Warning) Proof Culture in Machine Learning}

Google Scholar's most cited paper of 2020:\footnote{
    \tiny\url{https://www.natureindex.com/news-blog/google-scholar-reveals-most-influential-papers-research-citations-twenty-twenty}
}

\vspace{0.1in}
\includegraphics[width=\textwidth]{img/adam}

\pause
\citet{reddi2019convergence}
\begin{itemize}
\item
    Simple counter example to Adam paper's proofs
\item
    Provide a fixed, corrected algorithm AdamW
\item
    ``Only'' 1500 citations
\item
    Adam paper has $>60000$ citations since \citet{reddi2019convergence} published
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{(Content Warning) Proof Culture in Machine Learning}

\begin{tikzpicture}
\node at (0,0) {\includegraphics[width=2in]{img/facebookanon}};
\node at (6,0) {\parbox{2.4in}{
\begin{flushleft}
\Large
I don't care about theorems or proofs.
I only look at the experiments.

\vspace{0.2in}
-- Reviewer \#3
\end{flushleft}
}};

%\pause
    %\draw[red, line width=2pt] (3,0) -- (5.5,0);
    %\node at (7,-0.1) {\Large\color{red} cute animals};
\end{tikzpicture}

\end{frame}

### 2022-02-01 paper/slides/motivation-not.tex
colloquium checkpoint

\begin{frame}
\frametitle{Similar feature spaces}

\centering
\begin{tikzpicture}
\uncover<1>{\node{\includegraphics[height=3.0in]{img/dog-or-food1}};}
\uncover<2>{\node{\includegraphics[height=3.0in]{img/dog-or-food2}};}
\uncover<3>{\node{\includegraphics[height=3.0in]{img/dog-or-food3}};}
\uncover<4>{\node{\includegraphics[height=3.0in]{img/dog-or-food4}};}
\uncover<5>{\node{\includegraphics[height=3.0in]{img/dog-or-food5}};}
\uncover<6>{\node{\includegraphics[height=3.0in]{img/dog-or-food6}};}
\uncover<7>{\node{\includegraphics[height=3.0in]{img/dog-or-food7}};}
\end{tikzpicture}

%{
%\tiny
%\url{https://neurabites.com/muffin-or-chihuahua/}
%}
%
%These images are similar in \textbf{feature space} but not \textbf{class semantics}.
%
%We are interested only in \textbf{class semantics}.
\end{frame}

### 2022-02-01 paper/slides/motivation.old.tex
colloquium checkpoint

\ignore{
\begin{frame}{(Informal) Problem Statement}

Given input:

\begin{tikzpicture}
    [ inner sep=0cm
    , draw
    , node distance=0.15in
    ]
\node[] (b) at (3cm,0) {\includegraphics[width=1.7in]{img/Lakeland_Terrier}};
\node[draw, minimum width=0.5in, minimum height=1.5in, right=of b] (c) {\rotatebox{270}{feature generator}};
\node[draw, minimum width=0.5in, minimum height=1.5in, right=of c] (d) {\rotatebox{270}{logistic regression}};
\end{tikzpicture}

\vspace{1em}
Assign a class label:
\begin{itemize}
\item Animal
\item Not-animal
\end{itemize}

\ignore{
\begin{tikzpicture}
\tikzstyle{nome}=[draw, rectangle, fill=yellow!30,minimum width=9cm]
[ minimum width=2cm
, align=left
, anchor=west
, draw
, rectangle
]
\node[nome](animal){animal};
\node[nome, below of=animal]{not-animal};
\end{tikzpicture}
}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{(Informal) NOT The Problem}
ambiguity in the picture's subject (semantics problem)

pictures of plastic dog vs real dog (semantics problem; non-mathematical)

pictures of dogs vs buns (feature generation problem)
\end{frame}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ignore{
\begin{frame}
\frametitle{Problem Background}

\resizebox{!}{0.8\paperheight}{
\begin{tikzpicture}
    [ node distance = 0.15in
    ]
    \Large

\node
    [ inner sep=0
    ] (img) 
    {\includegraphics[height=2.5in]{img/Lakeland_Terrier}};

\uncover<1-3>{
\node
    [ below = of img
    , anchor=north
    , fill=darkgray
    , text height=2.5in
    , minimum height=1.15in
    , align=center
    , inner sep=0
    ]
    { \color{white} Machine Learning Model };
}

\uncover<4->{
\node 
    [ below = of img
    , anchor=north
    , fill=darkgray
    , text height=2.5in
    , minimum height=0.5in
    , align=center
    , inner sep=0
    , outer sep=0
    ](features)
    {\color{white}\centering Feature Generation};

\node
    [ below = of features
    , draw
    , text width = 3in
    , minimum height= 0.5in
    , align=center
    , inner sep=0
    , outer sep=0
    ](xentropy)
    {\parbox{\textwidth}{\centering Logistic Regression}};
\draw[->,line width=2pt] (features) -- (xentropy);
}

\uncover<1->{
\node
    [ below = 0.2in of xentropy
    , inner sep=0.1in
    , text width=2.8in
    , draw
    ]
    (classes)
    {
        %Class Predictions:
        %\vspace{0.1in}
        \begin{tikzpicture}
        %\small
        \tt
        \foreach  \l/\x[count=\y] in 
            { not-animal/4
            , animal/96
            }
        {\node[left,text width=1.0in] at (0,0.8*\y) {\l~~};
        \draw[draw=blue,fill={rgb,255:red,170; green,170; blue,255}] (0.0,0.8*\y-.3) rectangle (0.0+\x/100.0*3,0.8*\y+.3);
        \node[right] at (0.0+\x/100.0*3,.8*\y) {\x\!\%};
        }
        \end{tikzpicture}
    };

\node
    [ right = 0.2in of xentropy
    , inner sep=0.1in
    , text width=2.8in
    , draw
    ]
    (classes2)
    {
        \begin{tikzpicture}
        \tt
        \foreach  \l/\x[count=\y] in 
            { House/2
            , car/1
            , tree/1
            , dog/86
            , cat/8
            , Horse/1
            , cow/1
            }
        {\node[left,text width=1.0in] at (0,0.8*\y) {\l~~};
        \draw[draw=blue,fill={rgb,255:red,170; green,170; blue,255}] (0.0,0.8*\y-.3) rectangle (0.0+\x/100.0*3,0.8*\y+.3);
        \node[right] at (0.0+\x/100.0*3,.8*\y) {\x\!\%};
        }
        \end{tikzpicture}
    };
}

\draw[->,line width=2pt] (img) -- (features) ;
\draw[->,line width=2pt] (xentropy) -- (classes);

%%%%%%%%%%%%%%%%%%%%

\uncover<5,6>{
\node
    [right = 0.25in of features
    , text width = 5in
    ]
    (deep_place) {};

\node
    [ above = -2.0in of deep_place
    , text width = 5in
    ] (deep) {
    \baselineskip=16pt
    This is wHat \emph{deep learning} studies \\
    ~\\
    Lots of famous \emph{network architectures}:\\
    ~~~~LeNet \citep{lecun1998gradient} \\
    ~~~~AlexNet \citep{krizhevsky2012imagenet} \\
    ~~~~VGG \citep{simonyan2014very} \\
    ~~~~Inception v1 \citep{szegedy2015going} \\
    ~~~~Inception v2 \citep{ioffe2015batch} \\
    ~~~~Inception v3 \citep{szegedy2016rethinking} \\
    ~~~~Inception v4 \citep{he2016identity} \\
    ~~~~ResNet \citep{witten2016data} \\
    ~~~~ResNet2 \citep{he2016identity} \\
    ~~~~WideResNet \citep{zagoruyko2016wide} \\
    ~~~~SqueezeNet \citep{iandola2016squeezenet} \\
    ~~~~MobileNet \citep{howard2017mobilenets} \\
    ~~~~DenseNet \citep{huang2017densely} \\
    ~~~~ResNext \citep{lin2018focal} \\
    ~~~~NASNet \citep{zoph2018learning} \\
    %~~~~PNASNet \citep{liu2018progressive} \\
    %~~~~SqueezeExcitationNet \citep{hu2018squeeze} \\
    %~~~~MobileNet2 \citep{sandler2018mobilenetv2} \\
    ~~~~... \emph{and many more} ... \\
    ~\\
    \textbf{No theoretical guarantees}
    };
    \draw [decorate,decoration={brace,mirror,amplitude=10pt,raise=4pt, aspect=0.6},yshift=0pt]
        (deep.north west) -- (deep.south west) node [black,midway,anchor = west,xshift=0.8cm] {};
    }

\uncover<6>{\node at (3.5in,-3.25in) [ text width = 5in,align=center ] {\textbf{better than Humans in practice} };}
\uncover<6>{\node at (3.5in,-3.5in) [ text width = 4in,align=center ] {\textbf{treat as black box} };}

\ignore{
%\uncover<7->{
%\node
    %[ right = 0.25in of features
    %, text width = 3in
    %] (rd) {
        %Outputs a vector $\R^d$, $d$ is the number of features
    %};
    %}

\uncover<8->{
\node
    [ right = 0.25in of xentropy
    , text width = 6in
    ] (deep) {
        \baselineskip=16pt
        ~\\
        Known since the 1800s, good theoretical properties\\
        \vspace{0.15in}
        Let $d$ be number of features,\\
        \hspace{0.33in}$c$ be number of classes,\\
        \hspace{0.33in}$n$ be number of data points,\\
        then the generalization error = $\Theta\left(\sqrt{\frac{cd}{n}}\right)$
        \\
        \vspace{0.15in}
        \textbf{So more classes requires more data}
        ~\\
        %Known since at least \citet{nelder1972generalized}
    };
    \draw [decorate,decoration={brace,mirror,amplitude=10pt,raise=4pt},yshift=0pt]
        (deep.north west) -- (deep.south west) node [black,midway,anchor = west,xshift=0.8cm] {};
};
}
\end{tikzpicture}
}
\end{frame}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-02-01 paper/slides/results-summary.tex
colloquium checkpoint

\begin{frame}{(Informal) Main Result}

Let
\begin{itemize}
%\item $d$ features
\item $k$ be the number of classes, and%\uncover<2>{\textcolor{red}{, doubling dimension $c$}}
\item $n$ be the number of data points.
\end{itemize}

%The generalization error of the standard cross entropy loss decays as
%\begin{equation}
    %O(\sqrt{dk/n}).
%\end{equation}

Then almost all classification problems have
\begin{equation}
    \text{generalization error} = \Theta(\sqrt{k/n})
\end{equation}
in the PAC framework.

\uncover<2>{
    \textcolor{red}{(\emph{new})}
    Let
    \begin{itemize}
        \item $c$ be the doubling dimensionality of the classes.
    \end{itemize}
    Then we probide a simple algorithm with
    \begin{equation}
        \text{generalization error} = 
        \begin{cases}
            O(\sqrt{\log k/n}) & c \le 1 \\
            O(\sqrt{k^{1-c}/n}) & c > 1 \\
        \end{cases}
    \end{equation}
    and we conjecture that $\Theta(\sqrt{c/n})$ is optimal.
        %We provide a simple algorithm with generalization error
    %\begin{equation}
        %O(\sqrt{d\log k}/n)
    %\end{equation}
    }

\end{frame}

### 2022-02-01 paper/slides/sgd-xentropy.tex
colloquium checkpoint

\begin{frame}{Multiclass Classification I: Loss Function}

\vspace{0.1in}
The standard cross entropy loss is defined to be
\begin{equation}
    \label{eq:xentropy}
    \ell(W;(\x,y)) = - \log \frac {\exp(-\trans\w_y \x)}{\sum_{j=1}^k \exp(-\trans \w_j \x)}
\vspace{-0.1in}
\end{equation}
where
\begin{itemize}
    %\item $(\x, y)$ is an input data point
    \item $\x \in \R^d$ is an input feature vector
    \item $y \in \{1, 2, ..., k\}$ is the input class label
    \item $\w_i \in \R^d$ is the parameter vector for class $i$
    \item $W = (\w_1, \w_2, ..., \w_k) \in \R^{d\times k}$ is the parameter matrix
\end{itemize}

\uncover<2>{
\vspace{0.2in}
    \textbf{Goal:} Approximate the optimal parameter matrix
\begin{equation}
    W^* = \argmin_{W} \E \ell(W; (\x,y))
    .
\end{equation}
}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Multiclass Classification II: SGD}

Approximate $W^*$ using \emph{stochastic gradient descent} (SGD):
\begin{equation}
    W_{t+1} = W_t - \eta \nabla \ell(W_t, (\x_t, y_t))
\end{equation}
where $\eta$ is the step size/learning rate.

%\vspace{0.2in}
%As $t \to \infty$, $W_t \to W^*$.

%\vspace{0.2in}
\includegraphics[height=2in]{img/sgd}

{\tiny
Image Source: \url{https://sweta-nit.medium.com/batch-mini-batch-and-stochastic-gradient-descent-e9bc4cacd461}
}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ignore{
\begin{frame}{SGD}
We let $\theta^{(t)}$ denote the parameter value at iteration $t$,
and $\eta : \mathbb R$ be the step size.
Let $\nu_t$ be a noisy gradient of $f$ satisfying
\begin{equation}
    \E[\nu_t | \theta^{(t)}] = \nabla f(\theta^{(t)}).
\end{equation}
Then the parameter update for step $t$ is defined to be
\begin{equation}
    \theta^{(t+1)} = \theta^{(t)} - \eta \nabla \nu_t
    .
\end{equation}
When using parameter averaging, the final model parameters are defined to be
\begin{equation}
    \bar\theta = \frac1T \sum_{i=1}^T \theta^{(t)}
    .
\end{equation}
\end{frame}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ignore{
\begin{frame}{Multiclass Classification II: Objectives}

The \emph{true loss} is defined to be
\begin{equation}
    L_D(W) = \E_{(\x,y)\sim D} \ell(W; (\x, y))
\end{equation}
where $D$ is the unknown data distribution.

\vspace{0.2in}
The \emph{optimal parameter matrix} is 
\begin{equation}
    W^* = \argmin_{W} L_D(W)
\end{equation}

\end{frame}
}

### 2022-02-05 paper/slides/background-ml2.tex
colloquium

@@
 
-Standard Experimental Design:
-\begin{itemize}
-\item Split data into training/test set
-\item Train model on training set
-\item Evaluate model on the test set
-\end{itemize}
+\vspace{-0.1in}
+\begin{equation*}
+    \text{generalization error} = |\text{test error} - \text{training error}|
+\end{equation*}
 
-%\includegraphics[width=\textwidth]{img/llustration-of-the-underfitting-overfitting-issue-on-a-simple-regression-case-Data}
+\vspace{-0.3in}
+\begin{center}
+\resizebox{!}{2.5in}{
+    \small
+\begin{tikzpicture}
+\node {\includegraphics[height=2in,trim=100 0 0 0,clip]{img/over-under-fit}};
 
-\includegraphics[width=\textwidth]{img/over-under-fit}
+    \node at (-7.25,0) {};
 
+    \uncover<2->{
+    \draw[draw=red,line width=2pt] (-4.5,-2.5) -- (-3.95,-1.5);
+    \node at (-4,-2.75) {\color{red}high training error / high test error};
+    \node at (-4,-3.25) {\color{darkgreen} low generalization error};
+    \node at (-4,-3.75) {\color{red}(underfit)};
+}
+
+    \uncover<3-> {
+        \node at (3,-2.75) {\textcolor{darkgreen}{low training error} / \textcolor{red}{high test error}};
+    \node at (3,-3.25) {\color{red}high generalization error};
+    \node at (3,-3.75) {\color{red}(overfit)};
+
+    \draw[draw=red,line width=2pt] (3.5,-2.5) -- (2.95,-1.5);
+}
+
+    \uncover<4-> {
+    \node at (-0.5,3) {\color{darkgreen}low training error/low test error/low generalization error};
+    \draw[draw=darkgreen,line width=2pt] (-0.5,2.5) -- (-1,1.5);
+}
+
+    \uncover<5>{
+    \draw[->, line width=1.5pt,double distance=1pt] (-4.5,0.25) --(-1.5,0.25);
+    \node at(-4,0.5) {better features};
+}
+
+    \uncover<6>{
+    \draw[->, line width=1.5pt,double distance=1pt] (3.5,0.25) --(0.5,0.25);
+    \node at(4,0.5) {\textbf{this talk}};
+}
+\end{tikzpicture}
+}
+\end{center}
+
+    \vspace{-0.2in}
 {

### 2022-02-05 paper/slides/conjecture.tex
colloquium

\begin{frame}
\frametitle{Optimal Generalization Error}

\textbf{Recall:} standard generalization error bound is $\Theta(\sqrt{kd/n})$

\pause
\begin{block}{Conjecture}
If the classes have metric structure with doubling dimension $c$,
then 
\begin{equation}
\text{the optimal generalization error} = \Theta\left(\sqrt{cd/n}\right)
\end{equation}
\end{block}

\pause
Why?
\pause
\begin{itemize}
    \item if the metric is discrete (no assumptions), then $c=\Theta(k)$ recovering known bound
    \pause
\item if the metric is $\mathbb Z$, $k=\infty, c=\Theta(1)$ and the known bound is $O(\sqrt{d/n})$ via Poisson regression
    \pause
\item if the metric is $m$-sphere, then $c=\Theta(m)$ and prior work shows the bound is $O(\sqrt{md/n})$
via MvMF regression \citep{izbicki2019exploiting}
\end{itemize}

\end{frame}

### 2022-02-05 paper/slides/intuition.tex
colloquium

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Intuition}

$W$-parameterization learns everything from scratch

%Learning the Lakeland Terrier class from scratch is hard

\vspace{0.1in}
\begin{tabular}{m{0.7in}m{3.7in}}
    \includegraphics[height=0.5in]{img/Lakeland_Terrier} & How is \textbf{Lakeland Terrier} different than a tree? truck? person? horse? ... \\
    \includegraphics[height=0.5in]{img/Airedale} & How is \textbf{Airedale} different than a tree? truck? person? horse? ... \\
    \includegraphics[height=0.5in]{img/Irish-Terrier} & How is \textbf{Irish Terrier} different than a tree? truck? person? horse? ... \\
    \includegraphics[height=0.5in]{img/water_spaniel} & How is \textbf{Irish Spaniel} different than a tree? truck? person? horse? ... \\
\end{tabular}
\end{frame}

\begin{frame}
\frametitle{Intuition}

$U$/$V$-tree parameterizations learn 1 class from scratch

\vspace{0.1in}
    \begin{tabular}{m{0.7in}m{3.8in}}
        \includegraphics[height=0.5in]{img/Lakeland_Terrier} & How is \textbf{Lakeland Terrier} different than a tree? truck? person? horse? ... \\
\end{tabular}

\vspace{0.2in}
Learns only the difference between related classes

    \vspace{0.1in}
\begin{tabular}{m{0.7in}m{3.8in}}
    \includegraphics[height=0.5in]{img/Airedale} & \textbf{Airedale} is a big Lakeland Terrier \\
    \includegraphics[height=0.5in]{img/Irish-Terrier} & \textbf{Irish Terrier} is a Lakeland Terrier with brown fur \\
    \includegraphics[height=0.5in]{img/water_spaniel} & \textbf{Irish Spaniel} is a Lakeland Terrier with long dark fur and big ears\\
\end{tabular}
\ignore{
\pause
    \vspace{0.3in}
Learn related classes by analogy (i.e.\ learn the difference)

    \vspace{0.1in}
\begin{tabular}{m{0.7in}m{3.8in}}
    \includegraphics[height=0.5in]{img/Airedale} & Airedale is a big Lakeland Terrier \\
    \includegraphics[height=0.5in]{img/Irish-Terrier} & Irish Terrier is a Lakeland Terrier with brown fur \\
    \includegraphics[height=0.5in]{img/water_spaniel} & Irish Spaniel is a Lakeland Terrier with long dark fur and big ears\\
\end{tabular}
}

\ignore{
Once I learn the ``concept'' of a Lakeland Terrier

    \begin{center}
\includegraphics[height=1in]{img/Lakeland_Terrier}
    \end{center}

    \vspace{-0.1in}
    %\pause
I don't have to learn the concept of an Airdale from scratch

    \begin{center}
\includegraphics[height=1in]{img/Airedale}
    \end{center}

    \vspace{-0.1in}
I just learn the ``difference'' between these two classes
}

\end{frame}

### 2022-02-05 paper/slides/outline1.tex
colloquium

\begin{frame}{Summary (so far)}

\begin{itemize}
\item more classes $\Rightarrow$ harder problem
\begin{itemize}
\item $k$: num classes, $d$: num dimensions, $n$: num data points
\end{itemize}
\begin{equation*}
\text{(cross entropy) generalization error}
=
O\left(\sqrt{\frac{kd}{n}}\right)
~~~~~~~~~~
\end{equation*}
\item real world classes are highly structured

\begin{itemize}
\item the doubling dimension $c <\!\!< k$

\end{itemize}
\begin{equation*}
\text{(conjectured optimal) generalization error}
=
O\left(\sqrt{\frac{cd}{n}}\right)
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~.
\end{equation*}

\item \textbf{contribution:} $U$/$V$-tree loss exploits arbitrary metric structure

\begin{equation*}
\text{(tree loss) generalization error} = 
\begin{cases}
\sqrt{\frac{d\log k}{n}} & c\le 1 \\
\sqrt{\frac{dk^{1-1/c}}{n}} & c>1 \\
\end{cases}
\end{equation*}

\item \textbf{bonus:} best performance on synthetic and real world experiments

\end{itemize}

\vspace{-4in}
\begin{tikzpicture}
    \node at (0,0) {};
    \node at (0,4in) {};

    \node[anchor=north west,fill=white,minimum width=4.5in,minimum height=0.7in] at (0,2.94in) {};
    \node[anchor=north west,fill=white,minimum width=4.5in,minimum height=0.74in] at (0,2.04in) {};
    \node[anchor=north west,fill=white,minimum width=4.5in,minimum height=0.7in] at (0,1.04in) {};
    \node[anchor=north west,fill=white,minimum width=4.5in,minimum height=0.3in] at (0,0.3in) {};
\end{tikzpicture}
\end{frame}

### 2022-02-15 paper/paper.tex
colloquium checkpoint
camera ready

@@
 
-\usepackage{aistats2022}
+%\usepackage{aistats2022}
 % If your paper is accepted, change the options for the package
@@
 %
-%\usepackage[accepted]{aistats2022}
+\usepackage[accepted]{aistats2022}
 %
@@
 
-\aistatsauthor{ Yujie Wang \And Michael Izbicki  }
+\aistatsauthor{ Yujie Wang \And Mike Izbicki  }
 
@@
 Previous work on multi-class loss functions has focused on improving either the statistical or computational performance.
-Statistical work includes loss functions designed for hierarchichally structured labels \citep{cesa2006incremental,wu2017hierarchical},
+Statistical work includes loss functions designed for hierarchichally structured labels \citep{cesa2006incremental,wu2017hierarchical,bertinetto2020making},
 loss functions for improving top-$k$ accuracy \citep{lapin2016loss},
 or focusing on noisy labels \citep{sukhbaatar2014training,zhang2018generalized}.
-The work most similar to ours is the simloss \citep{Kobs2020SimLossCS},
+The work most similar to ours is the SimLoss \citep{Kobs2020SimLossCS},
 which also makes a metric assumption about the class label structure.
@@
 Figure \ref{fig:labeltree} (left) shows an example $U$-tree structure.
-The definition of a $U$-tree is motivated by the cover tree data structure \citep{beygelzimer2006cover},
+The definition of a $U$-tree is motivated by the cover tree data structure \citep{beygelzimer2006cover,izbicki2015faster},
 which generates $U$-tree structures given a metric over the class labels.
@@
 The magic of automatic differentiation will then take care of the rest and ensure that the underlying $U$ or $V$ matrix is optimized.
-Our TreeLoss library\footnote{URL blinded for peer review.} provides easy-to-use functions for generating these matrices,
+Our TreeLoss library\footnote{\url{https://github.com/cora1021/TreeLoss}} provides easy-to-use functions for generating these matrices,
 and so modifying code to work with the tree loss is a 1 line code change.
@@
 \end{equation}
-
 In order to bound this error, we make the following standard assumption about our data.
@@
     \label{ass:metric}
-    Let $\lambda >= 1$, and $d$ be a distance metric over the labels such that for all labels $i$ and $j$,
+    Let $\lambda \ge 1$, and $d$ be a distance metric over the labels such that for all labels $i$ and $j$,
 \begin{equation}
@@
 Instead, we mention only two important properties of the cover tree.
-First, it can be constructed in time $O(k)$,
+First, it can be constructed in time $O(k)$.
+This is independent of the number of training examples $n$,
 so building the $U$-tree structure is a cheap operation that has no meaningful impact on training performance.
@@
 We evaluate the tree loss on 4 synthetic and 3 real world experiments.
-We compare the tree loss to the standard cross entropy loss, the recently proposed simloss \citep{Kobs2020SimLossCS}, and the hierarchical softmax \citep{morin2005hierarchical}.
+We compare the tree loss to the standard cross entropy loss, the recently proposed SimLoss \citep{Kobs2020SimLossCS}, and the hierarchical softmax \citep{morin2005hierarchical}.
 The results confirm our theoretical findings from Section \ref{sec:theory} and demonstrate that the tree loss significantly improves the performance of these baseline losses in a wide range of scenarios.
@@
 so this plot compares performance on different problem difficulties.
-On maximally easy (large $d$) and hard (small $d$) problems,
-then the tree loss performs similarly to the other loss functions because the performance is dominated by the bayes error and no improvement is possible.
+On maximally easy (large $d$) and maximally hard (small $d$) problems,
+the tree loss performs similarly to the other loss functions because the performance is dominated by the bayes error and no improvement is possible.
 The main advantage of the tree loss is in the mid-difficulty problems.
@@
 The bottom-right plot tells a similar story but controls the difficulty of the problem directly by tuning the randomness $\sigma$.
-
-\ignore{
-From figure \ref{fig.1}, it is clear that the tree loss achieves the best performance. 
-The tree loss converges at a faster rate as number of data points and dimension of parameter matrix increase.
-If we increase the number of classes, the tree loss can keep a higher accuracy and the accuracy of SimLoss is higher than cross entropy loss and hierarchical softmax.
-It is as our expected, the tree loss can improve performance on large classes tasks.
-Besides, when we increase the noise in the dataset, the accuracy of all loss functions decrease, yet the tree loss decreases slower.
-Among the four loss functions, hierarchical softmax hurts the performance obviously. 
-We would not apply hierarchical softmax on real world data experiment in terms of computation.
-}
 
@@
 Recall that our theoretical results state that the convergence rate of SGD depends on a factor $\lambda$ that measures how well our metric over the class labels is able to predict the distances between the true parameter vectors.
+(See Assumption \ref{ass:metric}.)
 In this experiment, we study the effect of this $\lambda$ parameter on prediction accuracy.
@@
 and the less well known \emph{superclass accuracy} (SA) score.
-SA is a generalization of the top-1 accuracy proposed by the simloss paper \citep{Kobs2020SimLossCS}.
+SA is a generalization of the top-1 accuracy proposed by the SimLoss paper \citep{Kobs2020SimLossCS}.
 The idea is that misclassifying a \texttt{sheepdog} as a \texttt{husky} should be penalized less than misclassifying a \texttt{sheepdog} as a \texttt{bus} because the \texttt{sheepdog} and \texttt{husky} classes are more similar to each other.
@@
 Table \ref{table:results} shows that on each of these datasets and for each metric,
-the tree loss outperforms the baseline cross entropy loss and simloss.\footnote{We do not evaluate against the hierarchical softmax due to limited computational resources.
+the tree loss outperforms the baseline cross entropy loss and SimLoss.\footnote{We do not evaluate against the hierarchical softmax due to limited computational resources.
 The results on the synthetic data, however, suggest that the hierarchical softmax would have performed poorly.}
@@
 There are 4 class labels with no corresponding word2vec embedding,
-and so following the simloss paper we discard these classes.
+and so following the SimLoss paper we discard these classes.
 
@@
 The only difference between the three models is the final layer:
-one model uses the standard cross entropy loss, one uses the tree loss, and one uses the simloss.
+one model uses the standard cross entropy loss, one uses the tree loss, and one uses the SimLoss.
 The results shown in Table \ref{table:results} shows that the tree loss significantly outperforms the other losses.
@@
 
-We now consider the problem of predicting the emotions of twitter text.
+We now consider the problem of predicting the emotions of Twitter text.
 This is a very different domain than the image problems considered above,
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+%\newpage
 \bibliographystyle{plainnat}

### 2022-02-16 paper/paper.tex
camera ready

@@
 For each dataset, we report standard top-1 accuracy scores,
-and the less well known \emph{superclass accuracy} (SA) score.
-SA is a generalization of the top-1 accuracy proposed by the SimLoss paper \citep{Kobs2020SimLossCS}.
+and the less well known \emph{similarity accuracy} (SA) score.
+SA measures the classification by similarity.
 The idea is that misclassifying a \texttt{sheepdog} as a \texttt{husky} should be penalized less than misclassifying a \texttt{sheepdog} as a \texttt{bus} because the \texttt{sheepdog} and \texttt{husky} classes are more similar to each other.
@@
 and demonstrates that the tree loss works across many domains.
-We use the dataset collected by \citet{stoikos2020multilingual} for analyzing emotional response to Covid19 on Twitter.
-This dataset contains all geolocated tweets written in any language sent over the 6 month period between 1 January 2020 and 1 July 2020 that mention certain Covid19 keywords.
+We use the dataset collected by \citet{izbicki2019geolocating}.
+This dataset contains all geolocated tweets written in more than 100 language sent over the 4 year period between October 2017 and October 2021.
 Tweets in the dataset are preprocessed to have all emojis, usernames, and urls removed from the text,
@@
 \appendix
+
+\thispagestyle{empty}
+
+\setcounter{lemma}{0}
+\setcounter{assumption}{0}
+\setcounter{corollary}{0}
+\setcounter{theorem}{0}
+
+% For one-column format, uncomment the following:
+% \onecolumn \makesupplementtitle
+% For two-column format, uncomment the following:
+\twocolumn[ \makesupplementtitle ]
 

### 2022-02-16 paper/paper.tex
camera ready
update citation

@@
 and the less well known \emph{similarity accuracy} (SA) score.
-SA measures the classification by similarity.
+SA is a top-1 accuracy considering similarity.
 The idea is that misclassifying a \texttt{sheepdog} as a \texttt{husky} should be penalized less than misclassifying a \texttt{sheepdog} as a \texttt{bus} because the \texttt{sheepdog} and \texttt{husky} classes are more similar to each other.
@@
 and demonstrates that the tree loss works across many domains.
-We use the dataset collected by \citet{izbicki2019geolocating}.
-This dataset contains all geolocated tweets written in more than 100 language sent over the 4 year period between October 2017 and October 2021.
+We use the dataset collected by \citet{izbicki2019geolocating} and \citet{stoikos2020multilingual}.
+This dataset contains all geolocated tweets written in more than 100 language sent over the 4 year period between October 2017 and October 2021---approximately $5.5\times10^9$ tweets in total.
 Tweets in the dataset are preprocessed to have all emojis, usernames, and urls removed from the text,

### 2022-02-16 paper/paper.tex
fix typo

@@
 We use the dataset collected by \citet{izbicki2019geolocating} and \citet{stoikos2020multilingual}.
-This dataset contains all geolocated tweets written in more than 100 language sent over the 4 year period between October 2017 and October 2021---approximately $5.5\times10^9$ tweets in total.
+This dataset contains all geolocated tweets written in more than 100 languages sent over the 4 year period between October 2017 and October 2021---approximately $5.5\times10^9$ tweets in total.
 Tweets in the dataset are preprocessed to have all emojis, usernames, and urls removed from the text,
